### 2021-02-07 README.Rmd
first commit

---
title: "Hidden Talents Multiverse Analysis"
output: github_document
---

<style>
table{
  font-size: 14px;
}
td{
  vertical-align: top;
}
.gt_row{
  vertical-align: top;
}
</style>

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, message = F, warning = F)

library(tidyverse)
library(gt)
```

This repository contains all data, code, and output for a working manuscript by Young, Frankenhuis, and Ellis (in progress).

## Directory Structure

The names of each folder are intended to be self-explanatory. There are five top-level folders to organize the inputs and outputs of this project:

1. `codebooks/`: lists of variable names, labels, and value labels (where applicable).
2. `data/`: data, stored as an `.Rdata` file and `.csv` files.
3. `figures/`: all figures that are produced by R-scripts
4. `multiverse-objects/`: all `.Rdata` files containing objects necessary for performing multiverse analyses and storing intermediary results

Below is a simple visualization of the full directory structure.

```{r}
fs::dir_tree(".", regexp = "^README|.Rproj$", invert = T)
```

Each of the top-level folders are explained in more detail below:

## Codebooks

These are lists of variable names, labels, and value labels (where applicable). Their names correspond to the versions of the data they document (see Data below).

## Data

The raw data for this project contain all variables necessary to produce all multiverse outputs (cleaned data, multiverse datasets, effect sizes, plots). The raw data file is the only file that depends on other files/scripts to create, which saved elsewhere (for confidentiality reasons).

There are four versions of the data, which can be loaded as `R` objects or read/used as `.csv` files.

1. The raw data
2. The data after all *non-arbitrary* decisions were executed
3. A version of the previous step with overall composites for the IVs
4. A version of the data that contains variables for the multiverse analysis, only

All versions and codebooks are stored in `data/data2_analysis.Rdata`. In addition, the following `.csv` files were created to represent each version of the data separately. The prefixed numbers refer to the step in the process of going from raw to multiverse-ready data.

- `1-raw.csv`
- `2-non_arbitrary.csv`
- `3-composites.csv`
- `4-multiverse_base.csv`

A codebook for these data, including variable labels and value labels (if applicable), can be found in `codebook.csv` at the top level of this directory.

## Figures

These are all figures that are produced by R-scripts. They are divided into the following categories:

- Primary analysis figures
- Secondary analysis figures
  - Set 1
  - Set 2

## Multiverse-objects

There are four steps to doing the multiverse:

1. Specifying a grid of all possible arbitrary data processing decisions
2. Creating a "multiverse" of alternative data sets one could analyze
3. Analyzing each "universe" within the multiverse
4. Extracting the relevant information from the analyses (e.g., effect sizes, p-values, etc.)
5. Visualizing results or summarizing them in tables

This folder contains all objects necessary for representing each step. Specifically:

- `1-multiverse-datasets`: multiverse data sets with each data universe stored in a list. There is one list used for the composites and one list used for all components of each IV.
- `2-primary-analyses`: contain the multiverse of full results and extracted effects for the primary confirmatory and exploratory results
- `3-secondary-analyses`: contain the same objects as above for each set of secondary analyses.

## Data Processing Scripts

There are four types of R-scripts in this repository, each with a separate folder.

- `0-functions/`: custom R-functions written for this project
- `1-data-prep/`: Data processing scripts 
- `2-primary-analyses/`: Primary analysis scripts 
- `3-secondary-analyses/`: Secondary analysis scripts

Each script takes an input(s) and produces output(s). The table below provides an overview of the inputs and outputs of each script.

```{r}
file_list <- list.files("scripts", pattern = ".R$", full.names = T, recursive = T) %>% 
  map_df(function(x){
    script_text <- 
      read_lines(x) %>% 
      str_subset("load\\(\".*Rdata\"\\)|save.image\\(.*\\)|file = .*Rdata|filename = .*pdf|write_csv.*csv") %>% 
      str_remove_all(" |\"|\\(|\\)|,") %>% 
      str_c(collapse = " ") %>% 
      str_replace_all("load","input: ") %>% 
      str_replace("write_csv|save.imagefile=|save.image|filename=|file=","~output: ") %>% 
      str_replace_all("write_csv|save.imagefile=|save.image|filename=|file=","output: ") %>% 
      str_split("~", simplify = T)

    tibble(
      dir       = x %>% str_remove_all("scripts/") %>% str_remove_all("/.*") %>% str_remove("^\\d-"),
      script    = x %>% str_remove_all(".*/"),
      raw       = script_text %>% str_squish() %>% str_c(collapse = ", "),
      n_input   = str_count(script_text[1], "input"),
      input1    = script_text[1],
      input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br>") %>% ifelse(is.na(.),"",.),
      n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
      output1   = script_text[2],
      output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "\n- ") %>%  paste0("- ", .) %>% ifelse(. == "- NA","",.)
    )
  })

file_list %>% 
  select(dir,script, input, output) %>% 
  gt(id = "one", rowname_col = "row", groupname_col = "dir") %>% 
  fmt_markdown(columns = T) %>% 
  tab_options(
    row_group.font.weight = "bold",
  ) %>% 
  opt_css(
    css = "
    #one .gt_row {
      vertical-align: top;
    }
    "
  )
```

### 2021-02-07 scripts/1-data-prep/1-data-non-abritrary.R

@@ -1,0 +1,152 @@
+# Setup -------------------------------------------------------------------
+
+# Libraries
+library(tidyverse)
+library(sjlabelled)
+
+# my functions
+source("scripts/0-functions/create_codebook.R")
+
+# Data
+load("data/data1_raw.Rdata")
+
+# Non-arbitrary decisions -------------------------------------------------
+data2_non_arbitrary <- 
+  data1_raw %>% 
+  # Only completed task data
+  filter(
+    !(is.na(abs_updating) & is.na(eco_updating)),
+    !(is.na(abs_shifting_sc) & is.na(eco_shifting_sc)),
+  ) %>% 
+  # No interviewer coded impairments
+  filter(
+    non_arb_impaired == 0, 
+    non_arb_impaired_assent == 0 | is.na(non_arb_impaired_assent)
+  ) %>% 
+  # Only allow 1 missed attention check or all high/low responses to scales with reverse coded items
+  filter(
+    non_arb_attention_check <= 1 | is.na(non_arb_attention_check), 
+    non_arb_q_responses < 2 | is.na(non_arb_q_responses)
+  ) %>%
+  # No extreme distractions during the cognitive tasks
+  filter(non_arb_distractions < 2) %>%
+  # No participants receiving more than 60 minutes of Special Education per day
+  filter(non_arb_sped_60min != 1 | is.na(arb_sped)) %>% 
+  # Deal with siblings
+  mutate(
+    siblings = ifelse(siblings %in% c("wjms_sibling_000","bgc_sibling_000"),"sibling_000", siblings)
+  ) %>% 
+  # Put anyone who no longer has a sibling because of above steps into giant group
+  group_by(siblings) %>% 
+  mutate(siblings_n = n()) %>% 
+  ungroup() %>% 
+  mutate(siblings_id = ifelse(siblings_n == 1, "sibling_000", siblings)) %>% 
+  group_by(siblings_id) %>% 
+  # Count number of siblings each person has
+  mutate(siblings_n = n()) %>% 
+  ungroup() %>% 
+  select(-siblings) %>% 
+  var_labels(
+    siblings_id = "Sibling ID",
+    siblings_n  = "The number of siblings each participant has who also participated in this study "
+  )
+
+# Create Overall Composites -----------------------------------------------
+data3_composites <- 
+  data2_non_arbitrary %>% 
+  # Create overall IV composites
+  mutate(
[…]

### 2021-02-07 scripts/1-data-prep/2-primary-multiverse-datasets.R

@@ -1,0 +1,128 @@
+# Setup -------------------------------------------------------------------
+
+# Libraries
+library(tidyverse)
+library(tidymodels)
+
+# Data
+load("data/data2_analysis.Rdata")
+
+# Specification Grid -----------------------------------------------------------
+## Create a grid of all possible combinations of arbitrary data processing decisions
+## First, `expand_grid` creates all possible combinations from arbitrary variables
+## There are 6 variables each with two alternatives
+## 2*2*2*2*2*2 = 64 unique specifications
+spec_grid <- 
+  expand_grid(
+    sub_sample      = c(0,1),
+    distractions    = c(0,1),
+    attention_check = c(0,1),
+    sped            = c(0,1),
+    csd             = c(0,1),
+    shifting        = c(0,1)
+  ) %>% 
+  rownames_to_column("spec_number") %>% 
+  mutate(spec_number = as.numeric(spec_number)) %>% 
+  pivot_longer(!spec_number, names_to = "spec_var", values_to = "spec_value") %>% 
+  left_join(
+    tribble(
+      ~spec_var,         ~spec_value, ~spec_expr,                                              ~name,
+      "sub_sample",      0,           "arb_sample %in% c('wjms','bgc')",                       "Both Samples",
+      "sub_sample",      1,           "arb_sample == 'wjms'",                                  "Middle School Only",
+      "distractions",    0,           "arb_distractions %in% c(1,0)",                          "Minor Distract. Included",
+      "distractions",    1,           "arb_distractions == 0",                                 "Minor Distract. Excluded",
+      "attention_check", 0,           "arb_attention_check <= 1 | is.na(arb_attention_check)", "1 >= missed",
+      "attention_check", 1,           "arb_attention_check == 0 | is.na(arb_attention_check)", "None missed",
+      "sped",            0,           "arb_sped %in% c(1,0) | is.na(arb_sped)",                "Sp.Ed. Included",
+      "sped",            1,           "arb_sped == 0 | is.na(arb_sped)",                       "Sp.Ed. Excluded",
+      "csd",             0,           "0",                                                     "Not Included",
+      "csd",             1,           "1",                                                     "Residualized",
[…]

### 2021-02-07 scripts/1-data-prep/3-secondary-multiverse-datasets.R

@@ -1,0 +1,146 @@
+# Setup -------------------------------------------------------------------
+
+# Libraries
+library(tidyverse)
+library(tidymodels)
+
+# Data
+load("data/data2_analysis.Rdata")
+
+# Specification Grid -----------------------------------------------------------
+## Create a grid of all possible combinations of arbitrary data processing decisions
+## First, `expand_grid` creates all possible combinations from arbitrary variables
+## There are 6 variables each with two alternatives
+## For our expanded multiverse, we are adding IV subcomponent to our grid
+### 2*2*2*2*2*2 = 64 unique specifications
+### 64 * 3 = 192 specs for unpredictability
+### 64 * 3 = 192 specs for violence
+### 64 * 4 = 256 specs for SES
+### We'll keep them all in one data list of 192+192+256 = 640 datasest
+spec_grid <- 
+  expand_grid(
+    iv              = c(0:9),
+    sub_sample      = c(0,1),
+    distractions    = c(0,1),
+    attention_check = c(0,1),
+    sped            = c(0,1),
+    csd             = c(0,1),
+    shifting        = c(0,1)
+  ) %>% 
+  rownames_to_column("spec_number") %>% 
+  mutate(spec_number = as.numeric(spec_number)) %>% 
+  pivot_longer(!spec_number, names_to = "spec_var", values_to = "spec_value") %>% 
+  left_join(
+    tribble(
+      ~spec_var,         ~spec_value, ~spec_expr,                                              ~name,
+      "sub_sample",      0,           "arb_sample %in% c('wjms','bgc')",                       "Both Samples",
+      "sub_sample",      1,           "arb_sample == 'wjms'",                                  "Middle School Only",
+      "distractions",    0,           "arb_distractions %in% c(1,0)",                          "Minor Distract. Included",
+      "distractions",    1,           "arb_distractions == 0",                                 "Minor Distract. Excluded",
+      "attention_check", 0,           "arb_attention_check <= 1 | is.na(arb_attention_check)", "1 >= missed",
+      "attention_check", 1,           "arb_attention_check == 0 | is.na(arb_attention_check)", "None missed",
+      "sped",            0,           "arb_sped %in% c(1,0) | is.na(arb_sped)",                "Sp.Ed. Included",
+      "sped",            1,           "arb_sped == 0 | is.na(arb_sped)",                       "Sp.Ed. Excluded",
+      "csd",             0,           "0",                                                     "Not Included",
[…]

### 2021-02-07 scripts/2-primary-analyses/3-extract-effects.R

@@ -1,0 +1,125 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+
+# Load results
+load("multiverse-objects/2-primary-analyses/1-confirmatory-results.Rdata")
+load("multiverse-objects/2-primary-analyses/2-exploratory-results.Rdata")
+
+# Results prep ----------------------------------------------------------
+primary_pmap <-
+  list(
+    ls() %>% str_subset("^confirm|^explore") %>% map(function(x) eval(as.symbol(x))),
+    c(rep("Unpredictability",2), rep("Violence",2), rep("SES",2)),
+    c(rep(c("Attention-Shifting", "Working Memory Updating"),3)),
+    c(rep("Confirmatory",4), rep("Exploratory", 2))
+  )
+
+# Raw effect size data ----------------------------------------------------
+primary_effects_data <- 
+  primary_pmap %>% 
+  pmap_df(function(multiverse, iv, dv, hypoth){
+    
+    # All parameters from multiverse
+    params <-
+      multiverse %>% 
+      map_df(function(x){ 
+        bind_cols(
+          n = x$n_model_obs,
+          left_join(
+            x$model_tidy %>% select(mod_term:mod_p.value), 
+            x$model_std_effects %>% rename_with(~paste0("mod_",.x)), 
+            by = c("mod_term" = "mod_Parameter")
+          ),
+          x$specifications %>% 
+            select(-spec_expr) %>% 
+            pivot_wider(names_from = "spec_var", values_from = "name") %>% 
+            rename_with(.cols = !spec_number, ~paste0("spec_",.x))
+        ) 
+      }) %>% 
+      rename_with(tolower) %>% 
+      filter(!str_detect(mod_term, "^sd__")) %>% 
+      group_by(mod_term) %>% 
+      mutate(
+        spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),
+        median_dbl = median(mod_std_coefficient),
+        median_chr = median_dbl %>% round(2) %>% as.character,
+        pval_prop  = (sum(mod_p.value < .05)/64) * 100
+      ) %>% 
+      ungroup() %>% 
+      mutate(
+        mod_sig        = case_when(mod_p.value <  .05 & mod_std_coefficient > 0 ~ "pos-sig",
+                                   mod_p.value <  .05 & mod_std_coefficient < 0 ~ "neg-sig",
[…]

### 2021-02-07 scripts/2-primary-analyses/6-create-plots.R

@@ -1,0 +1,402 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+library(cowplot)
+library(see)
+
+# Load effect data.frames -------------------------------------------------
+load("multiverse-objects/2-primary-analyses/3-extracted-effects.Rdata")
+load("multiverse-objects/2-primary-analyses/5-bootstrapped-effects.Rdata")
+
+# ggplot2 theme -----------------------------------------------------------
+theme_set(
+  theme_bw() +
+    theme(
+      axis.line.x       = element_line(),
+      axis.text.x       = element_text(size = rel(.75)),
+      axis.title.x      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
+      axis.ticks.x      = element_line(),
+      axis.line.y       = element_blank(),
+      axis.text.y       = element_blank(),
+      axis.ticks.y      = element_blank(),
+      axis.title.y      = element_blank(),
+      panel.border      = element_blank(), 
+      panel.spacing.y   = unit(.5, "lines"),
+      plot.margin       = margin(2,.25,.25,.25,"lines"),
+      plot.background   = element_rect(color = NA),
+      plot.title        = element_text(size = rel(.9), hjust = .5),
+      plot.subtitle     = element_blank(),
+      panel.grid        = element_line(color = NA),
+      strip.background  = element_blank(), 
+      strip.placement   = "outside",
+      strip.text        = element_text(size = rel(.85), angle = 0)
+    )
+)
+
+pval_colors <- c("pos-sig" = "#FF7F00", "neg-sig" = "#1F78B4", "non" = "gray")
+my_alphas <- c(.3, 1)
+my_limits <- c(1,70)
+
+# Get bootstrapped medians ------------------------------------------------
+boot_medians <- 
+  boot_effects %>% 
+  filter((null_term == "main" & mod_term == "iv") | (null_term == "int" & mod_term == "iv:type_z")) %>% 
+  rename(term = mod_term) %>% 
+  group_by(spec_num, iv, dv, null_term) %>% 
+  summarize(
+    across(
+      starts_with("mod"), 
+      list(median = ~median(.x), lower = ~quantile(.x, probs = .025, names = F), upper = ~quantile(.x, probs = .975, names = F)),
+      .names = "{.col}_{.fn}")
+  ) %>%
[…]

### 2021-02-07 scripts/3-secondary-analyses/set-1/a2-extract-effects.R

@@ -1,0 +1,93 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+
+# Load effect data.frames -------------------------------------------------
+load("multiverse-objects/3-secondary-analyses/set-1/a1-results-ses-vio.Rdata")
+
+# Extract Parameters ------------------------------------------------------
+secondary1a_effects_data <-
+  map_df(secondary1a_ses_vio_updating, function(x){ 
+    bind_cols(
+      n = x$n_model_obs,
+      left_join(
+        x$model_tidy %>% select(mod_term:mod_p.value), 
+        x$model_std_effects %>% rename_with(~paste0("mod_",.x)), 
+        by = c("mod_term" = "mod_Parameter")
+      ),
+      x$specifications %>% 
+        select(-spec_expr) %>% 
+        pivot_wider(names_from = "spec_var", values_from = "name") %>% 
+        rename_with(.cols = !spec_number, ~paste0("spec_",.x))
+    )
+  }) %>% 
+  rename_with(tolower) %>% 
+  filter(!str_detect(mod_term, "^sd__")) %>% 
+  group_by(mod_term) %>% 
+  mutate(
+    spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),
+    median_dbl = median(mod_std_coefficient),
+    median_chr = median_dbl %>% round(2) %>% as.character,
+    pval_prop  = (sum(mod_p.value < .05)/64) * 100
+  ) %>% 
+  ungroup() %>% 
+  mutate(
+    mod_sig        = case_when(mod_p.value <  .05 & mod_std_coefficient > 0 ~ "pos-sig",
+                               mod_p.value <  .05 & mod_std_coefficient < 0 ~ "neg-sig",
+                               mod_p.value >= .05 ~ "non"),
+    mod_term_num   = case_when(str_detect(mod_term, "Intercept") ~ -1,
+                               mod_term == "age"          ~ 0,
+                               mod_term == "test_envr"    ~ 0,
+                               mod_term == "type_z"       ~ 1,
+                               mod_term == "vio_agg_z"    ~ 2,
+                               mod_term == "ses_agg_z"    ~ 2,
+                               str_detect(mod_term, ":")  ~ 3),
+    mod_term_label = case_when(str_detect(mod_term, "Intercept") ~ "Intercept",
+                               mod_term == "age"          ~ "Age",
[…]

### 2021-02-07 scripts/3-secondary-analyses/set-2/a1-analysis-adversity-components.R

@@ -1,0 +1,130 @@
+# Set up ------------------------------------------------------------------
+
+# Libraries
+library(tidyverse)
+library(lmerTest)
+library(broom.mixed)
+library(tidymodels)
+library(ggeffects)
+library(interactions)
+library(effectsize)
+
+# Data
+load("multiverse-objects/1-multiverse-datasets/datalist-all-ivs.Rdata")
+
+# Expanded Multiverse -----------------------------------------------------
+secondary_expanded_shifting <- 
+  multi_data_list %>% 
+  map(function(x){
+    
+    spec_number <- unique(x$specifications$spec_number)
+    mt_iv <- paste0(x$iv,"_z")
+    
+    message("Starting specification ", spec_number, " with IV: ", mt_iv)
+    
+    # Filter data according to task
+    data <- 
+      x$data_analysis %>% filter(task == "shifting") %>% 
+      mutate(iv = eval(parse(text = mt_iv)))
+    
+    # Run mixed model
+    mod <- lmer(score ~ iv*type_z + age + test_envr + (1|id), data = data)
+    
+    # Create tidied results data.frame
+    mod_tidy <-
+      mod %>%
+      tidy() %>%
+      rename_all(~paste0("mod_",.))
+    
+    # Create a tidy standardized coefficients data.frame
+    mod_standardized <- standardize_parameters(mod)
+    
+    # Create a data.frame with predicted effects at high and low predictor value for each task type
+    mod_effects <- ggpredict(mod, terms = c("iv [-1,1]", "type_z [-1,1]"))
+    ss_task <- sim_slopes(mod, pred = "iv", modx = "type_z", modx.values = c(-1,1))
+    ss_iv  <- sim_slopes(mod, pred = "type_z", modx = "iv", modx.values = c(-1,1))
+    
+    results <-
+      list(
+        iv                = x$iv,
+        n                 = x$n,
+        n_model           = nrow(mod@frame),
+        n_model_obs       = mod@frame %>% distinct(id) %>% nrow,
+        data_raw          = x$data_raw,
+        data_analysis     = data,
+        data_model        = mod@frame,
+        specifications    = x$specifications,
+        #model             = mod,
+        model_tidy        = mod_tidy,
+        model_std_effects = mod_standardized,
+        model_effects     = mod_effects,
+        simple_slopes     = list(task = ss_task, iv = ss_iv)
+      )
+    
[…]

### 2021-02-07 scripts/3-secondary-analyses/set-2/a2-extract-effects.R

@@ -1,0 +1,93 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+
+# Load results
+load("multiverse-objects/3-secondary-analyses/set-2/a1-results-expanded-shifting.Rdata")
+load("multiverse-objects/3-secondary-analyses/set-2/a1-results-expanded-updating.Rdata")
+
+# Results prep ----------------------------------------------------------
+secondary_pmap <-
+  list(
+    ls() %>% str_subset("^secondary_expanded") %>% map(function(x) eval(as.symbol(x))),
+    c("Attention-Shifting", "Working Memory Updating")
+  )
+
+# Raw effect size data ----------------------------------------------------
+secondary_set2_effects <- 
+  secondary_pmap %>% 
+  pmap_df(function(multiverse, dv){
+    # All parameters from multiverse
+    params <-
+      multiverse %>% 
+      map_df(function(x){ 
+        bind_cols(
+          iv = x$iv,
+          dv = dv,
+          n = x$n_model_obs,
+          left_join(
+            x$model_tidy %>% select(mod_term:mod_p.value), 
+            x$model_std_effects %>% rename_with(~paste0("mod_",.x)), 
+            by = c("mod_term" = "mod_Parameter")
+          ),
+          x$specifications %>% 
+            select(-spec_expr) %>% 
+            pivot_wider(names_from = "spec_var", values_from = "name") %>% 
+            rename_with(.cols = !spec_number, ~paste0("spec_",.x))
+        ) 
+      }) %>% 
+      rename_with(tolower) %>% 
+      filter(!str_detect(mod_term, "^sd__"))
+  })
+
+secondary_set2_effects_clean <- 
+  secondary_set2_effects %>% 
+  mutate(
+    iv_group = case_when(str_detect(iv, "^ses") ~ "SES",
+                         str_detect(iv, "^unp") ~ "Unpredictability",
+                         str_detect(iv, "^vio") ~ "Violence")
+  ) %>% 
+  group_by(iv, dv, mod_term) %>% 
+  mutate(
+    spec_sub_number = 1:n(),
+    spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),
+    median_dbl = median(mod_std_coefficient),
+    median_chr = median_dbl %>% round(2) %>% as.character,
+    pval_prop  = (sum(mod_p.value < .05)/64)
+  ) %>% 
[…]

### 2021-02-07 README.Rmd
add empty output directories

@@
 ---
-
-<style>
-table{
-  font-size: 14px;
-}
-td{
-  vertical-align: top;
-}
-.gt_row{
-  vertical-align: top;
-}
-</style>
 
@@
 
-This repository contains all data, code, and output for a working manuscript by Young, Frankenhuis, and Ellis (in progress).
+This repository contains data, code, and (some) output for a working manuscript by Young, Frankenhuis, and Ellis (in progress).
+
+## IMPORTANT
+
+The file sizes of many output files produced by scripts in this repository are very large.
+As a consequence, these output files are not tracked here (see .gitignore).
+To preserve the directory structure, files named `0-placeholder.txt` have been added to output directories.
+This ensures that, if you were to run code that produces output not tracked here, the correct directory exists so files can be reproduced and saved.
 
@@
   gt(id = "one", rowname_col = "row", groupname_col = "dir") %>% 
-  fmt_markdown(columns = T) %>% 
-  tab_options(
-    row_group.font.weight = "bold",
-  ) %>% 
-  opt_css(
-    css = "
-    #one .gt_row {
-      vertical-align: top;
-    }
-    "
-  )
+  fmt_markdown(columns = T)
 ```

### 2021-02-07 README.Rmd
add preregistration links to README

@@
 
-## IMPORTANT
+## IMPORTANT!!
 
@@
 To preserve the directory structure, files named `0-placeholder.txt` have been added to output directories.
-This ensures that, if you were to run code that produces output not tracked here, the correct directory exists so files can be reproduced and saved.
+This ensures that scripts can reproduce and save output to the correct directory (without having to manually add them).
+
+## Preregistration
+
+Details about the participants, methods, procedures, and analysis plans can be found on the Open Science Framework (OSF). Below are the relevant links for different aspects of the project:
+
+-   [OSF project](https://osf.io/6r95z/)
+-   [Original preregistration](https://osf.io/d2gz6/)
+-   [Overview of measures](https://osf.io/5kawy/), which fully describes what was collected (including measures not used/analyzed in this project).
+Specific variable codebooks for the current project are contained in this repository (see Codeboooks below).
+-   [Final preregistration](https://osf.io/4vsnz/) which also contains a preliminary write-up of the Methods for an eventual publication
+-   [Secondary analysis plan - set 1](https://osf.io/7fu35/)
+-   [Secondary analysis plan - set 2](https://osf.io/wcauf/)
 
@@
 -   Primary analysis figures
+
 -   Secondary analysis figures
+
     -   Set 1

### 2021-02-07 README.Rmd
fix typo
trying to fix the README table

@@
 -   [Overview of measures](https://osf.io/5kawy/), which fully describes what was collected (including measures not used/analyzed in this project).
-Specific variable codebooks for the current project are contained in this repository (see Codeboooks below).
+Variable codebooks for the current project are contained in this repository (see Codebooks below).
 -   [Final preregistration](https://osf.io/4vsnz/) which also contains a preliminary write-up of the Methods for an eventual publication
@@
   gt(id = "one", rowname_col = "row", groupname_col = "dir") %>% 
-  fmt_markdown(columns = T)
+  fmt_markdown(columns = T) %>% 
+  gt::as_raw_html()
 ```

### 2021-02-08 README.Rmd
separate script input-output table in README

@@
 
-Each script takes an input(s) and produces output(s). The table below provides an overview of the inputs and outputs of each script.
+Each script takes an input(s) and produces output(s). The tables below provides an overview of the inputs and outputs of each script.
 
@@
       input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
-      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br>") %>% ifelse(is.na(.),"",.),
+      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>%str_c(collapse = "\n- ") %>%  paste0("- ", .) %>% ifelse(. == "- ","",.),
       n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
@@
   }) 
+```
 
+### Data Prep
+
+```{r}
 file_list %>% 
-  select(dir,script, input, output) %>% 
-  gt(id = "one", rowname_col = "row", groupname_col = "dir") %>% 
+  select(dir, script, input, output) %>% 
+  filter(dir == "data-prep") %>% 
+  select(-dir) %>%
+  gt(id = "one", rowname_col = "row") %>% 
   fmt_markdown(columns = T) %>% 
-  gt::as_raw_html()
+  as_raw_html()
 ```
+
+### Primary Analyses
+
+```{r}
+file_list %>% 
+  select(dir, script, input, output) %>% 
+  filter(dir == "primary-analyses") %>% 
+  select(-dir) %>% 
+  gt(id = "one", rowname_col = "row") %>% 
+  fmt_markdown(columns = T) %>% 
+  as_raw_html()
+```
+
+### Seconary Analyses
+
+```{r}
+file_list %>% 
+  select(dir, script, input, output) %>% 
+  filter(dir == "secondary-analyses") %>% 
+  select(-dir) %>% 
+  gt(id = "one", rowname_col = "row") %>% 
+  fmt_markdown(columns = T) %>% 
+  as_raw_html()
+```

### 2021-06-27 manuscript/manuscript.Rmd
first commit

---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: false
    keep_tex: true
    extra_dependencies: ["booktabs","caption","longtable","float"]
geometry: margin=1in
mainfont: Times
fontsize: 11pt
endnote: no
header-includes:
- \usepackage{siunitx}
- \usepackage[utf8]{inputenc}
- \usepackage[english]{babel}
- \setlength{\parindent}{2em}
- \setlength{\parskip}{0em}
- \linespread{1.5}
- \usepackage{titlesec}
- \titleformat{\section}[block]{\normalsize\bfseries\filcenter}{}{1em}{}
- \titleformat{\subsubsection}[block]{\bfseries\itshape}{}{1em}{}
- \usepackage{indentfirst}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhf{}
- \fancyhead[R]{\thepage}
- \fancyhead[L]{HIDDEN TALENTS IN CONTEXT}
- \renewcommand\headrulewidth{0pt}
- \usepackage{fixltx2e}
- \usepackage{caption}
- \captionsetup[table]{labelfont={bf},labelformat={default}, labelsep={newline}}
- \captionsetup[figure]{labelfont={bf},labelformat={default}, labelsep={period}}
bibliography: references.bib
csl: nature.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "H",  
  fig.show = "asis",
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(kableExtra)
library(gt)

load("staged-objects.Rdata")
```

\pagebreak

\vspace*{1in}

# Hidden talents in context: Can ecologically-relevant stimuli improve cognitive performance among adversity-exposed youth?

\bigskip

\begin{center}

Ethan S. Young\textsuperscript{1,2}, Willem E. Frankenhuis\textsuperscript{1,2}, Danielle J. DelPriore\textsuperscript{3}, and Bruce J. Ellis\textsuperscript{4}

\textsuperscript{1}Department of Psychology, Utrecht University, the Netherlands

\textsuperscript{2}Behavioural Science Institute, Radboud University, the Netherlands

\textsuperscript{3}Division of Education, Human Development, and Social Sciences, Pennsylvania State University - Altoona, USA

\textsuperscript{4}Departments of Psychology and Anthropology, University of Utah, USA

\end{center}

\pagebreak

# Abstract

\noindent Children developing in harsh conditions often perform poorly on standard cognitive tests. However, the hidden talents approach proposes that performance for some abilities may be enhanced by adversity or improved under ecologically relevant conditions. We examine ecologically relevant content in cognitive testing. Sampling 618 socioeconomically diverse adolescents, we measured performance on two versions of an attention shifting and working memory updating task---one abstract, the other ecological. Across multiple sources, we measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions using a preregistered multiverse approach. We did not find adversity × task version interactions for attention shifting, but there were main effects of unpredictability and violence, indicating improved attention shifting irrespective of task version. For working memory updating, violence- and poverty-exposed youth performed worse on the abstract but not the ecological version, equalizing performance among adversity-exposed youth. We found no relation between updating performance and unpredictability.

*Keywords*: hidden talents, working memory updating, attention shifting, adversity, adaptations to stress

\pagebreak

# Hidden talents in context: Can ecologically-relevant stimuli improve cognitive performance among adversity-exposed youth?

Children living in harsh conditions tend to perform poorly on many cognitive tests. For example, children raised in poverty often show difficulties learning in school and score lower on standardized tests[@ursache2016a; @farah2006; @noble2007; @hackman2010]. Harsh and unpredictable environments are thought to cause high levels of chronic stress, which impacts brain regions responsible for memory and learning[@blair2012]. Thus, the general consensus is that exposure to adversity undermines cognitive development and leads to a host of cognitive impairments[@hackman2010]. Although it is clear that harsh environments are harmful to children, there is growing interest in the *hidden talents* *approach*, which proposes that some abilities may be enhanced by adversity, especially those abilities that are ecologically relevant to lived experience. Thus, hidden talents are skills and abilities that help children meet real-world challenges in adverse environments[@ellis2017; @ellis2020; @frankenhuis2013; @frankenhuis2020].

The hidden talents framework assumes that development shapes the skills and abilities of individuals in relation to their environment[@ellis2017; @ellis2020; @frankenhuis2013; @frankenhuis2020]. Accordingly, exposure to adversity should shape skills and abilities well-suited for dealing with the challenges associated with harsh environments. However, because specific dimensions of adversity (violence versus resource-scarcity) may pose unique challenges[@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity[@frankenhuis2020]. For instance, physically abused children can apparently detect angry facial expressions quickly and accurately[@gibb2009; @pollak2008; @pollak2009], people living in poverty have shown some evidence of enhanced social perception[@piff2018], and anxiously attached people are good at deception detection[@eindor2014; @shoda2013] to list a few examples (see[@ellis2017; @ellis2020] for reviews).

Although some abilities themselves are more ecologically relevant to specific dimensions of adversity, hidden talents may also emerge under ecologically relevant conditions. For example, previous studies of hidden talents have tested cognition under ecologically relevant *contexts and situations*. In particular, studies have experimentally manipulated the current context to be uncertain and mildly stressful (or not) and measured performance on executive functioning and working memory tasks[@mittal2015; @young2018] (but see[@nweze2021] for similar results without uncertainty). Strikingly, people from unpredictable environments showed improved performance on attention shifting and working memory updating tasks. However, this effect only emerged under conditions of uncertainty. There was no performance improvement under control conditions.

Hidden talents may also emerge when testing *content and stimuli* are ecologically relevant to adversity-exposed individuals. Typical cognitive tests use abstract content that is largely detached from the real world. Such abstract materials may disadvantage youth with limited exposure to formal education. Cultural psychologists and anthropologists have demonstrated this fact across the world. For example, people from low income and non-western cultures tend to perform worse on standard versions of cognitive tests, but this performance gap closes or disappears with more ecologically relevant versions of the same tests[@banerjee2017; @greenfield2014; @ogbu1981; @richardson1991; @schliemann2002]. These findings pose an important question: Can ecologically relevant testing materials improve cognitive performance among adversity-exposed youth?

One way to test this question is to simply replace sterile testing materials with ecologically relevant content. For example, one study tested memory and reasoning among young adults who varied in their exposures to violence[@frankenhuis2020a]. They created two versions of the memory and reasoning task, one neutral (chronological age) and one more ecologically relevant (social dominance). They found that people with more current exposures to violence were equally good, or even better, at memorizing social-dominance relationships compared to people with fewer exposures. Notably, such violence exposures were associated with worse memory for neutral (age) relationships. There were no associations revealed between violence exposures and reasoning performance. Overall, this study suggests that ecologically relevant testing materials may level the playing field for adversity-exposed youth[@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018]. In addition, although executive functions and working memory are related to many educational outcomes, it is unclear how schools and teachers might leverage skills that specifically depend on inducing uncertainty. That seems impractical, at best, and unethical, at worst.

Here we address this issue by evaluating the role of ecologically relevant content in attention shifting and working memory tasks. To do so, we sampled `r nrow(data2_non_arbitrary)` adolescents from a socioeconomically diverse population. Using interviews, self-reports, and school records, we measured exposure to environmental unpredictability, violence, and poverty. We then tested performance on two widely used tasks: attention shifting and working memory updating. There were two versions of each task. The first used standard abstract stimuli and the second replaced these stimuli with more ecologically relevant ones (see Figure \@ref(fig:figure1)). We then tested the interactive effect of task content and adversity exposure.

We expected adversity-exposed adolescents to benefit more from ecologically relevant stimuli (compared to abstract stimuli) than their counterparts. As such, our primary analyses involved two preregistered confirmatory analyses and one exploratory analysis. Our confirmatory analyses focused on environmental unpredictability and violence exposure because both dimensions have been associated with improved performance under ecologically relevant conditions (contexts and testing materials) and represent specific environmental challenges. Our exploratory analyses focused on exposure to poverty, which is both relevant to hidden talents (e.g., hidden talents could develop in response to specific challenges of poverty) and a general proxy to adversity rather than a specific exposure.

We also evaluated the relative robustness of our models to arbitrary data processing decisions using a multiverse analysis approach[@steegen2016; @simonsohn2020]. Specifically, we systematically and explicitly generated all possible combinations of (arbitrary) data processing decisions and analyzed them simultaneously. We conducted a separate multiverse analysis for each task (attention shifting and working memory updating) and each measure of adversity exposure combination. All multiverse analyses used the same underlying statistical models.

(ref:figure1) Schematic display of the attention shifting and working memory updating tasks: a) abstract attention shifting, b) ecological attention shifting, c) abstract working memory updating, and d) ecological working memory updating.

```{r figure1, fig.cap='(ref:figure1)'}
knitr::include_graphics("figure1.pdf")
```

# Results

## Overview

To test our hypotheses, we performed a set of primary and secondary analyses on attention-shifting and working memory performance. Our primary analyses tested the effects of task version, adversity dimensions, and adversity dimension × task version interactions. Specifically, we tested the main effect of environmental unpredictability (confirmatory), violence exposure (confirmatory), and poverty exposure (exploratory), and the interaction between each adversity dimension with task version (abstract vs. ecological) on attention-shifting and working memory performance. We ran separate analyses for each adversity dimension and outcome combination.

Before conducting analyses, we identified six arbitrary data processing decisions each with two alternatives (see Arbitrary Decisions section). These criteria were 1) including the after-school club sample or not; 2) including participants with minor distractions during testing or not; 3) including participants who missed one trap question or not (those who missed more than 1 were already excluded); 4) including participants receiving special education (participants receiving more \> 60 minutes/day were already excluded) or not; 5) including participants who performed at or below chance levels of accuracy on the attention-shifting task or not (see <https://osf.io/kvt5e/> for more information); and 6) residualizing social desirability scores out of adversity scores or not. Using all possible combinations of arbitrary decisions, we constructed a multiverse of `r length(multi_data_list)` datasets. The minimum and maximum sample sizes were `r map_dbl(multi_data_list, "n") %>% min()` and `r map_dbl(multi_data_list, "n") %>% max()`, respectively.

We ran the same underlying mixed-effects linear regression model. Analyses were conducted using R[@rcoreteam2020] and mixed models were fit using the lme4 package[@bates2015]. Our mixed-effects models included five fixed terms: the main effect of task version (ecological or abstract version, within-subjects), the main effect of childhood adversity (between-subjects), the interaction between task version and adversity exposure, the main effect of age (control variable), and the main effect of test distraction ratings (control variable). Task version was grand mean centered (abstract versions = -1, ecological versions = 1). All childhood adversity measures were standardized before model fitting, and all models included a random intercept for task version nested in participants.

Our models for attention shifting and working memory updating differed in one respect. Our sample included a small subset of siblings (*n* = `r txt6_sib$n`, `r txt6_sib$families` families). All sibling groups were pairs of two (`r txt6_sib$sizes$two` sibling pairs) except for `r english::as.english(txt6_sib$sizes$three)` group of three and `r english::as.english(txt6_sib$sizes$four)` group of four siblings. We computed intraclass correlations (ICCs) for sibling groups for attention-shifting and working memory updating scores. ICCs for attention shifting were essentially zero, but they were non-zero for working memory updating scores (*ICC~standard~* = `r txt6_sib$iccs$abs_update`, *ICC~ecological~* = `r txt6_sib$iccs$eco_update`). Thus, all models analyzing working memory updating included an additional random intercept for siblings. Non-siblings were given the same sibling-group code, so the model could compute an intercept for non-siblings.

To facilitate interpretation of multiverse results, we report median standardized $\beta$s, median 95% confidence intervals, and percent significant for each term in our model (see Table \@ref(tab:table2)). Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions. For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique[@simonsohn2020; @orben2019; @orben2019a] to compute overall p-values, which indicate whether a $\beta$ of a term is larger than expected given the null (the median $\beta$ = 0; see Statistical Inferences).

Table \@ref(tab:table1) displays bivariate associations between all composite measures of adversity, including components of each, and descriptive statistics. Our primary interests were the main effect of adversity and the interaction of adversity with task-version. Table \@ref(tab:table2) shows median effect sizes ($\beta$-coefficients), sample sizes, and bootstrapped *p*-values for attention shifting and working memory updating analyses for the main effect of adversity (unpredictability, violence, and poverty) and the interaction term (task version × adversity). Table \@ref(tab:table3) reports median simple effects of task version across high and low levels of adversity and median simple effects of adversity across abstract and ecologically relevant task versions.

```{r table1}
table.01.0 %>% 
  kbl(
    align = "lcccccccccc",  
    booktabs = T,
    escape = F,
    caption = "\\emph{Bivariate correlations and descriptive statistics for all measures of adversity and their subcomponents.}"
  ) %>% 
  add_header_above(c(" ","Unpredictability" = 3, "Violence" = 3, "Poverty" = 4)) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(
    general       = "Column headers denote adversity constructs and rows indicate components. The upper triangle contain sample sizes for each correlation.",
    general_title = "Note:", 
    symbol        = c("p < .05,","p < .01"),
    symbol_manual = c("*", "**"),
    footnote_as_chunk = T,
    title_format = "italic",
    threeparttable = T
  )
```

Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$1 *SD*) and low ($-$ *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction -coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).

We preregistered all primary analyses on the Open Science Framework (OSF; <https://osf.io/6r95z/>), including an updated primary analysis plan (<https://osf.io/4vsnz/>), which included more details. We conducted secondary analyses after our primary analyses (see Secondary Analyses below). Before conducting these analyses, we uploaded secondary analysis plans (see <https://osf.io/7fu35/> and <https://osf.io/wcauf/>), explaining the goals and purpose of each secondary analysis. A Red Team Critic[@market] successfully reproduced (<https://github.com/ethan-young/hidden-talents-multiverse/pull/1/>) and verified (REPORT XXX) all analyses prior to submission.

## Primary Analyses

### Attention Shifting

Across each set of multiverse analyses, there were significant main effects of task version. All median effects sizes for task version were $\beta$s = `r c(mod_terms1$shifting.unp.type_z$median_beta, mod_terms1$shifting.vio.type_z$median_beta, mod_terms1$shifting.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for multiverse models testing unpredictability, violence exposure, and poverty exposure, indicating that switch costs were moderately higher for the ecological version compared to the abstract version (see SI Figures 1-3). That is, reaction times on switch trials, compared to repeat trials, were longer when stimuli were ecologically relevant as opposed to abstract. However, there were no effects of age (all median $\beta$s = `r c(mod_terms1$shifting.unp.age$median_beta, mod_terms1$shifting.vio.age$median_beta, mod_terms1$shifting.ses.age$median_beta) %>% mean()`, all *ps* \>.05) or test distraction ratings (all median $\beta$ = `r c(mod_terms1$shifting.unp.test_envr$median_beta, mod_terms1$shifting.vio.test_envr$median_beta, mod_terms1$shifting.ses.test_envr$median_beta) %>% mean()`, all *ps* \> .05) on overall switch costs (see SI Figures 1-3).

(ref:figure2) Visualization of multiverse attention shifting results. Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.

```{r figure2, fig.height=7.5, fig.width=6.5, fig.cap='(ref:figure2)'}
fig2
```

Overall, there were no significant interaction effects between task version and unpredictability, violence exposure, or poverty exposure (see Table \@ref(tab:table2), Table \@ref(tab:table3), and Figure \@ref(fig:figure2)b). However, analyses produced main effects of unpredictability (median $\beta$ = `r mod_terms2$shifting.unp$median_beta_main`, `r mod_terms2$shifting.unp$p_percent_main %>% str_remove("\\.00")` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.unp$p_overall_main`) and violence exposure (median $\beta$ = `r mod_terms2$shifting.vio$median_beta_main`, `r mod_terms2$shifting.vio$p_percent_main` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.vio$p_overall_main`). (See Table \@ref(tab:table2).) There were no main effects of poverty exposure (median $\beta$ = `r mod_terms2$shifting.ses$median_beta_main`, no *ps* \< .05, overall *p* = `r mod_terms2$shifting.ses$p_overall_main`); see Table \@ref(tab:table2)). That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures are associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecologically relevant.

### Working Memory Updating

Across each set of multiverse analyses, there were again significant main effects of task version. All median effects sizes for task version were $\beta$s = `r c(mod_terms1$updating.unp.type_z$median_beta, mod_terms1$updating.vio.type_z$median_beta, mod_terms1$updating.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for models testing unpredictability, violence exposure, and poverty exposure, indicating that updating performance was better when stimuli were ecological relevant compared to abstract, on average (see SI Figures 4-6). There were also consistent main effects of age; median effects were $\beta$ = `r mod_terms1$updating.unp.age$median_beta` (all *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.age$median_beta` (all *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.age$median_beta` (all *ps* \< .05) for poverty exposure models (see SI Figures 4-6). That is, older adolescents scored higher on working memory updating, on average. Finally, there were some main effects of test environment distraction ratings. Median effects sizes were $\beta$ = `r mod_terms1$updating.unp.test_envr$median_beta` (`r (mod_terms1$updating.unp.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.test_envr$median_beta` (`r (mod_terms1$updating.vio.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.test_envr$median_beta` (`r (mod_terms1$updating.ses.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for poverty exposure models, indicating that more test distractions reduced working memory updating performance, on average (see SI Figures 4-6).

(ref:figure3) Visualization of multiverse working memory updating results. Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect. Proportions of each arbitrary decision with *p*-values < .05 are indicated on the right side of each specification grid. Blank proportions indicate proportions = 0.

```{r figure3, fig.height=7.5, fig.width=6.5, fig.cap='(ref:figure3)'}
fig3
```

```{r table2}
table.02.0 %>% 
  ungroup() %>% 
  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
  arrange(dv,iv) %>% 
  select(-dv) %>% 
  mutate(across(.cols = contains("p_percent"), ~ str_replace(.x, "%", "\\\\%"))) %>% 
   kable(
    col.names = c(" ","$\\beta$", "95\\% CI","\\emph{p} (\\%)","\\emph{p}", "$\\beta$", "95\\% CI","\\emph{p} (\\%)","\\emph{p}"),
    booktabs = T,
    escape = F,
    caption = "\\emph{Median standardized effects, 95\\% confidence intervals, percent significant, and bootstrapped p-values for the main effect of adversity and interaction terms for adversity by task version for attention shifting and working memory updating.}"
  ) %>% 
  add_header_above(c(" " = 1, "Main Effect" = 4, "Interaction" = 4)) %>% 
  group_rows(group_label = "Attention Shifting", start_row = 1, end_row = 3) %>% 
  group_rows(group_label = "Working Memory Updating", start_row = 4, end_row = 6) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(
    general = "The p (%) column reflects the number of analyses that produced p-values < .05 out of all analyses for a given multiverse analyses. The total number of analyses for each measure was 64. Overall p-values were computed using a bootstrapping resampling method and reflect the probability of obtaining an effect size as extreme or more extreme given the median effect is 0.",
    general_title = "Note:", 
    footnote_as_chunk = F,
    title_format = "italic",
    threeparttable = T
  )
```

Multiverse analyses revealed a main effect of poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_main`, all *ps* \< .05, bootstrapped *p* \< .001) but no main effects of unpredictability (median $\beta$ = `r mod_terms2$updating.unp$median_beta_main`, no *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.unp$p_overall_main`) or violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_main`, `r mod_terms2$updating.vio$p_percent_main` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_main`). Analyses also revealed two significant interactions: task version × violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_int`, `r mod_terms2$updating.vio$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_int`) and task version × poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_int`, `r mod_terms2$updating.ses$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.ses$p_overall_int`). Adolescents exposed to low levels of violence or poverty tended to perform better on the abstract working memory updating task (violence exposure median *b~abstract~* = `r simple_effects$updating.vio$beta_abs`, `r simple_effects$updating.vio$p_percent_abs` of *ps* \< .05; poverty exposure median *b~abstract~* = `r simple_effects$updating.ses$beta_abs`, all *ps* \< .05), compared to adolescents exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)). However, this performance gap closed on the ecological working memory task (violence exposure median *b~ecological~* = `r simple_effects$updating.vio$beta_eco`, no *ps* \< .05; poverty exposure median *b~ecological~* = `r simple_effects$updating.ses$beta_eco`, `r simple_effects$updating.ses$p_percent_eco` of *ps* \< .05). Put differently, adolescents exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically-relevant version compared to their own performance on the abstract version (median simple *b~high~ ~violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high~ ~poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas adolescents exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low~ ~violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low~ ~poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05). In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among adolescents exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).

```{r table3, results='asis'}
table.03.0 %>% 
  ungroup() %>%
  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
  arrange(dv,iv) %>% 
  select(-dv) %>% 
  mutate(across(.cols = contains("p_percent"), ~ str_replace(.x, "%", "\\\\%"))) %>% 
   kable(
    col.names = c(" ", "\\emph{b} (abs)", "\\emph{p} (\\%)","\\emph{b} (eco)", "\\emph{p} (\\%)", "\\emph{b} (low)", "\\emph{p} (\\%)","\\emph{b} (high)", "\\emph{p} (\\%)"),
    booktabs = T,
    escape = F,
    caption = "\\emph{Median simple effects (unstandardized) and percent significant for task version and adversity for attention shifting and working memory updating.}"
  ) %>% 
  add_header_above(c(" " = 1, "Task Version" = 4, "Adversity Exposure" = 4)) %>% 
  group_rows(group_label = "Attention Shifting", start_row = 1, end_row = 3) %>% 
  group_rows(group_label = "Working Memory Updating", start_row = 4, end_row = 6) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(
    general = "Simple effects for Task Version reflect the median effect of adversity in for the abstract version (abs) and ecological version (eco). Simple effects for Adversity reflect the effect of task version when adversity-exposure is low (-1 SD) and high (+1 SD). P-values < .05 out of all analyses for a given multiverse analyses. The total number of analyses for each measure was 64.",
    general_title = "Note:", 
    footnote_as_chunk = T,
    title_format = "italic",
    threeparttable = T
  )
```

## Secondary Analyses

We followed-up our primary analyses with two sets of secondary, exploratory analyses. We uploaded secondary analysis plans to the OSF prior to conducting them (see <https://osf.io/7fu35//> and <https://osf.io/wcauf//>). These analyses focused on two questions. First, in contrast to prior work[@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting). However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures. Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure) have unique associations with attention shifting and working memory updating performance. To address this, we expanded our multiverse approach to include each component of our predictor variables as additional arbitrary decisions.

The second question focused on the interactive effects of task version × violence exposure and task version × poverty exposure on working memory updating performance. Specifically, primary analyses revealed an equalization effect for both violence and poverty exposures on working memory updating. However, because measures of violence and poverty were not included in the same statistical model, it is unclear whether these interactions are independent. For example, one possibility is that exposures to violence and poverty are independently associated with working memory updating performance. Alternatively, they may overlap, reflecting the same association. To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty in the same model. If violence and poverty exposures interact independently with task version, both interaction terms should remain significant. However, if they represent overlapping effects on working memory updating performance, one or the other may drop out of significance, which would suggest that one or the other adversity dimension is driving the effects of the other.

### Exploring Components of Adversity Dimensions

We ran an expanded multiverse analysis to explore the effects of each component of our adversity composites on attention shifting and working memory updating performance. Environmental unpredictability contained two components, perceived unpredictability (self-reported) and an interview-based measure tabulating family disruptions, parental figures, and residential moves. Violence exposure contained two self-report components: neighborhood violence and exposure to/involvement in violence. Poverty exposure contained three components: parental education/occupation (interview), perceived resource scarcity (self-report), and school-coded economic disadvantage (fee waivers, free- or reduced-priced lunch, and homelessness).

For this expanded multiverse approach, we retained all original data processing decisions (i.e., original 64 combinations of decisions) and added an adversity component as an additional decision. For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures [attention shifting and working memory]). We applied the same approach to violence exposure (three violence variables, 384 analyses) and poverty exposure (four poverty variables, 512 analyses). The full results of these analyses are reported in the supplement (see SI Table 2).

For attention shifting, consistent with our primary analyses, there were no interactions for any component of adversity and task version (see SI Table 2 and SI Figures 7-9). However, there were a few main effects of adversity. First, primary analyses revealed, under some analytic decisions, a main effect of unpredictability. Upon inspection of each unpredictability component, this effect appeared to be entirely driven by self-reported perceived unpredictability. Specifically, no main effect *p*-values for interview-based unpredictability were \< .05, whereas `r secondary1_medians$shifting.unp.Perceived.iv$p_percent` were for perceived unpredictability (see SI Table 2, SI Table 3, and SI Figure 7). In addition, violence exposure revealed that our primary analyses were driven by neighborhood violence (`r secondary1_medians$shifting.vio.Neighborhood.iv$p_percent` of *ps* \< .05) and not by direct witnessing or involvement in fights (no *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 8). There were no main effects of poverty exposure components on attention shifting (see SI Table 2, SI Table 3, and SI Figure 9).

For working memory updating, there were no interaction between any unpredictability component (perceived or interview-based) and task-version (see SI Figure 10). However, our expanded analysis with violence exposure revealed that interactions obtained with the composite measure were not driven by neighborhood violence but instead by witnessing or involvement in violence (`r secondary1_medians$updating.vio.Fighting.iv_type_z$p_percent %>% str_remove("\\.00")` of interaction *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 11). No interactions were significant with the neighborhood violence component of the violence composite. For poverty exposure, interview-based parental occupational prestige and school-reported economic disadvantage showed some interaction effects (parental education/occupational prestige `r secondary1_medians$updating.ses.Parents.iv_type_z$p_percent` of *ps* \<.05; school coded economic disadvantage `r secondary1_medians$updating.ses.School.iv_type_z$p_percent` of *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 12). Self-reported perceived resource scarcity showed no interaction effects (see SI Table \@ref(tab:table2), SI Table 3, and SI Figure 12).

### Comparing Violence and Poverty Exposure Interactions with Task-Version

Our next secondary analysis was designed to compare the violence exposure × task-version interaction with poverty exposure × task-version interaction on working memory updating performance in the same model. To do so, we ran a multiverse analysis using the original set of `r length(multi_data_list)` data processing decisions. We entered the same controls, main effects of task-version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty exposure. Analyses revealed a main effect of poverty (`r secondary2_medians$ses_agg_z$p_percent` of *ps* \< .05); consistent with the primary analyses, lower poverty was associated with better updating performance under most analytic decisions. However, there were no main effects of violence exposure (no *ps* \< .05). For interactions, there were no effects of task version × poverty (no *ps* \< .05, see SI Figure 13) and only a small number of significant task version × violence exposure effects (`r secondary2_medians$type_z_vio_agg_z$p_percent` of *ps* \< .05, see SI Figure 13). More specifically, when both interactions were entered into the same model, only task-version × violence exposure remained significant, although only under a small set of analytic decisions.

Violence and poverty exposure interaction patterns were qualitatively similar to those obtained in our primary analyses (see Figure \@ref(fig:figure3)a and SI Figure 13). However, these secondary results suggest that the violence exposure interaction with task-version may be driving our poverty × task version results for working memory updating. One possibility is that the shared variance between poverty and violence exposures (*r* = `r txt5_cor$ses_vio$r`) is responsible for both interaction effects. In other words, although poverty and violence exposure are theoretically distinct, our poverty composite may capture poverty-related violence exposures (e.g., high poverty neighborhoods contain more crime) and therefore interact with task-version. When directly compared, explicit measures of violence exposure remain significant (although only under a small set of analytical decisions), whereas poverty interactions drop out entirely.

# Discussion

We examined how ecologically relevant testing materials affect cognitive performance among adversity-exposed youth. We measured three dimensions of adversity--- environmental unpredictability, violence exposure, and poverty---and tested performance on attention shifting and working memory updating tasks. We administered two versions of each task: one using abstract stimuli and the other using ecologically-relevant stimuli, allowing us to compare performance within- and between-subjects.

Leveraging multiverse analysis[@simonsohn2020; @steegen2016], we tested interactions between dimensions of adversity and task version on attention shifting and working memory updating performance. We did not find interaction effects for attention shifting. However, youth exposed to unpredictability and violence showed smaller switch costs on average, suggesting slightly improved attention shifting performance irrespective of task content. These findings partially diverge from prior work[@mittal2015; @nweze2021]. For example, whereas we found unpredictability was associated with improved attention shifting on average, Mittal and colleagues[@mittal2015] found no difference in performance under neutral conditions. And, although they improved attention shifting for those exposed to high unpredictability under uncertainty, it remains unclear how this effect relates to those obtained in the current study. In addition, Fields and colleages[@fieldsa] found caregiving instability was associated with improved attention shifting, but Nweze and colleagues[@nweze2021] found no association between adversity and attention shifting. However, they tested institutionalized children rather than measuring adversity dimensions[@nweze2021]. In general, we should interpret cautiously. Although we followed field standards for calculating switch costs by computing difference scores, such scores ignore participant-level reaction times. Mixed-modeling approaches can account for both overall reaction times and differences across switch and repeat trials, but require more statistical power to test three-way interactions. Future should consider more appropriate modeling approaches.

For working memory updating, we found lowered performance among violence- and poverty-exposed youth on the abstract working memory updating task compared to peers with reduced exposures. However, ecological materials produced an equalization effect: the updating performance gap between low and high-adversity exposed youth narrowed on the ecological updating task. Interestingly, updating performance was unrelated to unpredictability. These findings are partially consistent with prior work on adversity exposure and working memory updating performance[@young2018; @nweze2021]. For example, both Young and colleagues[@young2018] and the current study found lowered abstract working memory performance among high adversity-exposed individuals. Although performance with ecological stimuli is not directly comparable to performance under manipulated uncertainty, both studies reduced the updating performance gap under ecologically relevant conditions. However, there are also discrepancies. For example, Young and colleagues[@young2018] found effects with unpredictability and not poverty, whereas the current study found associations with violence and poverty but not unpredictability. Finally, Nweze and colleagues[@nweze2021] found improved working memory performance among institutionalized youth without ecological stimuli or uncertainty manipulations. However, both their adversity and working memory measures were different. Such inconsistencies could be attributed to differences in sampling (adults vs. adolescents), the sampled range of adversity exposure (restricted vs. broad), or methods/design (within- vs. between-subjects design; lab vs. community/school settings). Future research should address these inconsistencies.

Our first set of secondary analyses focused on the components of our adversity composites. For attention shifting performance, the main effect of our unpredictability composite appeared to be driven by self-reported perceived unpredictability and not by the interview-based measure which captured changes in youths' living situations. Likewise, the main effect of violence exposure appeared to be driven by neighborhood violence and not involvement or witnessing fights. For working memory updating, interaction effects involving violence exposure were driven by involvement or witnessing fights but not perceptions of neighborhood violence. All components of poverty exposure measures, except self-reported perceptions of resource scarcity, showed interactive effects with task version on working memory updating. Our second set of secondary analyses compared violence to poverty exposure in the same model. Findings suggest, at least when directly comparing interaction terms, violence exposure × task version predicted the working memory updating equalization effect whereas the poverty × task version interaction did not. Although interesting, all secondary analyses are exploratory, and should be interpreted with caution. Nonetheless, these analyses highlight the need to measure multiple dimensions of adversity, compare them, and consider each measure's report format and source.

Taken together, our equalization patterns of results are striking compared to the backdrop of developmental science, which almost exclusively reports lowered cognitive performance in people exposed to harsh rearing conditions. We also document lowered performance among adversity-exposed youth, but this effect was specific to tests with abstract stimuli, at least for working memory updating. When testing materials have more ecological relevance, adversity-exposed youth perform about as well as youth from affluent backgrounds. These effects have both practical and theoretical implications. Practically, these effects support the idea that ecologically relevant testing materials may "even the playing field" for adversity-exposed youth. That is, pending replication and extension, our data suggest leveraging ecologically relevant materials in education may hold promise for closing achievement gaps[@ellis2017; @ellis2020; @frankenhuis2020]. However, our data also suggest the effect of ecological content may be specific to particular abilities---ecological content actually *lowered* attention shifting performance for everyone compared to abstract content. This negative effect is consistent with other studies reporting lowered performance on tests with ecologically relevant content[@frankenhuis2020; @muskens2019; @duquennois].

Theoretically, our findings support the notion that hidden talents may emerge when using ecologically relevant testing materials, but they also raise questions. In particular, why should ecologically relevant stimuli equalize working memory updating performance for adversity-exposed youth compared to youth with reduced exposures? There are at least three possibilities. First, both impairment and enhancement processes could operate in parallel. While abstract working memory updating performance is impaired, ecological working memory updating performance is enhanced. However, this explanation is difficult to reconcile unless performance on tests with different content rely on or recruit different cognitive processes. If this is true, those mechanisms that process abstract content may be impaired but those that process ecological content are intact or enhanced. Second, there may be not impaired or enhanced processes at all. Instead, ecologically relevant stimuli may activate intact, but normally dormant or underrecruited, working memory updating processes. Thus, when tested under abstract testing conditions, cognitive processes operate at lower level (remain inactive) but operate normally with ecological testing materials. This makes sense if adversity limits energy and/or cognitive resources. Under such constraints, it may be adaptive to activate expensive cognitive processes only when necessary. Third, ecological testing materials may remove barriers, such as testing anxiety, that disadvantage adversity-exposed youth. Unlike the selective activation of cognitive resources, the additional stressors of testing are removed, allowing cognitive mechanisms to function normally. However, this explanation is difficult to reconcile with experimental work[@mittal2015; @young2018], which finds that mild stress/uncertainty improves performance. Future research should use research designs that can disentangle these explanations.

Our study has several strengths and limitations. First, we leveraged a within-person design, which illuminated the effects of ecological testing materials in the same person. However, the correspondence between each version of our tests was modest for working memory updating (*r* = `r txt5_cor$updating$r`) and low for attention shifting (*r* = `r txt5_cor$shifting$r`). Although the task structure was the same, it is unclear to what extent the ecological tests measured the same construct, especially for attention shifting. Second, although we found some effects of ecological testing materials, we measured previously documented hidden talents. To explore generalizability of ecological content across abilities, future research may create ecological versions of tests known to disadvantage adversity-exposed youth, such as inhibition[@young2018] or working memory retrieval[@young2018], and compare performance to abstract versions. Third, although we used interviews and self-report methods, all of our childhood adversity measures were cross-sectional and some were retrospective. These measurement limitations may be partially offset because our sample was still living in their developmental environment. However, this does not replace the need for prospective, longitudinal measures and cannot eliminate all biases associated with retrospective reporting[@reuben2016]. Thus, it remains unclear to what extent the current environment, rather than the developmental environment, is driving our findings.

Until recently, developmental science has almost exclusively reported lowered cognitive performance in people from harsh conditions. The hidden talents framework has challenged this notion and inspired researchers to document the strengths and abilities of people from adversity. Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might even the playing field for adversity-exposed youth. Theoretically, our data help to refine the hidden talents framework and illuminate future research questions surrounding the unique skills and abilities of people living in harsh conditions.

# Method

## Participants

The current study collected data from `r txt1_sam$raw$n$total` adolescents (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah. The first was a middle school and the second were 5 after-school clubs. The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse. According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers). The clubs (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`). `r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch and were also ethnically diverse.

We aggregated data from both sources and applied a set of five exclusion criteria. We applied these criteria before inspecting or testing any relations between predictors and outcomes. Specifically, we excluded participants: 1) with incomplete cognitive task data, 2) with apparent cognitive impairments (e.g., head injuries, disabilities, drug use), 3) who missed two or more trap questions, 4) exposed to extreme distractions during the assessment, and 5) who received more than 60 minutes per day of special education services. After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).

## Procedure

Data collection involved six parts: consent/assent, demographics form, cognitive testing, structured interview, questionnaire, and a debriefing. Consent was obtained from the primary parent or guardian before assessments and assent was obtained from the participant at the beginning of the session. On the demographics form, participants indicated if they were left-handed, their birthdate, and their racial and ethnic background.

Cognitive testing included abstract (i.e., standard) and ecological versions of an attention-shifting and working memory updating task. Task order (shifting versus updating) and version (abstract versus ecological) were counterbalanced across participants. Some participants started with the attention shifting and then moved to the updating tasks. For those starting with the shifting (or updating) tasks, some started with the abstract version and then completed the ecological version (and vice versa). Regardless of which task was first, participants always completed both versions of one task before moving to the other task.

The interview contained two parts. The first part was about participants' home and family life, such as their family composition, the number of adults in the household, and occupation and education information about caregivers. Participants also reported on the number of romantic partners their caregivers had and if these partners lived with the participant. The second part was about residential mobility. Participants listed all the homes they lived in from birth to age 13. For each home, they reported at which ages they lived in the home. If they moved, they also reported any changes in their family structure (loss or gain of adults in the home), social network (e.g., a new school), and/or town or city.

The questionnaire contained measures focused on the childhood environment. The measures included perceived unpredictability in the home, exposure to neighborhood violence, access to material resources, direct exposure to violence and fighting, and a child version of socially desirable responding.

Procedures across the middle school and after-school clubs were the same, with a few minor differences. First, participants in the clubs completed the tasks before the interview, but the opposite occurred in the middle school. The second was that, in the middle school, the questionnaire was completed in a separate session. Whereas the tasks and interview were completed in a small room, alone with the interviewer, the questionnaire was completed approximately two weeks later in a mass testing context (large computer room). This was done because the middle school was on a strict class schedule, which limited the length of individual sessions. In the clubs, sessions were conducted in the summer during flexible hours.

## Measures

### Attention Shifting

We measured attention shifting with two versions of the color--shape task[@mittal2015; @miyake2012; @friedman2008], which involves categorizing stimuli according to one of two rules (see below). On each trial, the rule is displayed on the top of the screen. Using arrow keys, participants categorized the stimulus as quickly and accurately as possible. Response options appeared at the bottom of the screen (see Figure \@ref(fig:figure1)).

On the abstract (standard) attention-shifting task, participants categorized colored (blue or yellow) shapes (squares or triangles) according to the 'color' or 'shape' rule (see Figure \@ref(fig:figure1)a). For example, if a blue triangle appeared on the screen and the rule was "color", participants categorized the blue triangle as blue. However, if the rule was "shape", participants instead categorized the blue triangle as a triangle.

The ecological attention-shifting task replaced shapes and colors with faces (see Figure \@ref(fig:figure1)b). Faces were either male or female (gender), and were happy or angry (emotion). If a happy female face appeared on screen and the rule was 'gender', for example, participants categorized the face as female. If the rule was 'emotion', participants instead categorized the face as happy. The stimuli for the ecological attention-shifting task were selected from the NimStim library[@tottenham2009]. The same female and male models were used for happy and angry expressions.

For both versions, there were two types of trials: repeat and switch. Repeat trials use the same rule as the previous trial. If the current and previous rule is 'color', for instance, the current trial is a repeat trial. Switch trials are trials where the rule changes from the previous trial. If the current rule is 'color' but the previous was 'shape' (or vice versa), the current trial is a switch trial.

Accuracy on attention-shifting tasks is normally high, and was in the current sample for both versions (*M~standard~* = `r (txt2_dvs$abs_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~standard~* = `r (txt2_dvs$abs_shifting_correct$sd/32 * 100) %>% round(2)`%; *M~ecological~* = `r (txt2_dvs$eco_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~ecological~* = `r (txt2_dvs$eco_shifting_correct$sd/32 * 100) %>% round(2)`%).Thus, instead of accuracy, attention-shifting ability is measured by comparing reaction times on repeat trials to switch trials. Reaction times on repeat trials are normally faster than switch trials; average repeat trial reaction times on the abstract and ecological versions were `r txt2_dvs$abs_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_re_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_re_rt$sd` *ms*), respectively. On switch trials, average reaction times were `r txt2_dvs$abs_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sw_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sw_rt$sd` *ms*) on the standard and ecological versions.

To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000]. We removed fast and slow reaction times and removed trials after incorrect responses (see <https://osf.io/74xjy/> for details). We then subtracted the average reaction time on valid switch trials from the average reaction time on valid repeat trials to calculate switch cost scores. The switch cost measures the relative delay in reaction time caused by switching between categorization rules. Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` ms (*SD* = `r txt2_dvs$eco_shifting_sc$sd` ms), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`). Higher switch costs mean longer reaction times on switch trials compared to repeat trials. Larger switch costs indicate less efficient attention shifting.

### Working Memory Updating

Working memory updating was measured using two versions of the continuous counters task[@unsworth2015; @unsworth2008; @young2018], in which participants track a sequence of stimuli containing three different objects (see Figure \@ref(fig:figure1)). Participants keep running counts of each object in sequences nine items long. Each object was displayed for one second at a time. At the end of each sequence, participants reported the number of times each object appeared. For each round, there were three possible correct answers, one for each object type.

In the abstract (standard) version, participants kept running counts of squares, circles, and triangles (see Figure \@ref(fig:figure1)c). The participant must keep track of each shape, updating counts as new shapes appeared, and report them at the end of the sequence. The ecological version followed the same format, but participants kept running counts of three different real-world objects (see Figure \@ref(fig:figure1)d): one positive (five-dollar bill), negative (angry face), and neutral (Salt Lake City bus).

Participants completed five rounds of both versions. The maximum score was 15 for each version (five rounds × three possible correct). On the abstract and ecological versions, participants averaged `r txt2_dvs$abs_updating$mean * 15` (*SD* = `r txt2_dvs$abs_updating$sd * 15`) and `r txt2_dvs$eco_updating$mean * 15` (*SD* = `r txt2_dvs$eco_updating$sd * 15`), respectively (*r* = `r txt5_cor$updating$r`). Higher scores indicate better working memory updating performance.

### Environmental Unpredictability

Our measure of environmental unpredictability integrated information from the interview and questionnaire. The interview contained three variables of interest. The first measured the level of exposure to living in a biologically non-intact family from birth to age 13. Interviewers asked participants about their family composition and the adults that lived with them in the home. If a participant's family composition changed, for example, because of a divorce, interviewers recorded the ages when participants experienced the change and for how long it persisted. A family was considered non-intact if the participant did not live with both biological parents during any period from birth to age 13. Based on the earliest age of disruption, we indexed the onset of exposure to a non-intact family by creating a four-level variable from 0 to 3. A 0 indicated the participant lived in an intact family (lived with both biological parents) from birth until age 13 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 0) %>% sum(na.rm=T)`); a 1 indicated that a disruption occurred after the age of 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 1) %>% sum(na.rm=T)`); a 2 indicated that a disruption occurred before age 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 2) %>% sum(na.rm=T)`); and a 3 indicated the participant was born into a non-intact family (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 3) %>% sum(na.rm=T)`). `r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T)`. `r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T) %>% english::as.english() %>% str_to_title()` participants had missing information.

The second interview variable tabulated the number of different parental figures (defined as spouses or boyfriends/girlfriends of the participant's mother and father) who lived in the same home with the participant. Trained interviewers tabulated the total number of co-residing parental figures, excluding the participant's biological mother and father (*M* = `r txt3_ivs$unp_interview_figures$mean`, *SD* = `r txt3_ivs$unp_interview_figures$sd`).

The third interview variable focused on residential changes from birth to age 13 (reported retrospectively). Specifically, interviewers probed participants about the number of different homes they lived in and, in particular, whether moving to a new home involved living with new or different adults. On average, participants experienced `r txt3_ivs$unp_interview_moves$mean` (*SD* = `r txt3_ivs$unp_interview_moves$sd`) that involved changes in residential adults.

The questionnaire included a measure of perceived childhood unpredictability[@mittal2015; @young2018; @szepsenwol2015]. Participants responded to six items that assessed exposure to unpredictability up to age 13: 1) "Things were pretty calm and stable in my house" (reversed); 2) "People moved in and out of my house a lot"; 3) "I had a hard time knowing what my parent(s) or other people in my house were going to say or do from day-to-day"; 4) "My parent(s) argued or fought a lot with each other or with other people"; 5) "My parent(s) changed jobs a lot"; 6) "My parental situation changed a lot (for example, divorce or separation of parents, parents starting new romantic relationships, parents leaving the home)". Participants rated each item on a scale from 1 (never true) to 5 (very often true). Responses to these items were averaged to create a self-reported perceived childhood unpredictability measure (*M* = `r txt3_ivs$unp_perceived$mean`, *SD* = `r txt3_ivs$unp_perceived$sd`, $\alpha$ = `r txt4_rel$unp`). Higher scores indicated more perceived exposure to unpredictable environments.

To create a composite measure of unpredictability, we aggregated across the interview and questionnaire. First, we created an interview-based measure of unpredictability using family disruptions, exposure to different parental figures, and residential moves involving new adults living in the home. We standardized these interview measures and then averaged them together ($\alpha$ = `r txt4_rel$unp_int`). We then aggregated this interview measure with self-reported perceived unpredictability from the questionnaire, standardizing each before averaging (*r* = `r txt5_cor$unp$r`). Higher scores indicated more exposure to unpredictability.

### Violence Exposure.

We measured violence exposure using the Neighborhood Violence Scale (NVS)[@frankenhuis2020a; @frankenhuis2018] and two items about witnessing and involvement in physical fights. The NVS contains 7 items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm". The physical fighting items asked about witnessing fights: "Based on your experiences at school and in your neighborhood, how many times did you see or hear someone being beaten up in real life?"; and involvement in fights: "How many times were you in a physical fight at school or in your neighborhood?". Both items were rated on a scale from 1 (0 times) to 8 (12 or more times).

Responses on the NVS were averaged to create a composite measure (*M* = `r txt3_ivs$vio_neighborhood$mean`, *SD* = `r txt3_ivs$vio_neighborhood$sd`, $\alpha$ = `r txt4_rel$vio`). Likewise, the two fighting were averaged together (*M* = `r txt3_ivs$vio_fighting$mean`, *SD* = `r txt3_ivs$vio_fighting$sd`). To create a violence exposure composite, the NVS composite and fighting composite were standardized and then averaged (*r* = `r txt5_cor$vio$r`). Higher scores indicated more exposure to violence.

### Poverty Exposure

We assessed each participant's poverty exposure using three information sources: interview-assessed parent education and occupational prestige, school or club-provided economic information, and perceived resource scarcity.

During the interview, participants reported their parents' education and primary occupation. For parental education level, participants reported whether their mother and father graduated high school, went to college, and if they obtained a bachelor's degree or higher. Responses to each question were coded as 0 = 'no' and 1 = 'yes'. These items were summed to create a four-level variable for each parent where 0 = did not graduate high school, 1 = graduated high school but did not attend any college, 2 = graduated high school and completed some college, and 3 = went to college and obtained a bachelor's degree or higher. Mother and father education were averaged to create a parental education score (*M* = `r txt3_ivs$ses_interview_edu$mean`, *SD* = `r txt3_ivs$ses_interview_edu$sd`).

Participants also reported their parents' occupation. Participants described, in general terms, their mother's and father's jobs and the kind of work involved. Trained coders cross-referenced these descriptions with 2010 census job codes[@hout2018]. We calculated mother and father occupational prestige by matching census codes with prestige ratings from an established occupational prestige rating dataset[@hout2016]. Prestige codes ranged from 0-100, with higher scores indicating higher occupational prestige for a particular job code. Mother and father prestige codes were averaged to create a parent occupational prestige score (*M* = `r txt3_ivs$ses_interview_occup$mean`, *SD* = `r txt3_ivs$ses_interview_occup$sd`).

We also obtained school or club-provided economic information. The middle school provided four information sources: 1) whether or not students were receiving free lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_frl == 1) %>% sum(na.rm=T)`); 2) whether or not they were receiving reduced-price lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_rel == 1) %>% sum(na.rm=T)`); 3) whether they were receiving fee waivers (*n* = `r (data2_non_arbitrary$ses_school_wjms_fee == 1) %>% sum(na.rm=T)`); and 4) if they were experiencing homelessness (*n* = `r (data2_non_arbitrary$ses_school_wjms_hom == 1) %>% sum(na.rm=T)`). These information sources were compiled to create a binary economic disadvantage variable. A participant was economically disadvantaged if they were receiving any benefits or experiencing homelessness (*n* = `r txt1_sam$non_arb$free_lunch$wjms`). In the afterschool clubs, free or reduced-price lunch status was provided by self-report, staff, and club enrollment forms and cross-referenced to determine economic disadvantage in the clubs (*n* = `r txt1_sam$non_arb$free_lunch$bgc`). Overall, `r (data2_non_arbitrary$ses_school_freelunch == 1) %>% sum(na.rm=T)` participants were receiving economic assistance, `r (data2_non_arbitrary$ses_school_freelunch == 0) %>% sum(na.rm=T)` were not, and `r sum(is.na(data2_non_arbitrary$ses_school_freelunch))` had missing economic information.

Participants also reported their perceived level of resource scarcity. They rated seven items from 1 (never true) to 5 (very often true): 1) "Your family had enough money to afford the kind of home you all needed"; "Your family had enough money to afford the kind of clothing you all needed"; 3) "Your family had enough money to afford the kind of food that you all needed"; 4) "Your family had enough money to afford the kind of medical care that you all needed"; 5) "I felt well-off (rich, wealthy) compared to other kids in my school"; 6) "I felt well-off (rich, wealthy) compared to other kids in my neighborhood"; and 7) "Your family struggled to make ends meet (get by financially)". The first six items were reversed, and all items were averaged to create a perceived resource scarcity measure (*M* = `r txt3_ivs$ses_perceived$mean`, *SD* = `r txt3_ivs$ses_perceived$sd`, $\alpha$ = `r txt4_rel$ses`). Higher scores indicated more perceived resource scarcity.

To create a poverty exposure composite, we combined parent education and occupational prestige (reversed), school/club reported economic disadvantage, and perceived resource scarcity. First, we standardized and averaged parent education and occupation (*r* = `r txt5_cor$edu_int$r`). Then, we recoded school-provided economic codes to be equal to half of a standard deviation above and below the mean (in terms of z-scores). Specifically, those receiving free or reduced-price lunch were coded as .5, and those who were not were coded as -.5. To create a final composite, we averaged parent education/occupation (standardized), perceived resource scarcity (standardized), and the recoded school/club economic disadvantage. Higher values indicated more exposure to poverty.

### Control Variables

We included two control variables: age and interviewer-rated distractions during testing. We included these because older adolescents tend to score higher on cognitive tests than younger adolescents[@best2010; @best2011; @huizinga2006], and disruptions during the tasks could negatively impact performance. Interviewers completed quantitative ratings of the testing environment including 1) the level of noise; 2) the level of chaos; 3) how often there were interruptions; and 4) how often the participant appeared distracted. Interviewers rated each item on a scale from 1 (not at all) to 7 (much more than average). Items were averaged to create a composite (*M* = `r txt3_ivs$test_envr$mean`, *SD* = `r txt3_ivs$test_envr$sd`), where higher scores indicate more distractions.

We also included the Child Social Desirability (CSD) scale[@miller2014]. The measure includes 14 items such as "Have you ever broken a rule?" and "Do you sometimes feel angry when you don't get your way?". Participants indicated 1 (yes) or 0 (no) for each item. More socially desirable responses were scored as 1. Items were then summed to create a social desirability index (*M* = `r txt3_ivs$csd$mean`, *SD* = `r txt3_ivs$csd$sd` , $\alpha$ = `r txt4_rel$csd`).

## Multiverse Setup

We used a multiverse analysis approach for all analyses[@steegen2016; @simonsohn2020; @orben2019; @orben2019a]. Researchers face many data processing decisions. These decisions fall into two classes: arbitrary and non-arbitrary decisions. Non-arbitrary decisions have clear theoretical, statistical, or practical justifications and are superior to alternatives. Arbitrary decisions are those that have (sometimes many) equally defensible alternatives. For example, excluding outliers at +/- 2.5 or 3 standard deviations above (or below) the sample mean could be equally defensible. Instead of cherry-picking one or getting pigeonholed with the other, multiverse analysis allows researchers to explicitly generate all possible combinations of (arbitrary) data processing decisions and analyze them together. In turn, researchers can systematically evaluate the robustness or sensitivity of their analysis across all possible data processing decisions.

### Arbitrary Decisions.

We identified six arbitrary data processing decisions. First, we conducted analyses with and without the after-school club sample. We did this because our procedure was slightly different across the two samples and the testing environment was more disruptive in the clubs compared with the middle school. Second, we conducted analyses with and without participants with minor distractions during testing. Third, we analyzed the data with and without participants who missed one trap question (those who missed more than 1 were already excluded). Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded). Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see <https://osf.io/kvt5e/> for more information).

Our last arbitrary data processing decision pertained to socially desirable responses. It is well-known that some youth tend to describe themselves in socially desirable ways. This raises concerns about the validity of self-reported childhood adversity measures: youth scoring higher on social desirability might underreport or underrate their exposures to negative experiences. Indeed, scores on the CSD were correlated with exposures to unpredictability (*r* = `r txt5_cor$csd_unp$r`) and violence (*r* = `r txt5_cor$csd_vio$r`), though not with poverty. One way to handle this issue is to statistically remove overlapping variance between social desirability and each predictor, using the leftover variance (e.g., the residual variance in childhood adversity exposures not associated with social desirability) as a predictor. Because it is unclear how social desirability might affect the interpretation of our models, we analyzed our data with residualized and non-residualized predictors.

### Statistical Inferences.

Multiverse analysis produces a distribution of effect sizes and test statistics across all combinations of analytic decisions (see Figures \@ref(fig:figure2) and 3). However, although these distributions provide rich descriptive information, they do not lend themselves to straightforward null-hypothesis tests. This is because each individual analysis in a multiverse is not independent. To address this, we used a bootstrapping technique designed for multiverse analysis[@simonsohn2020; @orben2019; @orben2019a]. This technique makes it possible to know if a multiverse analysis produced a median effect size larger than expected, given the null hypothesis (the median effect is 0).

For the current study, we calculated overall p-values for the main effect of adversity and the interaction effects (task version × adversity) of our primary analyses. To do so, we created 'null' attention-shifting and working memory updating scores[@simonsohn2020]. That is, we created outcome scores with the influence of the effect of interest (i.e., main effect or interaction) removed. More specifically, we multiplied the coefficient of interest (regression coefficient of the main effect of adversity or interaction effect) by each participant's raw predictor score (either adversity scores or task version × adversity scores) and subtracted the result from each participant's attention-shifting and working memory scores. Next, we randomly sampled participants (with replacement) to create 500 bootstrapped samples. Then, we ran the same multiverse analysis on each bootstrap sample using the null attention-shifting and working memory scores as outcome variables. Upon completion, we compared the median effects for each bootstrapped sample (500 median effect sizes) with our original median effects. To compute overall p-values, we divided the number of effect sizes obtained from the bootstrapped multiverse analyses that were larger than our original median effect sizes by the total number of bootstrapped samples. Importantly, we ran this procedure separately for each measure of adversity (unpredictability, violence exposure, and poverty exposure), outcome (attention shifting and working memory updating), and effect of interest (main effect or interaction effect) combination.

\pagebreak

# References

### 2021-06-27 manuscript/scripts/0-corr_table.R

@@ -1,0 +1,79 @@
+corr_table <- function (data, sample_size = T, use = "pairwise", method = "pearson", 
+                        stats = NULL, c.names = names(data), change = F, numbered = F, 
+                        flagged = T) {
+  
+  my_ifelse <- function(...) {
+    suppressWarnings(ifelse(...))
+  }
+  
+  descriptives <- describe(data) %>% as.data.frame() %>% round(2) 
+  corr_data <- corr.test(x = data, use = use, method = method)
+  ns <- corr_data$n
+  rs <- corr_data$r %>% round(2) %>% formatC(digits = 2, width = 3, flag = '0', format = 'f')
+  
+  descriptives <- 
+    descriptives %>% 
+    select(-vars) %>% 
+    rownames_to_column(var = "var") %>% 
+    mutate(across(3:13, ~ formatC(.x, digits = 2, width = 3, flag = '0', format = 'f'))) %>% 
+    pivot_longer(cols = c(-var), names_to = "stat", values_to = "value", values_transform = list(value = as.character)) %>% 
+    pivot_wider(names_from = var, values_from = value)
+  
+  if (!is.null(stats)) {
+    descriptives <- 
+      descriptives %>% 
+      filter(stat %in% stats) %>% 
+      slice(match(stats, stat)) %>% 
+      mutate(stat = str_to_title(stat), stat = ifelse(stat=="Sd","SD",stat))
+  }
+  if (flagged) {
+    ps <- 
+      corr_data$p %>% 
+      as.data.frame() %>% 
+      mutate(across(.cols = everything(), .fns = ~ my_ifelse(as.numeric(.x) <  .01, "**", as.character(.x)))) %>% 
+      mutate(across(.cols = everything(), .fns = ~ my_ifelse(as.numeric(.x) <= .05 & !is.na(as.numeric(.x)), "*", .x))) %>% 
+      mutate(across(.cols = everything(), .fns = ~ my_ifelse(as.numeric(.x) >  .05 & !is.na(as.numeric(.x)), " ", .x))) %>% 
+      as.matrix()
+    
+    flagged.rs <- 
+      paste(rs, ps, sep = "") %>% 
+      matrix(nrow = nrow(rs), ncol = ncol(rs))
+    
+    rs[lower.tri(rs)] <- flagged.rs[lower.tri(flagged.rs)]
+  }
+  
+  if (sample_size) {
[…]

### 2021-06-27 manuscript/scripts/figure-2-3.R

@@ -1,0 +1,351 @@
+# Get bootstrapped medians ------------------------------------------------
+boot_medians <- 
+  boot_effects %>% 
+  filter((null_term == "main" & mod_term == "iv") | (null_term == "int" & mod_term == "iv:type_z")) %>% 
+  rename(term = mod_term) %>% 
+  group_by(spec_num, iv, dv, null_term) %>% 
+  summarize(
+    across(
+      starts_with("mod"), 
+      list(median = ~median(.x), lower = ~quantile(.x, probs = .025, names = F), upper = ~quantile(.x, probs = .975, names = F)),
+      .names = "{.col}_{.fn}")
+  ) %>%
+  group_by(iv, dv, null_term) %>% 
+  mutate(spec_rank = as.numeric(fct_reorder(as_factor(spec_num), mod_std_coefficient_median))) %>% 
+  select(iv, dv, null_term, contains("mod_std_coefficient"), spec_rank) %>% 
+  rename(
+    null_effect = mod_std_coefficient_median,
+    null_lower  = mod_std_coefficient_lower,
+    null_upper  = mod_std_coefficient_upper
+  ) %>% 
+  mutate(
+    iv_long = case_when(iv == "ses" ~ "SES",
+                        iv == "unp" ~ "Unpredictability",
+                        iv == "vio" ~ "Violence"),
+    dv_long = case_when(dv == "shifting" ~ "Attention-Shifting",
+                        dv == "updating" ~ "Working Memory Updating"),
+    term_long = case_when(null_term == "main" ~ "Main Effect",
+                          null_term == "int" ~ "Interaction")
+  ) %>% 
+  ungroup()
+
+# Merge primary effects with bootstrapped effects -------------------------
+primary_plots_data <- 
+  left_join(
+    primary_effects_data,
+    boot_medians %>% select(ends_with("long"), spec_rank, null_effect, null_lower, null_upper),
+    by = c("iv" = "iv_long", "dv" = "dv_long", "mod_term_group" = "term_long", "spec_rank" = "spec_rank")
+  ) %>% 
+  filter(mod_term_group %in% c("Covariate", "Task-Type", "Main Effect", "Interaction")) %>% 
+  ungroup() %>% 
+  mutate(
+    mod_term_unique = case_when(mod_term_unique == "Task Type" ~ "Task~Version",
+                                mod_term_unique == "Test Environment" ~ "Test~Environment",
[…]

### 2021-06-27 manuscript/scripts/rmd-staging.R

@@ -1,0 +1,363 @@
+# Packages ----------------------------------------------------------------
+library(tidyverse)
+library(cowplot)
+library(see)
+library(gt)
+library(psych)
+library(lme4)
+library(performance)
+
+# ggplot2 theme -----------------------------------------------------------
+theme_set(
+  theme_bw() +
+    theme(
+      axis.line.y       = element_line(),
+      axis.text.y       = element_text(size = rel(.75)),
+      axis.title.y      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
+      axis.ticks.y      = element_line(),
+      axis.line.x       = element_blank(),
+      axis.text.x       = element_blank(),
+      axis.ticks.x      = element_blank(),
+      axis.title.x      = element_blank(),
+      panel.border      = element_blank(), 
+      panel.spacing.y   = unit(0.5, "lines"),
+      plot.margin       = margin(.25,.25,.25,.25,"lines"),
+      plot.background   = element_rect(color = NA),
+      plot.title        = element_text(size = rel(.85), hjust = 0, margin = margin(0,0,.5,0, "lines")),
+      plot.subtitle     = element_blank(),
+      panel.grid        = element_line(color = NA),
+      strip.background  = element_blank(), 
+      strip.placement   = "outside",
+      strip.text        = element_text(size = rel(.85), angle = 0)
+    )
+)
+
+pval_colors <- c("pos-sig" = "#006D77", "non" = "gray70")
+my_alphas <- c(.5, 1)
+my_limits <- c(1,70)
+
+# Objects -----------------------------------------------------------------
+load("multiverse-objects/1-multiverse-datasets/datalist-agg-ivs.Rdata")
+load("data/data2_analysis.Rdata")
+load("multiverse-objects/2-primary-analyses/3-extracted-effects.Rdata")
+load("multiverse-objects/2-primary-analyses/5-bootstrapped-effects.Rdata")
+load("multiverse-objects/3-secondary-analyses/set-2/a1-extracted-effects.Rdata")
+load("multiverse-objects/3-secondary-analyses/set-1/a2-extracted-effects.Rdata")
+
+# Tables -----------------------------------------------------------------
[…]

### 2021-06-27 manuscript/scripts/table1.R

@@ -1,0 +1,106 @@
+table.01.0 <- 
+  data4_multiverse_base %>% 
+  select(matches("unp_"), starts_with("vio"), starts_with("ses_")) %>% 
+  mutate(across(matches("ses_(interview|school|agg)"), ~ .x * -1)) %>% 
+  mutate(ses_perceived = 6-ses_perceived) %>% 
+  corr_table(
+    numbered = T, 
+    stats = c("min","median","max","range","mean","sd"),
+    c.names = names(.) %>% str_replace("_"," ") %>% str_to_title() %>% str_replace("Ses","SES") %>% str_replace("Agg","Composite") %>% str_replace("Neighborhood","Neigh."),
+    change = T
+  ) %>% 
+  mutate(Variable = str_remove(Variable, "Unp |Vio |SES "))
+
+
+table.01.1 <- 
+  table.01.0 %>% 
+  mutate(across(.cols = 2:11, ~ifelse(str_detect(.x, "\\."), str_replace(.x, " ", "\\\\hspace\\{1 pt\\} "), .x))) %>% 
+  gt(groupname_col = "stat_group") %>% 
+  cols_label(Variable = " ") %>% 
+  tab_spanner(c("Unpredictability"), columns = 2:4) %>% 
+  tab_spanner(c("Violence"), columns = 5:7) %>% 
+  tab_spanner(c("Poverty"), columns = 8:11) %>% 
+  tab_style(
+    style     = cell_text(weight = "bold"),
+    locations = cells_body(columns = 2, rows = 2)
+  ) %>%
+  tab_style(
+    style     = cell_text(weight = "bold"),
+    locations = cells_body(columns = 2:3, rows = 3)
+  ) %>%
+  tab_style(
+    style     = cell_text(weight = "bold"),
+    locations = cells_body(columns = 5, rows = 5)
+  ) %>%
+  tab_style(
+    style     = cell_text(weight = "bold"),
+    locations = cells_body(columns = 5:6, rows = 6)
+  ) %>%
+  tab_style(
+    style     = cell_text(weight = "bold"),
+    locations = cells_body(columns = 8, rows = 8)
+  ) %>%
+  tab_style(
+    style     = cell_text(weight = "bold"),
+    locations = cells_body(columns = 8:9, rows = 9)
+  ) %>%
+  tab_style(
+    style     = cell_text(weight = "bold"),
+    locations = cells_body(columns = 8:10, rows = 10)
+  ) %>%
+  tab_options(
[…]

### 2021-06-27 manuscript/scripts/table2.R

@@ -1,0 +1,121 @@
+# Bootstrapped medians ----------------------------------------------------
+boot_medians <- 
+  boot_effects %>% 
+  filter((null_term == "main" & mod_term == "iv") | (null_term == "int" & mod_term == "iv:type_z")) %>% 
+  rename(term = mod_term) %>% 
+  mutate(
+    across(
+      .cols = c(mod_estimate, mod_std.error, mod_statistic, mod_std_coefficient, mod_ci, mod_ci_low, mod_ci_high),
+      .fns = ~ifelse(str_detect(iv,"ses"), .x * -1, .x)
+    )
+  ) %>%
+  group_by(boot_num, iv, dv, null_term) %>% 
+  summarize(median_null = median(mod_std_coefficient))
+
+# Primary Analysis Medians ------------------------------------------------
+primary_medians <- 
+  primary_effects_data %>% 
+  select(spec_number,iv,dv, mod_term_group, mod_std_coefficient, mod_ci_high, mod_ci_low, n, mod_p.value) %>% 
+  filter(mod_term_group %in% c("Main Effect","Interaction")) %>% 
+  group_by(iv, dv, mod_term_group) %>% 
+  mutate(p_percent = (sum(mod_p.value < .05)/n())) %>% 
+  summarize(across(where(is.numeric), median)) %>% 
+  rename(null_term = mod_term_group) %>% 
+  transmute(
+    iv          = case_when(iv == "Unpredictability" ~ "unp", iv == "Violence" ~ "vio", iv == "SES" ~ "ses"),
+    dv          = ifelse(dv == "Attention-Shifting","shifting","updating"),
+    null_term   = ifelse(null_term == "Main Effect", "main", "int"),
+    median_beta = mod_std_coefficient,
+    median_lo   = mod_ci_low,
+    median_hi   = mod_ci_high,
+    median_n    = n,
+    p_percent   = p_percent
+  )
+
+# Table - Base ------------------------------------------------------------
+table.02.0 <- 
+  left_join(boot_medians, primary_medians, by = c("iv","dv", "null_term")) %>% 
+  arrange(dv, iv, boot_num) %>% 
+  group_by(iv, dv, null_term) %>% 
+  mutate(
+    is_sig = if_else(median_beta < 0, median_null < median_beta, median_null > median_beta)
+  ) %>% 
+  summarize(
+    p_overall   = sum(is_sig)/n(),
[…]

### 2021-06-27 manuscript/scripts/table3.R

@@ -1,0 +1,80 @@
+# Simple Slope medians ----------------------------------------------------
+primary_simple_effects <- 
+  primary_simple_slopes %>% 
+  group_by(iv,dv,level) %>% 
+  mutate(p_percent = (sum(p_value < .05)/64)) %>% 
+  summarize(across(where(is.numeric), median)) %>% 
+  select(iv, dv, level, beta, p_percent) %>% 
+  mutate(
+    dv        = ifelse(dv == "Working Memory Updating","WM Updating", "Attention Shifting"),
+    adversity = case_when(iv == "SES" & level == "high" ~ "low",
+                          iv == "SES" & level == "low"  ~ "high",
+                          T ~ level),
+    #adversity = level,
+    beta      = ifelse(dv == "WM Updating", beta*100, beta),
+    beta      = ifelse(str_detect(iv, "SES") & !level %in% c("low","high"), beta*-1, beta),
+    beta      = formatC(round(beta,2), digits = 2, width = 3, flag = '0', format = 'f'),
+    p_percent = formatC(round(p_percent*100, 2), digits = 2, width = 3, flag = '0', format = 'f') %>% paste0(.,"%"),
+    iv        = ifelse(iv == "SES", "Poverty", iv)
+  ) %>% 
+  select(-level) %>% 
+  pivot_wider(names_from = adversity, values_from = c(beta, p_percent))
+
+# Table 2 - Simple Slopes -------------------------------------------------
+table.03.0 <- 
+  primary_simple_effects %>% 
+  select(
+    matches("(beta|p_percent)_abs"),
+    matches("(beta|p_percent)_eco"),
+    matches("(beta|p_percent)_low"),
+    matches("(beta|p_percent)_high")
+  )
+
+table.03.1 <- 
+  table.03.0 %>% 
+  gt(groupname_col = "dv") %>% 
+  cols_label(
+    iv             = "", 
+    beta_abs       = md("*b* (abs)"),
+    beta_eco       = md("*b* (eco)"),
+    beta_low       = md("*b* (low)"),
+    beta_high      = md("*b* (high)"),
+    p_percent_abs  = md("*p* (\\%)"),
+    p_percent_eco  = md("*p* (\\%)"),
+    p_percent_low  = md("*p* (\\%)"),
+    p_percent_high = md("*p* (\\%)")
+  ) %>% 
[…]

### 2021-06-27 scripts/1-data-prep/1-data-non-abritrary.R

@@ -1,0 +1,156 @@
+# Setup -------------------------------------------------------------------
+
+# Libraries
+library(tidyverse)
+library(sjlabelled)
+
+# my functions
+source("scripts/0-functions/create_codebook.R")
+
+# Data
+load("data/data1_raw.Rdata")
+
+# Non-arbitrary decisions -------------------------------------------------
+data2_non_arbitrary <- 
+  data1_raw %>% 
+  # Only completed task data
+  filter(
+    !(is.na(abs_updating) & is.na(eco_updating)),
+    !(is.na(abs_shifting_sc) & is.na(eco_shifting_sc)),
+  ) %>% 
+  # No interviewer coded impairments
+  filter(
+    non_arb_impaired == 0, 
+    non_arb_impaired_assent == 0 | is.na(non_arb_impaired_assent)
+  ) %>% 
+  # Only allow 1 missed attention check or all high/low responses to scales with reverse coded items
+  filter(
+    non_arb_attention_check <= 1 | is.na(non_arb_attention_check), 
+    non_arb_q_responses < 2 | is.na(non_arb_q_responses)
+  ) %>%
+  # No extreme distractions during the cognitive tasks
+  filter(non_arb_distractions < 2) %>%
+  # No participants receiving more than 60 minutes of Special Education per day
+  filter(non_arb_sped_60min != 1 | is.na(arb_sped)) %>% 
+  # Deal with siblings
+  mutate(
+    siblings = ifelse(siblings %in% c("wjms_sibling_000","bgc_sibling_000"),"sibling_000", siblings)
+  ) %>% 
+  # Put anyone who no longer has a sibling because of above steps into giant group
+  group_by(siblings) %>% 
+  mutate(siblings_n = n()) %>% 
+  ungroup() %>% 
+  mutate(siblings_id = ifelse(siblings_n == 1, "sibling_000", siblings)) %>% 
+  group_by(siblings_id) %>% 
+  # Count number of siblings each person has
+  mutate(siblings_n = n()) %>% 
+  ungroup() %>% 
+  select(-siblings) %>% 
+  var_labels(
+    siblings_id = "Sibling ID",
+    siblings_n  = "The number of siblings each participant has who also participated in this study "
+  )
+
+# Create Overall Composites -----------------------------------------------
+data3_composites <- 
+  data2_non_arbitrary %>% 
+  # Create overall IV composites
+  mutate(
+    unp_interview   = rowMeans(scale(across(.cols = starts_with("unp_interview"))), na.rm = T),
[…]

### 2021-06-27 scripts/1-data-prep/3-secondary-multiverse-datasets.R

@@ -1,0 +1,151 @@
+# Setup -------------------------------------------------------------------
+
+# Libraries
+library(tidyverse)
+library(tidymodels)
+
+# Data
+load("data/data2_analysis.Rdata")
+
+# Specification Grid -----------------------------------------------------------
+## Create a grid of all possible combinations of arbitrary data processing decisions
+## First, `expand_grid` creates all possible combinations from arbitrary variables
+## There are 6 variables each with two alternatives
+## For our expanded multiverse, we are adding IV subcomponent to our grid
+### 2*2*2*2*2*2 = 64 unique specifications
+### 64 * 3 = 192 specs for unpredictability
+### 64 * 3 = 192 specs for violence
+### 64 * 4 = 256 specs for SES
+### We'll keep them all in one data list of 192+192+256 = 640 datasest
+spec_grid <- 
+  expand_grid(
+    iv              = c(0:9),
+    sub_sample      = c(0,1),
+    distractions    = c(0,1),
+    attention_check = c(0,1),
+    sped            = c(0,1),
+    csd             = c(0,1),
+    shifting        = c(0,1)
+  ) %>% 
+  rownames_to_column("spec_number") %>% 
+  mutate(spec_number = as.numeric(spec_number)) %>% 
+  pivot_longer(!spec_number, names_to = "spec_var", values_to = "spec_value") %>% 
+  left_join(
+    tribble(
+      ~spec_var,         ~spec_value, ~spec_expr,                                              ~name,
+      "sub_sample",      0,           "arb_sample %in% c('wjms','bgc')",                       "Both Samples",
+      "sub_sample",      1,           "arb_sample == 'wjms'",                                  "Middle School Only",
+      "distractions",    0,           "arb_distractions %in% c(1,0)",                          "Minor Distract. Included",
+      "distractions",    1,           "arb_distractions == 0",                                 "Minor Distract. Excluded",
+      "attention_check", 0,           "arb_attention_check <= 1 | is.na(arb_attention_check)", "1 >= missed",
+      "attention_check", 1,           "arb_attention_check == 0 | is.na(arb_attention_check)", "None missed",
+      "sped",            0,           "arb_sped %in% c(1,0) | is.na(arb_sped)",                "Sp.Ed. Included",
+      "sped",            1,           "arb_sped == 0 | is.na(arb_sped)",                       "Sp.Ed. Excluded",
+      "csd",             0,           "0",                                                     "Not Included",
[…]

### 2021-06-27 scripts/2-primary-analyses/1-confirmatory.R

@@ -1,0 +1,209 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+library(lmerTest)
+library(broom.mixed)
+library(tidymodels)
+library(ggeffects)
+library(interactions)
+library(effectsize)
+
+# Data
+load("multiverse-objects/1-multiverse-datasets/datalist-agg-ivs.Rdata")
+
+# Unpredictability and Shifting -------------------------------------------
+confirm_unp_shifting <- 
+  multi_data_list %>% 
+  map(function(x){
+    
+    spec_number <- unique(x$specifications$spec_number)
+    
+    # Filter data according to task
+    data <- x$data_analysis %>% filter(task == "shifting")
+    
+    # Run mixed model
+    mod <- lmer(score ~ unp_agg_z*type_z + age + test_envr + (1|id), data = data)
+    
+    # Create tidied results data.frame
+    mod_tidy <-
+      mod %>% 
+      tidy() %>% 
+      rename_all(~paste0("mod_",.))
+    
+    # Create a tidy standardized coefficients data.frame
+    mod_standardized <- standardize_parameters(mod)
+    
+    # Create a data.frame with predicted effects at high and low predictor value for each task type
+    mod_effects <- ggpredict(mod, terms = c("unp_agg_z [-1,1]", "type_z [-1,1]"))
+    ss_task <- sim_slopes(mod, pred = "unp_agg_z", modx = "type_z", modx.values = c(-1,1))
+    ss_unp  <- sim_slopes(mod, pred = "type_z", modx = "unp_agg_z", modx.values = c(-1,1))
+    
+    results <- 
+      list(
+        n                 = x$n,
+        n_model           = nrow(mod@frame),
+        n_model_obs       = mod@frame %>% distinct(id) %>% nrow,
+        data_raw          = x$data_raw,
+        data_analysis     = data,
+        data_model        = mod@frame,
+        specifications    = x$specifications,
+        model             = mod,
+        model_tidy        = mod_tidy,
+        model_std_effects = mod_standardized,
+        model_effects     = mod_effects,
+        simple_slopes     = list(task = ss_task, unp = ss_unp)
+      )
+    
+    message("dataset ", spec_number, " analyzed")
+    results
+  })
+
+# Unpredictability and Updating -------------------------------------------
+confirm_unp_updating <- 
+  multi_data_list %>% 
+  map(function(x){
+    
[…]

### 2021-06-27 scripts/2-primary-analyses/2-exploratory.R

@@ -1,0 +1,114 @@
+# Setup -------------------------------------------------------------------
+
+# Libraries
+library(tidyverse)
+library(lmerTest)
+library(broom.mixed)
+library(tidymodels)
+library(ggeffects)
+library(interactions)
+library(effectsize)
+
+# Data
+load("multiverse-objects/1-multiverse-datasets/datalist-agg-ivs.Rdata")
+
+# SES and Shifting ---------------------------------------------------
+explore_ses_shifting <- 
+  multi_data_list %>% 
+  map(function(x){
+    
+    spec_number <- unique(x$specifications$spec_number)
+    
+    # Filter data according to task
+    data <- x$data_analysis %>% filter(task == "shifting")
+    
+    # Run mixed model
+    mod <- lmer(score ~ ses_agg_z*type_z + age + test_envr + (1|id), data = data)
+    
+    # Create tidied results data.frame
+    mod_tidy <-
+      mod %>% 
+      tidy() %>% 
+      rename_all(~paste0("mod_",.))
+    
+    # Create a tidy standardized coefficients data.frame
+    mod_standardized <- standardize_parameters(mod)
+    
+    # Create a data.frame with predicted effects at high and low predictor value for each task type
+    mod_effects <- ggpredict(mod, terms = c("ses_agg_z [-1,1]", "type_z [-1,1]"))
+    ss_task <- sim_slopes(mod, pred = "ses_agg_z", modx = "type_z", modx.values = c(-1,1))
+    ss_ses  <- sim_slopes(mod, pred = "type_z", modx = "ses_agg_z", modx.values = c(-1,1))
+    
+    results <- 
+      list(
+        n                 = x$n,
+        n_model           = nrow(mod@frame),
+        n_model_obs       = mod@frame %>% distinct(id) %>% nrow,
+        data_raw          = x$data_raw,
+        data_analysis     = data,
+        data_model        = mod@frame,
+        specifications    = x$specifications,
+        model             = mod,
+        model_tidy        = mod_tidy,
+        model_std_effects = mod_standardized,
+        model_effects     = mod_effects,
+        simple_slopes     = list(task = ss_task, ses = ss_ses)
+      )
+    
+    message("dataset ", spec_number, " analyzed")
+    results
+  })
+
+# SES and Updating ---------------------------------------------------
+explore_ses_updating <- 
+  multi_data_list %>% 
+  map(function(x){
+    
[…]

### 2021-06-27 scripts/2-primary-analyses/3-extract-effects.R

@@ -1,0 +1,173 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+
+# Load results
+load("multiverse-objects/2-primary-analyses/1-confirmatory-results.Rdata")
+load("multiverse-objects/2-primary-analyses/2-exploratory-results.Rdata")
+
+# Results prep ----------------------------------------------------------
+primary_pmap <-
+  list(
+    ls() %>% str_subset("^confirm|^explore") %>% map(function(x) eval(as.symbol(x))),
+    c(rep("Unpredictability",2), rep("Violence",2), rep("SES",2)),
+    c(rep(c("Attention-Shifting", "Working Memory Updating"),3)),
+    c(rep("Confirmatory",4), rep("Exploratory", 2))
+  )
+
+# Raw effect size data ----------------------------------------------------
+primary_effects_data <- 
+  primary_pmap %>% 
+  pmap_df(function(multiverse, iv, dv, hypoth){
+    
+    # All parameters from multiverse
+    params <-
+      multiverse %>% 
+      map_df(function(x){ 
+        bind_cols(
+          n = x$n_model_obs,
+          left_join(
+            x$model_tidy %>% select(mod_term:mod_p.value), 
+            x$model_std_effects %>% rename_with(~paste0("mod_",.x)), 
+            by = c("mod_term" = "mod_Parameter")
+          ),
+          x$specifications %>% 
+            select(-spec_expr) %>% 
+            pivot_wider(names_from = "spec_var", values_from = "name") %>% 
+            rename_with(.cols = !spec_number, ~paste0("spec_",.x))
+        ) 
+      }) %>% 
+      rename_with(tolower) %>% 
+      filter(!str_detect(mod_term, "^sd__")) %>% 
+<<<<<<< HEAD
+      mutate(
+        # Do this to reverse code SES to match low SES to High poverty
+        across(
+          .cols = c(mod_estimate, mod_std.error, mod_statistic, mod_std_coefficient, mod_ci, mod_ci_low, mod_ci_high),
+          .fns = ~ifelse(str_detect(mod_term,"ses"), .x * -1, .x)
+        )
+      ) %>% 
+=======
+>>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
+      group_by(mod_term) %>% 
+      mutate(
+        spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),
[…]

### 2021-06-27 scripts/2-primary-analyses/4-bootstrap-setup.R

@@ -1,0 +1,142 @@
+# Setup -------------------------------------------------------------------
+library(tidyverse)
+library(lmerTest)
+library(broom.mixed)
+library(tidymodels)
+library(ggeffects)
+library(interactions)
+library(effectsize)
+
+# Multiverse data-list for primary analyses
+load("multiverse-objects/1-multiverse-datasets/datalist-agg-ivs.Rdata")
+
+# Coefficients from primary analyses
+load("multiverse-objects/2-primary-analyses/3-extracted-effects.Rdata")
+
+# Set seed for reproducibility
+set.seed(1234)
+
+# Create null data --------------------------------------------------------
+# Create K 'null' dvs, in my case 64
+## 1. Get coefficients from original multiverse
+## 2. Subtract coefficients from original dv, this creates K null dvs
+## 3. Compile a null dataset with all K outcomes
+
+# 1. All Unstandardized Effects -------------------------------------------
+boot_effects <- 
+  primary_effects_data %>% 
+  filter(str_detect(mod_term, "_z")) %>% 
+  select(iv, dv, spec_number,mod_term_group, mod_estimate) %>% 
+  pivot_wider(names_from = "mod_term_group",values_from = "mod_estimate") %>% 
+  mutate(iv = iv %>% str_to_lower() %>% str_replace("unpredictability","unp")) %>% 
+  rename(main_iv = `Main Effect`, main_type = `Task-Type`, int = Interaction) %>% 
+  arrange(spec_number,iv,dv)
+
+
+# 2. Giant null dataset ---------------------------------------------------
+## Input: 
+### - specification index (1:64)
+### - boot_effects, unstandardized effects from each spec index per iv-dv combination
+### - original data
+## Output:
+### - original data with null dvs per iv-dv-specification combination, in long form (data are row-binded per specification)
+boot1_null <- 
+  seq_along(multi_data_list) %>% 
+  map_df(function(x){
+    
+    # Unstandardized coefficients from shifting analyses
+    shifting <- 
+      boot_effects %>%
+      filter(spec_number == x, dv == "Attention-Shifting") %>% 
+      split(.$iv) %>% 
+      map(function(x){
+        x %>% select(main_iv, int) %>% as_vector()
+      })
+    
+    # Unstandardized coefficients from updating analyses
+    updating <- 
+      boot_effects %>%
+      filter(spec_number == x, dv == "Working Memory Updating") %>% 
[…]

### 2021-06-27 scripts/2-primary-analyses/5-bootstrap-spec-analysis.R

@@ -1,0 +1,256 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+library(lmerTest)
+library(broom.mixed)
+library(tidymodels)
+library(ggeffects)
+library(interactions)
+library(effectsize)
+
+# Data
+load("multiverse-objects/1-multiverse-datasets/datalist-agg-ivs.Rdata")
+load("multiverse-objects/2-primary-analyses/4-bootstrapped-data.Rdata")
+
+# Bootstrap Specifications Description ------------------------------------------------
+## Conduct specification analyses over 500 null datasets
+## The result should be 64 effect sizes * 500 null data sets
+## This will be done for each iv and dv combination
+## It will also be done for main effects of iv and interactions
+## For example, take Unpredictability. We Should have:
+## 500 bootstraps * 64 specifications * 2 DVs categories * 2 types of null effects
+
+# Bootstrap Loop -----------------------------------
+## The technique will be carried out in following steps:
+### 1 Iterate over 500 bootstrapped samples
+### 2 Do original specification analyses per bootstrap sample
+#### 2a Set up specifications
+#### 2b Create data
+#### 2c Create analysis data
+#### 2d Do specification analyses
+### 3 Save effect sizes 
+boot_effects <- 
+  map2_df(
+    boot_data_list,
+    seq_along(boot_data_list),
+    function(boot_data, boot_index){
+      
+      # 1 Iterate over bootstrap data sets ---------------
+      ## Tell user the current bootstrap dataset
+      ## Create a list of specifications and break them up per specification index
+      message("Starting specificaiton analysis for bootstrapped dataset ", boot_index)
+      spec_list <- split(spec_grid, spec_grid$spec_number)
+      
+      # 2 run specification analysis per bootstrap ---------------
+      # Loop through specifications to create data and run analysis
+      ## The loop takes two inputs: spec_list and an index
+      ### 1. `spec_list` is the list of all specifications from above
+      ### 2. `seq_along(spec_list)` generates a numeric vector from 1:64
+      ## This produces one output: a data.frame of the relevant effect sizes
+      spec_results <- map2_df(
+        spec_list,
+        seq_along(spec_list), 
+        function(boot_specs, boot_spec_number){
+          ## 2a meta info for specifications -----------------------------------------
+          ### tell user which specification we are starting
+          ### create data based on specifications
+          ### Determine if residulizing will occur
+          message("    bootstrap sample: ", boot_index, ", specification: ", boot_spec_number, " -- start")
+          
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-1/a1-analysis-ses-vio.R

@@ -1,0 +1,70 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+library(lmerTest)
+library(broom.mixed)
+library(tidymodels)
+library(ggeffects)
+library(interactions)
+library(effectsize)
+
+# Data
+load("multiverse-objects/1-multiverse-datasets/datalist-agg-ivs.Rdata")
+
+# Compare SES & Violence on Updating --------------------------------------
+secondary1a_ses_vio_updating <- 
+  multi_data_list %>% 
+  map(function(x){
+    
+    spec_number <- unique(x$specifications$spec_number)
+    
+    # Filter data according to task
+    data <- x$data_analysis %>% filter(task == "updating")
+    
+    # Run mixed model
+    mod <- lmer(score ~ ses_agg_z*type_z + vio_agg_z*type_z + age + test_envr + (1|id) + (1|siblings_id), data = data)
+    
+    # Create tidied results data.frame
+    mod_tidy <-
+      mod %>% 
+      tidy() %>% 
+      rename_all(~paste0("mod_",.))
+    
+    # Create a tidy standardized coefficients data.frame
+    mod_standardized <- standardize_parameters(mod)
+    
+    # Create a data.frame with predicted effects at high and low predictor value for each task type
+    mod_effects1 <- ggpredict(mod, terms = c("ses_agg_z [-1,1]", "type_z [-1,1]"))
+    mod_effects2 <- ggpredict(mod, terms = c("vio_agg_z [-1,1]", "type_z [-1,1]"))
+    ss1_task <- sim_slopes(mod, pred = "ses_agg_z", modx = "type_z", modx.values = c(-1,1))
+    ss1_ses  <- sim_slopes(mod, pred = "type_z", modx = "ses_agg_z", modx.values = c(-1,1))
+    ss2_task <- sim_slopes(mod, pred = "vio_agg_z", modx = "type_z", modx.values = c(-1,1))
+    ss2_vio  <- sim_slopes(mod, pred = "type_z", modx = "vio_agg_z", modx.values = c(-1,1))
+    
+    results <- 
+      list(
+        n                 = x$n,
+        n_model           = nrow(mod@frame),
+        n_model_obs       = mod@frame %>% distinct(id) %>% nrow,
+        data_raw          = x$data_raw,
+        data_analysis     = data,
+        data_model        = mod@frame,
+        specifications    = x$specifications,
+        model             = mod,
+        model_tidy        = mod_tidy,
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-1/a2-extract-effects.R

@@ -1,0 +1,139 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+
+# Load effect data.frames -------------------------------------------------
+load("multiverse-objects/3-secondary-analyses/set-1/a1-results-ses-vio.Rdata")
+
+# Extract Parameters ------------------------------------------------------
+secondary1a_effects_data <-
+  map_df(secondary1a_ses_vio_updating, function(x){ 
+    bind_cols(
+      n = x$n_model_obs,
+      left_join(
+        x$model_tidy %>% select(mod_term:mod_p.value), 
+        x$model_std_effects %>% rename_with(~paste0("mod_",.x)), 
+        by = c("mod_term" = "mod_Parameter")
+      ),
+      x$specifications %>% 
+        select(-spec_expr) %>% 
+        pivot_wider(names_from = "spec_var", values_from = "name") %>% 
+        rename_with(.cols = !spec_number, ~paste0("spec_",.x))
+    )
+  }) %>% 
+  rename_with(tolower) %>% 
+  filter(!str_detect(mod_term, "^sd__")) %>% 
+<<<<<<< HEAD
+  mutate(
+    # Do this to reverse code SES to match low SES to High poverty
+    across(
+      .cols = c(mod_estimate, mod_std.error, mod_statistic, mod_std_coefficient, mod_ci, mod_ci_low, mod_ci_high),
+      .fns = ~ifelse(str_detect(mod_term,"ses"), .x * -1, .x)
+    )
+  ) %>% 
+=======
+>>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
+  group_by(mod_term) %>% 
+  mutate(
+    spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),
+    median_dbl = median(mod_std_coefficient),
+    median_chr = median_dbl %>% round(2) %>% as.character,
+    pval_prop  = (sum(mod_p.value < .05)/64) * 100
+  ) %>% 
+  ungroup() %>% 
+  mutate(
+    mod_sig        = case_when(mod_p.value <  .05 & mod_std_coefficient > 0 ~ "pos-sig",
+                               mod_p.value <  .05 & mod_std_coefficient < 0 ~ "neg-sig",
+                               mod_p.value >= .05 ~ "non"),
+    mod_term_num   = case_when(str_detect(mod_term, "Intercept") ~ -1,
+                               mod_term == "age"          ~ 0,
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-1/a3-create-plots.R

@@ -1,0 +1,285 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+library(cowplot)
+
+# Load Data ---------------------------------------------------------------
+load("multiverse-objects/3-secondary-analyses/set-1/a2-extracted-effects.Rdata")
+
+# ggplot2 theme -----------------------------------------------------------
+theme_set(
+  theme_bw() +
+    theme(
+      axis.line.x       = element_line(),
+      axis.text.x       = element_text(size = rel(.75)),
+      axis.title.x      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
+      axis.ticks.x      = element_line(),
+      axis.line.y       = element_blank(),
+      axis.text.y       = element_blank(),
+      axis.ticks.y      = element_blank(),
+      axis.title.y      = element_blank(),
+      panel.border      = element_blank(), 
+      panel.spacing.y   = unit(.5, "lines"),
+      plot.margin       = margin(2,.25,.25,.25,"lines"),
+      plot.background   = element_rect(color = NA),
+      plot.title        = element_text(size = rel(.9), hjust = .5),
+      plot.subtitle     = element_blank(),
+      panel.grid        = element_line(color = NA),
+      strip.background  = element_blank(), 
+      strip.placement   = "outside",
+      strip.text        = element_text(size = rel(.85), angle = 0)
+    )
+)
+
+pval_colors <- c("pos-sig" = "#FF7F00", "neg-sig" = "#1F78B4", "non" = "gray")
+my_limits <- c(1,70)
+
+# Spec Curve --------------------------------------------------------------
+spec_curves <- 
+  map(c("Main Effect","Interaction"), function(x){
+    
+    effs <- 
+      secondary1a_effects_data %>% 
+      filter(mod_term_group == x) %>% 
+      mutate(iv = ifelse(str_detect(mod_term,"vio"),"Violence","SES"))
+    
+    medians <- 
+      secondary1a_effects_medians %>% 
+      filter(mod_term_group == x) %>% 
+      mutate(iv = ifelse(str_detect(mod_term,"vio"),"Violence","SES"))
+    
+    eff_curve <- 
+      effs %>% 
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-1/b1-analysis-ses-components.R

@@ -1,0 +1,165 @@
+# Setup -------------------------------------------------------------------
+
+# Libraries
+library(tidyverse)
+library(lmerTest)
+library(broom.mixed)
+library(tidymodels)
+library(ggeffects)
+library(interactions)
+library(effectsize)
+
+# Data
+load("multiverse-objects/1-multiverse-datasets/datalist-agg-ivs.Rdata")
+
+# Perceived SES & Updating ------------------------------------------------
+secondary1b_ses_perceived <- 
+  multi_data_list %>% 
+  map(function(x){
+    
+    spec_number <- unique(x$specifications$spec_number)
+    
+    # Filter data according to task
+    data <- x$data_analysis %>% filter(task == "updating")
+    
+    # Run mixed model
+    mod <- lmer(score ~ ses_perceived_z*type_z + age + test_envr + (1|id) + (1|siblings_id), data = data)
+    
+    # Create tidied results data.frame
+    mod_tidy <-
+      mod %>% 
+      tidy() %>% 
+      rename_all(~paste0("mod_",.))
+    
+    # Create a tidy standardized coefficients data.frame
+    mod_standardized <- standardize_parameters(mod)
+    
+    # Create a data.frame with predicted effects at high and low predictor value for each task type
+    mod_effects <- ggpredict(mod, terms = c("ses_perceived_z [-1,1]", "type_z [-1,1]"))
+    ss_task <- sim_slopes(mod, pred = "ses_perceived_z", modx = "type_z", modx.values = c(-1,1))
+    ss_ses  <- sim_slopes(mod, pred = "type_z", modx = "ses_perceived_z", modx.values = c(-1,1))
+    
+    results <- 
+      list(
+        n                 = x$n,
+        n_model           = nrow(mod@frame),
+        n_model_obs       = mod@frame %>% distinct(id) %>% nrow,
+        data_raw          = x$data_raw,
+        data_analysis     = data,
+        data_model        = mod@frame,
+        specifications    = x$specifications,
+        model             = mod,
+        model_tidy        = mod_tidy,
+        model_std_effects = mod_standardized,
+        model_effects     = mod_effects,
+        simple_slopes     = list(task = ss_task, ses = ss_ses)
+      )
+    
+    message("dataset ", spec_number, " analyzed")
+    results
+  })
+
+# Parent education/occupation & Updating ----------------------------------
+secondary1b_ses_interview <- 
+  multi_data_list %>% 
+  map(function(x){
+    
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-1/b2-extract-effects.R

@@ -1,0 +1,115 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+
+# Load results
+load("multiverse-objects/3-secondary-analyses/set-1/b1-results-ses-components.Rdata")
+
+# Results prep ----------------------------------------------------------
+secondary1b_pmap <-
+  list(
+    ls() %>% str_subset("^secondary1b_") %>% map(function(x) eval(as.symbol(x))),
+    c("Parent SES", "Perceived SES", "School SES"),
+    rep("Working Memory Updating",3)
+  )
+
+# Raw effect size data ----------------------------------------------------
+secondary1b_effects_data <- 
+  secondary1b_pmap %>% 
+  pmap_df(function(multiverse, iv, dv){
+    
+    # All parameters from multiverse
+    params <-
+      multiverse %>% 
+      map_df(function(x){ 
+        bind_cols(
+          n = x$n_model_obs,
+          left_join(
+            x$model_tidy %>% select(mod_term:mod_p.value), 
+            x$model_std_effects %>% rename_with(~paste0("mod_",.x)), 
+            by = c("mod_term" = "mod_Parameter")
+          ),
+          x$specifications %>% 
+            select(-spec_expr) %>% 
+            pivot_wider(names_from = "spec_var", values_from = "name") %>% 
+            rename_with(.cols = !spec_number, ~paste0("spec_",.x))
+        )
+      }) %>% 
+      rename_with(tolower) %>% 
+      filter(!str_detect(mod_term, "^sd__")) %>% 
+      group_by(mod_term) %>% 
+      mutate(
+        spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),
+        median_dbl = median(mod_std_coefficient),
+        median_chr = median_dbl %>% round(2) %>% as.character,
+        pval_prop  = (sum(mod_p.value < .05)/64) * 100
+      ) %>% 
+      ungroup() %>% 
+      mutate(
+        mod_sig        = case_when(mod_p.value <  .05 & mod_std_coefficient > 0 ~ "pos-sig",
+                                   mod_p.value <  .05 & mod_std_coefficient < 0 ~ "neg-sig",
+                                   mod_p.value >= .05 ~ "non"),
+        mod_term_num   = case_when(str_detect(mod_term, "Intercept") ~ -1,
+                                   mod_term == "age"          ~ 0,
+                                   mod_term == "test_envr"    ~ 0,
+                                   mod_term == "type_z"       ~ 1,
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-1/b3-create-plots.R

@@ -1,0 +1,285 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+library(cowplot)
+
+# Load effect data.frames -------------------------------------------------
+load("multiverse-objects/3-secondary-analyses/set-1/b2-extracted-effects.Rdata")
+
+# ggplot2 theme -----------------------------------------------------------
+theme_set(
+  theme_bw() +
+    theme(
+      axis.line.x       = element_line(),
+      axis.text.x       = element_text(size = rel(.75)),
+      axis.title.x      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
+      axis.ticks.x      = element_line(),
+      axis.line.y       = element_blank(),
+      axis.text.y       = element_blank(),
+      axis.ticks.y      = element_blank(),
+      axis.title.y      = element_blank(),
+      panel.border      = element_blank(), 
+      panel.spacing.y   = unit(.5, "lines"),
+      plot.margin       = margin(2,.25,.25,.25,"lines"),
+      plot.background   = element_rect(color = NA),
+      plot.title        = element_text(size = rel(.9), hjust = .5),
+      plot.subtitle     = element_blank(),
+      panel.grid        = element_line(color = NA),
+      strip.background  = element_blank(), 
+      strip.placement   = "outside",
+      strip.text        = element_text(size = rel(.85), angle = 0)
+    )
+)
+
+pval_colors <- c("pos-sig" = "#FF7F00", "neg-sig" = "#1F78B4", "non" = "gray")
+my_limits <- c(1,70)
+
+# specification curve -----------------------------------------------------
+spec_curves <- 
+  map(c("Working Memory Updating"), function(x){
+    map(c("Main Effect","Interaction"), function(y){
+      
+      effs <- 
+        secondary1b_effects_data %>% 
+        filter(dv == x, mod_term_group == y)
+      
+      medians <- 
+        secondary1b_effects_data %>% 
+        filter(dv == x, mod_term_group == y)
+      
+      eff_curve <- 
+        effs %>% 
+        ggplot(aes(x = mod_std_coefficient, y = spec_rank, color = mod_sig)) +
+        geom_ribbon(
+          aes(xmin = mod_ci_low, xmax = mod_ci_high, y = spec_rank),
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-2/a2-extract-effects.R

@@ -1,0 +1,143 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+
+# Load results
+load("multiverse-objects/3-secondary-analyses/set-2/a1-results-expanded-shifting.Rdata")
+load("multiverse-objects/3-secondary-analyses/set-2/a1-results-expanded-updating.Rdata")
+
+# Results prep ----------------------------------------------------------
+secondary_pmap <-
+  list(
+    ls() %>% str_subset("^secondary_expanded") %>% map(function(x) eval(as.symbol(x))),
+    c("Attention-Shifting", "Working Memory Updating")
+  )
+
+# Raw effect size data ----------------------------------------------------
+secondary_set2_effects <- 
+  secondary_pmap %>% 
+  pmap_df(function(multiverse, dv){
+    # All parameters from multiverse
+    params <-
+      multiverse %>% 
+      map_df(function(x){ 
+        bind_cols(
+          iv = x$iv,
+          dv = dv,
+          n = x$n_model_obs,
+          left_join(
+            x$model_tidy %>% select(mod_term:mod_p.value), 
+            x$model_std_effects %>% rename_with(~paste0("mod_",.x)), 
+            by = c("mod_term" = "mod_Parameter")
+          ),
+          x$specifications %>% 
+            select(-spec_expr) %>% 
+            pivot_wider(names_from = "spec_var", values_from = "name") %>% 
+            rename_with(.cols = !spec_number, ~paste0("spec_",.x))
+        ) 
+      }) %>% 
+      rename_with(tolower) %>% 
+<<<<<<< HEAD
+      filter(!str_detect(mod_term, "^sd__")) %>% 
+      mutate(
+        # Do this to reverse code SES to match low SES to High poverty
+        across(
+          .cols = c(mod_estimate, mod_std.error, mod_statistic, mod_std_coefficient, mod_ci, mod_ci_low, mod_ci_high),
+          .fns = ~ifelse(str_detect(iv,"ses"), .x * -1, .x)
+        )
+      )
+=======
+      filter(!str_detect(mod_term, "^sd__"))
+>>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
+  })
+
+secondary_set2_effects_clean <- 
+  secondary_set2_effects %>% 
+  mutate(
+    iv_group = case_when(str_detect(iv, "^ses") ~ "SES",
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-2/a3-create-plots.R

@@ -1,0 +1,583 @@
+# Setup -------------------------------------------------------------------
+# Libraries
+library(tidyverse)
+library(cowplot)
+
+# Load effect data.frames -------------------------------------------------
+load("multiverse-objects/3-secondary-analyses/set-2/a1-extracted-effects.Rdata")
+
+# ggplot2 theme -----------------------------------------------------------
+theme_set(
+  theme_bw() +
+    theme(
+      axis.line.x       = element_line(),
+      axis.text.x       = element_text(size = rel(.75)),
+      axis.title.x      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
+      axis.ticks.x      = element_line(),
+      axis.line.y       = element_blank(),
+      axis.text.y       = element_blank(),
+      axis.ticks.y      = element_blank(),
+      axis.title.y      = element_blank(),
+      panel.border      = element_blank(), 
+      panel.spacing.y   = unit(.5, "lines"),
+      plot.margin       = margin(2,.25,.25,.25,"lines"),
+      plot.background   = element_rect(color = NA),
+      plot.title        = element_text(size = rel(.9), hjust = 0.5),
+      plot.subtitle     = element_blank(),
+      panel.grid        = element_line(color = NA),
+      strip.background  = element_blank(), 
+      strip.placement   = "outside",
+      strip.text        = element_text(size = rel(.85), angle = 0)
+    )
+)
+
+pval_colors <- c("pos-sig" = "#FF7F00", "neg-sig" = "#1F78B4", "non" = "gray")
+my_limits <- c(1,70)
+
+
+# Plotting Data -----------------------------------------------------------
+secondary_set2_plots_data <- 
+  secondary_set2_effects_clean %>% 
+  mutate(
+    mod_term_group = case_when(str_detect(mod_term, "^iv$") ~ "Main Effect",
+                               str_detect(mod_term, ":")    ~ "Interaction"),
+    iv             = factor(iv, 
+                            levels = c("unp_agg", "unp_interview","unp_perceived",
+                                       "vio_agg", "vio_neighborhood","vio_fighting",
+                                       "ses_agg", "ses_perceived","ses_school","ses_interview"),
[…]

### 2021-06-27 supplement/scripts/1-covariates.R

@@ -1,0 +1,259 @@
+# Effects Data -----------------------------------------------------------
+primary_plots_data <- 
+  primary_effects_data %>% 
+  filter(mod_term_group %in% c("Covariate","Task-Type","Main Effect", "Interaction")) %>% 
+  ungroup() %>% 
+  mutate(
+    mod_term_unique = case_when(mod_term_unique == "Task Type" ~ "Task~Version",
+                                mod_term_unique == "Test Environment" ~ "Test~Environment",
+                                str_detect(mod_term_unique,"symbol") ~ str_replace(mod_term_unique,"Task-Version","Task~Version"),
+                                T ~ mod_term_unique),
+    mod_term_num   = case_when(str_detect(mod_term_unique, "Unp~sym") ~ 4,
+                               str_detect(mod_term_unique, "Vio~sym") ~ 5,
+                               str_detect(mod_term_unique, "SES~sym") ~ 6,
+                               T ~ mod_term_num),
+    mod_term_label = fct_reorder(mod_term_unique, mod_term_num)
+  )
+
+# Making Specification Curves -----------------------------------------------------------
+spec_curves1 <- 
+  map(c("Attention-Shifting","Working Memory Updating"), function(x){
+    
+    # Setup
+    dv_which <- x
+    
+    map(c("Unpredictability","Violence","SES"), function(y){
+      
+      effs <- 
+        primary_plots_data %>% 
+        filter(dv == x, iv == y) %>% 
+        mutate(
+          hypoth = factor(hypoth, c("Exploratory", "Confirmatory")),
+          mod_sig = ifelse(mod_sig != "non", "pos-sig", mod_sig)
+        )
+      
+      medians <- 
+        primary_plots_data %>% 
+        filter(dv == x, iv == y) %>% 
+        mutate(
+          hypoth = factor(hypoth, c("Exploratory", "Confirmatory")),
+          mod_sig = ifelse(mod_sig != "non", "pos-sig", mod_sig)
+        )
+      
+      spec_grid_data <- 
+        effs %>% 
+        select(mod_term_label, dv, hypoth, starts_with("spec"), mod_p.value, mod_sig) %>% 
+        mutate(mod_sig = ifelse(mod_sig != "non", "pos-sig", mod_sig)) %>% 
[…]

### 2021-06-27 supplement/scripts/2-secondary1.R

@@ -1,0 +1,366 @@
+# Analysis effect sizes ---------------------------------------------------
+secondary1b_plots_data <- 
+  secondary_set2_effects_clean %>% 
+  mutate(
+    mod_term_group = case_when(str_detect(mod_term, "^iv$") ~ "Main Effect",
+                               str_detect(mod_term, ":")    ~ "Interaction"),
+    iv             = factor(iv, 
+                            levels = c("unp_agg", "unp_interview","unp_perceived",
+                                       "vio_agg", "vio_neighborhood","vio_fighting",
+                                       "ses_agg", "ses_perceived","ses_school","ses_interview"),
+                            labels = c("Composite", "Interview", "Perceived",
+                                       "Composite", "Neighborhood","Fighting",
+                                       "Composite", "Perceived","School","Interview")),
+    pval_prop      = paste0(round(pval_prop*100,2),"% ps < .05"),
+    mod_sig = ifelse(mod_sig != "non", "pos-sig", mod_sig)
+  )
+
+secondary1b_int_plots <- 
+  secondary_set2_effects_points %>% 
+  mutate(
+    iv = factor(iv, 
+                levels = c("unp_agg", "unp_interview","unp_perceived",
+                           "vio_agg", "vio_neighborhood","vio_fighting",
+                           "ses_agg", "ses_perceived","ses_school","ses_interview"),
+                labels = c("Composite", "Interview", "Perceived",
+                           "Composite", "Neighborhood","Fighting",
+                           "Composite", "Perceived","School","Interview")),
+    mod_sig = ifelse(mod_sig != "non", "pos-sig", mod_sig)
+  )
+
+# specification curve -----------------------------------------------------
+spec_curves2 <- 
+  map(c("Attention-Shifting","Working Memory Updating"), function(x){
+    
+    # Setup
+    dv_which <- x
+    
+    map(c("Unpredictability", "Violence", "SES"), function(y){
+      
+      effs <- 
+        secondary1b_plots_data %>% 
+        filter(dv == x, iv_group == y, mod_term_group == "Interaction")
+      
+      medians <- 
+        secondary1b_plots_data %>% 
+        filter(dv == x, iv_group == y, mod_term_group == "Interaction") 
+      
+      spec_grid_data <- 
+        effs %>% 
[…]

### 2021-06-27 supplement/scripts/3-secondary2.R

@@ -1,0 +1,251 @@
+# Secondary effects -------------------------------------------------------
+secondary1a_plot_data <- 
+  secondary1a_effects_data %>% 
+  mutate(
+    iv = case_when(str_detect(mod_term, "ses")~"SES", str_detect(mod_term,"vio") ~ "Violence", T ~ NA_character_),
+    iv = factor(iv, c("Violence","SES")),
+    mod_sig = ifelse(mod_sig != "non", "pos-sig", mod_sig)
+  )
+
+# specification curve -----------------------------------------------------
+spec_curves3 <- 
+  map(c("Working Memory Updating"), function(x){
+    
+    # Setup
+    dv_which <- x
+    
+    effs <- 
+      secondary1a_plot_data %>% 
+      filter(dv == x, mod_term_group == "Interaction")
+    
+    medians <- 
+      secondary1a_plot_data %>% 
+      filter(dv == x, mod_term_group == "Interaction")
+    
+    spec_grid_data <- 
+      effs %>% 
+      select(iv, dv, starts_with("spec"), mod_p.value, mod_sig) %>% 
+      pivot_longer(cols = spec_sub_sample:spec_shifting, names_to = "spec_var", values_to = "spec_value") %>% 
+      ungroup()
+    
+    int_points <- 
+      secondary1a_effects_points %>% 
+      mutate(
+        iv        = factor(iv, c("Violence","SES")),
+        predicted = ifelse(dv == "Working Memory Updating", predicted*100, predicted),
+        dv        = ifelse(dv == "Working Memory Updating", "WM Updating", dv),
+        dv        = ifelse(dv == "Attention-Shifting", paste(dv,"(ms)\n"), paste(dv,"(% correct)\n")),
+        x         = ifelse(iv == "SES", x *-1, x),
+        x         = factor(x, levels = c(-1,1), labels = c("Low","High")),
+        x_spec    = paste0(x,"_",spec_number),
+        group     = as.numeric(group),
+        group_adj = ifelse(x == "Low", group - .1, group + .1),
+        group_jit = jitter(group_adj,.05, .05),
+        group_bx  = ifelse(group == 1, group_adj - .4, group_adj + .4)
+      )
+    
+    # Plots
+    eff_curve <- 
+      effs %>% 
+      ggplot(aes(y = mod_std_coefficient, x = spec_rank, color = mod_sig)) +
+      geom_ribbon(
+        aes(ymin = mod_ci_low, ymax = mod_ci_high, x = spec_rank),
+        fill = "gray90",
[…]

### 2021-06-27 supplement/scripts/4-tables.R

@@ -1,0 +1,329 @@
+# Primary Analyses - Covariates -------------------------------------------
+si_table.01.0 <- 
+  primary_effects_data %>% 
+  select(spec_number,iv,dv, mod_term_group, mod_term_label, mod_term_num, mod_std_coefficient, mod_ci_high, mod_ci_low, n, mod_p.value) %>% 
+  filter(mod_term_group %in% c("Covariate","Task-Type","Main Effect","Interaction")) %>% 
+  mutate(mod_term_label = ifelse(mod_term_label == "Task Type", "Task Version", mod_term_label)) %>% 
+  group_by(iv, dv, mod_term_label, mod_term_num, .drop = F) %>% 
+  mutate(p_percent = (sum(mod_p.value < .05)/64)) %>% 
+  summarize(across(where(is.numeric), median)) %>% 
+  transmute(
+    mod_term_num   = mod_term_num,
+    mod_term_label = mod_term_label,
+    median_beta    = mod_std_coefficient,
+    median_lo      = mod_ci_low,
+    median_hi      = mod_ci_high,
+    median_n       = n,
+    p_percent      = p_percent
+  ) %>% 
+  mutate(
+    dv             = ifelse(dv == "Attention-Shifting","shifting","updating"),
+    median_beta    = formatC(round(median_beta,2), digits = 2, width = 3, flag = '0', format = 'f'),
+    median_n       = formatC(round(median_n), digits = 0, format = 'f'),
+    p_percent      = formatC(round(p_percent*100, 2), digits = 2, width = 3, flag = '0', format = 'f') %>% paste0(.,"%"),
+    ci_lo          = formatC(round(median_lo,2), digits = 2, width = 3, flag = '0', format = 'f'),
+    ci_hi          = formatC(round(median_hi,2), digits = 2, width = 3, flag = '0', format = 'f'),
+    ci             = glue::glue("[{ci_lo}, {ci_hi}]"),
+    mod_term_label = fct_reorder(mod_term_label, mod_term_num)
+  ) %>% 
+  arrange(iv,dv,mod_term_num) %>% 
+  select(
+    iv, dv, mod_term_label, median_beta, ci, p_percent, median_n
+  ) %>% 
+  ungroup() %>% 
+  pivot_wider(names_from = dv, values_from = c(median_n,median_beta,ci,p_percent)) %>% 
+  select(iv, mod_term_label, ends_with("shifting"), ends_with("updating")) %>% 
+  mutate(
[…]

### 2021-06-27 supplement/scripts/rmd-staging.R

@@ -1,0 +1,68 @@
+# Packages ----------------------------------------------------------------
+library(tidyverse)
+library(cowplot)
+library(see)
+library(gt)
+
+# ggplot2 theme -----------------------------------------------------------
+theme_set(
+  theme_bw() +
+    theme(
+      axis.line.y       = element_line(),
+      axis.text.y       = element_text(size = rel(.75)),
+      axis.title.y      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
+      axis.ticks.y      = element_line(),
+      axis.line.x       = element_blank(),
+      axis.text.x       = element_blank(),
+      axis.ticks.x      = element_blank(),
+      axis.title.x      = element_blank(),
+      panel.border      = element_blank(), 
+      panel.spacing.y   = unit(0.5, "lines"),
+      plot.margin       = margin(.25,.25,.25,.25,"lines"),
+      plot.background   = element_rect(color = NA),
+      plot.title        = element_text(size = rel(.85), hjust = 0, margin = margin(0,0,.5,0, "lines")),
+      plot.subtitle     = element_blank(),
+      panel.grid        = element_line(color = NA),
+      strip.background  = element_blank(), 
+      strip.placement   = "outside",
+      strip.text        = element_text(size = rel(.85), angle = 0)
+    )
+)
+
+pval_colors <- c("pos-sig" = "#006D77", "non" = "gray70")
+my_alphas <- c(.5, 1)
+my_limits <- c(1,70)
+
+# Multiverse Objects ----
+load("multiverse-objects/2-primary-analyses/3-extracted-effects.Rdata")
+load("multiverse-objects/3-secondary-analyses/set-2/a1-extracted-effects.Rdata")
+load("multiverse-objects/3-secondary-analyses/set-1/a2-extracted-effects.Rdata")
+
+# Make plots and tables ----
+source("supplement/scripts/1-covariates.R")
+source("supplement/scripts/2-secondary1.R")
+source("supplement/scripts/3-secondary2.R")
+source("supplement/scripts/4-tables.R")
+
+# Save the entire image ---------------------------------------------------
+save(
+  si_table.01.1,
+  shifting_unp,
+  shifting_vio,
+  shifting_ses,
+  updating_unp,
+  updating_vio,
+  updating_ses,
+  si_table.02.0,
+  si_table.03.0,
+  unp_shifting,
+  vio_shifting,
[…]

### 2021-06-27 README.Rmd
Fix typo in README
manually merge changes

@@
 
-The names of each folder are intended to be self-explanatory. There are five top-level folders to organize the inputs and outputs of this project:
+The names of each folder are intended to be self-explanatory. There are six top-level folders to organize the inputs and outputs of this project:
 
@@
 2.  `data/`: data, stored as an `.Rdata` file and `.csv` files.
-3.  `figures/`: all figures that are produced by R-scripts
-4.  `multiverse-objects/`: all `.Rdata` files containing objects necessary for performing multiverse analyses and storing intermediary results
+3.  `manuscript`: a manuscript written in R markdown for submission to a journal.
+4.  `multiverse-objects/`: all `.Rdata` files containing objects necessary for performing multiverse analyses and storing intermediary results.
+5.  `scripts/`: R-scripts that read, analyze, and produce all multiverse objects.
+6.  `supplement/`: a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.
 
@@
 ```{r}
-fs::dir_tree(".", regexp = "^README|.Rproj$", invert = T)
+fs::dir_tree(".", regexp = "^README|.Rproj$|log$|tex$|_files|resources", invert = T)
 ```
@@
 
-## Figures
+## Manuscript
 
-These are all figures that are produced by R-scripts. They are divided into the following categories:
-
--   Primary analysis figures
-
--   Secondary analysis figures
-
-    -   Set 1
-    -   Set 2
+This directory contains the manuscript for this project.
+It was written in R Markdown and is 100% reproducible.
+The `.Rmd` fie contains the written text with all figures, tables, and in-text statistics.
+All outputs reported in the manuscript were staged prior to compiling into a `.pdf` document and stored in a `.Rdata` file called `staged-objects.Rdata`.
+The R Markdown document reads these staged files to make the overall document easier to read.
+The scripts that produce the staged objects are located in the `manuscript/scripts/` directory and are named to be self-explanatory.
+The `rmd-staging.R` script reads necessary data/objects from the `multiverse-objects/` directory and sources the other scripts to produce the objects needed for the manuscript.
 
@@
 
--   `0-functions/`: custom R-functions written for this project
+-   `0-functions/`: Custom R-functions written for this project
 -   `1-data-prep/`: Data processing scripts
@@
   gt(id = "one", rowname_col = "row") %>% 
-  fmt_markdown(columns = T) %>% 
+  fmt_markdown(columns = everything()) %>% 
   as_raw_html()
@@
   gt(id = "one", rowname_col = "row") %>% 
-  fmt_markdown(columns = T) %>% 
+  fmt_markdown(columns = everything()) %>% 
   as_raw_html()
 ```
+
+## Supplement
+
+This directory contains the supplement to the manuscript described above.
+The supplement was produced using the same approach as the manuscript: it was written in R Markdown, is 100% reproducible, and all outputs were staged prior to compiling into a `.pdf`.
+The staged objects are stored in `supplement/staged-objects.Rdata`.
+The scripts that produce the staged objects are located in the `supplement/scripts/` directory and are named to be self-explanatory.
+The `rmd-staging.R` script reads necessary data/objects from the `multiverse-objects/` directory and sources the other scripts to produce the objects needed for the supplement.

### 2021-06-27 scripts/1-data-prep/1-data-non-abritrary.R

@@ -73,15 +73,9 @@ data3_composites <-
     starts_with("non_arb"),
     starts_with("arb"),
     matches("^test_envr"), 
-<<<<<<< HEAD
-<<<<<<< HEAD
     matches("^csd(\\d|\\d\\d|)$"),
-=======
     matches("^csd(\\d|)$"),
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
     matches("^csd(\\d|)$"),
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
     matches("^unp_perceived"),
     matches("^unp_interview"),
     unp_agg,

### 2021-06-27 scripts/1-data-prep/3-secondary-multiverse-datasets.R

@@ -46,18 +46,12 @@ spec_grid <-
       "shifting",        0,           "(arb_abs_shift/32) > 0 & (arb_eco_shift/32) > 0",       "Include Acc. < 65%",
       "shifting",        1,           "(arb_abs_shift/32) > .65 & (arb_eco_shift/32) > .65",   "Exclude Acc. < 65%",
       "iv",              0,           "unp_agg",                                               "Unp Composite",
-<<<<<<< HEAD
-<<<<<<< HEAD
       "iv",              1,           "unp_interview",                                         "Unp Interview",
       "iv",              2,           "unp_perceived",                                         "Unp Perceived",
-=======
       "iv",              1,           "unp_interview",                                         "Unp Perceived",
       "iv",              2,           "unp_perceived",                                         "Unp Interview",
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
       "iv",              1,           "unp_interview",                                         "Unp Perceived",
       "iv",              2,           "unp_perceived",                                         "Unp Interview",
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
       "iv",              3,           "vio_agg",                                               "Vio Composite",
       "iv",              4,           "vio_neighborhood",                                      "Vio Neighborhood",
       "iv",              5,           "vio_fighting",                                          "Vio Fighting",

### 2021-06-27 scripts/2-primary-analyses/3-extract-effects.R

@@ -39,8 +39,6 @@ primary_effects_data <-
       }) %>% 
       rename_with(tolower) %>% 
       filter(!str_detect(mod_term, "^sd__")) %>% 
-<<<<<<< HEAD
-<<<<<<< HEAD
       mutate(
         # Do this to reverse code SES to match low SES to High poverty
         across(
@@ -48,10 +46,6 @@ primary_effects_data <-
           .fns = ~ifelse(str_detect(mod_term,"ses"), .x * -1, .x)
         )
       ) %>% 
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
       group_by(mod_term) %>% 
       mutate(
         spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),
@@ -129,8 +123,6 @@ primary_effects_points <-
       select(iv, dv, hypoth, spec_number, mod_sig)
   )
 
-<<<<<<< HEAD
-<<<<<<< HEAD
 # Simple Slopes -----------------------------------------------------------
 primary_simple_slopes <- 
   primary_pmap %>% 
@@ -162,21 +154,11 @@ primary_simple_slopes <-
       )
   })
 
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
 # save data ---------------------------------------------------------------
 save(
   primary_effects_data,
   primary_effects_medians,
   primary_effects_points,
-<<<<<<< HEAD
-<<<<<<< HEAD
   primary_simple_slopes,
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
   file = "multiverse-objects/2-primary-analyses/3-extracted-effects.Rdata"
 )

### 2021-06-27 scripts/3-secondary-analyses/set-1/a2-extract-effects.R

@@ -23,8 +23,6 @@ secondary1a_effects_data <-
   }) %>% 
   rename_with(tolower) %>% 
   filter(!str_detect(mod_term, "^sd__")) %>% 
-<<<<<<< HEAD
-<<<<<<< HEAD
   mutate(
     # Do this to reverse code SES to match low SES to High poverty
     across(
@@ -32,10 +30,6 @@ secondary1a_effects_data <-
       .fns = ~ifelse(str_detect(mod_term,"ses"), .x * -1, .x)
     )
   ) %>% 
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
   group_by(mod_term) %>% 
   mutate(
     spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),
@@ -97,8 +91,6 @@ secondary1a_effects_points <-
       select(mod_term, dv, spec_number, mod_sig)
   )
 
-<<<<<<< HEAD
-<<<<<<< HEAD
 # Simple Slopes -----------------------------------------------------------
 secondary1a_simple_slopes <- 
   secondary1a_ses_vio_updating %>% 
@@ -128,21 +120,11 @@ secondary1a_simple_slopes <-
     )
   })
 
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
 # Save --------------------------------------------------------------------
 save(
   secondary1a_effects_data,
   secondary1a_effects_medians, 
   secondary1a_effects_points, 
-<<<<<<< HEAD
-<<<<<<< HEAD
   secondary1a_simple_slopes,
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
   file = "multiverse-objects/3-secondary-analyses/set-1/a2-extracted-effects.Rdata"
 )

### 2021-06-27 scripts/3-secondary-analyses/set-2/a2-extract-effects.R

@@ -37,8 +37,6 @@ secondary_set2_effects <-
         ) 
       }) %>% 
       rename_with(tolower) %>% 
-<<<<<<< HEAD
-<<<<<<< HEAD
       filter(!str_detect(mod_term, "^sd__")) %>% 
       mutate(
         # Do this to reverse code SES to match low SES to High poverty
@@ -47,12 +45,8 @@ secondary_set2_effects <-
           .fns = ~ifelse(str_detect(iv,"ses"), .x * -1, .x)
         )
       )
-=======
       filter(!str_detect(mod_term, "^sd__"))
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
       filter(!str_detect(mod_term, "^sd__"))
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
   })
 
 secondary_set2_effects_clean <- 
@@ -100,8 +94,6 @@ secondary_set2_effects_points <-
     by = c("iv" = "iv", "dv" = "dv", "spec_number" = "spec_number")
   )
 
-<<<<<<< HEAD
-<<<<<<< HEAD
 # Simple Slopes -----------------------------------------------------------
 secondary_set2_simple_slopes <- 
   secondary_pmap %>% 
@@ -134,20 +126,10 @@ secondary_set2_simple_slopes <-
       })
   })
 
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
 # save data ---------------------------------------------------------------
 save(
   secondary_set2_effects_clean,
   secondary_set2_effects_points,
-<<<<<<< HEAD
-<<<<<<< HEAD
   secondary_set2_simple_slopes,
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
-=======
->>>>>>> a0940e3bd988ef96e84639d84f581ebe385b1ee1
   file = "multiverse-objects/3-secondary-analyses/set-2/a1-extracted-effects.Rdata"
 )

### 2021-06-27 scripts/2-primary-analyses/6-create-plots.R
remove plotting scripts

@@ -1,402 +1,0 @@
-# Setup -------------------------------------------------------------------
-# Libraries
-library(tidyverse)
-library(cowplot)
-library(see)
-
-# Load effect data.frames -------------------------------------------------
-load("multiverse-objects/2-primary-analyses/3-extracted-effects.Rdata")
-load("multiverse-objects/2-primary-analyses/5-bootstrapped-effects.Rdata")
-
-# ggplot2 theme -----------------------------------------------------------
-theme_set(
-  theme_bw() +
-    theme(
-      axis.line.x       = element_line(),
-      axis.text.x       = element_text(size = rel(.75)),
-      axis.title.x      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
-      axis.ticks.x      = element_line(),
-      axis.line.y       = element_blank(),
-      axis.text.y       = element_blank(),
-      axis.ticks.y      = element_blank(),
-      axis.title.y      = element_blank(),
-      panel.border      = element_blank(), 
-      panel.spacing.y   = unit(.5, "lines"),
-      plot.margin       = margin(2,.25,.25,.25,"lines"),
-      plot.background   = element_rect(color = NA),
-      plot.title        = element_text(size = rel(.9), hjust = .5),
-      plot.subtitle     = element_blank(),
-      panel.grid        = element_line(color = NA),
-      strip.background  = element_blank(), 
-      strip.placement   = "outside",
-      strip.text        = element_text(size = rel(.85), angle = 0)
-    )
-)
-
-pval_colors <- c("pos-sig" = "#FF7F00", "neg-sig" = "#1F78B4", "non" = "gray")
-my_alphas <- c(.3, 1)
-my_limits <- c(1,70)
-
-# Get bootstrapped medians ------------------------------------------------
-boot_medians <- 
-  boot_effects %>% 
-  filter((null_term == "main" & mod_term == "iv") | (null_term == "int" & mod_term == "iv:type_z")) %>% 
-  rename(term = mod_term) %>% 
-  group_by(spec_num, iv, dv, null_term) %>% 
-  summarize(
-    across(
-      starts_with("mod"), 
-      list(median = ~median(.x), lower = ~quantile(.x, probs = .025, names = F), upper = ~quantile(.x, probs = .975, names = F)),
-      .names = "{.col}_{.fn}")
-  ) %>%
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-1/a3-create-plots.R

@@ -1,285 +1,0 @@
-# Setup -------------------------------------------------------------------
-# Libraries
-library(tidyverse)
-library(cowplot)
-
-# Load Data ---------------------------------------------------------------
-load("multiverse-objects/3-secondary-analyses/set-1/a2-extracted-effects.Rdata")
-
-# ggplot2 theme -----------------------------------------------------------
-theme_set(
-  theme_bw() +
-    theme(
-      axis.line.x       = element_line(),
-      axis.text.x       = element_text(size = rel(.75)),
-      axis.title.x      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
-      axis.ticks.x      = element_line(),
-      axis.line.y       = element_blank(),
-      axis.text.y       = element_blank(),
-      axis.ticks.y      = element_blank(),
-      axis.title.y      = element_blank(),
-      panel.border      = element_blank(), 
-      panel.spacing.y   = unit(.5, "lines"),
-      plot.margin       = margin(2,.25,.25,.25,"lines"),
-      plot.background   = element_rect(color = NA),
-      plot.title        = element_text(size = rel(.9), hjust = .5),
-      plot.subtitle     = element_blank(),
-      panel.grid        = element_line(color = NA),
-      strip.background  = element_blank(), 
-      strip.placement   = "outside",
-      strip.text        = element_text(size = rel(.85), angle = 0)
-    )
-)
-
-pval_colors <- c("pos-sig" = "#FF7F00", "neg-sig" = "#1F78B4", "non" = "gray")
-my_limits <- c(1,70)
-
-# Spec Curve --------------------------------------------------------------
-spec_curves <- 
-  map(c("Main Effect","Interaction"), function(x){
-    
-    effs <- 
-      secondary1a_effects_data %>% 
-      filter(mod_term_group == x) %>% 
-      mutate(iv = ifelse(str_detect(mod_term,"vio"),"Violence","SES"))
-    
-    medians <- 
-      secondary1a_effects_medians %>% 
-      filter(mod_term_group == x) %>% 
-      mutate(iv = ifelse(str_detect(mod_term,"vio"),"Violence","SES"))
-    
-    eff_curve <- 
-      effs %>% 
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-1/b3-create-plots.R

@@ -1,285 +1,0 @@
-# Setup -------------------------------------------------------------------
-# Libraries
-library(tidyverse)
-library(cowplot)
-
-# Load effect data.frames -------------------------------------------------
-load("multiverse-objects/3-secondary-analyses/set-1/b2-extracted-effects.Rdata")
-
-# ggplot2 theme -----------------------------------------------------------
-theme_set(
-  theme_bw() +
-    theme(
-      axis.line.x       = element_line(),
-      axis.text.x       = element_text(size = rel(.75)),
-      axis.title.x      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
-      axis.ticks.x      = element_line(),
-      axis.line.y       = element_blank(),
-      axis.text.y       = element_blank(),
-      axis.ticks.y      = element_blank(),
-      axis.title.y      = element_blank(),
-      panel.border      = element_blank(), 
-      panel.spacing.y   = unit(.5, "lines"),
-      plot.margin       = margin(2,.25,.25,.25,"lines"),
-      plot.background   = element_rect(color = NA),
-      plot.title        = element_text(size = rel(.9), hjust = .5),
-      plot.subtitle     = element_blank(),
-      panel.grid        = element_line(color = NA),
-      strip.background  = element_blank(), 
-      strip.placement   = "outside",
-      strip.text        = element_text(size = rel(.85), angle = 0)
-    )
-)
-
-pval_colors <- c("pos-sig" = "#FF7F00", "neg-sig" = "#1F78B4", "non" = "gray")
-my_limits <- c(1,70)
-
-# specification curve -----------------------------------------------------
-spec_curves <- 
-  map(c("Working Memory Updating"), function(x){
-    map(c("Main Effect","Interaction"), function(y){
-      
-      effs <- 
-        secondary1b_effects_data %>% 
-        filter(dv == x, mod_term_group == y)
-      
-      medians <- 
-        secondary1b_effects_data %>% 
-        filter(dv == x, mod_term_group == y)
-      
-      eff_curve <- 
-        effs %>% 
-        ggplot(aes(x = mod_std_coefficient, y = spec_rank, color = mod_sig)) +
-        geom_ribbon(
-          aes(xmin = mod_ci_low, xmax = mod_ci_high, y = spec_rank),
[…]

### 2021-06-27 scripts/3-secondary-analyses/set-2/a3-create-plots.R

@@ -1,583 +1,0 @@
-# Setup -------------------------------------------------------------------
-# Libraries
-library(tidyverse)
-library(cowplot)
-
-# Load effect data.frames -------------------------------------------------
-load("multiverse-objects/3-secondary-analyses/set-2/a1-extracted-effects.Rdata")
-
-# ggplot2 theme -----------------------------------------------------------
-theme_set(
-  theme_bw() +
-    theme(
-      axis.line.x       = element_line(),
-      axis.text.x       = element_text(size = rel(.75)),
-      axis.title.x      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
-      axis.ticks.x      = element_line(),
-      axis.line.y       = element_blank(),
-      axis.text.y       = element_blank(),
-      axis.ticks.y      = element_blank(),
-      axis.title.y      = element_blank(),
-      panel.border      = element_blank(), 
-      panel.spacing.y   = unit(.5, "lines"),
-      plot.margin       = margin(2,.25,.25,.25,"lines"),
-      plot.background   = element_rect(color = NA),
-      plot.title        = element_text(size = rel(.9), hjust = 0.5),
-      plot.subtitle     = element_blank(),
-      panel.grid        = element_line(color = NA),
-      strip.background  = element_blank(), 
-      strip.placement   = "outside",
-      strip.text        = element_text(size = rel(.85), angle = 0)
-    )
-)
-
-pval_colors <- c("pos-sig" = "#FF7F00", "neg-sig" = "#1F78B4", "non" = "gray")
-my_limits <- c(1,70)
-
-
-# Plotting Data -----------------------------------------------------------
-secondary_set2_plots_data <- 
-  secondary_set2_effects_clean %>% 
-  mutate(
-    mod_term_group = case_when(str_detect(mod_term, "^iv$") ~ "Main Effect",
-                               str_detect(mod_term, ":")    ~ "Interaction"),
-    iv             = factor(iv, 
-                            levels = c("unp_agg", "unp_interview","unp_perceived",
-                                       "vio_agg", "vio_neighborhood","vio_fighting",
-                                       "ses_agg", "ses_perceived","ses_school","ses_interview"),
[…]

### 2021-06-28 manuscript/manuscript.Rmd
fix links and figure placement

@@
 endnote: no
+urlcolor: blue
 header-includes:
@@
   fig.align = "center",
-  fig.pos = "H",  
+  fig.pos = "!",  
   fig.show = "asis",
@@
 Before conducting analyses, we identified six arbitrary data processing decisions each with two alternatives (see Arbitrary Decisions section).
-These criteria were 1) including the after-school club sample or not; 2) including participants with minor distractions during testing or not; 3) including participants who missed one trap question or not (those who missed more than 1 were already excluded); 4) including participants receiving special education (participants receiving more \> 60 minutes/day were already excluded) or not; 5) including participants who performed at or below chance levels of accuracy on the attention-shifting task or not (see <https://osf.io/kvt5e/> for more information); and 6) residualizing social desirability scores out of adversity scores or not.
+These criteria were 1) including the after-school club sample or not; 2) including participants with minor distractions during testing or not; 3) including participants who missed one trap question or not (those who missed more than 1 were already excluded); 4) including participants receiving special education (participants receiving more \> 60 minutes/day were already excluded) or not; 5) including participants who performed at or below chance levels of accuracy on the attention-shifting task or not (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information); and 6) residualizing social desirability scores out of adversity scores or not.
 Using all possible combinations of arbitrary decisions, we constructed a multiverse of `r length(multi_data_list)` datasets.
@@
 
-Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$1 *SD*) and low ($-$ *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction -coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).
+Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction -coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).
 
-We preregistered all primary analyses on the Open Science Framework (OSF; <https://osf.io/6r95z/>), including an updated primary analysis plan (<https://osf.io/4vsnz/>), which included more details.
+We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd), including an [updated primary analysis plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
 We conducted secondary analyses after our primary analyses (see Secondary Analyses below).
-Before conducting these analyses, we uploaded secondary analysis plans (see <https://osf.io/7fu35/> and <https://osf.io/wcauf/>), explaining the goals and purpose of each secondary analysis.
-A Red Team Critic[@market] successfully reproduced (<https://github.com/ethan-young/hidden-talents-multiverse/pull/1/>) and verified (REPORT XXX) all analyses prior to submission.
+Before conducting these analyses, we uploaded secondary analysis plans (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd), explaining the goals and purpose of each secondary analysis.
+A Red Team Critic[@market] successfully reproduced and verified (REPORT XXX) all analyses prior to submission.
 
@@
 That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures are associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecologically relevant.
-
-### Working Memory Updating
-
-Across each set of multiverse analyses, there were again significant main effects of task version.
-All median effects sizes for task version were $\beta$s = `r c(mod_terms1$updating.unp.type_z$median_beta, mod_terms1$updating.vio.type_z$median_beta, mod_terms1$updating.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for models testing unpredictability, violence exposure, and poverty exposure, indicating that updating performance was better when stimuli were ecological relevant compared to abstract, on average (see SI Figures 4-6).
-There were also consistent main effects of age; median effects were $\beta$ = `r mod_terms1$updating.unp.age$median_beta` (all *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.age$median_beta` (all *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.age$median_beta` (all *ps* \< .05) for poverty exposure models (see SI Figures 4-6).
-That is, older adolescents scored higher on working memory updating, on average.
-Finally, there were some main effects of test environment distraction ratings.
-Median effects sizes were $\beta$ = `r mod_terms1$updating.unp.test_envr$median_beta` (`r (mod_terms1$updating.unp.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.test_envr$median_beta` (`r (mod_terms1$updating.vio.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.test_envr$median_beta` (`r (mod_terms1$updating.ses.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for poverty exposure models, indicating that more test distractions reduced working memory updating performance, on average (see SI Figures 4-6).
-
-(ref:figure3) Visualization of multiverse working memory updating results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
-Proportions of each arbitrary decision with *p*-values < .05 are indicated on the right side of each specification grid.
-Blank proportions indicate proportions = 0.
-
-```{r figure3, fig.height=7.5, fig.width=6.5, fig.cap='(ref:figure3)'}
-fig3
-```
 
@@
 
+### Working Memory Updating
+
+Across each set of multiverse analyses, there were again significant main effects of task version.
+All median effects sizes for task version were $\beta$s = `r c(mod_terms1$updating.unp.type_z$median_beta, mod_terms1$updating.vio.type_z$median_beta, mod_terms1$updating.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for models testing unpredictability, violence exposure, and poverty exposure, indicating that updating performance was better when stimuli were ecological relevant compared to abstract, on average (see SI Figures 4-6).
+There were also consistent main effects of age; median effects were $\beta$ = `r mod_terms1$updating.unp.age$median_beta` (all *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.age$median_beta` (all *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.age$median_beta` (all *ps* \< .05) for poverty exposure models (see SI Figures 4-6).
+That is, older adolescents scored higher on working memory updating, on average.
+Finally, there were some main effects of test environment distraction ratings.
+Median effects sizes were $\beta$ = `r mod_terms1$updating.unp.test_envr$median_beta` (`r (mod_terms1$updating.unp.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.test_envr$median_beta` (`r (mod_terms1$updating.vio.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.test_envr$median_beta` (`r (mod_terms1$updating.ses.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for poverty exposure models, indicating that more test distractions reduced working memory updating performance, on average (see SI Figures 4-6).
+
 Multiverse analyses revealed a main effect of poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_main`, all *ps* \< .05, bootstrapped *p* \< .001) but no main effects of unpredictability (median $\beta$ = `r mod_terms2$updating.unp$median_beta_main`, no *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.unp$p_overall_main`) or violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_main`, `r mod_terms2$updating.vio$p_percent_main` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_main`).
@@
 In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among adolescents exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
+
+(ref:figure3) Visualization of multiverse working memory updating results.
+Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
+Proportions of each arbitrary decision with *p*-values < .05 are indicated on the right side of each specification grid.
+Blank proportions indicate proportions = 0.
+
+```{r figure3, fig.height=7.5, fig.width=6.5, fig.cap='(ref:figure3)'}
+fig3
+```
+
+## Secondary Analyses
+
+We followed-up our primary analyses with two sets of secondary, exploratory analyses.
+We uploaded secondary analysis plans to the OSF prior to conducting them (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)).
+These analyses focused on two questions.
+First, in contrast to prior work[@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting).
+However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures.
+Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure) have unique associations with attention shifting and working memory updating performance.
+To address this, we expanded our multiverse approach to include each component of our predictor variables as additional arbitrary decisions.
+
+The second question focused on the interactive effects of task version × violence exposure and task version × poverty exposure on working memory updating performance.
+Specifically, primary analyses revealed an equalization effect for both violence and poverty exposures on working memory updating.
+However, because measures of violence and poverty were not included in the same statistical model, it is unclear whether these interactions are independent.
+For example, one possibility is that exposures to violence and poverty are independently associated with working memory updating performance.
+Alternatively, they may overlap, reflecting the same association.
+To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty in the same model.
+If violence and poverty exposures interact independently with task version, both interaction terms should remain significant.
+However, if they represent overlapping effects on working memory updating performance, one or the other may drop out of significance, which would suggest that one or the other adversity dimension is driving the effects of the other.
 
@@
 ```
-
-## Secondary Analyses
-
-We followed-up our primary analyses with two sets of secondary, exploratory analyses.
-We uploaded secondary analysis plans to the OSF prior to conducting them (see <https://osf.io/7fu35//> and <https://osf.io/wcauf//>).
-These analyses focused on two questions.
-First, in contrast to prior work[@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting).
-However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures.
-Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure) have unique associations with attention shifting and working memory updating performance.
-To address this, we expanded our multiverse approach to include each component of our predictor variables as additional arbitrary decisions.
-
-The second question focused on the interactive effects of task version × violence exposure and task version × poverty exposure on working memory updating performance.
-Specifically, primary analyses revealed an equalization effect for both violence and poverty exposures on working memory updating.
-However, because measures of violence and poverty were not included in the same statistical model, it is unclear whether these interactions are independent.
-For example, one possibility is that exposures to violence and poverty are independently associated with working memory updating performance.
-Alternatively, they may overlap, reflecting the same association.
-To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty in the same model.
-If violence and poverty exposures interact independently with task version, both interaction terms should remain significant.
-However, if they represent overlapping effects on working memory updating performance, one or the other may drop out of significance, which would suggest that one or the other adversity dimension is driving the effects of the other.
 
@@
 To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000].
-We removed fast and slow reaction times and removed trials after incorrect responses (see <https://osf.io/74xjy/> for details).
+We removed fast and slow reaction times and removed trials after incorrect responses (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
 We then subtracted the average reaction time on valid switch trials from the average reaction time on valid repeat trials to calculate switch cost scores.
@@
 Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded).
-Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see <https://osf.io/kvt5e/> for more information).
+Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
 

### 2021-06-28 README.Rmd
fix README md file

@@
   gt(id = "one", rowname_col = "row") %>% 
-  fmt_markdown(columns = everything()) %>% 
-  as_raw_html()
+  fmt_markdown(columns = everything()) 
 ```
@@
   gt(id = "one", rowname_col = "row") %>% 
-  fmt_markdown(columns = everything()) %>% 
-  as_raw_html()
+  fmt_markdown(columns = everything())
 ```

### 2021-06-28 README.Rmd
fixing markdown tables in RREADME

@@
       input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
-      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>%str_c(collapse = "\n- ") %>%  paste0("- ", .) %>% ifelse(. == "- ","",.),
+      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>% ifelse(. == " ","",.),
       n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
@@
       output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
-      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "\n- ") %>%  paste0("- ", .) %>% ifelse(. == "- NA","",.)
+      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>%  ifelse(. == "NA","",.)
     )
@@
   select(-dir) %>% 
-  gt(id = "one", rowname_col = "row") %>% 
-  fmt_markdown(columns = everything()) 
+  knitr::kable(format = "pipe")
 ```
@@
   select(-dir) %>% 
-  gt(id = "one", rowname_col = "row") %>% 
-  fmt_markdown(columns = everything())
+  knitr::kable(format = "pipe")
 ```

### 2021-06-28 README.Rmd
fixing the tables a different way

@@
       input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
-      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>% ifelse(. == " ","",.),
+      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = ", ") %>% ifelse(. == ", ","",.),
       n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
@@
       output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
-      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>%  ifelse(. == "NA","",.)
+      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = ", ") %>%  ifelse(. == ", NA","",.)
     )

### 2021-06-28 README.Rmd
trying yet another way

@@
   select(-dir) %>% 
-  knitr::kable(format = "pipe")
+  knitr::kable(format = "simple")
 ```

### 2021-06-28 README.Rmd
makeing sure markdown tables are displayed in OSF

--- 2021-06-28 README.Rmd
@@
 
-```{r}
+```{r, results='asis'}
+data_prep <- 
   file_list %>% 
@@
   filter(dir == "data-prep") %>% 
-  select(-dir) %>% 
-  knitr::kable(format = "pipe")
+  select(-dir)
+
+cat(
+  "|script|input|output|",
+  "|------|-----|------|",
+  glue::glue_data(
+    data_prep,
+    "|{script}|{input}|{output}|"
+  ),
+  sep = "\n"
+)
 ```
@@
 
-```{r}
+```{r, results='asis'}
+primary_analyses <- 
   file_list %>% 
@@
   filter(dir == "primary-analyses") %>% 
-  select(-dir) %>% 
-  knitr::kable(format = "pipe")
+  select(-dir)
+
+cat(
+  "|script|input|output|",
+  "|------|-----|------|",
+  glue::glue_data(
+    primary_analyses,
+    "|{script}|{input}|{output}|"
+  ),
+  sep = "\n"
+)
 ```
@@
 
-```{r}
+```{r, results='asis'}
+secondary_analyses <- 
   file_list %>% 
@@
   filter(dir == "secondary-analyses") %>% 
-  select(-dir) %>% 
-  knitr::kable(format = "pipe")
+  select(-dir)
+
+cat(
+  "|script|input|output|",
+  "|------|-----|------|",
+  glue::glue_data(
+    secondary_analyses,
+    "|{script}|{input}|{output}|"
+  ),
+  sep = "\n"
+)
 ```

### 2021-06-28 README.Rmd
another attempt to fix tables for OSF

@@
 title: "Hidden Talents Multiverse Analysis"
-output: github_document
+output: md_document
 ---
@@
 library(gt)
+library(glue)
+library(htmltools)
 ```
@@
       input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
-      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = ", ") %>% ifelse(. == ", ","",.),
+      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>% ifelse(. == "<br> ","",.),
       n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
@@
       output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
-      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = ", ") %>%  ifelse(. == ", NA","",.)
+      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>%  ifelse(. == "<br> NA","",.)
     )
@@
   ),
-  sep = "\n"
+  sep = "\n "
 )

### 2021-06-28 README.Rmd
another attempt
revert  README.Rmd back to a github_document output
trying, again :(
testing something out

@@
   ),
-  sep = "\n "
+  sep = "\n"
 )
 ```
+
+|script|input|output|
+|------|-----|------|
+|1-data-non-abritrary.R|data1_raw.Rdata|1-raw.csv<br> 2-non_arbitrary.csv<br> 3-composites.csv<br> 4-multiverse_base.csv<br> vars1_raw.csv<br> vars2_non_arbitrary.csv<br> vars3_composites.csv<br> vars4_multiverse_base.csv<br> data2_analysis.Rdata|
+|2-primary-multiverse-datasets.R|data2_analysis.Rdata|datalist-agg-ivs.Rdata|
+|3-secondary-multiverse-datasets.R|data2_analysis.Rdata|datalist-all-ivs.Rdata|
 

### 2021-06-28 README.Rmd
trying another thing
anonymize readme file

@@
 title: "Hidden Talents Multiverse Analysis"
-output: md_document
+output: github_document
 ---
@@
 
-This repository contains data, code, and (some) output for a working manuscript by Young, Frankenhuis, and Ellis (in progress).
+This repository contains data, code, and (some) output for a working manuscript.
 

### 2021-07-02 manuscript/manuscript.Rmd
add red team links

@@
 - \captionsetup[figure]{labelfont={bf},labelformat={default}, labelsep={period}}
+- \usepackage{lineno}
+- \linenumbers
 bibliography: references.bib
@@
 
-\pagebreak
-
-\vspace*{1in}
-
-# Hidden talents in context: Can ecologically-relevant stimuli improve cognitive performance among adversity-exposed youth?
-
-\bigskip
-
-\begin{center}
-
-Ethan S. Young\textsuperscript{1,2}, Willem E. Frankenhuis\textsuperscript{1,2}, Danielle J. DelPriore\textsuperscript{3}, and Bruce J. Ellis\textsuperscript{4}
-
-\textsuperscript{1}Department of Psychology, Utrecht University, the Netherlands
-
-\textsuperscript{2}Behavioural Science Institute, Radboud University, the Netherlands
-
-\textsuperscript{3}Division of Education, Human Development, and Social Sciences, Pennsylvania State University - Altoona, USA
-
-\textsuperscript{4}Departments of Psychology and Anthropology, University of Utah, USA
-
-\end{center}
-
-\pagebreak
-
 # Abstract
@@
 \noindent Children developing in harsh conditions often perform poorly on standard cognitive tests.
-However, the hidden talents approach proposes that performance for some abilities may be enhanced by adversity or improved under ecologically relevant conditions.
+However, the hidden talents approach proposes that performance for some abilities may be enhanced by adversity or improved under ecologically-relevant conditions.
 We examine ecologically relevant content in cognitive testing.
@@
 However, because specific dimensions of adversity (violence versus resource-scarcity) may pose unique challenges[@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity[@frankenhuis2020].
-For instance, physically abused children can apparently detect angry facial expressions quickly and accurately[@gibb2009; @pollak2008; @pollak2009], people living in poverty have shown some evidence of enhanced social perception[@piff2018], and anxiously attached people are good at deception detection[@eindor2014; @shoda2013] to list a few examples (see[@ellis2017; @ellis2020] for reviews).
+For instance, physically abused children can detect angry facial expressions quickly and accurately[@gibb2009; @pollak2008; @pollak2009], people living in poverty have shown some evidence of enhanced social perception[@piff2018], and anxiously attached people are good at deception detection[@eindor2014; @shoda2013] (see[@ellis2017; @ellis2020] for reviews).
 
@@
 For example, one study tested memory and reasoning among young adults who varied in their exposures to violence[@frankenhuis2020a].
-They created two versions of the memory and reasoning task, one neutral (chronological age) and one more ecologically relevant (social dominance).
+They created two versions of a memory and reasoning task, one neutral (chronological age) and one more ecologically relevant (social dominance).
 They found that people with more current exposures to violence were equally good, or even better, at memorizing social-dominance relationships compared to people with fewer exposures.
@@
 Before conducting these analyses, we uploaded secondary analysis plans (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd), explaining the goals and purpose of each secondary analysis.
-A Red Team Critic[@market] successfully reproduced and verified (REPORT XXX) all analyses prior to submission.
+A Red Team Critic[@market] successfully reproduced and verified (see this [red team report](https://osf.io/xv94z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)) all analyses prior to submission.
 
@@
 Mixed-modeling approaches can account for both overall reaction times and differences across switch and repeat trials, but require more statistical power to test three-way interactions.
-Future should consider more appropriate modeling approaches.
+Future research should consider more appropriate modeling approaches.
 
@@
 If this is true, those mechanisms that process abstract content may be impaired but those that process ecological content are intact or enhanced.
-Second, there may be not impaired or enhanced processes at all.
+Second, there may not be impaired or enhanced processes at all.
 Instead, ecologically relevant stimuli may activate intact, but normally dormant or underrecruited, working memory updating processes.
-Thus, when tested under abstract testing conditions, cognitive processes operate at lower level (remain inactive) but operate normally with ecological testing materials.
+Thus, when tested under abstract testing conditions, cognitive processes operate at a lower level (remain inactive) but operate normally with ecological testing materials.
 This makes sense if adversity limits energy and/or cognitive resources.

### 2021-07-02 README.Rmd
add a how to reproduce this repo section to README

@@
 This ensures that scripts can reproduce and save output to the correct directory (without having to manually add them).
+
+To reproduce this repository, see [How to reproduce this respository](#repro) below.
 
@@
 The `rmd-staging.R` script reads necessary data/objects from the `multiverse-objects/` directory and sources the other scripts to produce the objects needed for the supplement.
+
+## How to reproduce this repository {#repro}
+
+To reproduce this repository, download all files locally.
+You can do this by cloning the repository or downloading the files directly as a .zip file.
+Because many of the objects are very large (i.e., those containing multiverse data and results), they are not included in this repository.
+However, the scripts will create all necessary outputs to reproduce all data and files.
+Below is the exact order these scripts should be ran:
+
+### 1.  Data Preparation
+
+1. `1-data-prep/1-data-non-arbitrary.R`
+2. `1-data-prep/2-primary-multiverse-datasets.R`
+3. `1-data-prep/3-sedoncary-multiverse-datasets.R`
+
+### 2.  Primary Analyses
+
+1. `2-primary-analyses/1-confirmatory.R`: conducts unpredictability and violence multiverse analyses for attention-shifting and working memory updating.
+2. `2-primary-analyses/1-exploratory.R`: conducts poverty multiverse analyses for attention-shifting and working memory updating.
+3. `2-primary-analyses/1-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting.
+4. `2-primary-analyses/1-bootstrap-setup.R`: sets up bootstrap samples for bootstrapping technique .
+5. `2-primary-analyses/1-bootstrap-spec-analysis.R`: runs specification analyses over all bootstrapped samples to obtain overall *p*-values.
+
+### 3. Secondary Analyses
+
+1. Set 1
+    1. `3-secondary-analyses/set-1/a1-analysis-ses-vio.R`: conducts secondary analysis labeled "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript
+    2.
+`3-secondary-analyses/set-1/a2-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting for the analysis labeld "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript.
+    3.
+`3-secondary-analyses/set-1/b1-analysis-ses-components.R`: conducts an analysis of the components of poverty, which is redundant with the secondary analysis labeled "Exploring Components of Adversity Dimensions", which is conducted below in Set 2.
+    4. `3-secondary-analyses/set-1/b2-extract-effects.R`: extracts effects for poverty component multiverse analyses.
+2. Set 2
+    1.
+`3-secondary-analyses/set-2/a1-analysis-adversity-components.R`: conducts an analysis of the components of all adversity composites for the secondary analysis labeled "Exploring Components of Adversity Dimensions" (this is an expansion of the above secondary analysis for the components of poverty in Set 1)
+    2. `3-secondary-analyses/set-2/a2-extract-effects.R`: extracts effects for adversity component multiverse analyses.
+
+### 4. Manuscript
+
+1.
+`manuscript/scripts/rmd-staging.R`: loads all necessary data and multiverse objects, computes all necessary in-text statistics, and sources the following scripts to create tables and figures for the manuscript stored in `manuscirpt/staged-objects.Rdata`:
+    - `table1.R`
+    - `table2.R`
+    - `table3.R`
+    - `figure2-3.R`
+2. `manuscript/manuscript.Rmd`: loads `manuscript/staged-objects.Rdata` and knits together the written manuscript and all statistics, tables, and figures computed by the staging script above.
+
+### 5. Supplement
+
+1.
+`supplement/scripts/rmd-staging.R`: loads all necessary data and multiverse objects and sources the following scripts to create tables and figures for the supplement stored in `supplement/staged-objects.Rdata`:
+    - `1-covariates.R`
+    - `2-secondary1.R`
+    - `3-secondary2.R`
+    - `4-tables.R`
+2. `supplement/supplement.Rmd`: loads `supplement/staged-objects.Rdata` and knits together the written supplement and all tables and figures computed by the staging script above.

### 2021-07-04 manuscript/manuscript.Rmd
final touches to manuscript

@@
 \noindent Children developing in harsh conditions often perform poorly on standard cognitive tests.
-However, the hidden talents approach proposes that performance for some abilities may be enhanced by adversity or improved under ecologically-relevant conditions.
+However, the hidden talents approach proposes that performance for some abilities may be enhanced by adversity or improved under ecologically relevant conditions.
 We examine ecologically relevant content in cognitive testing.
-Sampling 618 socioeconomically diverse adolescents, we measured performance on two versions of an attention shifting and working memory updating task---one abstract, the other ecological.
+Sampling 618 socioeconomically diverse adolescents, we measured performance on two versions of an attention-shifting and working memory updating task---one abstract, the other ecological.
 Across multiple sources, we measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions using a preregistered multiverse approach.
@@
 
-# Hidden talents in context: Can ecologically-relevant stimuli improve cognitive performance among adversity-exposed youth?
+# Hidden talents in context: Can ecologically relevant stimuli improve cognitive performance among adversity-exposed youth?
 
@@
 In particular, studies have experimentally manipulated the current context to be uncertain and mildly stressful (or not) and measured performance on executive functioning and working memory tasks[@mittal2015; @young2018] (but see[@nweze2021] for similar results without uncertainty).
-Strikingly, people from unpredictable environments showed improved performance on attention shifting and working memory updating tasks.
+Strikingly, people from unpredictable environments showed improved performance on attention-shifting and working memory updating tasks.
 However, this effect only emerged under conditions of uncertainty.
@@
 There were no associations revealed between violence exposures and reasoning performance.
-Overall, this study suggests that ecologically relevant testing materials may level the playing field for adversity-exposed youth[@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
+Overall, this study suggests that ecologically relevant testing materials may "level the playing field" for adversity-exposed youth[@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
 In addition, although executive functions and working memory are related to many educational outcomes, it is unclear how schools and teachers might leverage skills that specifically depend on inducing uncertainty.
@@
 
-Here we address this issue by evaluating the role of ecologically relevant content in attention shifting and working memory tasks.
+Here we address this issue by evaluating the role of ecologically relevant content in attention-shifting and working memory tasks.
 To do so, we sampled `r nrow(data2_non_arbitrary)` adolescents from a socioeconomically diverse population.
@@
 
-# Results
+# Results {#results}
 
-## Overview
+## Overview {#overview}
 
@@
 
-Before conducting analyses, we identified six arbitrary data processing decisions each with two alternatives (see Arbitrary Decisions section).
+Before conducting analyses, we identified six arbitrary data processing decisions each with two alternatives (see [Arbitrary Decisions](#abritrary) section).
 These criteria were 1) including the after-school club sample or not; 2) including participants with minor distractions during testing or not; 3) including participants who missed one trap question or not (those who missed more than 1 were already excluded); 4) including participants receiving special education (participants receiving more \> 60 minutes/day were already excluded) or not; 5) including participants who performed at or below chance levels of accuracy on the attention-shifting task or not (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information); and 6) residualizing social desirability scores out of adversity scores or not.
@@
 Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions.
-For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique[@simonsohn2020; @orben2019; @orben2019a] to compute overall p-values, which indicate whether a $\beta$ of a term is larger than expected given the null (the median $\beta$ = 0; see Statistical Inferences).
+For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique[@simonsohn2020; @orben2019; @orben2019a] to compute overall *p*-values, which indicate whether a $\beta$ of a term is larger than expected given the null (the median $\beta$ = 0; see [Statistical Inferences](#inference)).
 
@@
 Our primary interests were the main effect of adversity and the interaction of adversity with task-version.
-Table \@ref(tab:table2) shows median effect sizes ($\beta$-coefficients), sample sizes, and bootstrapped *p*-values for attention shifting and working memory updating analyses for the main effect of adversity (unpredictability, violence, and poverty) and the interaction term (task version × adversity).
+Table \@ref(tab:table2) shows median effect sizes ($\beta$-coefficients), sample sizes, and bootstrapped *p*-values for attention-shifting and working memory updating analyses for the main effect of adversity (unpredictability, violence, and poverty) and the interaction term (task version × adversity).
 Table \@ref(tab:table3) reports median simple effects of task version across high and low levels of adversity and median simple effects of adversity across abstract and ecologically relevant task versions.
@@
 We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd), including an [updated primary analysis plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
-We conducted secondary analyses after our primary analyses (see Secondary Analyses below).
+We conducted secondary analyses after our primary analyses (see [Secondary Analyses](#secondary) below).
 Before conducting these analyses, we uploaded secondary analysis plans (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd), explaining the goals and purpose of each secondary analysis.
@@
 
-## Primary Analyses
+## Primary Analyses {#primary}
 
-### Attention Shifting
+### Attention Shifting {#primary-shifting}
 
 Across each set of multiverse analyses, there were significant main effects of task version.
-All median effects sizes for task version were $\beta$s = `r c(mod_terms1$shifting.unp.type_z$median_beta, mod_terms1$shifting.vio.type_z$median_beta, mod_terms1$shifting.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for multiverse models testing unpredictability, violence exposure, and poverty exposure, indicating that switch costs were moderately higher for the ecological version compared to the abstract version (see SI Figures 1-3).
+All median effects sizes for task version were $\beta$s = `r c(mod_terms1$shifting.unp.type_z$median_beta, mod_terms1$shifting.vio.type_z$median_beta, mod_terms1$shifting.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for multiverse models testing unpredictability, violence exposure, and poverty exposure, indicating that switch costs (see [Attention Shifting](#shifting) for switch cost explanation) were moderately higher for the ecological version compared to the abstract version (see SI Figures 1-3).
 That is, reaction times on switch trials, compared to repeat trials, were longer when stimuli were ecologically relevant as opposed to abstract.
@@
 (See Table \@ref(tab:table2).) There were no main effects of poverty exposure (median $\beta$ = `r mod_terms2$shifting.ses$median_beta_main`, no *ps* \< .05, overall *p* = `r mod_terms2$shifting.ses$p_overall_main`); see Table \@ref(tab:table2)).
-That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures are associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecologically relevant.
+That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures were associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecologically relevant.
 
@@
 
-### Working Memory Updating
+### Working Memory Updating {#primary-updating}
 
@@
 However, this performance gap closed on the ecological working memory task (violence exposure median *b~ecological~* = `r simple_effects$updating.vio$beta_eco`, no *ps* \< .05; poverty exposure median *b~ecological~* = `r simple_effects$updating.ses$beta_eco`, `r simple_effects$updating.ses$p_percent_eco` of *ps* \< .05).
-Put differently, adolescents exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically-relevant version compared to their own performance on the abstract version (median simple *b~high~ ~violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high~ ~poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas adolescents exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low~ ~violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low~ ~poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
+Put differently, adolescents exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically relevant version compared to their own performance on the abstract version (median simple *b~high~ ~violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high~ ~poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas adolescents exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low~ ~violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low~ ~poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
 In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among adolescents exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
@@
 
-## Secondary Analyses
+## Secondary Analyses {#secondary}
 
@@
 However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures.
-Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure) have unique associations with attention shifting and working memory updating performance.
+Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure; see [Measures](#measures) section) have unique associations with attention shifting and working memory updating performance.
 To address this, we expanded our multiverse approach to include each component of our predictor variables as additional arbitrary decisions.
@@
 
-### Exploring Components of Adversity Dimensions
+### Exploring Components of Adversity Dimensions {#secondary1}
 
-We ran an expanded multiverse analysis to explore the effects of each component of our adversity composites on attention shifting and working memory updating performance.
+We ran an expanded multiverse analysis to explore the effects of each component of our adversity composites (see [Measures](#measures) section) on attention shifting and working memory updating performance.
 Environmental unpredictability contained two components, perceived unpredictability (self-reported) and an interview-based measure tabulating family disruptions, parental figures, and residential moves.
@@
 
-For this expanded multiverse approach, we retained all original data processing decisions (i.e., original 64 combinations of decisions) and added an adversity component as an additional decision.
+For this expanded multiverse approach, we retained all original data processing decisions (i.e., original 64 combinations of decisions) and added adversity component as an additional decision.
 For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures [attention shifting and working memory]).
@@
 
-### Comparing Violence and Poverty Exposure Interactions with Task-Version
+### Comparing Violence and Poverty Exposure Interactions with Task-Version {#secondary2}
 
@@
 In other words, although poverty and violence exposure are theoretically distinct, our poverty composite may capture poverty-related violence exposures (e.g., high poverty neighborhoods contain more crime) and therefore interact with task-version.
-When directly compared, explicit measures of violence exposure remain significant (although only under a small set of analytical decisions), whereas poverty interactions drop out entirely.
+When directly compared, explicit measures of violence exposure remained significant (although only under a small set of analytical decisions), whereas poverty interactions dropped out entirely.
 
-# Discussion
+# Discussion {#discussion}
 
 We examined how ecologically relevant testing materials affect cognitive performance among adversity-exposed youth.
-We measured three dimensions of adversity--- environmental unpredictability, violence exposure, and poverty---and tested performance on attention shifting and working memory updating tasks.
-We administered two versions of each task: one using abstract stimuli and the other using ecologically-relevant stimuli, allowing us to compare performance within- and between-subjects.
+We measured three dimensions of adversity--- environmental unpredictability, violence exposure, and poverty---and tested performance on attention-shifting and working memory updating tasks.
+We administered two versions of each task: one using abstract stimuli and the other using ecologically relevant stimuli, allowing us to compare performance within- and between-subjects.
 
@@
 And, although they improved attention shifting for those exposed to high unpredictability under uncertainty, it remains unclear how this effect relates to those obtained in the current study.
-In addition, Fields and colleages[@fieldsa] found caregiving instability was associated with improved attention shifting, but Nweze and colleagues[@nweze2021] found no association between adversity and attention shifting.
+In addition, Fields and colleagues[@fieldsa] found caregiving instability was associated with improved attention shifting, but Nweze and colleagues[@nweze2021] found no association between adversity and attention shifting.
 However, they tested institutionalized children rather than measuring adversity dimensions[@nweze2021].
@@
 For working memory updating, we found lowered performance among violence- and poverty-exposed youth on the abstract working memory updating task compared to peers with reduced exposures.
-However, ecological materials produced an equalization effect: the updating performance gap between low and high-adversity exposed youth narrowed on the ecological updating task.
+However, ecological materials produced an equalization effect: the updating performance gap between low and high adversity-exposed youth narrowed on the ecological updating task.
 Interestingly, updating performance was unrelated to unpredictability.
@@
 The hidden talents framework has challenged this notion and inspired researchers to document the strengths and abilities of people from adversity.
-Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might even the playing field for adversity-exposed youth.
+Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might "even the playing field" for adversity-exposed youth.
 Theoretically, our data help to refine the hidden talents framework and illuminate future research questions surrounding the unique skills and abilities of people living in harsh conditions.
 
-# Method
+# Method {#method}
 
-## Participants
+## Participants {#participants}
 
@@
 
-## Procedure
+## Procedure {#procedure}
 
@@
 
-## Measures
+## Measures {#measures}
 
-### Attention Shifting
+### Attention Shifting {#shifting}
 
@@
 We removed fast and slow reaction times and removed trials after incorrect responses (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
-We then subtracted the average reaction time on valid switch trials from the average reaction time on valid repeat trials to calculate switch cost scores.
+We then subtracted the average reaction time on valid repeat trials from the average reaction time on valid switch trials to calculate switch cost scores (*M~switch~* - *M~repeat~*).
 The switch cost measures the relative delay in reaction time caused by switching between categorization rules.
@@
 
-### Working Memory Updating
+### Working Memory Updating {#updating}
 
@@
 The participant must keep track of each shape, updating counts as new shapes appeared, and report them at the end of the sequence.
-The ecological version followed the same format, but participants kept running counts of three different real-world objects (see Figure \@ref(fig:figure1)d): one positive (five-dollar bill), negative (angry face), and neutral (Salt Lake City bus).
+The ecological version followed the same format, but participants kept running counts of three different real-world objects (see Figure \@ref(fig:figure1)d): one positive (five-dollar bill), one negative (angry face), and one neutral (Salt Lake City bus).
 
@@
 
-### Environmental Unpredictability
+### Environmental Unpredictability {#unp}
 
@@
 
-### Violence Exposure.
+### Violence Exposure {#vio}
 
@@
 
-### Poverty Exposure
+### Poverty Exposure {#poverty}
 
@@
 
-### Control Variables
+### Control Variables {#controls}
 
@@
 
-## Multiverse Setup
+## Multiverse Setup {#multiverse}
 
@@
 
-### Arbitrary Decisions.
+### Arbitrary Decisions {#abritrary}
 
@@
 
-### Statistical Inferences.
+### Statistical Inferences {#inference}
 
@@
 
-For the current study, we calculated overall p-values for the main effect of adversity and the interaction effects (task version × adversity) of our primary analyses.
+For the current study, we calculated overall *p*-values for the main effect of adversity and the interaction effects (task version × adversity) of our primary analyses.
 To do so, we created 'null' attention-shifting and working memory updating scores[@simonsohn2020].
@@
 Upon completion, we compared the median effects for each bootstrapped sample (500 median effect sizes) with our original median effects.
-To compute overall p-values, we divided the number of effect sizes obtained from the bootstrapped multiverse analyses that were larger than our original median effect sizes by the total number of bootstrapped samples.
+To compute overall *p*-values, we divided the number of effect sizes obtained from the bootstrapped multiverse analyses that were larger than our original median effect sizes by the total number of bootstrapped samples.
 Importantly, we ran this procedure separately for each measure of adversity (unpredictability, violence exposure, and poverty exposure), outcome (attention shifting and working memory updating), and effect of interest (main effect or interaction effect) combination.
@@
 
-# References
+# References {#refs}

### 2021-07-13 manuscript/manuscript.Rmd
add a statement about two-sided p-values

@@
 To facilitate interpretation of multiverse results, we report median standardized $\beta$s, median 95% confidence intervals, and percent significant for each term in our model (see Table \@ref(tab:table2)).
-Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions.
+Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect (two-sided *p*-value < .05) for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions.
 For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique[@simonsohn2020; @orben2019; @orben2019a] to compute overall *p*-values, which indicate whether a $\beta$ of a term is larger than expected given the null (the median $\beta$ = 0; see [Statistical Inferences](#inference)).

### 2021-09-27 manuscript/manuscript.Rmd
update repo for Child Development

--- 2021-07-04 manuscript/manuscript.Rmd
@@
     keep_tex: true
-    extra_dependencies: ["booktabs","caption","longtable","float"]
+    extra_dependencies: ["booktabs","longtable"]
 geometry: margin=1in
 mainfont: Times
-fontsize: 11pt
+fontsize: 12pt
 endnote: no
@@
 header-includes:
+- \usepackage{float}
 - \usepackage{siunitx}
@@
 - \setlength{\parskip}{0em}
-- \linespread{1.5}
+- \linespread{2}
 - \usepackage{titlesec}
-- \titleformat{\section}[block]{\normalsize\bfseries\filcenter}{}{1em}{}
-- \titleformat{\subsubsection}[block]{\bfseries\itshape}{}{1em}{}
+- \titleformat{\section}[block]{\normalsize\bfseries\filcenter}{}{}{}
+- \titleformat{\subsection}[block]{\normalsize\bfseries}{}{}{}
+- \titleformat{\subsubsection}[block]{\bfseries\itshape}{}{}{}
+- \titlespacing{\section}{0pt}{0pt}{0pt}
+- \titlespacing{\subsection}{0pt}{0pt}{0pt}
+- \titlespacing{\subsubsection}{0pt}{0pt}{0pt}
 - \usepackage{indentfirst}
@@
 - \usepackage{caption}
+- \usepackage{setspace}
 - \captionsetup[table]{labelfont={bf},labelformat={default}, labelsep={newline}}
@@
 - \usepackage{lineno}
-- \linenumbers
 bibliography: references.bib
-csl: nature.csl
+csl: apa.csl
 ---
@@
   fig.align = "center",
-  fig.pos = "!",  
+  fig.pos = "!t", 
+  out.extra = "",
   fig.show = "asis",
@@
 
-\noindent Children developing in harsh conditions often perform poorly on standard cognitive tests.
-However, the hidden talents approach proposes that performance for some abilities may be enhanced by adversity or improved under ecologically relevant conditions.
-We examine ecologically relevant content in cognitive testing.
-Sampling 618 socioeconomically diverse adolescents, we measured performance on two versions of an attention-shifting and working memory updating task---one abstract, the other ecological.
-Across multiple sources, we measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions using a preregistered multiverse approach.
-We did not find adversity × task version interactions for attention shifting, but there were main effects of unpredictability and violence, indicating improved attention shifting irrespective of task version.
-For working memory updating, violence- and poverty-exposed youth performed worse on the abstract but not the ecological version, equalizing performance among adversity-exposed youth.
-We found no relation between updating performance and unpredictability.
+\noindent Adversity-exposed youth often perform poorly on standard cognitive tests.
+However, the hidden talents approach proposes some abilities are enhanced by adversity, especially under ecologically relevant conditions.
+Sampling 618 adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r (txt1_sam$non_arb$race$non_white/txt1_sam$non_arb$n$total * 100) %>% round(2)`% non-White), we administered two versions of an attention shifting and working memory updating task—one abstract, one ecological.
+We measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions.
+There were no interactions for attention shifting, but there were main effects of unpredictability and violence, indicating improved attention shifting, on average.
+For working memory updating, violence- and poverty-exposed youth performed worse on the abstract but not the ecological version, equalizing performance.
+We found no relation between updating and unpredictability.
 
@@
 Children living in harsh conditions tend to perform poorly on many cognitive tests.
-For example, children raised in poverty often show difficulties learning in school and score lower on standardized tests[@ursache2016a; @farah2006; @noble2007; @hackman2010].
-Harsh and unpredictable environments are thought to cause high levels of chronic stress, which impacts brain regions responsible for memory and learning[@blair2012].
-Thus, the general consensus is that exposure to adversity undermines cognitive development and leads to a host of cognitive impairments[@hackman2010].
+For example, children raised in poverty often show difficulties learning in school and score lower on standardized tests [@ursache2016a; @farah2006; @noble2007; @hackman2010].
+Harsh and unpredictable environments are thought to cause high levels of chronic stress, which impacts brain regions responsible for memory and learning [@blair2012].
+Thus, the general consensus is that exposure to adversity undermines cognitive development and leads to a host of cognitive impairments [@hackman2010].
 Although it is clear that harsh environments are harmful to children, there is growing interest in the *hidden talents* *approach*, which proposes that some abilities may be enhanced by adversity, especially those abilities that are ecologically relevant to lived experience.
-Thus, hidden talents are skills and abilities that help children meet real-world challenges in adverse environments[@ellis2017; @ellis2020; @frankenhuis2013; @frankenhuis2020].
+Thus, hidden talents are skills and abilities that help children meet real-world challenges in adverse environments [@ellis2017; @ellis2020; @frankenhuis2013; @frankenhuis2020].
 
-The hidden talents framework assumes that development shapes the skills and abilities of individuals in relation to their environment[@ellis2017; @ellis2020; @frankenhuis2013; @frankenhuis2020].
+The hidden talents framework assumes that development shapes the skills and abilities of individuals in relation to their environment [@ellis2017; @ellis2020; @frankenhuis2013; @frankenhuis2020].
 Accordingly, exposure to adversity should shape skills and abilities well-suited for dealing with the challenges associated with harsh environments.
-However, because specific dimensions of adversity (violence versus resource-scarcity) may pose unique challenges[@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity[@frankenhuis2020].
-For instance, physically abused children can detect angry facial expressions quickly and accurately[@gibb2009; @pollak2008; @pollak2009], people living in poverty have shown some evidence of enhanced social perception[@piff2018], and anxiously attached people are good at deception detection[@eindor2014; @shoda2013] (see[@ellis2017; @ellis2020] for reviews).
+However, because specific dimensions of adversity (violence versus resource-scarcity) may pose unique challenges [@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity [@frankenhuis2020].
+For instance, physically abused children can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], people living in poverty have shown some evidence of enhanced social perception [@piff2018], and anxiously attached people are good at deception detection [@eindor2014; @shoda2013] to list a few examples [see @ellis2017; @ellis2020 for reviews].
 
@@
 For example, previous studies of hidden talents have tested cognition under ecologically relevant *contexts and situations*.
-In particular, studies have experimentally manipulated the current context to be uncertain and mildly stressful (or not) and measured performance on executive functioning and working memory tasks[@mittal2015; @young2018] (but see[@nweze2021] for similar results without uncertainty).
+In particular, studies have experimentally manipulated the current context to be uncertain and mildly stressful (or not) and measured performance on executive functioning and working memory tasks [@mittal2015; @young2018; but see @nweze2021 for similar results without uncertainty].
 Strikingly, people from unpredictable environments showed improved performance on attention-shifting and working memory updating tasks.
@@
 Cultural psychologists and anthropologists have demonstrated this fact across the world.
-For example, people from low income and non-western cultures tend to perform worse on standard versions of cognitive tests, but this performance gap closes or disappears with more ecologically relevant versions of the same tests[@banerjee2017; @greenfield2014; @ogbu1981; @richardson1991; @schliemann2002].
+For example, people from low income and non-western cultures tend to perform worse on standard versions of cognitive tests, but this performance gap closes or disappears with more ecologically relevant versions of the same tests [@banerjee2017; @greenfield2014; @ogbu1981; @richardson1991; @schliemann2002].
 These findings pose an important question: Can ecologically relevant testing materials improve cognitive performance among adversity-exposed youth?
@@
 One way to test this question is to simply replace sterile testing materials with ecologically relevant content.
-For example, one study tested memory and reasoning among young adults who varied in their exposures to violence[@frankenhuis2020a].
+For example, one study tested memory and reasoning among young adults who varied in their exposures to violence [@frankenhuis2020a].
 They created two versions of a memory and reasoning task, one neutral (chronological age) and one more ecologically relevant (social dominance).
@@
 There were no associations revealed between violence exposures and reasoning performance.
-Overall, this study suggests that ecologically relevant testing materials may "level the playing field" for adversity-exposed youth[@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
+Overall, this study suggests that ecologically relevant testing materials may "level the playing field" for adversity-exposed youth [@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
 In addition, although executive functions and working memory are related to many educational outcomes, it is unclear how schools and teachers might leverage skills that specifically depend on inducing uncertainty.
@@
 
-We also evaluated the relative robustness of our models to arbitrary data processing decisions using a multiverse analysis approach[@steegen2016; @simonsohn2020].
+We also evaluated the relative robustness of our models to arbitrary data processing decisions using a multiverse analysis approach [@steegen2016; @simonsohn2020].
 Specifically, we systematically and explicitly generated all possible combinations of (arbitrary) data processing decisions and analyzed them simultaneously.
@@
 
+# Method {#method}
+
+## Participants {#participants}
+
+The current study collected data from `r txt1_sam$raw$n$total` adolescents (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah.
+The first was a middle school and the second were 5 after-school clubs.
+The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse (`r (txt1_sam$raw$race$non_white/txt1_sam$raw$n$total * 100) %>% round(2)`% non-White; `r (txt1_sam$raw$race$hispanic/txt1_sam$raw$n$total * 100) %>% round(2)`% Hispanic).
+According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers).
+The clubs (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`).
+`r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch and were also ethnically diverse.
+
+We aggregated data from both sources and applied a set of five exclusion criteria.
+We applied these criteria before inspecting or testing any relations between predictors and outcomes.
+Specifically, we excluded participants: 1) with incomplete cognitive task data, 2) with apparent cognitive impairments (e.g., head injuries, disabilities, drug use), 3) who missed two or more trap questions, 4) exposed to extreme distractions during the assessment, and 5) who received more than 60 minutes per day of special education services.
+After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).
+
+## Procedure {#procedure}
+
+Data collection involved six parts: consent/assent, demographics form, cognitive testing, structured interview, questionnaire, and a debriefing.
+Consent was obtained from the primary parent or guardian before assessments and assent was obtained from the participant at the beginning of the session.
+On the demographics form, participants indicated if they were left-handed, their birthdate, and their racial and ethnic background.
+
+Cognitive testing included abstract (i.e., standard) and ecological versions of an attention-shifting and working memory updating task.
+Task order (shifting versus updating) and version (abstract versus ecological) were counterbalanced across participants.
+Some participants started with the attention shifting and then moved to the updating tasks.
+For those starting with the shifting (or updating) tasks, some started with the abstract version and then completed the ecological version (and vice versa).
+Regardless of which task was first, participants always completed both versions of one task before moving to the other task.
+
+The interview contained two parts.
+The first part was about participants' home and family life, such as their family composition, the number of adults in the household, and occupation and education information about caregivers.
+Participants also reported on the number of romantic partners their caregivers had and if these partners lived with the participant.
+The second part was about residential mobility.
+Participants listed all the homes they lived in from birth to age 13.
+For each home, they reported at which ages they lived in the home.
+If they moved, they also reported any changes in their family structure (loss or gain of adults in the home), social network (e.g., a new school), and/or town or city.
+
+The questionnaire contained measures focused on the childhood environment.
+The measures included perceived unpredictability in the home, exposure to neighborhood violence, access to material resources, direct exposure to violence and fighting, and a child version of socially desirable responding.
+
+Procedures across the middle school and after-school clubs were the same, with a few minor differences.
+First, participants in the clubs completed the tasks before the interview, but the opposite occurred in the middle school.
+The second was that, in the middle school, the questionnaire was completed in a separate session.
+Whereas the tasks and interview were completed in a small room, alone with the interviewer, the questionnaire was completed approximately two weeks later in a mass testing context (large computer room).
+This was done because the middle school was on a strict class schedule, which limited the length of individual sessions.
+In the clubs, sessions were conducted in the summer during flexible hours.
+
+## Measures {#measures}
+
+### Attention Shifting {#shifting}
+
+We measured attention shifting with two versions of the color--shape task [@mittal2015; @miyake2012; @friedman2008], which involves categorizing stimuli according to one of two rules (see below).
+On each trial, the rule is displayed on the top of the screen.
+Using arrow keys, participants categorized the stimulus as quickly and accurately as possible.
+Response options appeared at the bottom of the screen (see Figure \@ref(fig:figure1)).
+
+On the abstract (standard) attention-shifting task, participants categorized colored (blue or yellow) shapes (squares or triangles) according to the 'color' or 'shape' rule (see Figure \@ref(fig:figure1)a).
+For example, if a blue triangle appeared on the screen and the rule was "color", participants categorized the blue triangle as blue.
+However, if the rule was "shape", participants instead categorized the blue triangle as a triangle.
+
+The ecological attention-shifting task replaced shapes and colors with faces (see Figure \@ref(fig:figure1)b).
+Faces were either male or female (gender), and were happy or angry (emotion).
+If a happy female face appeared on screen and the rule was 'gender', for example, participants categorized the face as female.
+If the rule was 'emotion', participants instead categorized the face as happy.
+The stimuli for the ecological attention-shifting task were selected from the NimStim library [@tottenham2009].
+The same female and male models were used for happy and angry expressions.
+
+For both versions, there were two types of trials: repeat and switch.
+Repeat trials use the same rule as the previous trial.
+If the current and previous rule is 'color', for instance, the current trial is a repeat trial.
+Switch trials are trials where the rule changes from the previous trial.
+If the current rule is 'color' but the previous was 'shape' (or vice versa), the current trial is a switch trial.
+
+Accuracy on attention-shifting tasks is normally high, and was in the current sample for both versions (*M~standard~* = `r (txt2_dvs$abs_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~standard~* = `r (txt2_dvs$abs_shifting_correct$sd/32 * 100) %>% round(2)`%; *M~ecological~* = `r (txt2_dvs$eco_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~ecological~* = `r (txt2_dvs$eco_shifting_correct$sd/32 * 100) %>% round(2)`%).Thus, instead of accuracy, attention-shifting ability is measured by comparing reaction times on repeat trials to switch trials.
+Reaction times on repeat trials are normally faster than switch trials; average repeat trial reaction times on the abstract and ecological versions were `r txt2_dvs$abs_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_re_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_re_rt$sd` *ms*), respectively.
+On switch trials, average reaction times were `r txt2_dvs$abs_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sw_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sw_rt$sd` *ms*) on the standard and ecological versions.
+
+To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000].
+We removed fast and slow reaction times and removed trials after incorrect responses (see [attention shifting data cleaning procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
+We then subtracted the average reaction time on valid repeat trials from the average reaction time on valid switch trials to calculate switch cost scores (*M~switch~* - *M~repeat~*).
+The switch cost measures the relative delay in reaction time caused by switching between categorization rules.
+Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` ms (*SD* = `r txt2_dvs$eco_shifting_sc$sd` ms), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`).
+Higher switch costs mean longer reaction times on switch trials compared to repeat trials.
+Larger switch costs indicate less efficient attention shifting.
+
+### Working Memory Updating {#updating}
+
+Working memory updating was measured using two versions of the continuous counters task [@unsworth2015; @unsworth2008; @young2018], in which participants track a sequence of stimuli containing three different objects (see Figure \@ref(fig:figure1)).
+Participants keep running counts of each object in sequences nine items long.
+Each object was displayed for one second at a time.
+At the end of each sequence, participants reported the number of times each object appeared.
+For each round, there were three possible correct answers, one for each object type.
+
+In the abstract (standard) version, participants kept running counts of squares, circles, and triangles (see Figure \@ref(fig:figure1)c).
+The participant must keep track of each shape, updating counts as new shapes appeared, and report them at the end of the sequence.
+The ecological version followed the same format, but participants kept running counts of three different real-world objects (see Figure \@ref(fig:figure1)d): one positive (five-dollar bill), one negative (angry face), and one neutral (Salt Lake City bus).
+
+Participants completed five rounds of both versions.
+The maximum score was 15 for each version (five rounds × three possible correct).
+On the abstract and ecological versions, participants averaged `r txt2_dvs$abs_updating$mean * 15` (*SD* = `r txt2_dvs$abs_updating$sd * 15`) and `r txt2_dvs$eco_updating$mean * 15` (*SD* = `r txt2_dvs$eco_updating$sd * 15`), respectively (*r* = `r txt5_cor$updating$r`).
+Higher scores indicate better working memory updating performance.
+
+### Environmental Unpredictability {#unp}
+
+Our measure of environmental unpredictability integrated information from the interview and questionnaire.
+The interview contained three variables of interest.
+The first measured the level of exposure to living in a biologically non-intact family from birth to age 13.
+Interviewers asked participants about their family composition and the adults that lived with them in the home.
+If a participant's family composition changed, for example, because of a divorce, interviewers recorded the ages when participants experienced the change and for how long it persisted.
+A family was considered non-intact if the participant did not live with both biological parents during any period from birth to age 13.
+Based on the earliest age of disruption, we indexed the onset of exposure to a non-intact family by creating a four-level variable from 0 to 3.
+A 0 indicated the participant lived in an intact family (lived with both biological parents) from birth until age 13 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 0) %>% sum(na.rm=T)`); a 1 indicated that a disruption occurred after the age of 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 1) %>% sum(na.rm=T)`); a 2 indicated that a disruption occurred before age 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 2) %>% sum(na.rm=T)`); and a 3 indicated the participant was born into a non-intact family (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 3) %>% sum(na.rm=T)`).
+`r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T)`.
+`r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T) %>% english::as.english() %>% str_to_title()` participants had missing information.
+
+The second interview variable tabulated the number of different parental figures (defined as spouses or boyfriends/girlfriends of the participant's mother and father) who lived in the same home with the participant.
+Trained interviewers tabulated the total number of co-residing parental figures, excluding the participant's biological mother and father (*M* = `r txt3_ivs$unp_interview_figures$mean`, *SD* = `r txt3_ivs$unp_interview_figures$sd`).
+
+The third interview variable focused on residential changes from birth to age 13 (reported retrospectively).
+Specifically, interviewers probed participants about the number of different homes they lived in and, in particular, whether moving to a new home involved living with new or different adults.
+On average, participants experienced `r txt3_ivs$unp_interview_moves$mean` (*SD* = `r txt3_ivs$unp_interview_moves$sd`) moves that involved changes in residential adults.
+
+The questionnaire included a measure of perceived childhood unpredictability [@mittal2015; @young2018; @szepsenwol2015].
+Participants responded to six items that assessed exposure to unpredictability up to age 13: 1) "Things were pretty calm and stable in my house" (reversed); 2) "People moved in and out of my house a lot"; 3) "I had a hard time knowing what my parent(s) or other people in my house were going to say or do from day-to-day"; 4) "My parent(s) argued or fought a lot with each other or with other people"; 5) "My parent(s) changed jobs a lot"; 6) "My parental situation changed a lot (for example, divorce or separation of parents, parents starting new romantic relationships, parents leaving the home)".
+Participants rated each item on a scale from 1 (never true) to 5 (very often true).
+Responses to these items were averaged to create a self-reported perceived childhood unpredictability measure (*M* = `r txt3_ivs$unp_perceived$mean`, *SD* = `r txt3_ivs$unp_perceived$sd`, $\alpha$ = `r txt4_rel$unp`).
+Higher scores indicated more perceived exposure to unpredictable environments.
+
+To create a composite measure of unpredictability, we aggregated across the interview and questionnaire.
+First, we created an interview-based measure of unpredictability using family disruptions, exposure to different parental figures, and residential moves involving new adults living in the home.
+We standardized these interview measures and then averaged them together ($\alpha$ = `r txt4_rel$unp_int`).
+We then aggregated this interview measure with self-reported perceived unpredictability from the questionnaire, standardizing each before averaging (*r* = `r txt5_cor$unp$r`).
+Higher scores indicated more exposure to unpredictability.
+
+### Violence Exposure {#vio}
+
+We measured violence exposure using the Neighborhood Violence Scale [NVS, @frankenhuis2020a; @frankenhuis2018] and two items about witnessing and involvement in physical fights.
+The NVS contains 7 items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm".
+The physical fighting items asked about witnessing fights: "Based on your experiences at school and in your neighborhood, how many times did you see or hear someone being beaten up in real life?"; and involvement in fights: "How many times were you in a physical fight at school or in your neighborhood?".
+Both items were rated on a scale from 1 (0 times) to 8 (12 or more times).
+
+Responses on the NVS were averaged to create a composite measure (*M* = `r txt3_ivs$vio_neighborhood$mean`, *SD* = `r txt3_ivs$vio_neighborhood$sd`, $\alpha$ = `r txt4_rel$vio`).
+Likewise, the two fighting were averaged together (*M* = `r txt3_ivs$vio_fighting$mean`, *SD* = `r txt3_ivs$vio_fighting$sd`).
+To create a violence exposure composite, the NVS composite and fighting composite were standardized and then averaged (*r* = `r txt5_cor$vio$r`).
+Higher scores indicated more exposure to violence.
+
+### Poverty Exposure {#poverty}
+
+We assessed each participant's poverty exposure using three information sources: interview-assessed parent education and occupational prestige, school or club-provided economic information, and perceived resource scarcity.
+
+During the interview, participants reported their parents' education and primary occupation.
+For parental education level, participants reported whether their mother and father graduated high school, went to college, and if they obtained a bachelor's degree or higher.
+Responses to each question were coded as 0 = 'no' and 1 = 'yes'.
+These items were summed to create a four-level variable for each parent where 0 = did not graduate high school, 1 = graduated high school but did not attend any college, 2 = graduated high school and completed some college, and 3 = went to college and obtained a bachelor's degree or higher.
+Mother and father education were averaged to create a parental education score (*M* = `r txt3_ivs$ses_interview_edu$mean`, *SD* = `r txt3_ivs$ses_interview_edu$sd`).
+
+Participants also reported their parents' occupation.
+Participants described, in general terms, their mother's and father's jobs and the kind of work involved.
+Trained coders cross-referenced these descriptions with 2010 census job codes [@hout2018].
+We calculated mother and father occupational prestige by matching census codes with prestige ratings from an established occupational prestige rating dataset [@hout2016].
+Prestige codes ranged from 0-100, with higher scores indicating higher occupational prestige for a particular job code.
+Mother and father prestige codes were averaged to create a parent occupational prestige score (*M* = `r txt3_ivs$ses_interview_occup$mean`, *SD* = `r txt3_ivs$ses_interview_occup$sd`).
+
+We also obtained school or club-provided economic information.
+The middle school provided four information sources: 1) whether or not students were receiving free lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_frl == 1) %>% sum(na.rm=T)`); 2) whether or not they were receiving reduced-price lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_rel == 1) %>% sum(na.rm=T)`); 3) whether they were receiving fee waivers (*n* = `r (data2_non_arbitrary$ses_school_wjms_fee == 1) %>% sum(na.rm=T)`); and 4) if they were experiencing homelessness (*n* = `r (data2_non_arbitrary$ses_school_wjms_hom == 1) %>% sum(na.rm=T)`).
+These information sources were compiled to create a binary economic disadvantage variable.
+A participant was economically disadvantaged if they were receiving any benefits or experiencing homelessness (*n* = `r txt1_sam$non_arb$free_lunch$wjms`).
+In the afterschool clubs, free or reduced-price lunch status was provided by self-report, staff, and club enrollment forms and cross-referenced to determine economic disadvantage in the clubs (*n* = `r txt1_sam$non_arb$free_lunch$bgc`).
+Overall, `r (data2_non_arbitrary$ses_school_freelunch == 1) %>% sum(na.rm=T)` participants were receiving economic assistance, `r (data2_non_arbitrary$ses_school_freelunch == 0) %>% sum(na.rm=T)` were not, and `r sum(is.na(data2_non_arbitrary$ses_school_freelunch))` had missing economic information.
+
+Participants also reported their perceived level of resource scarcity.
+They rated seven items from 1 (never true) to 5 (very often true): 1) "Your family had enough money to afford the kind of home you all needed"; "Your family had enough money to afford the kind of clothing you all needed"; 3) "Your family had enough money to afford the kind of food that you all needed"; 4) "Your family had enough money to afford the kind of medical care that you all needed"; 5) "I felt well-off (rich, wealthy) compared to other kids in my school"; 6) "I felt well-off (rich, wealthy) compared to other kids in my neighborhood"; and 7) "Your family struggled to make ends meet (get by financially)".
+The first six items were reversed, and all items were averaged to create a perceived resource scarcity measure (*M* = `r txt3_ivs$ses_perceived$mean`, *SD* = `r txt3_ivs$ses_perceived$sd`, $\alpha$ = `r txt4_rel$ses`).
+Higher scores indicated more perceived resource scarcity.
+
+To create a poverty exposure composite, we combined parent education and occupational prestige (reversed), school/club reported economic disadvantage, and perceived resource scarcity.
+First, we standardized and averaged parent education and occupation (*r* = `r txt5_cor$edu_int$r`).
+Then, we recoded school-provided economic codes to be equal to half of a standard deviation above and below the mean (in terms of z-scores).
+Specifically, those receiving free or reduced-price lunch were coded as .5, and those who were not were coded as -.5.
+To create a final composite, we averaged parent education/occupation (standardized), perceived resource scarcity (standardized), and the recoded school/club economic disadvantage.
+Higher values indicated more exposure to poverty.
+
+### Control Variables {#controls}
+
+We included two control variables: age and interviewer-rated distractions during testing.
+We included these because older adolescents tend to score higher on cognitive tests than younger adolescents [@best2010; @best2011; @huizinga2006], and disruptions during the tasks could negatively impact performance.
+Interviewers completed quantitative ratings of the testing environment including 1) the level of noise; 2) the level of chaos; 3) how often there were interruptions; and 4) how often the participant appeared distracted.
+Interviewers rated each item on a scale from 1 (not at all) to 7 (much more than average).
+Items were averaged to create a composite (*M* = `r txt3_ivs$test_envr$mean`, *SD* = `r txt3_ivs$test_envr$sd`), where higher scores indicate more distractions.
+
+We also included the Child Social Desirability (CSD) scale [@miller2014].
+The measure includes 14 items such as "Have you ever broken a rule?" and "Do you sometimes feel angry when you don't get your way?".
+Participants indicated 1 (yes) or 0 (no) for each item.
+More socially desirable responses were scored as 1.
+Items were then summed to create a social desirability index (*M* = `r txt3_ivs$csd$mean`, *SD* = `r txt3_ivs$csd$sd` , $\alpha$ = `r txt4_rel$csd`).
+
 # Results {#results}
 
-## Overview {#overview}
+## Data Analysis Strategy {#multiverse}
+
+We used a multiverse analysis approach for all analyses to systematically evaluate the robustness (or sensitivity) of analyses across all arbitrary data processing decisions [see  @simonsohn2020; @steegen2016 for details].
+We identified six arbitrary data processing decisions.
+First, we conducted analyses with and without the after-school club sample.
+We did this because our procedure was slightly different across the two samples and the testing environment was more disruptive in the clubs compared with the middle school.
+Second, we conducted analyses with and without participants with minor distractions during testing.
+Third, we analyzed the data with and without participants who missed one trap question (those who missed more than 1 were already excluded).
+Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded).
+Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [attention shifting data cleaning procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
+
+Our last arbitrary data processing decision pertained to socially desirable responses.
+It is well-known that some youth tend to describe themselves in socially desirable ways.
+This raises concerns about the validity of self-reported childhood adversity measures: youth scoring higher on social desirability might underreport or underrate their exposures to negative experiences.
+Indeed, scores on the CSD were correlated with exposures to unpredictability (*r* = `r txt5_cor$csd_unp$r`) and violence (*r* = `r txt5_cor$csd_vio$r`), though not with poverty.
+One way to handle this issue is to statistically remove overlapping variance between social desirability and each predictor, using the leftover variance (e.g., the residual variance in childhood adversity exposures not associated with social desirability) as a predictor.
+Because it is unclear how social desirability might affect the interpretation of our models, we analyzed our data with residualized and non-residualized predictors.
 
@@
 We ran separate analyses for each adversity dimension and outcome combination.
-
-Before conducting analyses, we identified six arbitrary data processing decisions each with two alternatives (see [Arbitrary Decisions](#abritrary) section).
-These criteria were 1) including the after-school club sample or not; 2) including participants with minor distractions during testing or not; 3) including participants who missed one trap question or not (those who missed more than 1 were already excluded); 4) including participants receiving special education (participants receiving more \> 60 minutes/day were already excluded) or not; 5) including participants who performed at or below chance levels of accuracy on the attention-shifting task or not (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information); and 6) residualizing social desirability scores out of adversity scores or not.
 Using all possible combinations of arbitrary decisions, we constructed a multiverse of `r length(multi_data_list)` datasets.
@@
 We ran the same underlying mixed-effects linear regression model.
-Analyses were conducted using R[@rcoreteam2020] and mixed models were fit using the lme4 package[@bates2015].
+Analyses were conducted using R [@rcoreteam2020] and mixed models were fit using the lme4 package [@bates2015].
 Our mixed-effects models included five fixed terms: the main effect of task version (ecological or abstract version, within-subjects), the main effect of childhood adversity (between-subjects), the interaction between task version and adversity exposure, the main effect of age (control variable), and the main effect of test distraction ratings (control variable).
@@
 To facilitate interpretation of multiverse results, we report median standardized $\beta$s, median 95% confidence intervals, and percent significant for each term in our model (see Table \@ref(tab:table2)).
-Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions.
-For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique[@simonsohn2020; @orben2019; @orben2019a] to compute overall *p*-values, which indicate whether a $\beta$ of a term is larger than expected given the null (the median $\beta$ = 0; see [Statistical Inferences](#inference)).
+Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect (two-sided *p*-value \< .05) for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions.
+For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique to compute overall *p*-values.
+The technique makes it possible to know if a multiverse analysis produced a median effect size larger than expected, given the null hypothesis that the median $\beta$ = 0 [see @simonsohn2020 for details].
 
@@
 
-```{r table1}
+```{r table1, results='asis'}
 table.01.0 %>% 
@@
     escape = F,
-    caption = "\\emph{Bivariate correlations and descriptive statistics for all measures of adversity and their subcomponents.}"
+    caption = "\\emph{Bivariate correlations and descriptive statistics for measures of adversity and their components.}"
   ) %>% 
   add_header_above(c(" ","Unpredictability" = 3, "Violence" = 3, "Poverty" = 4)) %>% 
-  kable_styling(latex_options = "scale_down") %>% 
+  kable_styling(latex_options = c("scale_down", "hold_position")) %>% 
   footnote(
@@
 
-Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction -coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).
+Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction $\beta$-coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).
 
-We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd), including an [updated primary analysis plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
+We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), including an [updated primary analysis plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
 We conducted secondary analyses after our primary analyses (see [Secondary Analyses](#secondary) below).
-Before conducting these analyses, we uploaded secondary analysis plans (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd), explaining the goals and purpose of each secondary analysis.
-A Red Team Critic[@market] successfully reproduced and verified (see this [red team report](https://osf.io/xv94z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)) all analyses prior to submission.
+Before conducting these analyses, we uploaded secondary analysis plans (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), explaining the goals and purpose of each secondary analysis.
+A Red Team Critic [@redteammarket2021] successfully reproduced and verified (see this [red team report](https://osf.io/xv94z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)) all analyses prior to submission.
 
@@
 
-```{r figure2, fig.height=7.5, fig.width=6.5, fig.cap='(ref:figure2)'}
+```{r figure2, fig.height=7.25, fig.width=6.25, fig.cap='(ref:figure2)'}
 fig2
@@
 
-```{r table2}
+```{r table2, results='asis'}
 table.02.0 %>% 
@@
     general_title = "Note:", 
-    footnote_as_chunk = F,
+    footnote_as_chunk = T,
     title_format = "italic",
@@
 However, this performance gap closed on the ecological working memory task (violence exposure median *b~ecological~* = `r simple_effects$updating.vio$beta_eco`, no *ps* \< .05; poverty exposure median *b~ecological~* = `r simple_effects$updating.ses$beta_eco`, `r simple_effects$updating.ses$p_percent_eco` of *ps* \< .05).
-Put differently, adolescents exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically relevant version compared to their own performance on the abstract version (median simple *b~high~ ~violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high~ ~poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas adolescents exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low~ ~violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low~ ~poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
+Put differently, adolescents exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically relevant version compared to their own performance on the abstract version (median simple *b~highviolence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~highpoverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas adolescents exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~lowviolence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~lowpoverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
 In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among adolescents exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
@@
 Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
-Proportions of each arbitrary decision with *p*-values < .05 are indicated on the right side of each specification grid.
+Proportions of each arbitrary decision with *p*-values \< .05 are indicated on the right side of each specification grid.
 Blank proportions indicate proportions = 0.
 
-```{r figure3, fig.height=7.5, fig.width=6.5, fig.cap='(ref:figure3)'}
+```{r figure3, fig.height=7.25, fig.width=6.25, fig.cap='(ref:figure3)'}
 fig3
@@
 These analyses focused on two questions.
-First, in contrast to prior work[@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting).
+First, in contrast to prior work [@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting).
 However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures.
@@
 
-Leveraging multiverse analysis[@simonsohn2020; @steegen2016], we tested interactions between dimensions of adversity and task version on attention shifting and working memory updating performance.
+Leveraging multiverse analysis [@simonsohn2020; @steegen2016], we tested interactions between dimensions of adversity and task version on attention shifting and working memory updating performance.
 We did not find interaction effects for attention shifting.
 However, youth exposed to unpredictability and violence showed smaller switch costs on average, suggesting slightly improved attention shifting performance irrespective of task content.
-These findings partially diverge from prior work[@mittal2015; @nweze2021].
-For example, whereas we found unpredictability was associated with improved attention shifting on average, Mittal and colleagues[@mittal2015] found no difference in performance under neutral conditions.
+These findings partially diverge from prior work [@mittal2015; @nweze2021].
+For example, whereas we found unpredictability was associated with improved attention shifting on average, Mittal and colleagues [-@mittal2015] found no difference in performance under neutral conditions.
 And, although they improved attention shifting for those exposed to high unpredictability under uncertainty, it remains unclear how this effect relates to those obtained in the current study.
-In addition, Fields and colleagues[@fieldsa] found caregiving instability was associated with improved attention shifting, but Nweze and colleagues[@nweze2021] found no association between adversity and attention shifting.
-However, they tested institutionalized children rather than measuring adversity dimensions[@nweze2021].
+In addition, Fields and colleagues [-@fields2021] found caregiving instability was associated with improved attention shifting, but Nweze and colleagues [-@nweze2021] found no association between adversity and attention shifting.
+However, they tested institutionalized children rather than measuring adversity dimensions [@nweze2021].
 In general, we should interpret cautiously.
@@
 Interestingly, updating performance was unrelated to unpredictability.
-These findings are partially consistent with prior work on adversity exposure and working memory updating performance[@young2018; @nweze2021].
-For example, both Young and colleagues[@young2018] and the current study found lowered abstract working memory performance among high adversity-exposed individuals.
+These findings are partially consistent with prior work on adversity exposure and working memory updating performance [@young2018; @nweze2021].
+For example, both Young and colleagues [-@young2018] and the current study found lowered abstract working memory performance among high adversity-exposed individuals.
 Although performance with ecological stimuli is not directly comparable to performance under manipulated uncertainty, both studies reduced the updating performance gap under ecologically relevant conditions.
 However, there are also discrepancies.
-For example, Young and colleagues[@young2018] found effects with unpredictability and not poverty, whereas the current study found associations with violence and poverty but not unpredictability.
-Finally, Nweze and colleagues[@nweze2021] found improved working memory performance among institutionalized youth without ecological stimuli or uncertainty manipulations.
+For example, Young and colleagues [-@young2018] found effects with unpredictability and not poverty, whereas the current study found associations with violence and poverty but not unpredictability.
+Finally, Nweze and colleagues [-@nweze2021] found improved working memory performance among institutionalized youth without ecological stimuli or uncertainty manipulations.
 However, both their adversity and working memory measures were different.
@@
 Practically, these effects support the idea that ecologically relevant testing materials may "even the playing field" for adversity-exposed youth.
-That is, pending replication and extension, our data suggest leveraging ecologically relevant materials in education may hold promise for closing achievement gaps[@ellis2017; @ellis2020; @frankenhuis2020].
+That is, pending replication and extension, our data suggest leveraging ecologically relevant materials in education may hold promise for closing achievement gaps [@ellis2017; @ellis2020; @frankenhuis2020].
 However, our data also suggest the effect of ecological content may be specific to particular abilities---ecological content actually *lowered* attention shifting performance for everyone compared to abstract content.
-This negative effect is consistent with other studies reporting lowered performance on tests with ecologically relevant content[@frankenhuis2020; @muskens2019; @duquennois].
+This negative effect is consistent with other studies reporting lowered performance on tests with ecologically relevant content [@frankenhuis2020; @muskens2019; @duquennois].
 
@@
 Unlike the selective activation of cognitive resources, the additional stressors of testing are removed, allowing cognitive mechanisms to function normally.
-However, this explanation is difficult to reconcile with experimental work[@mittal2015; @young2018], which finds that mild stress/uncertainty improves performance.
+However, this explanation is difficult to reconcile with experimental work [@mittal2015; @young2018], which finds that mild stress/uncertainty improves performance.
 Future research should use research designs that can disentangle these explanations.
@@
 Second, although we found some effects of ecological testing materials, we measured previously documented hidden talents.
-To explore generalizability of ecological content across abilities, future research may create ecological versions of tests known to disadvantage adversity-exposed youth, such as inhibition[@young2018] or working memory retrieval[@young2018], and compare performance to abstract versions.
+To explore generalizability of ecological content across abilities, future research may create ecological versions of tests known to disadvantage adversity-exposed youth, such as inhibition [@young2018] or working memory retrieval [@young2018], and compare performance to abstract versions.
 Third, although we used interviews and self-report methods, all of our childhood adversity measures were cross-sectional and some were retrospective.
 These measurement limitations may be partially offset because our sample was still living in their developmental environment.
-However, this does not replace the need for prospective, longitudinal measures and cannot eliminate all biases associated with retrospective reporting[@reuben2016].
+However, this does not replace the need for prospective, longitudinal measures and cannot eliminate all biases associated with retrospective reporting [@reuben2016].
 Thus, it remains unclear to what extent the current environment, rather than the developmental environment, is driving our findings.
@@
 
-# Method {#method}
-
-## Participants {#participants}
-
-The current study collected data from `r txt1_sam$raw$n$total` adolescents (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah.
-The first was a middle school and the second were 5 after-school clubs.
-The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse.
-According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers).
-The clubs (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`).
-`r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch and were also ethnically diverse.
-
-We aggregated data from both sources and applied a set of five exclusion criteria.
-We applied these criteria before inspecting or testing any relations between predictors and outcomes.
-Specifically, we excluded participants: 1) with incomplete cognitive task data, 2) with apparent cognitive impairments (e.g., head injuries, disabilities, drug use), 3) who missed two or more trap questions, 4) exposed to extreme distractions during the assessment, and 5) who received more than 60 minutes per day of special education services.
-After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).
-
-## Procedure {#procedure}
-
-Data collection involved six parts: consent/assent, demographics form, cognitive testing, structured interview, questionnaire, and a debriefing.
-Consent was obtained from the primary parent or guardian before assessments and assent was obtained from the participant at the beginning of the session.
-On the demographics form, participants indicated if they were left-handed, their birthdate, and their racial and ethnic background.
-
-Cognitive testing included abstract (i.e., standard) and ecological versions of an attention-shifting and working memory updating task.
-Task order (shifting versus updating) and version (abstract versus ecological) were counterbalanced across participants.
-Some participants started with the attention shifting and then moved to the updating tasks.
-For those starting with the shifting (or updating) tasks, some started with the abstract version and then completed the ecological version (and vice versa).
-Regardless of which task was first, participants always completed both versions of one task before moving to the other task.
-
-The interview contained two parts.
-The first part was about participants' home and family life, such as their family composition, the number of adults in the household, and occupation and education information about caregivers.
-Participants also reported on the number of romantic partners their caregivers had and if these partners lived with the participant.
-The second part was about residential mobility.
-Participants listed all the homes they lived in from birth to age 13.
-For each home, they reported at which ages they lived in the home.
-If they moved, they also reported any changes in their family structure (loss or gain of adults in the home), social network (e.g., a new school), and/or town or city.
-
-The questionnaire contained measures focused on the childhood environment.
-The measures included perceived unpredictability in the home, exposure to neighborhood violence, access to material resources, direct exposure to violence and fighting, and a child version of socially desirable responding.
-
-Procedures across the middle school and after-school clubs were the same, with a few minor differences.
-First, participants in the clubs completed the tasks before the interview, but the opposite occurred in the middle school.
-The second was that, in the middle school, the questionnaire was completed in a separate session.
-Whereas the tasks and interview were completed in a small room, alone with the interviewer, the questionnaire was completed approximately two weeks later in a mass testing context (large computer room).
-This was done because the middle school was on a strict class schedule, which limited the length of individual sessions.
-In the clubs, sessions were conducted in the summer during flexible hours.
-
-## Measures {#measures}
-
-### Attention Shifting {#shifting}
-
-We measured attention shifting with two versions of the color--shape task[@mittal2015; @miyake2012; @friedman2008], which involves categorizing stimuli according to one of two rules (see below).
-On each trial, the rule is displayed on the top of the screen.
-Using arrow keys, participants categorized the stimulus as quickly and accurately as possible.
-Response options appeared at the bottom of the screen (see Figure \@ref(fig:figure1)).
-
-On the abstract (standard) attention-shifting task, participants categorized colored (blue or yellow) shapes (squares or triangles) according to the 'color' or 'shape' rule (see Figure \@ref(fig:figure1)a).
-For example, if a blue triangle appeared on the screen and the rule was "color", participants categorized the blue triangle as blue.
-However, if the rule was "shape", participants instead categorized the blue triangle as a triangle.
-
-The ecological attention-shifting task replaced shapes and colors with faces (see Figure \@ref(fig:figure1)b).
-Faces were either male or female (gender), and were happy or angry (emotion).
-If a happy female face appeared on screen and the rule was 'gender', for example, participants categorized the face as female.
-If the rule was 'emotion', participants instead categorized the face as happy.
-The stimuli for the ecological attention-shifting task were selected from the NimStim library[@tottenham2009].
-The same female and male models were used for happy and angry expressions.
-
-For both versions, there were two types of trials: repeat and switch.
-Repeat trials use the same rule as the previous trial.
-If the current and previous rule is 'color', for instance, the current trial is a repeat trial.
-Switch trials are trials where the rule changes from the previous trial.
-If the current rule is 'color' but the previous was 'shape' (or vice versa), the current trial is a switch trial.
-
-Accuracy on attention-shifting tasks is normally high, and was in the current sample for both versions (*M~standard~* = `r (txt2_dvs$abs_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~standard~* = `r (txt2_dvs$abs_shifting_correct$sd/32 * 100) %>% round(2)`%; *M~ecological~* = `r (txt2_dvs$eco_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~ecological~* = `r (txt2_dvs$eco_shifting_correct$sd/32 * 100) %>% round(2)`%).Thus, instead of accuracy, attention-shifting ability is measured by comparing reaction times on repeat trials to switch trials.
-Reaction times on repeat trials are normally faster than switch trials; average repeat trial reaction times on the abstract and ecological versions were `r txt2_dvs$abs_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_re_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_re_rt$sd` *ms*), respectively.
-On switch trials, average reaction times were `r txt2_dvs$abs_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sw_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sw_rt$sd` *ms*) on the standard and ecological versions.
-
-To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000].
-We removed fast and slow reaction times and removed trials after incorrect responses (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
-We then subtracted the average reaction time on valid repeat trials from the average reaction time on valid switch trials to calculate switch cost scores (*M~switch~* - *M~repeat~*).
-The switch cost measures the relative delay in reaction time caused by switching between categorization rules.
-Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` ms (*SD* = `r txt2_dvs$eco_shifting_sc$sd` ms), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`).
-Higher switch costs mean longer reaction times on switch trials compared to repeat trials.
-Larger switch costs indicate less efficient attention shifting.
-
-### Working Memory Updating {#updating}
-
-Working memory updating was measured using two versions of the continuous counters task[@unsworth2015; @unsworth2008; @young2018], in which participants track a sequence of stimuli containing three different objects (see Figure \@ref(fig:figure1)).
-Participants keep running counts of each object in sequences nine items long.
-Each object was displayed for one second at a time.
-At the end of each sequence, participants reported the number of times each object appeared.
-For each round, there were three possible correct answers, one for each object type.
-
-In the abstract (standard) version, participants kept running counts of squares, circles, and triangles (see Figure \@ref(fig:figure1)c).
-The participant must keep track of each shape, updating counts as new shapes appeared, and report them at the end of the sequence.
-The ecological version followed the same format, but participants kept running counts of three different real-world objects (see Figure \@ref(fig:figure1)d): one positive (five-dollar bill), one negative (angry face), and one neutral (Salt Lake City bus).
-
-Participants completed five rounds of both versions.
-The maximum score was 15 for each version (five rounds × three possible correct).
-On the abstract and ecological versions, participants averaged `r txt2_dvs$abs_updating$mean * 15` (*SD* = `r txt2_dvs$abs_updating$sd * 15`) and `r txt2_dvs$eco_updating$mean * 15` (*SD* = `r txt2_dvs$eco_updating$sd * 15`), respectively (*r* = `r txt5_cor$updating$r`).
-Higher scores indicate better working memory updating performance.
-
-### Environmental Unpredictability {#unp}
-
-Our measure of environmental unpredictability integrated information from the interview and questionnaire.
-The interview contained three variables of interest.
-The first measured the level of exposure to living in a biologically non-intact family from birth to age 13.
-Interviewers asked participants about their family composition and the adults that lived with them in the home.
-If a participant's family composition changed, for example, because of a divorce, interviewers recorded the ages when participants experienced the change and for how long it persisted.
-A family was considered non-intact if the participant did not live with both biological parents during any period from birth to age 13.
-Based on the earliest age of disruption, we indexed the onset of exposure to a non-intact family by creating a four-level variable from 0 to 3.
-A 0 indicated the participant lived in an intact family (lived with both biological parents) from birth until age 13 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 0) %>% sum(na.rm=T)`); a 1 indicated that a disruption occurred after the age of 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 1) %>% sum(na.rm=T)`); a 2 indicated that a disruption occurred before age 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 2) %>% sum(na.rm=T)`); and a 3 indicated the participant was born into a non-intact family (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 3) %>% sum(na.rm=T)`).
-`r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T)`.
-`r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T) %>% english::as.english() %>% str_to_title()` participants had missing information.
-
-The second interview variable tabulated the number of different parental figures (defined as spouses or boyfriends/girlfriends of the participant's mother and father) who lived in the same home with the participant.
-Trained interviewers tabulated the total number of co-residing parental figures, excluding the participant's biological mother and father (*M* = `r txt3_ivs$unp_interview_figures$mean`, *SD* = `r txt3_ivs$unp_interview_figures$sd`).
-
-The third interview variable focused on residential changes from birth to age 13 (reported retrospectively).
-Specifically, interviewers probed participants about the number of different homes they lived in and, in particular, whether moving to a new home involved living with new or different adults.
-On average, participants experienced `r txt3_ivs$unp_interview_moves$mean` (*SD* = `r txt3_ivs$unp_interview_moves$sd`) that involved changes in residential adults.
-
-The questionnaire included a measure of perceived childhood unpredictability[@mittal2015; @young2018; @szepsenwol2015].
-Participants responded to six items that assessed exposure to unpredictability up to age 13: 1) "Things were pretty calm and stable in my house" (reversed); 2) "People moved in and out of my house a lot"; 3) "I had a hard time knowing what my parent(s) or other people in my house were going to say or do from day-to-day"; 4) "My parent(s) argued or fought a lot with each other or with other people"; 5) "My parent(s) changed jobs a lot"; 6) "My parental situation changed a lot (for example, divorce or separation of parents, parents starting new romantic relationships, parents leaving the home)".
-Participants rated each item on a scale from 1 (never true) to 5 (very often true).
-Responses to these items were averaged to create a self-reported perceived childhood unpredictability measure (*M* = `r txt3_ivs$unp_perceived$mean`, *SD* = `r txt3_ivs$unp_perceived$sd`, $\alpha$ = `r txt4_rel$unp`).
-Higher scores indicated more perceived exposure to unpredictable environments.
-
-To create a composite measure of unpredictability, we aggregated across the interview and questionnaire.
-First, we created an interview-based measure of unpredictability using family disruptions, exposure to different parental figures, and residential moves involving new adults living in the home.
-We standardized these interview measures and then averaged them together ($\alpha$ = `r txt4_rel$unp_int`).
-We then aggregated this interview measure with self-reported perceived unpredictability from the questionnaire, standardizing each before averaging (*r* = `r txt5_cor$unp$r`).
-Higher scores indicated more exposure to unpredictability.
-
-### Violence Exposure {#vio}
-
-We measured violence exposure using the Neighborhood Violence Scale (NVS)[@frankenhuis2020a; @frankenhuis2018] and two items about witnessing and involvement in physical fights.
-The NVS contains 7 items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm".
-The physical fighting items asked about witnessing fights: "Based on your experiences at school and in your neighborhood, how many times did you see or hear someone being beaten up in real life?"; and involvement in fights: "How many times were you in a physical fight at school or in your neighborhood?".
-Both items were rated on a scale from 1 (0 times) to 8 (12 or more times).
-
-Responses on the NVS were averaged to create a composite measure (*M* = `r txt3_ivs$vio_neighborhood$mean`, *SD* = `r txt3_ivs$vio_neighborhood$sd`, $\alpha$ = `r txt4_rel$vio`).
-Likewise, the two fighting were averaged together (*M* = `r txt3_ivs$vio_fighting$mean`, *SD* = `r txt3_ivs$vio_fighting$sd`).
-To create a violence exposure composite, the NVS composite and fighting composite were standardized and then averaged (*r* = `r txt5_cor$vio$r`).
-Higher scores indicated more exposure to violence.
-
-### Poverty Exposure {#poverty}
-
-We assessed each participant's poverty exposure using three information sources: interview-assessed parent education and occupational prestige, school or club-provided economic information, and perceived resource scarcity.
-
-During the interview, participants reported their parents' education and primary occupation.
-For parental education level, participants reported whether their mother and father graduated high school, went to college, and if they obtained a bachelor's degree or higher.
-Responses to each question were coded as 0 = 'no' and 1 = 'yes'.
-These items were summed to create a four-level variable for each parent where 0 = did not graduate high school, 1 = graduated high school but did not attend any college, 2 = graduated high school and completed some college, and 3 = went to college and obtained a bachelor's degree or higher.
-Mother and father education were averaged to create a parental education score (*M* = `r txt3_ivs$ses_interview_edu$mean`, *SD* = `r txt3_ivs$ses_interview_edu$sd`).
-
-Participants also reported their parents' occupation.
-Participants described, in general terms, their mother's and father's jobs and the kind of work involved.
-Trained coders cross-referenced these descriptions with 2010 census job codes[@hout2018].
-We calculated mother and father occupational prestige by matching census codes with prestige ratings from an established occupational prestige rating dataset[@hout2016].
-Prestige codes ranged from 0-100, with higher scores indicating higher occupational prestige for a particular job code.
-Mother and father prestige codes were averaged to create a parent occupational prestige score (*M* = `r txt3_ivs$ses_interview_occup$mean`, *SD* = `r txt3_ivs$ses_interview_occup$sd`).
-
-We also obtained school or club-provided economic information.
-The middle school provided four information sources: 1) whether or not students were receiving free lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_frl == 1) %>% sum(na.rm=T)`); 2) whether or not they were receiving reduced-price lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_rel == 1) %>% sum(na.rm=T)`); 3) whether they were receiving fee waivers (*n* = `r (data2_non_arbitrary$ses_school_wjms_fee == 1) %>% sum(na.rm=T)`); and 4) if they were experiencing homelessness (*n* = `r (data2_non_arbitrary$ses_school_wjms_hom == 1) %>% sum(na.rm=T)`).
-These information sources were compiled to create a binary economic disadvantage variable.
-A participant was economically disadvantaged if they were receiving any benefits or experiencing homelessness (*n* = `r txt1_sam$non_arb$free_lunch$wjms`).
-In the afterschool clubs, free or reduced-price lunch status was provided by self-report, staff, and club enrollment forms and cross-referenced to determine economic disadvantage in the clubs (*n* = `r txt1_sam$non_arb$free_lunch$bgc`).
-Overall, `r (data2_non_arbitrary$ses_school_freelunch == 1) %>% sum(na.rm=T)` participants were receiving economic assistance, `r (data2_non_arbitrary$ses_school_freelunch == 0) %>% sum(na.rm=T)` were not, and `r sum(is.na(data2_non_arbitrary$ses_school_freelunch))` had missing economic information.
-
-Participants also reported their perceived level of resource scarcity.
-They rated seven items from 1 (never true) to 5 (very often true): 1) "Your family had enough money to afford the kind of home you all needed"; "Your family had enough money to afford the kind of clothing you all needed"; 3) "Your family had enough money to afford the kind of food that you all needed"; 4) "Your family had enough money to afford the kind of medical care that you all needed"; 5) "I felt well-off (rich, wealthy) compared to other kids in my school"; 6) "I felt well-off (rich, wealthy) compared to other kids in my neighborhood"; and 7) "Your family struggled to make ends meet (get by financially)".
-The first six items were reversed, and all items were averaged to create a perceived resource scarcity measure (*M* = `r txt3_ivs$ses_perceived$mean`, *SD* = `r txt3_ivs$ses_perceived$sd`, $\alpha$ = `r txt4_rel$ses`).
-Higher scores indicated more perceived resource scarcity.
-
-To create a poverty exposure composite, we combined parent education and occupational prestige (reversed), school/club reported economic disadvantage, and perceived resource scarcity.
-First, we standardized and averaged parent education and occupation (*r* = `r txt5_cor$edu_int$r`).
-Then, we recoded school-provided economic codes to be equal to half of a standard deviation above and below the mean (in terms of z-scores).
-Specifically, those receiving free or reduced-price lunch were coded as .5, and those who were not were coded as -.5.
-To create a final composite, we averaged parent education/occupation (standardized), perceived resource scarcity (standardized), and the recoded school/club economic disadvantage.
-Higher values indicated more exposure to poverty.
-
-### Control Variables {#controls}
-
-We included two control variables: age and interviewer-rated distractions during testing.
-We included these because older adolescents tend to score higher on cognitive tests than younger adolescents[@best2010; @best2011; @huizinga2006], and disruptions during the tasks could negatively impact performance.
-Interviewers completed quantitative ratings of the testing environment including 1) the level of noise; 2) the level of chaos; 3) how often there were interruptions; and 4) how often the participant appeared distracted.
-Interviewers rated each item on a scale from 1 (not at all) to 7 (much more than average).
-Items were averaged to create a composite (*M* = `r txt3_ivs$test_envr$mean`, *SD* = `r txt3_ivs$test_envr$sd`), where higher scores indicate more distractions.
-
-We also included the Child Social Desirability (CSD) scale[@miller2014].
-The measure includes 14 items such as "Have you ever broken a rule?" and "Do you sometimes feel angry when you don't get your way?".
-Participants indicated 1 (yes) or 0 (no) for each item.
-More socially desirable responses were scored as 1.
-Items were then summed to create a social desirability index (*M* = `r txt3_ivs$csd$mean`, *SD* = `r txt3_ivs$csd$sd` , $\alpha$ = `r txt4_rel$csd`).
-
-## Multiverse Setup {#multiverse}
-
-We used a multiverse analysis approach for all analyses[@steegen2016; @simonsohn2020; @orben2019; @orben2019a].
-Researchers face many data processing decisions.
-These decisions fall into two classes: arbitrary and non-arbitrary decisions.
-Non-arbitrary decisions have clear theoretical, statistical, or practical justifications and are superior to alternatives.
-Arbitrary decisions are those that have (sometimes many) equally defensible alternatives.
-For example, excluding outliers at +/- 2.5 or 3 standard deviations above (or below) the sample mean could be equally defensible.
-Instead of cherry-picking one or getting pigeonholed with the other, multiverse analysis allows researchers to explicitly generate all possible combinations of (arbitrary) data processing decisions and analyze them together.
-In turn, researchers can systematically evaluate the robustness or sensitivity of their analysis across all possible data processing decisions.
-
-### Arbitrary Decisions {#abritrary}
-
-We identified six arbitrary data processing decisions.
-First, we conducted analyses with and without the after-school club sample.
-We did this because our procedure was slightly different across the two samples and the testing environment was more disruptive in the clubs compared with the middle school.
-Second, we conducted analyses with and without participants with minor distractions during testing.
-Third, we analyzed the data with and without participants who missed one trap question (those who missed more than 1 were already excluded).
-Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded).
-Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
-
-Our last arbitrary data processing decision pertained to socially desirable responses.
-It is well-known that some youth tend to describe themselves in socially desirable ways.
-This raises concerns about the validity of self-reported childhood adversity measures: youth scoring higher on social desirability might underreport or underrate their exposures to negative experiences.
-Indeed, scores on the CSD were correlated with exposures to unpredictability (*r* = `r txt5_cor$csd_unp$r`) and violence (*r* = `r txt5_cor$csd_vio$r`), though not with poverty.
-One way to handle this issue is to statistically remove overlapping variance between social desirability and each predictor, using the leftover variance (e.g., the residual variance in childhood adversity exposures not associated with social desirability) as a predictor.
-Because it is unclear how social desirability might affect the interpretation of our models, we analyzed our data with residualized and non-residualized predictors.
-
-### Statistical Inferences {#inference}
-
-Multiverse analysis produces a distribution of effect sizes and test statistics across all combinations of analytic decisions (see Figures \@ref(fig:figure2) and 3).
-However, although these distributions provide rich descriptive information, they do not lend themselves to straightforward null-hypothesis tests.
-This is because each individual analysis in a multiverse is not independent.
-To address this, we used a bootstrapping technique designed for multiverse analysis[@simonsohn2020; @orben2019; @orben2019a].
-This technique makes it possible to know if a multiverse analysis produced a median effect size larger than expected, given the null hypothesis (the median effect is 0).
-
-For the current study, we calculated overall *p*-values for the main effect of adversity and the interaction effects (task version × adversity) of our primary analyses.
-To do so, we created 'null' attention-shifting and working memory updating scores[@simonsohn2020].
-That is, we created outcome scores with the influence of the effect of interest (i.e., main effect or interaction) removed.
-More specifically, we multiplied the coefficient of interest (regression coefficient of the main effect of adversity or interaction effect) by each participant's raw predictor score (either adversity scores or task version × adversity scores) and subtracted the result from each participant's attention-shifting and working memory scores.
-Next, we randomly sampled participants (with replacement) to create 500 bootstrapped samples.
-Then, we ran the same multiverse analysis on each bootstrap sample using the null attention-shifting and working memory scores as outcome variables.
-Upon completion, we compared the median effects for each bootstrapped sample (500 median effect sizes) with our original median effects.
-To compute overall *p*-values, we divided the number of effect sizes obtained from the bootstrapped multiverse analyses that were larger than our original median effect sizes by the total number of bootstrapped samples.
-Importantly, we ran this procedure separately for each measure of adversity (unpredictability, violence exposure, and poverty exposure), outcome (attention shifting and working memory updating), and effect of interest (main effect or interaction effect) combination.
-
 \pagebreak

### 2021-09-27 manuscript/scripts/rmd-staging.R

@@ -91,7 +91,11 @@ txt1_sam <-
         n    = data %>% pull(ses_school_freelunch) %>% sum(na.rm=T),
         bgc  = data %>% filter(sample_code == "bgc") %>% pull(ses_school_freelunch) %>% sum(na.rm=T),
         wjms = data %>% filter(sample_code == "wjms") %>% pull(ses_school_freelunch) %>% sum(na.rm=T)
-      ) 
+      ),
+      race = list(
+        non_white = data %>% filter(race != 4) %>% nrow(),
+        hispanic  = data %>% filter(hispanic == 1) %>% nrow()
+      )
     )
   }) 
 

### 2021-09-27 scripts/1-data-prep/1-data-non-abritrary.R

@@ -48,7 +48,16 @@ data2_non_arbitrary <-
   select(-siblings) %>% 
   var_labels(
     siblings_id = "Sibling ID",
-    siblings_n  = "The number of siblings each participant has who also participated in this study "
+    siblings_n  = "The number of siblings each participant has who also participated in this study"
+  ) %>% 
+  sjlabelled::val_labels(
+    race = c("Asian" = 1,
+             "Native American" = 2,
+             "African American" = 3,
+             "White" = 4,
+             "Hispanic" = 5,
+             "Pacific Islander" = 6,
+             "Multiple" = 7)
   )
 
 # Create Overall Composites -----------------------------------------------
@@ -69,7 +78,7 @@ data3_composites <-
   select(
     id, sample_code, interviewer, site, classroom, 
     siblings_id, has_sibling, siblings_n,
-    sex, ethnicity, age, 
+    sex, race, hispanic, age, 
     starts_with("non_arb"),
     starts_with("arb"),
     matches("^test_envr"), 

### 2021-09-27 manuscript/scripts/rmd-staging.R
update participants section

@@ -38,6 +38,7 @@ my_limits <- c(1,70)
 
 # Objects -----------------------------------------------------------------
 load("multiverse-objects/1-multiverse-datasets/datalist-agg-ivs.Rdata")
+load("data/data1_raw.Rdata")
 load("data/data2_analysis.Rdata")
 load("multiverse-objects/2-primary-analyses/3-extracted-effects.Rdata")
 load("multiverse-objects/2-primary-analyses/5-bootstrapped-effects.Rdata")
@@ -343,6 +344,7 @@ secondary2_medians <-
 
 # Save the entire image ---------------------------------------------------
 save(
+  data1_raw,
   data2_non_arbitrary,
   data3_composites,
   multi_data_list,

### 2021-09-29 supplement/scripts/1-covariates.R
add .docx format for manuscript and supplement

@@ -185,7 +185,7 @@ shifting_unp <-
     spec_curves1[[1]][[1]]$eff_curve,
     spec_curves1[[1]][[1]]$sample_sizes,
     spec_curves1[[1]][[1]]$spec_grid,
-    nrow  = 6,
+    nrow  = 4,
     ncol  = 1, 
     align = "v", 
     axis  = "lr",
@@ -198,7 +198,7 @@ shifting_vio <-
     spec_curves1[[1]][[2]]$eff_curve,
     spec_curves1[[1]][[2]]$sample_sizes,
     spec_curves1[[1]][[2]]$spec_grid,
-    nrow  = 6,
+    nrow  = 4,
     ncol  = 1, 
     align = "v", 
     axis  = "lr",
@@ -211,7 +211,7 @@ shifting_ses <-
     spec_curves1[[1]][[3]]$eff_curve,
     spec_curves1[[1]][[3]]$sample_sizes,
     spec_curves1[[1]][[3]]$spec_grid,
-    nrow  = 6,
+    nrow  = 4,
     ncol  = 1, 
     align = "v", 
     axis  = "lr",
@@ -225,7 +225,7 @@ updating_unp <-
     spec_curves1[[2]][[1]]$eff_curve,
     spec_curves1[[2]][[1]]$sample_sizes,
     spec_curves1[[2]][[1]]$spec_grid,
-    nrow  = 6,
+    nrow  = 4,
     ncol  = 1, 
     align = "v", 
     axis  = "lr",
@@ -238,7 +238,7 @@ updating_vio <-
     spec_curves1[[2]][[2]]$eff_curve,
     spec_curves1[[2]][[2]]$sample_sizes,
     spec_curves1[[2]][[2]]$spec_grid,
-    nrow  = 6,
+    nrow  = 4,
     ncol  = 1, 
     align = "v", 
     axis  = "lr",
@@ -251,7 +251,7 @@ updating_ses <-
     spec_curves1[[2]][[3]]$eff_curve,
     spec_curves1[[2]][[3]]$sample_sizes,
     spec_curves1[[2]][[3]]$spec_grid,
-    nrow  = 6,
+    nrow  = 4,
     ncol  = 1, 
     align = "v", 
     axis  = "lr",

### 2021-12-21 README.Rmd
fixing scripts - CD revision 1

@@
 
-To reproduce this repository, see [How to reproduce this respository](#repro) below.
+To reproduce this repository, see [How to reproduce this respository](#how-to-reproduce-this-repository) below.
 
@@
 2.  `data/`: data, stored as an `.Rdata` file and `.csv` files.
-3.  `manuscript`: a manuscript written in R markdown for submission to a journal.
+3.  `manuscript/`: a manuscript written in R markdown for submission to a journal.
 4.  `multiverse-objects/`: all `.Rdata` files containing objects necessary for performing multiverse analyses and storing intermediary results.
@@
 
-- `1-multiverse-datasets`: multiverse data sets with each data universe stored in a list. There is one list used for the composites and one list used for all components of each IV.
-- `2-primary-analyses`: contain the multiverse of full results and extracted effects for the primary confirmatory and exploratory results
-- `3-secondary-analyses`: contain the same objects as above for each set of secondary analyses.
+- `1-multiverse-datasets/`: multiverse data sets with each data universe stored in a list. There is one list used for the composites and one list used for all components of each IV.
+- `2-primary-analyses/`: contain the multiverse of full results and extracted effects for the primary confirmatory and exploratory results
+- `3-secondary-analyses/`: contain the same objects as above for each set of secondary analyses.
 
@@
 
-|script|input|output|
-|------|-----|------|
-|1-data-non-abritrary.R|data1_raw.Rdata|1-raw.csv<br> 2-non_arbitrary.csv<br> 3-composites.csv<br> 4-multiverse_base.csv<br> vars1_raw.csv<br> vars2_non_arbitrary.csv<br> vars3_composites.csv<br> vars4_multiverse_base.csv<br> data2_analysis.Rdata|
-|2-primary-multiverse-datasets.R|data2_analysis.Rdata|datalist-agg-ivs.Rdata|
-|3-secondary-multiverse-datasets.R|data2_analysis.Rdata|datalist-all-ivs.Rdata|
-
 ### Primary Analyses
@@
 
-## How to reproduce this repository {#repro}
+## How to reproduce this repository
 
@@
 1. `2-primary-analyses/1-confirmatory.R`: conducts unpredictability and violence multiverse analyses for attention-shifting and working memory updating.
-2. `2-primary-analyses/1-exploratory.R`: conducts poverty multiverse analyses for attention-shifting and working memory updating.
-3. `2-primary-analyses/1-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting.
-4. `2-primary-analyses/1-bootstrap-setup.R`: sets up bootstrap samples for bootstrapping technique .
-5. `2-primary-analyses/1-bootstrap-spec-analysis.R`: runs specification analyses over all bootstrapped samples to obtain overall *p*-values.
+2. `2-primary-analyses/2-exploratory.R`: conducts poverty multiverse analyses for attention-shifting and working memory updating.
+3. `2-primary-analyses/3-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting.
+4. `2-primary-analyses/4-bootstrap-setup.R`: sets up bootstrap samples for bootstrapping technique .
+5. `2-primary-analyses/5-bootstrap-spec-analysis.R`: runs specification analyses over all bootstrapped samples to obtain overall *p*-values.
 
@@
     2.
-`3-secondary-analyses/set-1/a2-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting for the analysis labeld "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript.
+`3-secondary-analyses/set-1/a2-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting for the analysis labeled "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript.
     3.

### 2021-12-21 manuscript/manuscript.Rmd
fixing scripts - CD revision 1

@@
 However, the hidden talents approach proposes some abilities are enhanced by adversity, especially under ecologically relevant conditions.
-Sampling 618 adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r (txt1_sam$non_arb$race$non_white/txt1_sam$non_arb$n$total * 100) %>% round(2)`% non-White), we administered two versions of an attention shifting and working memory updating task—one abstract, one ecological.
+Sampling 618 adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White), we administered two versions of an attention shifting and working memory updating task—one abstract, one ecological.
 We measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions.
@@
 The first was a middle school and the second were 5 after-school clubs.
-The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse (`r (txt1_sam$raw$race$non_white/txt1_sam$raw$n$total * 100) %>% round(2)`% non-White; `r (txt1_sam$raw$race$hispanic/txt1_sam$raw$n$total * 100) %>% round(2)`% Hispanic).
+The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse: `r data1_raw %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data1_raw %>% filter(race == 2) %>%nrow()` as Native American, `r data1_raw %>% filter(race == 3) %>% nrow()` as African American, `r data1_raw %>% filter(race == 4) %>% nrow()` as White, `r data1_raw %>% filter(race == 5) %>% nrow()` as Hispanic, `r data1_raw %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data1_raw %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data1_raw %>% filter(is.na(race)) %>% nrow()` were missing.
 According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers).
@@
 After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).
+In terms of racial identity, `r data2_non_arbitrary %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data2_non_arbitrary %>% filter(race == 2) %>%nrow()` as Native American, `r data2_non_arbitrary %>% filter(race == 3) %>% nrow()` as African American, `r data2_non_arbitrary %>% filter(race == 4) %>% nrow()` as White, `r data2_non_arbitrary %>% filter(race == 5) %>% nrow()` as Hispanic, `r data2_non_arbitrary %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data2_non_arbitrary %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data2_non_arbitrary %>% filter(is.na(race)) %>% nrow()` were missing.
 

### 2021-12-21 manuscript/manuscript_docx.Rmd
fixing scripts - CD revision 1

--- 2021-12-21 manuscript/manuscript.Rmd
@@
 ---
-output:
-  bookdown::pdf_document2:
-    latex_engine: xelatex
-    toc: false
-    number_sections: false
-    keep_tex: true
-    extra_dependencies: ["booktabs","longtable"]
-geometry: margin=1in
-mainfont: Times
-fontsize: 12pt
-endnote: no
-urlcolor: blue
-header-includes:
-- \usepackage{float}
-- \usepackage{siunitx}
-- \usepackage[utf8]{inputenc}
-- \usepackage[english]{babel}
-- \setlength{\parindent}{2em}
-- \setlength{\parskip}{0em}
-- \linespread{2}
-- \usepackage{titlesec}
-- \titleformat{\section}[block]{\normalsize\bfseries\filcenter}{}{}{}
-- \titleformat{\subsection}[block]{\normalsize\bfseries}{}{}{}
-- \titleformat{\subsubsection}[block]{\bfseries\itshape}{}{}{}
-- \titlespacing{\section}{0pt}{0pt}{0pt}
-- \titlespacing{\subsection}{0pt}{0pt}{0pt}
-- \titlespacing{\subsubsection}{0pt}{0pt}{0pt}
-- \usepackage{indentfirst}
-- \usepackage{fancyhdr}
-- \pagestyle{fancy}
-- \fancyhf{}
-- \fancyhead[R]{\thepage}
-- \fancyhead[L]{HIDDEN TALENTS IN CONTEXT}
-- \renewcommand\headrulewidth{0pt}
-- \usepackage{fixltx2e}
-- \usepackage{caption}
-- \usepackage{setspace}
-- \captionsetup[table]{labelfont={bf},labelformat={default}, labelsep={newline}}
-- \captionsetup[figure]{labelfont={bf},labelformat={default}, labelsep={period}}
-- \usepackage{lineno}
 bibliography: references.bib
 csl: apa.csl
+output:
+  officedown::rdocx_document:
+    reference_docx: reference-doc.docx
+    page_margins:
+      bottom: 1
+      top: 1
+      right: 1
+      left: 1
+      header: .5
+      footer: 0
+      gutter: 0
+    plots:
+      align: center
+      caption:
+        style: Image Caption
+        pre: 'Figure '
+        sep: '. '
+    tables:
+      caption:
+        style: Table Caption
+        pre: 'Table '
+        sep: '. '
 ---
@@
 ```{r setup, include=FALSE}
+# set up chunk options
 knitr::opts_chunk$set(
@@
 
+# load libraries
 library(tidyverse)
-library(kableExtra)
-library(gt)
+library(officer)
+library(flextable)
 
+# load all data and objects
 load("staged-objects.Rdata")
+
+# set up flextable for tables
+set_flextable_defaults(
+  font.family = "Times", 
+  font.size = 10,
+  font.color = "black",
+  line_spacing = 1,
+  padding.bottom = 1, 
+  padding.top = 1,
+  padding.left = 1,
+  padding.right = 1
+)
 ```
@@
 
-(ref:figure1) Schematic display of the attention shifting and working memory updating tasks: a) abstract attention shifting, b) ecological attention shifting, c) abstract working memory updating, and d) ecological working memory updating.
-
-```{r figure1, fig.cap='(ref:figure1)'}
+```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap='Schematic display of the attention shifting and working memory updating tasks: a) abstract attention shifting, b) ecological attention shifting, c) abstract working memory updating, and d) ecological working memory updating.'}
 knitr::include_graphics("figure1.pdf")
@@
 
-```{r table1, results='asis'}
+```{r table1, tab.id = "table1", tab.cap.style = "Table Caption", tab.cap="Bivariate correlations and descriptive statistics for measures of adversity and their components."}
 table.01.0 %>% 
-  kbl(
-    align = "lcccccccccc",  
-    booktabs = T,
-    escape = F,
-    caption = "\\emph{Bivariate correlations and descriptive statistics for measures of adversity and their components.}"
+  add_column(.after = 4,"empty1" = "") %>% 
+  add_column(.after = 8,"empty2" = "") %>% 
+  flextable() %>%
+  width("empty1", width = .2) %>% 
+  width("empty2", width = .2) %>% 
+  width(j = 1, width = .75) %>% 
+  set_header_labels(Variable = "", empty1 = "", empty2 = "") %>% 
+  add_header_row(
+    values = c(" ", "Unpredictability", " ", "Violence", " ", "Poverty"),
+    colwidths = c(1, 3, 1, 3, 1, 4)
   ) %>% 
-  add_header_above(c(" ","Unpredictability" = 3, "Violence" = 3, "Poverty" = 4)) %>% 
-  kable_styling(latex_options = c("scale_down", "hold_position")) %>% 
-  footnote(
-    general       = "Column headers denote adversity constructs and rows indicate components. The upper triangle contain sample sizes for each correlation.",
-    general_title = "Note:", 
-    symbol        = c("p < .05,","p < .01"),
-    symbol_manual = c("*", "**"),
-    footnote_as_chunk = T,
-    title_format = "italic",
-    threeparttable = T
+  border_remove() %>% 
+  border(i = 1, j = c("1","2","3","4","5","6","7","8","9","10"), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 16, border.bottom = fp_border_default(), part = "body") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  set_table_properties(width = 1, layout = "autofit") %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 13
+  ) %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 13
+  ) %>% 
+    add_footer_row(
+    values = " ",
+    colwidths = 13
+  ) %>% 
+  compose(
+    i = 1, j = 1, 
+    as_paragraph(as_i("Note: "), "Column headers denote adversity constructs and rows indicate components. The upper triangle contain sample sizes for each correlation."), 
+    part = "footer"
+  ) %>% 
+  compose(
+    i = 2, j = 1, 
+    as_paragraph(as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
+    part = "footer"
   ) 
@@
 
-(ref:figure2) Visualization of multiverse attention shifting results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
-
-```{r figure2, fig.height=7.25, fig.width=6.25, fig.cap='(ref:figure2)'}
+```{r figure2, fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results.
+Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
 fig2
@@
 
-```{r table2, results='asis'}
+```{r table2, tab.id = "table2", tab.cap.style = "Table Caption", tab.cap = "Median standardized effects, 95% confidence intervals, percent significant, and bootstrapped p-values for the main effect of adversity and interaction terms for adversity by task version for attention shifting and working memory updating."}
 table.02.0 %>% 
@@
   select(-dv) %>% 
-  mutate(across(.cols = contains("p_percent"), ~ str_replace(.x, "%", "\\\\%"))) %>% 
-   kable(
-    col.names = c(" ","$\\beta$", "95\\% CI","\\emph{p} (\\%)","\\emph{p}", "$\\beta$", "95\\% CI","\\emph{p} (\\%)","\\emph{p}"),
-    booktabs = T,
-    escape = F,
-    caption = "\\emph{Median standardized effects, 95\\% confidence intervals, percent significant, and bootstrapped p-values for the main effect of adversity and interaction terms for adversity by task version for attention shifting and working memory updating.}"
+  add_column(.after = 5,"empty1" = "") %>% 
+  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
+  add_row(.after = 4, "iv" = "Working Memory Updating") %>% 
+  flextable() %>% 
+  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 5, j1 = 1, j2 = 10) %>% 
+  bold(i = c(1,5), j = 1) %>% 
+  padding(i = c(2:4, 6:8), j = 1, padding.left = 10) %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(iv = "", empty1 = "", ci_main = "95% CI", ci_int = "95% CI") %>% 
+  add_header_row(
+    values = c(" ", "Main Effect", " ", "Interaction"),
+    colwidths = c(1, 4, 1, 4)
   ) %>% 
-  add_header_above(c(" " = 1, "Main Effect" = 4, "Interaction" = 4)) %>% 
-  group_rows(group_label = "Attention Shifting", start_row = 1, end_row = 3) %>% 
-  group_rows(group_label = "Working Memory Updating", start_row = 4, end_row = 6) %>% 
-  kable_styling(latex_options = "scale_down") %>% 
-  footnote(
-    general = "The p (%) column reflects the number of analyses that produced p-values < .05 out of all analyses for a given multiverse analyses.
+  compose(i = 2, j = c(2,7), as_paragraph("\U1D6FD"), part = "header") %>% 
+  compose(i = 2, j = c(4,9), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p")), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 8, border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  set_table_properties(width = 1, layout = "autofit") %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 10
+  ) %>% 
+    add_footer_row(
+    values = " ",
+    colwidths = 10
+  ) %>% 
+  compose(
+    i = 1, j = 1, 
+    as_paragraph(as_i("Note: "), "The p (%) column reflects the number of analyses that produced p-values < .05 out of all analyses for a given multiverse analyses.
 The total number of analyses for each measure was 64.
-Overall p-values were computed using a bootstrapping resampling method and reflect the probability of obtaining an effect size as extreme or more extreme given the median effect is 0.",
-    general_title = "Note:", 
-    footnote_as_chunk = T,
-    title_format = "italic",
-    threeparttable = T
+Overall p-values were computed using a bootstrapping resampling method and reflect the probability of obtaining an effect size as extreme or more extreme given the median effect is 0."),
+    part = "footer"
   )
@@
 
-(ref:figure3) Visualization of multiverse working memory updating results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
-Proportions of each arbitrary decision with *p*-values \< .05 are indicated on the right side of each specification grid.
-Blank proportions indicate proportions = 0.
-
-```{r figure3, fig.height=7.25, fig.width=6.25, fig.cap='(ref:figure3)'}
+```{r figure3, fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results.
+Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
+Proportions of each arbitrary decision with *p*-values < .05 are indicated on the right side of each specification grid.
+Blank proportions indicate proportions = 0."}
 fig3
@@
 
-```{r table3, results='asis'}
+```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap = "Median simple effects (unstandardized) and percent significant for task version and adversity for attention shifting and working memory updating."}
 table.03.0 %>% 
@@
   select(-dv) %>% 
-  mutate(across(.cols = contains("p_percent"), ~ str_replace(.x, "%", "\\\\%"))) %>% 
-   kable(
-    col.names = c(" ", "\\emph{b} (abs)", "\\emph{p} (\\%)","\\emph{b} (eco)", "\\emph{p} (\\%)", "\\emph{b} (low)", "\\emph{p} (\\%)","\\emph{b} (high)", "\\emph{p} (\\%)"),
-    booktabs = T,
-    escape = F,
-    caption = "\\emph{Median simple effects (unstandardized) and percent significant for task version and adversity for attention shifting and working memory updating.}"
+  add_column(.after = 5,"empty1" = "") %>% 
+  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
+  add_row(.after = 4, "iv" = "Working Memory Updating") %>% 
+  flextable() %>% 
+  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 5, j1 = 1, j2 = 10) %>% 
+  bold(i = c(1,5), j = 1) %>% 
+  padding(i = c(2:4, 6:8), j = 1, padding.left = 10) %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(iv = "", empty1 = "") %>% 
+  add_header_row(
+    values = c(" ", "Task Version", " ", "Adversity Exposure"),
+    colwidths = c(1, 4, 1, 4)
   ) %>% 
-  add_header_above(c(" " = 1, "Task Version" = 4, "Adversity Exposure" = 4)) %>% 
-  group_rows(group_label = "Attention Shifting", start_row = 1, end_row = 3) %>% 
-  group_rows(group_label = "Working Memory Updating", start_row = 4, end_row = 6) %>% 
-  kable_styling(latex_options = "scale_down") %>% 
-  footnote(
-    general = "Simple effects for Task Version reflect the median effect of adversity in for the abstract version (abs) and ecological version (eco).
+  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
+  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
+  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
+  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 8, border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  fontsize(size = 11, part = "body") %>%
+  set_table_properties(width = 1, layout = "autofit") %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 10
+  ) %>% 
+    add_footer_row(
+    values = " ",
+    colwidths = 10
+  ) %>% 
+  compose(
+    i = 1, j = 1, 
+    as_paragraph(as_i("Note: "), "Simple effects for Task Version reflect the median effect of adversity in for the abstract version (abstract) and ecological version (ecological).
 Simple effects for Adversity reflect the effect of task version when adversity-exposure is low (-1 SD) and high (+1 SD).
 P-values < .05 out of all analyses for a given multiverse analyses.
-The total number of analyses for each measure was 64.",
-    general_title = "Note:", 
-    footnote_as_chunk = T,
-    title_format = "italic",
-    threeparttable = T
+The total number of analyses for each measure was 64."),
+    part = "footer"
   )
@@
 For poverty exposure, interview-based parental occupational prestige and school-reported economic disadvantage showed some interaction effects (parental education/occupational prestige `r secondary1_medians$updating.ses.Parents.iv_type_z$p_percent` of *ps* \<.05; school coded economic disadvantage `r secondary1_medians$updating.ses.School.iv_type_z$p_percent` of *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 12).
-Self-reported perceived resource scarcity showed no interaction effects (see SI Table \@ref(tab:table2), SI Table 3, and SI Figure 12).
+Self-reported perceived resource scarcity showed no interaction effects (see SI Table 2, SI Table 3, and SI Figure 12).
 

### 2021-12-21 supplement/supplement.Rmd
fixing scripts - CD revision 1

---
title: "Supplementary Material"
subtitle: "*Can real-world stimuli improve cognitive performance for children living in adversity?*"
output:
   bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: false
    lof: yes
    toc: false
    extra_dependencies: ["booktabs","caption","longtable","float"]
    keep_tex: true
geometry: margin=.5in
mainfont: Times
fontsize: 11pt
urlcolor: blue
header-includes:
- \usepackage{siunitx}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.align = 'center', fig.pos = "H", fig.show = 'asis')

library(tidyverse)
library(gt)

load("staged-objects.Rdata")
```

# Overview

This document contains two parts. First, we report our full multiverse primary analyses, including covariates (e.g., age and distractions during cognitive testing). Second, we provide visualizations for both of our secondary, exploratory analyses. The first set were focused on exploring the components of adversity dimensions. The second focuses on comparing violence $\times$ task version interaction with poverty $\times$ task version interaction.

Below are links to each of these sections:

**[Primary Analyses](#sec1)**

- [SI Table 1](#tab1) (Median Effects)
- *Attention Shifting*
  - [SI Figure 1](#fig1) (Unpredictability)
  - [SI Figure 2](#fig2) (Violence Exposure)
  - [SI Figure 3](#fig3) (Poverty Exposure)
- *Working Memory Updating*
  - [SI Figure 4](#fig4) (Unpredictability)
  - [SI Figure 5](#fig5) (Violence Exposure)
  - [SI Figure 6](#fig6) (Poverty Exposure)

**[Secondary Analyses](#sec2)**

- *[Exploring Components of Adversity Dimensions](#sec2a)*
  - [SI Table 2](#tab2) (Median Effects)
  - [SI Table 3](#tab3) (Median Simple Effects)
  - *Attention Shifting*
    - [SI Figure 7](#fig7) (Unpredictability)
    - [SI Figure 8](#fig8) (Violence Exposure)
    - [SI Figure 9](#fig9) (poverty)
  - *Working Memory Updating*
    - [SI Figure 10](#fig10) (Unpredictability)
    - [SI Figure 11](#fig11) (Violence Exposure)
    - [SI Figure 12](#fig12) (Poverty Exposure)
- *[Comparing Violence and Poverty Exposure](#sec2b)*
  - [SI Table 4](#tab4) (Median Effects)
  - [SI Table 5](#tab5) (Median Simple Effects)
  - [SI Figure 13](#fig13) (Poverty vs Violence)

\pagebreak

# Primary Analyses - Covariates {#sec1}

We report multiverse plots for all terms in each of our primary analyses. In brief, our mixed-effects models included the following fixed terms: the main effect of task version (abstract or ecological version, within-subjects), the main effect of childhood adversity (between-subjects), the interaction between task version and adversity measure, the main effect of age (control variable), and the main effect of test distraction ratings (control variable). Task version was grand mean centered; scores on the abstract versions were coded as -1 and 1 for the ecological version. All childhood adversity measures were standardized before model fitting and all models included a random intercept for task version nested in participants.

For a table of all results:

 - [SI Table 1](#tab1) (Median Effects)

For attention shifting plots:

 - [SI Figure 1](#fig1) (Unpredictability)
 - [SI Figure 2](#fig2) (Violence Exposure)
 - [SI Figure 3](#fig3) (Poverty Exposure)

For working memory updating plots:

 - [SI Figure 4](#fig4) (Unpredictability)
 - [SI Figure 5](#fig5) (Violence Exposure)
 - [SI Figure 6](#fig6) (Poverty Exposure)

\pagebreak

### SI Table 1. Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for all terms predicting attention shifting. {#tab1}

```{r sitables1, results='asis'}
si_table.01.1 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  cat()
```

\pagebreak

### SI Figure 1. Unpredictability and Attention Shifting specification plot with all covariates. {#fig1}

```{r sifig1, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_unp
```

\pagebreak

### SI Figure 2. Violence exposure and Attention Shifting specification plot with all covariates. {#fig2}

```{r sifig2, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_vio
```

\pagebreak

### SI Figure 3. Poverty and Attention Shifting specification plot with all covariates. {#fig3}

```{r sifig3, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
shifting_ses
```

\pagebreak

### SI Figure 4. Unpredictability and working memory updating specification plot with all covariates. {#fig4}

```{r sifig4, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_unp
```

\pagebreak

### SI Figure 5. Violence exposure and working memory updating specification plot with all covariates. {#fig5}

```{r sifig5, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_vio
```

\pagebreak

### SI Figure 6. Poverty and working memory updating specification plot with all covariates. {#fig6}

```{r sifig6, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
updating_ses
```

\pagebreak

# Secondary Analyses {#sec2}

We followed-up our primary analyses with two sets of secondary, exploratory analyses. Secondary analysis plans were uploaded to OSF prior to conducting them (see https://osf.io/7fu35/ and https://osf.io/wcauf/). These analyses were focused on two questions. First, in contrast to prior work (i.e., Mittal et al., 2015; Young et al., 2018) we found no interactive effect for environmental unpredictability and task version on attention shifting or working memory updating performance (but some evidence for main effects on attention shifting). However, prior work has measured retrospective perceptions of environmental unpredictability whereas the current combined perceptions with objective, interview-based measures. Thus, one possibility is specific components of our adversity measures may have unique effects on attention shifting and working memory updating. To address this, we expanded our multiverse approach to include each version of our independent variables as a arbitrary data decision.

The second question focused on the interactive effects of task version $\times$ violence exposure and task version $\times$ poverty on working memory updating performance. Specifically, primary analyses revealed an equalization effect for both violence and poverty exposure. However, because violence and poverty were not included in the same underlying model, the extent to which they are independent is unclear. For example, one possibility is that violence and poverty exposure exert unique and independent effects on working memory updating. Alternatively, these interactions could reflect the same effect. To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, poverty and violence, and two interaction terms: task version × violence exposure and task version × poverty in the same model. If violence exposure and poverty interact independently with task version, both interactions should remain significant. However, if they overlap, one effect may be driving the other.

## Exploring Components of Adversity Dimensions {#sec2a}

We ran an expanded multiverse analysis to explore the effects of each component making up our adversity composites. Environmental unpredictability contained two components, perceived unpredictability (self-reported) and an interview-based measure tabulating family disruptions, parental transitions and residential moves. Violence exposure contained two self-reports: neighborhood violence and exposure to and involvement in violence. Poverty exposure contained three components: parental education/occupation, perceived resource scarcity, and school-coded economic disadvantage (e.g., fee waivers, free or reduced priced lunch, and homelessness).

For this expanded multiverse approach, we retained all original data processing decisions and added an adversity component as an additional decision. For environmental unpredictability, we analyzed  both unpredictability components and the composite (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 192 analyses (64 original $\times$ three versions of unpredictability). The same approach was applied to violence exposure (3 violence exposure variables, 192 analyses) and poverty exposure (4 poverty variables, 256 analyses).

For tables of all median effects and simple effects:

 - [SI Table 2](#tab2) (Median Effects)
 - [SI Table 3](#tab3) (Simple Effects)

For attention shifting plots:

 - [SI Figure 7](#fig7) (Unpredictability)
 - [SI Figure 8](#fig8) (Violence Exposure)
 - [SI Figure 9](#fig9) (Poverty Exposure)

For working memory updating plots:

 - [SI Figure 10](#fig10) (Unpredictability)
 - [SI Figure 11](#fig11) (Violence Exposure)
 - [SI Figure 12](#fig12) (Poverty Exposure)

\pagebreak

### SI Table 2. Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for main effects of adversity components and interactions with task version for attention shifting and working memory updating.{#tab2}

```{r sitables2, results='asis'}
si_table.02.0 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
  cat()
```

\pagebreak

### SI Table 3. Median simple slopes (unstandardized) and percent significant for adversity component interactions with task version for attention shifting and working memory updating. {#tab3}

```{r sitables3, results='asis'}
si_table.03.0 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  cat()
```

\pagebreak

### SI Figure 7. Unpredictability components and attention shifting multiverse results. {#fig7}

```{r sifig7, fig.width=8, fig.height=7.5, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids task version by unpredictability components."}
unp_shifting
```

\pagebreak

### SI Figure 8. Violence exposure components and attention shifting multiverse results. {#fig8}

```{r sifig8, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
vio_shifting
```

\pagebreak

### SI Figure 9. Poverty components and attention shifting multiverse results. {#fig9}

```{r sifig9, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
ses_shifting
```

\pagebreak

### SI Figure 10. Unpredictability components and working memory updating multiverse results. {#fig10}

```{r sifig10, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by unpredictability component interactions"}
unp_updating
```

\pagebreak

### SI Figure 11. Violence exposure components and working memory updating multiverse results. {#fig11}

```{r sifig11, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
vio_updating
```

\pagebreak

### SI Figure 12. Poverty components and working memory updating multiverse results. {#fig12}

```{r sifig12, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
ses_updating
```

\pagebreak

## Comparing Violence and Poverty Exposure {#sec2b}

Our second set of secondary analyses focused on the interactive effects of task version × violence exposure and task version × poverty exposure on working memory updating performance. Specifically, primary analyses revealed an equalization effect for both violence and poverty exposure. However, because violence and poverty were not included in the same underlying model, it is unclear if each interaction is independent from the other. For example, one possibility is that violence exposure and poverty exert unique and independent effects on working memory updating. Alternatively, these interactions could reflect the same effect. To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, Poverty and violence, and two interaction terms: task version × violence exposure and task version × poverty exposure in the same model.

For results see:

- [SI Table 4](#tab4) (Median Effects)
- [SI Table 5]($tab5) (Simple Effects)
- [SI Figure 13](#fig13) (Plots)

\pagebreak

### SI Table 4. Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for multiverse analyses comparing Poverty $\times$ task version and violence $\times$ task version interactions.{#tab4}

```{r sitables4, results='asis'}
si_table.04.0 %>% 
  as_latex() %>% 
  as.character() %>% 
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
  cat()
```

### SI Table 5. Median simple slopes (unstandardized) and percent significant for multiverse analyses comparing Poverty $\times$ task version and violence $\times$ task version interactions. {#tab5}

```{r sitables5, results='asis'}
si_table.05.0 %>%
  as_latex() %>%
  as.character() %>%
  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>%
  cat()
```

\pagebreak

### SI Figure 13. Multiverse results for Poverty and violence exposure interactions with task version in the same model. {#fig13}

```{r sifig13, fig.height=7.5, fig.width=5.25, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence and task version by poverty"}
vio_ses_updating
```

### 2021-12-21 supplement/supplement_docx.Rmd
fixing scripts - CD revision 1

--- 2021-12-21 supplement/supplement.Rmd
@@
 output:
-   bookdown::pdf_document2:
-    latex_engine: xelatex
-    number_sections: false
-    lof: yes
-    toc: false
-    extra_dependencies: ["booktabs","caption","longtable","float"]
-    keep_tex: true
-geometry: margin=.5in
-mainfont: Times
-fontsize: 11pt
-urlcolor: blue
-header-includes:
-- \usepackage{siunitx}
+  officedown::rdocx_document:
+    reference_docx: reference-doc.docx
+    page_size:
+      width: 8.5
+      height: 11
+      orient: "portrait"
+    page_margins:
+      bottom: .5
+      top: .5
+      right: .25
+      left: .25
+      header: 0
+      footer: 0
+      gutter: 0
+    plots:
+      align: center
+      style: Normal
+      caption:
+        style: Image Caption
+        pre: 'SI Figure '
+        sep: '. '
+    tables:
+      caption:
+        style: Table Caption
+        pre: 'SI Table '
+        sep: '. '
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.align = 'center', fig.pos = "H", fig.show = 'asis')
+# set up chunk options
+knitr::opts_chunk$set(
+  echo = F,
+  fig.align = "center",
+  fig.pos = "!t", 
+  fig.show = "asis",
+  fig.width = 8, 
+  fig.height = 7.5,
+  dpi = 600,
+  out.extra = "",
+  message = FALSE,
+  warning = FALSE
+)
 
+# load libraries
 library(tidyverse)
-library(gt)
+library(officer)
+library(flextable)
 
+# load all data and objects
 load("staged-objects.Rdata")
+
+# set up flextable for tables
+set_flextable_defaults(
+  font.family = "Times", 
+  font.size = 10,
+  font.color = "black",
+  line_spacing = 1,
+  padding.bottom = 1, 
+  padding.top = 1,
+  padding.left = 1,
+  padding.right = 1
+)
 ```
@@
 
-```{r sitables1, results='asis'}
-si_table.01.1 %>% 
-  as_latex() %>% 
-  as.character() %>% 
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
-  cat()
+```{r sitables1}
+si_table.01.1$`_data` %>% 
+  add_column(.after = 6,"empty1" = "") %>% 
+  add_row(.before = 1, "mod_term_label" = "Unpredictability") %>% 
+  add_row(.after = 6, "mod_term_label" = "Violence") %>% 
+  add_row(.after = 12, "mod_term_label" = "Poverty") %>%
+  select(-iv) %>% 
+  flextable() %>% 
+  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 7, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 12, j1 = 1, j2 = 10) %>% 
+  bold(i = c(1,7,13), j = 1) %>% 
+  padding(i = c(2:6, 8:12, 14:18), j = 1, padding.left = 10) %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(
+    iv = "", mod_term_label = "Term", 
+    empty1 = "", 
+    ci_shifting = "95% CI", 
+    ci_updating = "95% CI"
+    ) %>% 
+  add_header_row(
+    values = c(" ", "Attention Shifting", " ", "Working Memory Updating"),
+    colwidths = c(1, 4, 1, 4)
+  ) %>% 
+  compose(i = 2, j = c(2,7), as_paragraph(as_i("N")), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph("\U1D6FD"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 18, border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  set_table_properties(width = 1, layout = "autofit")
 ```
@@
 
-```{r sifig1, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig1, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
 shifting_unp
@@
 
-```{r sifig2, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig2, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
 shifting_vio
@@
 
-```{r sifig3, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig3, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
 shifting_ses
@@
 
-```{r sifig4, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig4, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
 updating_unp
@@
 
-```{r sifig5, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
 updating_vio
@@
 
-```{r sifig6, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig6, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
 updating_ses
@@
 
-For tables of all median effects and simple effects:
+**For tables of all median effects and simple effects:**
 
@@
 
-For attention shifting plots:
+**For attention shifting plots:**
 
@@
 
-For working memory updating plots:
+**For working memory updating plots:**
 
@@
 
-```{r sitables2, results='asis'}
-si_table.02.0 %>% 
-  as_latex() %>% 
-  as.character() %>% 
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
-  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
-  cat()
+```{r sitables2}
+si_table.02.0$`_data` %>% 
+  mutate(mod_term_label = str_replace(mod_term_label,"\\$\\\\times\\$","x")) %>% 
+  add_column(.after = 6,"empty1" = "") %>% 
+  add_row(.before = 1, "mod_term_label" = "Unpredictability") %>% 
+  add_row(.after = 7, "mod_term_label" = "Violence") %>% 
+  add_row(.after = 14, "mod_term_label" = "Poverty") %>%
+  select(-iv) %>% 
+  flextable() %>% 
+  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 8, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 15, j1 = 1, j2 = 10) %>% 
+  bold(i = c(1,8,15), j = 1) %>% 
+  padding(i = c(2:7, 9:14, 16:23), j = 1, padding.left = 10) %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(
+    iv = "", mod_term_label = " ", 
+    empty1 = "", 
+    ci_shifting = "95% CI", 
+    ci_updating = "95% CI"
+    ) %>% 
+  add_header_row(
+    values = c(" ", "Attention Shifting", " ", "Working Memory Updating"),
+    colwidths = c(1, 4, 1, 4)
+  ) %>% 
+  compose(i = 2, j = c(2,7), as_paragraph(as_i("N")), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph("\U1D6FD"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  align(i = 2, j = 1, align = "left", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 23, border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  set_table_properties(width = 1, layout = "autofit")
 ```
@@
 
-```{r sitables3, results='asis'}
-si_table.03.0 %>% 
-  as_latex() %>% 
-  as.character() %>% 
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
-  cat()
+```{r sitables3}
+si_table.03.0$`_data` %>% 
+  add_column(.after = 6,"empty1" = "") %>% 
+  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
+  add_row(.after = 11, "iv" = "Working Memory Updating") %>%
+  select(-dv) %>% 
+  flextable() %>% 
+  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 12, j1 = 1, j2 = 10) %>% 
+  bold(i = c(1,12), j = 1) %>% 
+  padding(i = c(2:11, 13:22), j = 1, padding.left = 10) %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(iv = "", empty1 = "") %>% 
+  add_header_row(
+    values = c(" ", "Task Version", " ", "Adversity Exposure"),
+    colwidths = c(1, 4, 1, 4)
+  ) %>% 
+  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
+  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
+  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
+  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = c(11,22), border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  fontsize(size = 11, part = "body") %>%
+  set_table_properties(width = 1, layout = "autofit")
 ```
@@
 
-```{r sifig7, fig.width=8, fig.height=7.5, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids task version by unpredictability components."}
+```{r sifig7, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids task version by unpredictability components."}
 unp_shifting
@@
 
-```{r sifig8, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
+```{r sifig8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
 vio_shifting
@@
 
-```{r sifig9, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
+```{r sifig9, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
 ses_shifting
@@
 
-```{r sifig10, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by unpredictability component interactions"}
+```{r sifig10, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by unpredictability component interactions"}
 unp_updating
@@
 
-```{r sifig11, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
+```{r sifig11, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
 vio_updating
@@
 
-```{r sifig12, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
+```{r sifig12, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
 ses_updating
@@
 
-```{r sitables4, results='asis'}
-si_table.04.0 %>% 
-  as_latex() %>% 
-  as.character() %>% 
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
-  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
-  cat()
+```{r sitables4}
+si_table.04.0$`_data` %>% 
+  mutate(mod_term_label = str_replace(mod_term_label,"\\$\\\\times\\$","x")) %>% 
+  flextable() %>% 
+  set_header_labels(
+    iv = "", mod_term_label = " ", 
+    empty1 = "", 
+    ci = "95% CI"
+  ) %>% 
+  compose(i = 1, j = c(2), as_paragraph("\U1D6FD"), part = "header") %>% 
+  compose(i = 1, j = c(4), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  compose(i = 1, j = c(5), as_paragraph("median ", as_i("N")), part = "header") %>% 
+  fontsize(size = 11, part = "body") %>%
+  set_table_properties(width = .5, layout = "autofit")
 ```
@@
 
-```{r sitables5, results='asis'}
-si_table.05.0 %>%
-  as_latex() %>%
-  as.character() %>%
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>%
-  cat()
+```{r sitables5}
+si_table.05.0$`_data` %>% 
+  add_column(.after = 5,"empty1" = "") %>% 
+  flextable() %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(iv = "", empty1 = "") %>% 
+  add_header_row(
+    values = c(" ", "Task Version", " ", "Adversity Exposure"),
+    colwidths = c(1, 4, 1, 4)
+  ) %>% 
+  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
+  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
+  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
+  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = c(2), border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  fontsize(size = 11, part = "body") %>%
+  set_table_properties(width = .75, layout = "autofit")
 ```

### 2021-12-21 manuscript/scripts/figure-2-3.R

@@ -290,12 +290,15 @@ spec_curves <-
     if(dv_which == "Attention-Shifting"){
       int_plots <- 
         int_plots +
-        ylab("Switch Cost (ms)\n")
+        scale_y_reverse(n.breaks = 5) +
+        ylab("Switch Cost (ms)\n") +
+        theme(legend.position = c(.25,.8))
     }
     
     if(dv_which == "Working Memory Updating"){
       int_plots <- 
         int_plots +
+        scale_y_continuous(breaks = seq(69, 77, 2)) +
         ylab("% correct\n")
     }
     
@@ -313,7 +316,7 @@ fig2 <-
   ggdraw() +
   draw_plot(
     plot_grid(
-      spec_curves[[1]]$interactions,
+      spec_curves[[1]]$interactions ,
       spec_curves[[1]]$p_curve,
       spec_curves[[1]]$eff_curve,
       spec_curves[[1]]$sample_sizes,
@@ -324,6 +327,7 @@ fig2 <-
       axis  = "lr",
       rel_heights = c(.25,.15,.2,.1,.3)
     ) +
+      draw_plot_label(c("(faster)","(slower)"), x = 0.075, y = c(.95, .78), size = 8, vjust = 1, hjust = 0, fontface = "italic") +
       draw_plot_label(c("a","b","c","d","e"), x = 1, y = c(.95, .75, .6, .4, .3), size = 10, vjust = 1, hjust = 1), 
     x = 0, y = 0, width = 1, height = .95
   ) + 
@@ -344,6 +348,7 @@ fig3 <-
       axis  = "lr",
       rel_heights = c(.25,.15,.2,.1,.3)
     ) +
+      draw_plot_label(c("(more accurate)","(less accurate)"), x = 0.11, y = c(.95, .785), size = 8, vjust = 1, hjust = 1, fontface = "italic") +
       draw_plot_label(c("a","b","c","d","e"), x = 1, y = c(.95, .75, .6, .4, .3), size = 10, vjust = 1, hjust = 1), 
     x = 0, y = 0, width = 1, height = .95
   ) + 

### 2021-12-21 scripts/1-data-prep/3-secondary-multiverse-datasets.R

@@ -48,10 +48,6 @@ spec_grid <-
       "iv",              0,           "unp_agg",                                               "Unp Composite",
       "iv",              1,           "unp_interview",                                         "Unp Interview",
       "iv",              2,           "unp_perceived",                                         "Unp Perceived",
-      "iv",              1,           "unp_interview",                                         "Unp Perceived",
-      "iv",              2,           "unp_perceived",                                         "Unp Interview",
-      "iv",              1,           "unp_interview",                                         "Unp Perceived",
-      "iv",              2,           "unp_perceived",                                         "Unp Interview",
       "iv",              3,           "vio_agg",                                               "Vio Composite",
       "iv",              4,           "vio_neighborhood",                                      "Vio Neighborhood",
       "iv",              5,           "vio_fighting",                                          "Vio Fighting",

### 2021-12-21 supplement/scripts/rmd-staging.R

@@ -3,6 +3,7 @@ library(tidyverse)
 library(cowplot)
 library(see)
 library(gt)
+library(psych)
 
 # ggplot2 theme -----------------------------------------------------------
 theme_set(
@@ -34,11 +35,15 @@ my_alphas <- c(.5, 1)
 my_limits <- c(1,70)
 
 # Multiverse Objects ----
+load("multiverse-objects/1-multiverse-datasets/datalist-agg-ivs.Rdata")
+load("data/data1_raw.Rdata")
+load("data/data2_analysis.Rdata")
 load("multiverse-objects/2-primary-analyses/3-extracted-effects.Rdata")
 load("multiverse-objects/3-secondary-analyses/set-2/a1-extracted-effects.Rdata")
 load("multiverse-objects/3-secondary-analyses/set-1/a2-extracted-effects.Rdata")
 
 # Make plots and tables ----
+source("supplement/scripts/0-corr_table.R")
 source("supplement/scripts/1-covariates.R")
 source("supplement/scripts/2-secondary1.R")
 source("supplement/scripts/3-secondary2.R")

### 2022-01-18 README.Rmd
fix typos in README
CD revision 1, updaating manuscript and supplement

@@
 ---
-title: "Hidden Talents Multiverse Analysis"
+title: "Hidden Talents in Context: Multiverse analysis repository"
 output: github_document
@@
 
-This repository contains data, code, and (some) output for a working manuscript.
+This repository contains data, code, and (some) output for a manuscript entitled "Hidden talents in context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth" submitted to and under review at *Child Development*.
 
@@
 The `.Rmd` fie contains the written text with all figures, tables, and in-text statistics.
-All outputs reported in the manuscript were staged prior to compiling into a `.pdf` document and stored in a `.Rdata` file called `staged-objects.Rdata`.
+All outputs reported in the manuscript were staged prior to compiling into a `.docx` document and stored in a `.Rdata` file called `staged-objects.Rdata`.
 The R Markdown document reads these staged files to make the overall document easier to read.
@@
 
-### Seconary Analyses
+### Secondary Analyses
 
@@
 This directory contains the supplement to the manuscript described above.
-The supplement was produced using the same approach as the manuscript: it was written in R Markdown, is 100% reproducible, and all outputs were staged prior to compiling into a `.pdf`.
+The supplement was produced using the same approach as the manuscript: it was written in R Markdown, is 100% reproducible, and all outputs were staged prior to compiling into a `.docx`.
 The staged objects are stored in `supplement/staged-objects.Rdata`.
@@
 2. `1-data-prep/2-primary-multiverse-datasets.R`
-3. `1-data-prep/3-sedoncary-multiverse-datasets.R`
+3. `1-data-prep/3-secondary-multiverse-datasets.R`
 
@@
     - `4-tables.R`
+    - `5-tables-r1.R`
 2. `supplement/supplement.Rmd`: loads `supplement/staged-objects.Rdata` and knits together the written supplement and all tables and figures computed by the staging script above.

### 2022-01-18 manuscript/manuscript.Rmd
CD revision 1, updaating manuscript and supplement

@@
   message = FALSE,
+  tab.topcaption = T,
   warning = FALSE
@@
 
-\noindent Adversity-exposed youth often perform poorly on standard cognitive tests.
+\noindent Adversity-exposed youth tend to score lower on cognitive tests.
 However, the hidden talents approach proposes some abilities are enhanced by adversity, especially under ecologically relevant conditions.
-Sampling 618 adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White), we administered two versions of an attention shifting and working memory updating task—one abstract, one ecological.
+Sampling `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White), we administered two versions of an attention shifting and working memory updating task---one abstract, one ecological.
 We measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions.
-There were no interactions for attention shifting, but there were main effects of unpredictability and violence, indicating improved attention shifting, on average.
-For working memory updating, violence- and poverty-exposed youth performed worse on the abstract but not the ecological version, equalizing performance.
-We found no relation between updating and unpredictability.
+There were no interactions for attention shifting.
+For working memory updating, youth exposed to violence and poverty scored lower than their peers with abstract stimuli but just as well with ecological stimuli.
+These results are striking compared to contemporary developmental science, which almost exclusively reports lowered performance among adversity-exposed youth.
 
@@
 
-# Hidden talents in context: Can ecologically relevant stimuli improve cognitive performance among adversity-exposed youth?
+# Hidden talents in context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth
 
-Children living in harsh conditions tend to perform poorly on many cognitive tests.
-For example, children raised in poverty often show difficulties learning in school and score lower on standardized tests [@ursache2016a; @farah2006; @noble2007; @hackman2010].
-Harsh and unpredictable environments are thought to cause high levels of chronic stress, which impacts brain regions responsible for memory and learning [@blair2012].
-Thus, the general consensus is that exposure to adversity undermines cognitive development and leads to a host of cognitive impairments [@hackman2010].
-Although it is clear that harsh environments are harmful to children, there is growing interest in the *hidden talents* *approach*, which proposes that some abilities may be enhanced by adversity, especially those abilities that are ecologically relevant to lived experience.
-Thus, hidden talents are skills and abilities that help children meet real-world challenges in adverse environments [@ellis2017; @ellis2020; @frankenhuis2013; @frankenhuis2020].
+Youth living in adverse conditions tend to score lower on cognitive tests than youth in supportive conditions.
+For example, youth raised in poverty are more likely to have difficulties learning in school and score lower on standardized tests [@farah2006; @hackman2010; @noble2007; @ursache2016a].
+Harsh and unpredictable environments are thought to cause high levels of chronic stress, which can impair brain regions responsible for memory and learning [@blair2012].
+Thus, the contemporary view is that exposure to adversity undermines cognitive development and leads to a host of cognitive deficits [see @duncan2017; @hackman2010; @mclaughlin2019; @pechtel2011 for reviews].
+Although it is clear that harsh and unpredictable environments are harmful to youth, there is growing interest in the *hidden talents approach*, which proposes that some abilities may be enhanced by adversity, especially skills and abilities that help youth meet real-world challenges in adverse environments [@ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013].
 
-The hidden talents framework assumes that development shapes the skills and abilities of individuals in relation to their environment [@ellis2017; @ellis2020; @frankenhuis2013; @frankenhuis2020].
-Accordingly, exposure to adversity should shape skills and abilities well-suited for dealing with the challenges associated with harsh environments.
-However, because specific dimensions of adversity (violence versus resource-scarcity) may pose unique challenges [@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity [@frankenhuis2020].
-For instance, physically abused children can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], people living in poverty have shown some evidence of enhanced social perception [@piff2018], and anxiously attached people are good at deception detection [@eindor2014; @shoda2013] to list a few examples [see @ellis2017; @ellis2020 for reviews].
+The hidden talents framework assumes that development shapes the skills and abilities of individuals in relation to their environment [see @ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013 for reviews] and assumes development tailors skills and abilities in relation to their environment.
+Accordingly, exposure to adversity should shape skills and abilities well-suited for dealing with the challenges associated with harsh and unpredictable environments.However, because specific dimensions of adversity (violence versus resource-scarcity) may pose unique challenges [@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity [@frankenhuis2020].
+For instance, some evidence suggests physically abused youth can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], people living in poverty have more accurate social perception [@bjornsdottir2017; @dietze2021; @piff2018], and anxiously attached people can more accurately detect deception [@eindor2014; @shoda2013] to list a few examples [see @ellis2017; @ellis2020 for reviews].
 
@@
 For example, previous studies of hidden talents have tested cognition under ecologically relevant *contexts and situations*.
-In particular, studies have experimentally manipulated the current context to be uncertain and mildly stressful (or not) and measured performance on executive functioning and working memory tasks [@mittal2015; @young2018; but see @nweze2021 for similar results without uncertainty].
-Strikingly, people from unpredictable environments showed improved performance on attention-shifting and working memory updating tasks.
-However, this effect only emerged under conditions of uncertainty.
-There was no performance improvement under control conditions.
+In particular, studies have experimentally manipulated the current context to be uncertain and mildly stressful (or not) and measured performance on executive functioning and working memory tasks [@mittal2015; @young2018].
+Strikingly, people from unpredictable environments showed more efficient switching on attention shifting tasks and more accurate responses on working memory updating tasks, but this effect only emerged under conditions of uncertainty.
+There was no performance increase under control conditions.
+However, some studies have found similar patterns without uncertainty [see @fields2021 for attention shifting and @nweze2021 for working memory].
 
-Hidden talents may also emerge when testing *content and stimuli* are ecologically relevant to adversity-exposed individuals.
+Hidden talents may also emerge when testing *content and stimuli* are more ecologically relevant and concrete.
 Typical cognitive tests use abstract content that is largely detached from the real world.
@@
 Cultural psychologists and anthropologists have demonstrated this fact across the world.
-For example, people from low income and non-western cultures tend to perform worse on standard versions of cognitive tests, but this performance gap closes or disappears with more ecologically relevant versions of the same tests [@banerjee2017; @greenfield2014; @ogbu1981; @richardson1991; @schliemann2002].
-These findings pose an important question: Can ecologically relevant testing materials improve cognitive performance among adversity-exposed youth?
+For example, people from non-Western cultures tend to score lower than people in Western cultures on standard versions of cognitive tests, but this performance gap closes or disappears with more ecologically relevant versions of the same tests [@banerjee2017; @greenfield2014; @ogbu1981; @richardson1991; @schliemann2002].
+This work challenges the assumption that "baseline" performance is best captured by standard/abstract tests.
+In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020].
+These ideas also pose an important question: do adversity-exposed youth score higher on tests with ecological stimuli relative to those with abstract stimuli?
 
-One way to test this question is to simply replace sterile testing materials with ecologically relevant content.
+One way to test this question is to replace sterile testing materials with ecologically relevant content from the real world.
 For example, one study tested memory and reasoning among young adults who varied in their exposures to violence [@frankenhuis2020a].
 They created two versions of a memory and reasoning task, one neutral (chronological age) and one more ecologically relevant (social dominance).
-They found that people with more current exposures to violence were equally good, or even better, at memorizing social-dominance relationships compared to people with fewer exposures.
-Notably, such violence exposures were associated with worse memory for neutral (age) relationships.
-There were no associations revealed between violence exposures and reasoning performance.
-Overall, this study suggests that ecologically relevant testing materials may "level the playing field" for adversity-exposed youth [@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
-In addition, although executive functions and working memory are related to many educational outcomes, it is unclear how schools and teachers might leverage skills that specifically depend on inducing uncertainty.
+They found that people with more *current* exposures to violence were equally, or more, accurate when memorizing social-dominance relationships than people with fewer exposures.
+Notably, such violence exposures were associated with less accurate memory for neutral (age) relationships.
+This pattern was specific *current* exposures: people with more *childhood* exposures to violence memorized both content types less accurately.
+There were no associations between violence exposures and reasoning performance.
+Overall, this study suggests that ecologically relevant testing materials may in some conditions 'level the playing field' for adversity-exposed youth [@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
+
+Together, research testing performance in ecologically relevant contexts/situations and using ecologically relevant materials have generated innovative ideas and findings.
+Nonetheless, it remains unclear whether or how these ideas and findings can be practically applied.
+For example, narrow abilities, such as memorizing social dominance hierarchies or accurately detecting anger in faces, seem to have limited practical value in educational contexts.
+In addition, although executive functions and working memory are related to many educational outcomes, it is unclear how schools and teachers might leverage skills and abilities that specifically depend on inducing uncertainty.
 That seems impractical, at best, and unethical, at worst.
@@
 Here we address this issue by evaluating the role of ecologically relevant content in attention-shifting and working memory tasks.
-To do so, we sampled `r nrow(data2_non_arbitrary)` adolescents from a socioeconomically diverse population.
+We define ecological relevant content as testing material that resemble the local environment and therefore have more meaning and consequence.
+We used two criteria for stimulus selection.
+First, we selected stimuli that youth would encounter and interact with on a daily basis.
+Second, we selected stimuli believed to be more consequential or salient to adversity-exposed youth.
+For example, money is more consequential and perhaps salient to adversity-exposed youth than other neutral objects (a book, dishes, etc.).
+In addition, we target both between-subjects and within-subject improvement as patterns of interest.
+That is, improved performance compared to oneself (within-subjects -- one's performance on abstract compared to ecologically task versions), compared to others (between-subjects -- high versus low adversity), or some combination, are each theoretically important patterns of improvement.
+Our specific expectation was that all youth would score higher on tasks with ecological stimuli.
+However, we expected this increase to be larger among youth living in adverse conditions compared to youth in supportive conditions.
+
+To address our research questions, we sampled `r nrow(data2_non_arbitrary)` youth from a socioeconomically diverse population.
 Using interviews, self-reports, and school records, we measured exposure to environmental unpredictability, violence, and poverty.
+We used these information sources to arrive at a "best estimate" for each construct.
+Our a priori assumption was that each information source (e.g., interview, self-report, school provided information) would correlate within constructs, which was largely true (see Table \@ref(tab:table1)).
+
 We then tested performance on two widely used tasks: attention shifting and working memory updating.
 There were two versions of each task.
-The first used standard abstract stimuli and the second replaced these stimuli with more ecologically relevant ones (see Figure \@ref(fig:figure1)).
+The first used standard abstract stimuli and the second replaced these stimuli with more ecological stimuli from the real-world (see Figure 1).
 We then tested the interactive effect of task content and adversity exposure.
-
-We expected adversity-exposed adolescents to benefit more from ecologically relevant stimuli (compared to abstract stimuli) than their counterparts.
 As such, our primary analyses involved two preregistered confirmatory analyses and one exploratory analysis.
-Our confirmatory analyses focused on environmental unpredictability and violence exposure because both dimensions have been associated with improved performance under ecologically relevant conditions (contexts and testing materials) and represent specific environmental challenges.
-Our exploratory analyses focused on exposure to poverty, which is both relevant to hidden talents (e.g., hidden talents could develop in response to specific challenges of poverty) and a general proxy to adversity rather than a specific exposure.
+Our confirmatory analyses focused on environmental unpredictability and violence exposure.
+Both dimensions have been associated with improved performance under ecologically relevant conditions (contexts and testing materials) and represent specific environmental challenges.
+Our exploratory analyses focused on exposure to poverty.
+Poverty is both relevant to hidden talents (e.g., hidden talents could develop in response to specific challenges of poverty) and a general proxy to adversity rather than a specific exposure.
 
@@
 
-The current study collected data from `r txt1_sam$raw$n$total` adolescents (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah.
+The current study collected data from `r txt1_sam$raw$n$total` youth (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah.
 The first was a middle school and the second were 5 after-school clubs.
@@
 Specifically, we excluded participants: 1) with incomplete cognitive task data, 2) with apparent cognitive impairments (e.g., head injuries, disabilities, drug use), 3) who missed two or more trap questions, 4) exposed to extreme distractions during the assessment, and 5) who received more than 60 minutes per day of special education services.
-After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` adolescents (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).
+After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).
 In terms of racial identity, `r data2_non_arbitrary %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data2_non_arbitrary %>% filter(race == 2) %>%nrow()` as Native American, `r data2_non_arbitrary %>% filter(race == 3) %>% nrow()` as African American, `r data2_non_arbitrary %>% filter(race == 4) %>% nrow()` as White, `r data2_non_arbitrary %>% filter(race == 5) %>% nrow()` as Hispanic, `r data2_non_arbitrary %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data2_non_arbitrary %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data2_non_arbitrary %>% filter(is.na(race)) %>% nrow()` were missing.
@@
 
-Data collection involved six parts: consent/assent, demographics form, cognitive testing, structured interview, questionnaire, and a debriefing.
+Data collection involved six parts: consent/assent, demographics form, cognitive testing, structured interview, questionnaire, and debriefing.
 Consent was obtained from the primary parent or guardian before assessments and assent was obtained from the participant at the beginning of the session.
@@
 On the abstract (standard) attention-shifting task, participants categorized colored (blue or yellow) shapes (squares or triangles) according to the 'color' or 'shape' rule (see Figure \@ref(fig:figure1)a).
-For example, if a blue triangle appeared on the screen and the rule was "color", participants categorized the blue triangle as blue.
-However, if the rule was "shape", participants instead categorized the blue triangle as a triangle.
+For example, if a blue triangle appeared on the screen and the rule was 'color', participants categorized the blue triangle as blue.
+However, if the rule was 'shape', participants instead categorized the blue triangle as a triangle.
 
@@
 To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000].
-We removed fast and slow reaction times and removed trials after incorrect responses (see [attention shifting data cleaning procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
+We removed fast and slow reaction times and removed trials after incorrect responses (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
 We then subtracted the average reaction time on valid repeat trials from the average reaction time on valid switch trials to calculate switch cost scores (*M~switch~* - *M~repeat~*).
 The switch cost measures the relative delay in reaction time caused by switching between categorization rules.
-Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` ms (*SD* = `r txt2_dvs$eco_shifting_sc$sd` ms), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`).
+Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sc$sd` *ms*), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`).
 Higher switch costs mean longer reaction times on switch trials compared to repeat trials.
-Larger switch costs indicate less efficient attention shifting.
+Higher switch costs indicate less efficient attention shifting.
 
@@
 To create a composite measure of unpredictability, we aggregated across the interview and questionnaire.
-First, we created an interview-based measure of unpredictability using family disruptions, exposure to different parental figures, and residential moves involving new adults living in the home.
+First, we created an interview-based measure of unpredictability using family intactness or disruptions, exposure to different parental figures, and residential moves involving new adults living in the home.
 We standardized these interview measures and then averaged them together ($\alpha$ = `r txt4_rel$unp_int`).
@@
 
-We measured violence exposure using the Neighborhood Violence Scale [NVS, @frankenhuis2020a; @frankenhuis2018] and two items about witnessing and involvement in physical fights.
-The NVS contains 7 items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm".
+We measured violence exposure using the Neighborhood Violence Scale [@frankenhuis2020a; @frankenhuis2018] and two items about witnessing and involvement in physical fights.
+The measure contains 7 items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm".
 The physical fighting items asked about witnessing fights: "Based on your experiences at school and in your neighborhood, how many times did you see or hear someone being beaten up in real life?"; and involvement in fights: "How many times were you in a physical fight at school or in your neighborhood?".
@@
 
-Responses on the NVS were averaged to create a composite measure (*M* = `r txt3_ivs$vio_neighborhood$mean`, *SD* = `r txt3_ivs$vio_neighborhood$sd`, $\alpha$ = `r txt4_rel$vio`).
-Likewise, the two fighting were averaged together (*M* = `r txt3_ivs$vio_fighting$mean`, *SD* = `r txt3_ivs$vio_fighting$sd`).
-To create a violence exposure composite, the NVS composite and fighting composite were standardized and then averaged (*r* = `r txt5_cor$vio$r`).
+Responses were averaged to create a composite measure of neighborhood violence (*M* = `r txt3_ivs$vio_neighborhood$mean`, *SD* = `r txt3_ivs$vio_neighborhood$sd`, $\alpha$ = `r txt4_rel$vio`).
+Likewise, the two fighting items were averaged together (*M* = `r txt3_ivs$vio_fighting$mean`, *SD* = `r txt3_ivs$vio_fighting$sd`).
+To create a violence exposure composite, the neighborhood violence composite and fighting composite were standardized and then averaged (*r* = `r txt5_cor$vio$r`).
 Higher scores indicated more exposure to violence.
@@
 We included two control variables: age and interviewer-rated distractions during testing.
-We included these because older adolescents tend to score higher on cognitive tests than younger adolescents [@best2010; @best2011; @huizinga2006], and disruptions during the tasks could negatively impact performance.
+We included these because older youth tend to score higher on cognitive tests than younger youth [@best2010; @best2011; @huizinga2006], and disruptions during the tasks could negatively impact performance.
 Interviewers completed quantitative ratings of the testing environment including 1) the level of noise; 2) the level of chaos; 3) how often there were interruptions; and 4) how often the participant appeared distracted.
@@
 
-We also included the Child Social Desirability (CSD) scale [@miller2014].
+We also included the Child Social Desirability scale [@miller2014].
 The measure includes 14 items such as "Have you ever broken a rule?" and "Do you sometimes feel angry when you don't get your way?".
@@
 More socially desirable responses were scored as 1.
-Items were then summed to create a social desirability index (*M* = `r txt3_ivs$csd$mean`, *SD* = `r txt3_ivs$csd$sd` , $\alpha$ = `r txt4_rel$csd`).
+Items were then summed to create a social desirability index (*M* = `r txt3_ivs$csd$mean`, *SD* = `r txt3_ivs$csd$sd`, $\alpha$ = `r txt4_rel$csd`).
 
@@
 Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded).
-Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [attention shifting data cleaning procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
+Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
 
@@
 This raises concerns about the validity of self-reported childhood adversity measures: youth scoring higher on social desirability might underreport or underrate their exposures to negative experiences.
-Indeed, scores on the CSD were correlated with exposures to unpredictability (*r* = `r txt5_cor$csd_unp$r`) and violence (*r* = `r txt5_cor$csd_vio$r`), though not with poverty.
+Indeed, scores on the Child Social Desirability scale were correlated with exposures to unpredictability (*r* = `r txt5_cor$csd_unp$r`) and violence (*r* = `r txt5_cor$csd_vio$r`), though not with poverty.
 One way to handle this issue is to statistically remove overlapping variance between social desirability and each predictor, using the leftover variance (e.g., the residual variance in childhood adversity exposures not associated with social desirability) as a predictor.
@@
 
-```{r table1, results='asis'}
+```{r table1, tab.id = "table1", tab.cap.style = "Table Caption", tab.cap="Bivariate correlations and descriptive statistics for adversity measures."}
 table.01.0 %>% 
-  kbl(
-    align = "lcccccccccc",  
-    booktabs = T,
-    escape = F,
-    caption = "\\emph{Bivariate correlations and descriptive statistics for measures of adversity and their components.}"
+  add_column(.after = 4,"empty1" = "") %>% 
+  add_column(.after = 8,"empty2" = "") %>% 
+  flextable() %>%
+  width("empty1", width = .2) %>% 
+  width("empty2", width = .2) %>% 
+  width(j = 1, width = .75) %>% 
+  set_header_labels(Variable = "", empty1 = "", empty2 = "") %>% 
+  add_header_row(
+    values = c(" ", "Unpredictability", " ", "Violence", " ", "Poverty"),
+    colwidths = c(1, 3, 1, 3, 1, 4)
   ) %>% 
-  add_header_above(c(" ","Unpredictability" = 3, "Violence" = 3, "Poverty" = 4)) %>% 
-  kable_styling(latex_options = c("scale_down", "hold_position")) %>% 
-  footnote(
-    general       = "Column headers denote adversity constructs and rows indicate components. The upper triangle contain sample sizes for each correlation.",
-    general_title = "Note:", 
-    symbol        = c("p < .05,","p < .01"),
-    symbol_manual = c("*", "**"),
-    footnote_as_chunk = T,
-    title_format = "italic",
-    threeparttable = T
+  border_remove() %>% 
+  border(i = 1, j = c("1","2","3","4","5","6","7","8","9","10"), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 16, border.bottom = fp_border_default(), part = "body") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  set_table_properties(width = 1, layout = "autofit") %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 13
+  ) %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 13
+  ) %>% 
+  compose(
+    i = 1, j = 1, 
+    as_paragraph(as_i("Note: "), "Column headers denote adversity constructs and rows indicate components. The upper triangle contains sample sizes for each correlation."), 
+    part = "footer"
+  ) %>% 
+  compose(
+    i = 2, j = 1, 
+    as_paragraph(as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
+    part = "footer"
   ) 
@@
 
-We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), including an [updated primary analysis plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
+We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), including an [Updated Primary Analysis Plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
 We conducted secondary analyses after our primary analyses (see [Secondary Analyses](#secondary) below).
-Before conducting these analyses, we uploaded secondary analysis plans (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), explaining the goals and purpose of each secondary analysis.
-A Red Team Critic [@redteammarket2021] successfully reproduced and verified (see this [red team report](https://osf.io/xv94z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)) all analyses prior to submission.
+Before conducting these analyses, we uploaded secondary analysis plans (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), explaining the goals and purpose of each secondary analysis.
+A Red Team Critic [@redteammarket2021] successfully reproduced and verified (see this [Red Team Report](https://osf.io/xv94z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)) all analyses prior to submission.
 
@@
 
-(ref:figure2) Visualization of multiverse attention shifting results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
-
-```{r figure2, fig.height=7.25, fig.width=6.25, fig.cap='(ref:figure2)'}
+```{r figure2, fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results.
+Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure (y-axis was reversed so that higher values = faster shifting), b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
 fig2
@@
 Overall, there were no significant interaction effects between task version and unpredictability, violence exposure, or poverty exposure (see Table \@ref(tab:table2), Table \@ref(tab:table3), and Figure \@ref(fig:figure2)b).
-However, analyses produced main effects of unpredictability (median $\beta$ = `r mod_terms2$shifting.unp$median_beta_main`, `r mod_terms2$shifting.unp$p_percent_main %>% str_remove("\\.00")` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.unp$p_overall_main`) and violence exposure (median $\beta$ = `r mod_terms2$shifting.vio$median_beta_main`, `r mod_terms2$shifting.vio$p_percent_main` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.vio$p_overall_main`).
-(See Table \@ref(tab:table2).) There were no main effects of poverty exposure (median $\beta$ = `r mod_terms2$shifting.ses$median_beta_main`, no *ps* \< .05, overall *p* = `r mod_terms2$shifting.ses$p_overall_main`); see Table \@ref(tab:table2)).
+However, analyses produced main effects of unpredictability (median $\beta$ = `r mod_terms2$shifting.unp$median_beta_main`, `r mod_terms2$shifting.unp$p_percent_main %>% str_remove("\\.00")` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.unp$p_overall_main`) and violence exposure (median $\beta$ = `r mod_terms2$shifting.vio$median_beta_main`, `r mod_terms2$shifting.vio$p_percent_main` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.vio$p_overall_main`; see Table \@ref(tab:table2)).
+There were no main effects of poverty exposure (median $\beta$ = `r mod_terms2$shifting.ses$median_beta_main`, no *ps* \< .05, overall *p* = `r mod_terms2$shifting.ses$p_overall_main`; see Table \@ref(tab:table2)).
 That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures were associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecologically relevant.
 
-```{r table2, results='asis'}
+```{r table2, tab.id = "table2", tab.cap.style = "Table Caption", tab.cap = "Median standardized effects, 95% confidence intervals, percent significant, and bootstrapped p-values for the main effect of adversity and adversity by task version interactions."}
 table.02.0 %>% 
@@
 There were also consistent main effects of age; median effects were $\beta$ = `r mod_terms1$updating.unp.age$median_beta` (all *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.age$median_beta` (all *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.age$median_beta` (all *ps* \< .05) for poverty exposure models (see SI Figures 4-6).
-That is, older adolescents scored higher on working memory updating, on average.
+That is, older youth scored higher on working memory updating, on average.
 Finally, there were some main effects of test environment distraction ratings.
@@
 Analyses also revealed two significant interactions: task version × violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_int`, `r mod_terms2$updating.vio$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_int`) and task version × poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_int`, `r mod_terms2$updating.ses$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.ses$p_overall_int`).
-Adolescents exposed to low levels of violence or poverty tended to perform better on the abstract working memory updating task (violence exposure median *b~abstract~* = `r simple_effects$updating.vio$beta_abs`, `r simple_effects$updating.vio$p_percent_abs` of *ps* \< .05; poverty exposure median *b~abstract~* = `r simple_effects$updating.ses$beta_abs`, all *ps* \< .05), compared to adolescents exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)).
+Youth exposed to low levels of violence or poverty tended to perform better on the abstract working memory updating task (violence exposure median *b~abstract~* = `r simple_effects$updating.vio$beta_abs`, `r simple_effects$updating.vio$p_percent_abs` of *ps* \< .05; poverty exposure median *b~abstract~* = `r simple_effects$updating.ses$beta_abs`, all *ps* \< .05), compared to youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)).
 However, this performance gap closed on the ecological working memory task (violence exposure median *b~ecological~* = `r simple_effects$updating.vio$beta_eco`, no *ps* \< .05; poverty exposure median *b~ecological~* = `r simple_effects$updating.ses$beta_eco`, `r simple_effects$updating.ses$p_percent_eco` of *ps* \< .05).
-Put differently, adolescents exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically relevant version compared to their own performance on the abstract version (median simple *b~highviolence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~highpoverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas adolescents exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~lowviolence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~lowpoverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
-In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among adolescents exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
+Put differently, youth exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically relevant version compared to their own performance on the abstract version (median simple *b~high-violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high-poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas youth exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low-violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low-poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
+In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
 
-(ref:figure3) Visualization of multiverse working memory updating results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure, b) plots *p*-curves associated with each interaction term, c) plots sorted interaction $\beta$-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
-Proportions of each arbitrary decision with *p*-values \< .05 are indicated on the right side of each specification grid.
+```{r figure3, fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results.
+Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure, b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
+Proportions of each arbitrary decision with p-values < .05 are indicated on the right side of each specification grid.
 Blank proportions indicate proportions = 0.
-
-```{r figure3, fig.height=7.25, fig.width=6.25, fig.cap='(ref:figure3)'}
+Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 fig3
@@
 We followed-up our primary analyses with two sets of secondary, exploratory analyses.
-We uploaded secondary analysis plans to the OSF prior to conducting them (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)).
+We uploaded secondary analysis plans to the OSF prior to conducting them (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)).
 These analyses focused on two questions.
@@
 
-```{r table3, results='asis'}
+```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap = "Median simple effects (unstandardized) and percent significant for task version and adversity."}
 table.03.0 %>% 
@@
   select(-dv) %>% 
-  mutate(across(.cols = contains("p_percent"), ~ str_replace(.x, "%", "\\\\%"))) %>% 
-   kable(
-    col.names = c(" ", "\\emph{b} (abs)", "\\emph{p} (\\%)","\\emph{b} (eco)", "\\emph{p} (\\%)", "\\emph{b} (low)", "\\emph{p} (\\%)","\\emph{b} (high)", "\\emph{p} (\\%)"),
-    booktabs = T,
-    escape = F,
-    caption = "\\emph{Median simple effects (unstandardized) and percent significant for task version and adversity for attention shifting and working memory updating.}"
+  add_column(.after = 5,"empty1" = "") %>% 
+  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
+  add_row(.after = 4, "iv" = "Working Memory Updating") %>% 
+  flextable() %>% 
+  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 5, j1 = 1, j2 = 10) %>% 
+  bold(i = c(1,5), j = 1) %>% 
+  padding(i = c(2:4, 6:8), j = 1, padding.left = 10) %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(iv = "", empty1 = "") %>% 
+  add_header_row(
+    values = c(" ", "Task Version", " ", "Adversity Exposure"),
+    colwidths = c(1, 4, 1, 4)
   ) %>% 
-  add_header_above(c(" " = 1, "Task Version" = 4, "Adversity Exposure" = 4)) %>% 
-  group_rows(group_label = "Attention Shifting", start_row = 1, end_row = 3) %>% 
-  group_rows(group_label = "Working Memory Updating", start_row = 4, end_row = 6) %>% 
-  kable_styling(latex_options = "scale_down") %>% 
-  footnote(
-    general = "Simple effects for Task Version reflect the median effect of adversity in for the abstract version (abs) and ecological version (eco).
-Simple effects for Adversity reflect the effect of task version when adversity-exposure is low (-1 SD) and high (+1 SD).
+  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
+  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
+  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
+  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 8, border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  fontsize(size = 11, part = "body") %>%
+  set_table_properties(width = 1, layout = "autofit") %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 10
+  ) %>% 
+    add_footer_row(
+    values = " ",
+    colwidths = 10
+  ) %>% 
+  compose(
+    i = 1, j = 1, 
+    as_paragraph(as_i("Note: "), "Simple effects for Task Version reflect the median effect of adversity in for the abstract version (abstract) and ecological version (ecological).
+Simple effects for Adversity reflect the effect of task version when adversity exposure is low (-1 SD) and high (+1 SD).
 P-values < .05 out of all analyses for a given multiverse analyses.
-The total number of analyses for each measure was 64.",
-    general_title = "Note:", 
-    footnote_as_chunk = T,
-    title_format = "italic",
-    threeparttable = T
+The total number of analyses for each measure was 64."),
+    part = "footer"
   )
@@
 For this expanded multiverse approach, we retained all original data processing decisions (i.e., original 64 combinations of decisions) and added adversity component as an additional decision.
-For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures [attention shifting and working memory]).
+For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures (attention shifting and working memory).
 We applied the same approach to violence exposure (three violence variables, 384 analyses) and poverty exposure (four poverty variables, 512 analyses).
@@
 We measured three dimensions of adversity--- environmental unpredictability, violence exposure, and poverty---and tested performance on attention-shifting and working memory updating tasks.
-We administered two versions of each task: one using abstract stimuli and the other using ecologically relevant stimuli, allowing us to compare performance within- and between-subjects.
+We administered two versions of each task: one using abstract stimuli and the other using ecological, real-world stimuli, allowing us to compare performance within- and between-subjects.
 
@@
 We did not find interaction effects for attention shifting.
-However, youth exposed to unpredictability and violence showed smaller switch costs on average, suggesting slightly improved attention shifting performance irrespective of task content.
-These findings partially diverge from prior work [@mittal2015; @nweze2021].
+However, youth exposed to unpredictability and violence showed lower switch costs on average, suggesting slightly improved attention shifting performance irrespective of task content.
+These findings are consistent with a recent study showing that higher caregiving instability was associated with improved attention shifting [@fields2021].
+However, our findings also partially diverge from prior work [@mittal2015; @nweze2021].
 For example, whereas we found unpredictability was associated with improved attention shifting on average, Mittal and colleagues [-@mittal2015] found no difference in performance under neutral conditions.
-And, although they improved attention shifting for those exposed to high unpredictability under uncertainty, it remains unclear how this effect relates to those obtained in the current study.
-In addition, Fields and colleagues [-@fields2021] found caregiving instability was associated with improved attention shifting, but Nweze and colleagues [-@nweze2021] found no association between adversity and attention shifting.
-However, they tested institutionalized children rather than measuring adversity dimensions [@nweze2021].
+And, although they found improved attention shifting for those exposed to high unpredictability under uncertainty, it remains unclear how this effect relates to those obtained in the current study.
+In addition, Nweze and colleagues [-@nweze2021] found no association between adversity and attention shifting, but they tested institutionalized children rather than measuring adversity dimensions.
 In general, we should interpret cautiously.
@@
 Mixed-modeling approaches can account for both overall reaction times and differences across switch and repeat trials, but require more statistical power to test three-way interactions.
-Future research should consider more appropriate modeling approaches.
+Future research should consider modeling approaches that capture participant-level reaction times and differences across conditions.
 
-For working memory updating, we found lowered performance among violence- and poverty-exposed youth on the abstract working memory updating task compared to peers with reduced exposures.
+For working memory updating, we found lowered performance among violence- and poverty-exposed youth on the abstract working memory updating task than peers with reduced exposures.
 However, ecological materials produced an equalization effect: the updating performance gap between low and high adversity-exposed youth narrowed on the ecological updating task.
 Interestingly, updating performance was unrelated to unpredictability.
-These findings are partially consistent with prior work on adversity exposure and working memory updating performance [@young2018; @nweze2021].
+These findings are partially consistent with prior work on adversity exposure and working memory updating performance [@nweze2021; @young2018].
 For example, both Young and colleagues [-@young2018] and the current study found lowered abstract working memory performance among high adversity-exposed individuals.
@@
 However, both their adversity and working memory measures were different.
-Such inconsistencies could be attributed to differences in sampling (adults vs.
-adolescents), the sampled range of adversity exposure (restricted vs.
+
+Overall, inconsistencies across prior work and the current attention-shifting and working memory updating findings could be attributed to differences in sampling (adults vs.
+youth), the sampled range of adversity exposure (restricted vs.
 broad), or methods/design (within- vs.
@@
 community/school settings).
-Future research should address these inconsistencies.
+Future research should both address these inconsistencies and conduct more direct replications of individuals studies to converge on reliable patterns.
 
@@
 Findings suggest, at least when directly comparing interaction terms, violence exposure × task version predicted the working memory updating equalization effect whereas the poverty × task version interaction did not.
+
+There are many possible explanations for the diverging adversity component patterns.
+First, some information sources may be more accurate than others.
+For example, asking about the number of fights one has been involved in or witnessed might be easier to report than asking broader questions about neighborhood danger.
+Second, for different cognitive abilities, objective versus subjective reports may be more relevant.
+For example, for attention-shifting, perceptions appeared to matter whereas objective events did for working memory updating.
+Third, although adversity components were correlated in the moderate range---as typically observed in the literature [@dong2004a; @green2010; @jacobs2012; @matsumoto2021; @mclaughlin2012; @smith2021]---they may measure different constructs.
+For example, more objective indicators might capture aspects of the broader ecology but subjective, self-reported measures capture how youth have internalized and perceived their environment and family life.
 Although interesting, all secondary analyses are exploratory, and should be interpreted with caution.
@@
 
-Taken together, our equalization patterns of results are striking compared to the backdrop of developmental science, which almost exclusively reports lowered cognitive performance in people exposed to harsh rearing conditions.
-We also document lowered performance among adversity-exposed youth, but this effect was specific to tests with abstract stimuli, at least for working memory updating.
-When testing materials have more ecological relevance, adversity-exposed youth perform about as well as youth from affluent backgrounds.
+Taken together, our equalization patterns of results are striking compared to the backdrop of developmental science, which almost exclusively reports lowered cognitive performance in people exposed to harsh environments.
+We also document lowered performance among adversity-exposed youth, but this effect was specific to abstract stimuli, at least for working memory updating.
+When testing materials were more concrete, adversity-exposed youth perform about as well as youth from supportive backgrounds.
+
 These effects have both practical and theoretical implications.
-Practically, these effects support the idea that ecologically relevant testing materials may "even the playing field" for adversity-exposed youth.
+Practically, these effects support the idea that ecologically relevant testing materials may 'even the playing field' for adversity-exposed youth.
 That is, pending replication and extension, our data suggest leveraging ecologically relevant materials in education may hold promise for closing achievement gaps [@ellis2017; @ellis2020; @frankenhuis2020].
-However, our data also suggest the effect of ecological content may be specific to particular abilities---ecological content actually *lowered* attention shifting performance for everyone compared to abstract content.
-This negative effect is consistent with other studies reporting lowered performance on tests with ecologically relevant content [@frankenhuis2020; @muskens2019; @duquennois].
+In fact, programs for gifted students from low-income backgrounds already leverage concrete learning materials [@vantassel-baska2018].
+However, our data also suggest the effect of ecological content may be specific to particular abilities: ecological content actually lowered attention shifting performance for everyone compared to abstract content.
+This negative effect is consistent with other studies reporting lowered performance on tests with ecologically relevant content [@duquennois2022; @frankenhuis2020; @muskens2019].
 
 Theoretically, our findings support the notion that hidden talents may emerge when using ecologically relevant testing materials, but they also raise questions.
-In particular, why should ecologically relevant stimuli equalize working memory updating performance for adversity-exposed youth compared to youth with reduced exposures?
+In particular, why should ecologically relevant stimuli equalize working memory updating performance for adversity-exposed youth than youth with reduced exposures?
 There are at least three possibilities.
-First, both impairment and enhancement processes could operate in parallel.
-While abstract working memory updating performance is impaired, ecological working memory updating performance is enhanced.
-However, this explanation is difficult to reconcile unless performance on tests with different content rely on or recruit different cognitive processes.
-If this is true, those mechanisms that process abstract content may be impaired but those that process ecological content are intact or enhanced.
-Second, there may not be impaired or enhanced processes at all.
-Instead, ecologically relevant stimuli may activate intact, but normally dormant or underrecruited, working memory updating processes.
-Thus, when tested under abstract testing conditions, cognitive processes operate at a lower level (remain inactive) but operate normally with ecological testing materials.
+First, adversity exposure could simultaneously lower and improve performance.
+While abstract working memory updating performance is lowered, ecological working memory updating performance is improved.
+However, this explanation requires that different cognitive mechanisms process different classes of stimuli, even on tests of the same ability.
+If this is true, those mechanisms that process abstract content underperform compared to those that process ecological content.
+Second, there may be no actual differences in underlying abilities.
+Instead, ecologically relevant stimuli may activate intact, but dormant or underrecruited, working memory updating processes.
+Thus, when adversity-exposed youth are tested under abstract testing conditions, their cognitive processes operate at a lower level (remain inactive) but operate equally well with ecological testing materials.
 This makes sense if adversity limits energy and/or cognitive resources.
 Under such constraints, it may be adaptive to activate expensive cognitive processes only when necessary.
-Third, ecological testing materials may remove barriers, such as testing anxiety, that disadvantage adversity-exposed youth.
-Unlike the selective activation of cognitive resources, the additional stressors of testing are removed, allowing cognitive mechanisms to function normally.
-However, this explanation is difficult to reconcile with experimental work [@mittal2015; @young2018], which finds that mild stress/uncertainty improves performance.
+Third, ecological testing materials may remove barriers, such as testing anxiety or test unfamiliarity, that disadvantage adversity-exposed youth.
+Unlike the selective activation of cognitive resources, the additional stressors of testing are removed, allowing cognitive mechanisms to operate unimpeded.
+However, this explanation is difficult to reconcile with experimental work which finds that mild stress/uncertainty improves performance [@mittal2015; @young2018].
 Future research should use research designs that can disentangle these explanations.
@@
 Although the task structure was the same, it is unclear to what extent the ecological tests measured the same construct, especially for attention shifting.
-Second, although we found some effects of ecological testing materials, we measured previously documented hidden talents.
-To explore generalizability of ecological content across abilities, future research may create ecological versions of tests known to disadvantage adversity-exposed youth, such as inhibition [@young2018] or working memory retrieval [@young2018], and compare performance to abstract versions.
-Third, although we used interviews and self-report methods, all of our childhood adversity measures were cross-sectional and some were retrospective.
+For example, switch costs were larger on the ecological version suggesting this version was more difficult than the abstract version.
+That is, holding ecological relevance constant, tests can vary in difficulty and vice versa.
+Here, we are unable to fully tease apart difficulty and ecological validity.
+Future research would benefit from considering the difficulty of ecological relevance manipulations.
+Second, our strategy for creating ecological test versions was to select stimuli believed to be more salient or impactful to adversity-exposed youth.
+However, we did not independently assess the ecological validity of our real-world stimuli.
+Thus, it is unclear whether our tests were specifically matched to the actual experiences of adversity-exposed youth or more ecologically relevant for these youth than for those from supportive conditions.
+Third, we leveraged multiverse analysis to examine the robustness of our findings to arbitrary data processing decisions.
+Though powerful, the technique is relatively new and should always be interpreted with caution.
+For instance, as with other statistical techniques, researchers might disagree over which data processing decisions are arbitrary [@delgiudice2021].
+Fourth, although we found some effects of ecological testing materials, we measured abilities that have shown some evidence of adversity-related enhancement.
+To explore generalizability of ecological content across abilities, future research may create ecological versions of tests known to disadvantage adversity-exposed youth, such as inhibition or working memory retrieval [@mittal2015; @young2018], and compare performance to abstract versions.
+Finally, although we used interviews and self-report methods, all of our childhood adversity measures were cross-sectional and some were retrospective.
 These measurement limitations may be partially offset because our sample was still living in their developmental environment.
@@
 The hidden talents framework has challenged this notion and inspired researchers to document the strengths and abilities of people from adversity.
-Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might "even the playing field" for adversity-exposed youth.
 Theoretically, our data help to refine the hidden talents framework and illuminate future research questions surrounding the unique skills and abilities of people living in harsh conditions.
+Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might ‘even the playing field’ for adversity-exposed youth.
 

### 2022-01-18 supplement/supplement.Rmd
CD revision 1, updaating manuscript and supplement

@@
 title: "Supplementary Material"
-subtitle: "*Can real-world stimuli improve cognitive performance for children living in adversity?*"
+subtitle: "*Hidden Talents in Context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth*"
 output:
-   bookdown::pdf_document2:
-    latex_engine: xelatex
-    number_sections: false
-    lof: yes
-    toc: false
-    extra_dependencies: ["booktabs","caption","longtable","float"]
-    keep_tex: true
-geometry: margin=.5in
-mainfont: Times
-fontsize: 11pt
-urlcolor: blue
-header-includes:
-- \usepackage{siunitx}
+  officedown::rdocx_document:
+    reference_docx: reference-doc.docx
+    page_size:
+      width: 8.5
+      height: 11
+      orient: "portrait"
+    page_margins:
+      bottom: .5
+      top: .5
+      right: .25
+      left: .25
+      header: 0
+      footer: 0
+      gutter: 0
+    plots:
+      align: center
+      style: Normal
+      caption:
+        style: Image Caption
+        pre: 'SI Figure '
+        sep: '. '
+    tables:
+      style: Table
+      layout: autofit
+      width: 1.0
+      caption:
+        style: Caption
+        pre: 'SI Table '
+        sep: '. '
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.align = 'center', fig.pos = "H", fig.show = 'asis')
+# load libraries
+library(tidyverse)
+library(officer)
+library(officedown)
+library(flextable)
 
-library(tidyverse)
-library(gt)
+# set up chunk options
+knitr::opts_chunk$set(
+  echo = F,
+  fig.align = "center",
+  fig.pos = "!t", 
+  fig.show = "asis",
+  fig.width = 8, 
+  fig.height = 7.5,
+  dpi = 600,
+  out.extra = "",
+  message = F,
+  tab.topcaption = T,
+  warning = F
+)
 
+# set up flextable for tables
+set_flextable_defaults(
+  font.family = "Times", 
+  font.size = 10,
+  font.color = "black",
+  line_spacing = 1,
+  padding.bottom = 1, 
+  padding.top = 1,
+  padding.left = 1,
+  padding.right = 1
+)
+
+# load all data and objects
 load("staged-objects.Rdata")
@@
 
-This document contains two parts.
+This document contains three parts.
 First, we report our full multiverse primary analyses, including covariates (e.g., age and distractions during cognitive testing).
@@
 The second focuses on comparing violence $\times$ task version interaction with poverty $\times$ task version interaction.
+Third, we report descriptive statistics and bivariate correlations among all indices of adversity (unpredictability, violence, and poverty exposure).
 
@@
 
+**[Descriptive Statistics for all Adversity Indices](#sec3)**
+
+- [SI Table 6](#tab6) (Unpredictability)
+- [SI Table 7](#tab7) (Violence Exposure)
+- [SI Table 8](#tab8) (Poverty)
+
 \pagebreak
@@
 
-### SI Table 1. Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for all terms predicting attention shifting. {#tab1}
+### Median Effect Sizes {#tab1}
 
-```{r sitables1, results='asis'}
-si_table.01.1 %>% 
-  as_latex() %>% 
-  as.character() %>% 
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
-  cat()
+```{r sitables1, tab.id = "sitables1", tab.cap = "Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for all terms predicting attention shifting."}
+si_table.01.1$`_data` %>% 
+  add_column(.after = 6,"empty1" = "") %>% 
+  add_row(.before = 1, "mod_term_label" = "Unpredictability") %>% 
+  add_row(.after = 6, "mod_term_label" = "Violence") %>% 
+  add_row(.after = 12, "mod_term_label" = "Poverty") %>%
+  select(-iv) %>% 
+  flextable() %>% 
+  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 7, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 12, j1 = 1, j2 = 10) %>% 
+  bold(i = c(1,7,13), j = 1) %>% 
+  padding(i = c(2:6, 8:12, 14:18), j = 1, padding.left = 10) %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(
+    iv = "", mod_term_label = "Term", 
+    empty1 = "", 
+    ci_shifting = "95% CI", 
+    ci_updating = "95% CI"
+    ) %>% 
+  add_header_row(
+    values = c(" ", "Attention Shifting", " ", "Working Memory Updating"),
+    colwidths = c(1, 4, 1, 4)
+  ) %>% 
+  compose(i = 2, j = c(2,7), as_paragraph(as_i("N")), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph("\U1D6FD"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 18, border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  set_table_properties(width = 1, layout = "autofit")
 ```
@@
 
-### SI Figure 1. Unpredictability and Attention Shifting specification plot with all covariates. {#fig1}
+### Unpredictability and Attention Shifting specification plot with all covariates. {#fig1}
 
-```{r sifig1, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig1, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 shifting_unp
@@
 
-### SI Figure 2. Violence exposure and Attention Shifting specification plot with all covariates. {#fig2}
+### Violence exposure and Attention Shifting specification plot with all covariates. {#fig2}
 
-```{r sifig2, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig2, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 shifting_vio
@@
 
-### SI Figure 3. Poverty and Attention Shifting specification plot with all covariates. {#fig3}
+### Poverty and Attention Shifting specification plot with all covariates. {#fig3}
 
-```{r sifig3, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig3, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 shifting_ses
@@
 
-### SI Figure 4. Unpredictability and working memory updating specification plot with all covariates. {#fig4}
+### Unpredictability and working memory updating specification plot with all covariates. {#fig4}
 
-```{r sifig4, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig4, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 updating_unp
@@
 
-### SI Figure 5. Violence exposure and working memory updating specification plot with all covariates. {#fig5}
+### Violence exposure and working memory updating specification plot with all covariates. {#fig5}
 
-```{r sifig5, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 updating_vio
@@
 
-### SI Figure 6. Poverty and working memory updating specification plot with all covariates. {#fig6}
+### Poverty and working memory updating specification plot with all covariates. {#fig6}
 
-```{r sifig6, fig.height=10, fig.width=8.5, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term."}
+```{r sifig6, fig.cap="P-curves, effect size curves, sample sizes, and specification grids for each model term. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 updating_ses
@@
 
-### SI Table 2.
-Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for main effects of adversity components and interactions with task version for attention shifting and working memory updating.{#tab2}
+### Median Effect Sizes {#tab2}
 
-```{r sitables2, results='asis'}
-si_table.02.0 %>% 
-  as_latex() %>% 
-  as.character() %>% 
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
-  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
-  cat()
+```{r sitables2, tab.id = "sitables2", tab.cap = "Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for main effects of adversity components and interactions with task version for attention shifting and working memory updating."}
+si_table.02.0$`_data` %>% 
+  mutate(mod_term_label = str_replace(mod_term_label,"\\$\\\\times\\$","x")) %>% 
+  add_column(.after = 6,"empty1" = "") %>% 
+  add_row(.before = 1, "mod_term_label" = "Unpredictability") %>% 
+  add_row(.after = 7, "mod_term_label" = "Violence") %>% 
+  add_row(.after = 14, "mod_term_label" = "Poverty") %>%
+  select(-iv) %>% 
+  flextable() %>% 
+  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 8, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 15, j1 = 1, j2 = 10) %>% 
+  bold(i = c(1,8,15), j = 1) %>% 
+  padding(i = c(2:7, 9:14, 16:23), j = 1, padding.left = 10) %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(
+    iv = "", mod_term_label = " ", 
+    empty1 = "", 
+    ci_shifting = "95% CI", 
+    ci_updating = "95% CI"
+  ) %>% 
+  add_header_row(
+    values = c(" ", "Attention Shifting", " ", "Working Memory Updating"),
+    colwidths = c(1, 4, 1, 4)
+  ) %>% 
+  compose(i = 2, j = c(2,7), as_paragraph(as_i("N")), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph("\U1D6FD"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  align(i = 2, j = 1, align = "left", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 23, border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  set_table_properties(width = 1, layout = "autofit")
 ```
@@
 
-### SI Table 3. Median simple slopes (unstandardized) and percent significant for adversity component interactions with task version for attention shifting and working memory updating. {#tab3}
+### Median Simple Effects {#tab3}
 
-```{r sitables3, results='asis'}
-si_table.03.0 %>% 
-  as_latex() %>% 
-  as.character() %>% 
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
-  cat()
+```{r sitables3, tab.id = "sitables3", tab.cap = " Median simple slopes (unstandardized) and percent significant for adversity component interactions with task version for attention shifting and working memory updating."}
+si_table.03.0$`_data` %>% 
+  add_column(.after = 6,"empty1" = "") %>% 
+  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
+  add_row(.after = 11, "iv" = "Working Memory Updating") %>%
+  select(-dv) %>% 
+  flextable() %>% 
+  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
+  merge_h_range(i = 12, j1 = 1, j2 = 10) %>% 
+  bold(i = c(1,12), j = 1) %>% 
+  padding(i = c(2:11, 13:22), j = 1, padding.left = 10) %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(iv = "", empty1 = "") %>% 
+  add_header_row(
+    values = c(" ", "Task Version", " ", "Adversity Exposure"),
+    colwidths = c(1, 4, 1, 4)
+  ) %>% 
+  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
+  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
+  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
+  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = c(11,22), border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  fontsize(size = 11, part = "body") %>% 
+  set_table_properties(width = 1, layout = "autofit")
 ```
@@
 
-### SI Figure 7. Unpredictability components and attention shifting multiverse results. {#fig7}
+### Unpredictability components and attention shifting multiverse results. {#fig7}
 
-```{r sifig7, fig.width=8, fig.height=7.5, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids task version by unpredictability components."}
+```{r sifig7, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids task version by unpredictability components."}
 unp_shifting
@@
 
-### SI Figure 8. Violence exposure components and attention shifting multiverse results. {#fig8}
+### Violence exposure components and attention shifting multiverse results. {#fig8}
 
-```{r sifig8, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
+```{r sifig8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions.
+Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 vio_shifting
@@
 
-### SI Figure 9. Poverty components and attention shifting multiverse results. {#fig9}
+### Poverty components and attention shifting multiverse results. {#fig9}
 
-```{r sifig9, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
+```{r sifig9, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions.
+Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 ses_shifting
@@
 
-### SI Figure 10. Unpredictability components and working memory updating multiverse results. {#fig10}
+### Unpredictability components and working memory updating multiverse results. {#fig10}
 
-```{r sifig10, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by unpredictability component interactions"}
+```{r sifig10, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by unpredictability component interactions.
+Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 unp_updating
@@
 
-### SI Figure 11. Violence exposure components and working memory updating multiverse results. {#fig11}
+### Violence exposure components and working memory updating multiverse results. {#fig11}
 
-```{r sifig11, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions"}
+```{r sifig11, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence exposure component interactions.
+Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 vio_updating
@@
 
-### SI Figure 12. Poverty components and working memory updating multiverse results. {#fig12}
+### Poverty components and working memory updating multiverse results. {#fig12}
 
-```{r sifig12, fig.height=7.5, fig.width=8, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions"}
+```{r sifig12, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by Poverty component interactions.
+Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 ses_updating
@@
 
-### SI Table 4.
-Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for multiverse analyses comparing Poverty $\times$ task version and violence $\times$ task version interactions.{#tab4}
+### Median Effects {#tab4}
 
-```{r sitables4, results='asis'}
-si_table.04.0 %>% 
-  as_latex() %>% 
-  as.character() %>% 
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>% 
-  str_replace_all("\\\\\\$\\\\textbackslash times\\\\\\$", "$\\\\times$") %>% 
-  cat()
+```{r sitables4, tab.id = "sitables4", tab.cap = "Median effect sizes, 95% confidence intervals, percent significant, and sample sizes for multiverse analyses comparing Poverty by task version and violence by task version interactions."}
+si_table.04.0$`_data` %>% 
+  mutate(mod_term_label = str_replace(mod_term_label,"\\$\\\\times\\$","x")) %>% 
+  flextable() %>% 
+  set_header_labels(
+    iv = "", mod_term_label = " ", 
+    empty1 = "", 
+    ci = "95% CI"
+  ) %>% 
+  compose(i = 1, j = c(2), as_paragraph("\U1D6FD"), part = "header") %>% 
+  compose(i = 1, j = c(4), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  compose(i = 1, j = c(5), as_paragraph("median ", as_i("N")), part = "header") %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 5
+  ) %>% 
+  set_table_properties(width = 1, layout = "autofit")
 ```
 
-### SI Table 5. Median simple slopes (unstandardized) and percent significant for multiverse analyses comparing Poverty $\times$ task version and violence $\times$ task version interactions. {#tab5}
+### Median Simple Effects {#tab5}
 
-```{r sitables5, results='asis'}
-si_table.05.0 %>%
-  as_latex() %>%
-  as.character() %>%
-  str_replace_all("\\\\textbackslash Beta", "$\\\\beta$") %>%
-  cat()
+```{r sitables5, tab.id = "sitables5", tab.cap = "Median simple slopes (unstandardized) and percent significant for multiverse analyses comparing Poverty by task version and violence by task version interactions."}
+si_table.05.0$`_data` %>% 
+  add_column(.after = 5,"empty1" = "") %>% 
+  flextable() %>% 
+  width("empty1", width = .2) %>% 
+  set_header_labels(iv = "", empty1 = "") %>% 
+  add_header_row(
+    values = c(" ", "Task Version", " ", "Adversity Exposure"),
+    colwidths = c(1, 4, 1, 4)
+  ) %>% 
+  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
+  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
+  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
+  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
+  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
+  align(i = 1:2, align = "center", part = "header") %>% 
+  border_remove() %>% 
+  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
+  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
+  border(i = c(2), border.bottom = fp_border_default(), part = "body") %>% 
+  bold(i = 1:2, part = "header") %>% 
+  fontsize(size = 11, part = "body") %>%
+  add_footer_row(
+    values = " ",
+    colwidths = 10
+  ) %>% 
+  set_table_properties(width = 1, layout = "autofit")
 ```
@@
 
-### SI Figure 13. Multiverse results for Poverty and violence exposure interactions with task version in the same model. {#fig13}
+### Multiverse results for Poverty and violence exposure interactions with task version in the same model. {#fig13}
 
@@
 ```
+
+\pagebreak
+
+# Descriptive Statistics of Adversity Indices {#sec3}
+
+```{r sitables6, tab.id = "sitables6", tab.cap = "Correlations and descriptive statistics for interview-based and perceived unpredictability."}
+si_table.06.0 %>% 
+  flextable() %>% 
+  set_header_labels(Variable = "") %>% 
+  set_table_properties(width = 1, layout = "autofit") %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 5
+  ) %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 5
+  ) %>% 
+  compose(
+    i = 1, j = 1, 
+    as_paragraph(as_i("Note: "), as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
+    part = "footer"
+  ) 
+```
+
+```{r sitables7, tab.id="sitables7", tab.cap="Correlations and descriptive statistics for witnessing and involvement in fights and perceived neighborhood violence.
+Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
+si_table.07.0 %>% 
+  flextable() %>% 
+  set_header_labels(Variable = "") %>% 
+  set_table_properties(width = 1, layout = "autofit") %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 4
+  ) %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 4
+  ) %>% 
+  compose(
+    i = 1, j = 1, 
+    as_paragraph(as_i("Note: "), as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
+    part = "footer"
+  ) 
+```
+
+```{r sitables8, tab.id="sitables8", tab.cap="Correlations and descriptive statistics for interview, school, and perceived poverty variables."}
+si_table.08.0 %>% 
+  flextable() %>% 
+  set_header_labels(Variable = "") %>% 
+  set_table_properties(width = 1, layout = "autofit") %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 5
+  ) %>% 
+  add_footer_row(
+    values = " ",
+    colwidths = 5
+  ) %>% 
+  compose(
+    i = 1, j = 1, 
+    as_paragraph(as_i("Note: "), as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
+    part = "footer"
+  ) 
+```

### 2022-01-18 manuscript/scripts/figure-2-3.R

@@ -327,7 +327,7 @@ fig2 <-
       axis  = "lr",
       rel_heights = c(.25,.15,.2,.1,.3)
     ) +
-      draw_plot_label(c("(faster)","(slower)"), x = 0.075, y = c(.95, .78), size = 8, vjust = 1, hjust = 0, fontface = "italic") +
+      draw_plot_label(c("(faster)","(slower)"), x = 0.15, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic") +
       draw_plot_label(c("a","b","c","d","e"), x = 1, y = c(.95, .75, .6, .4, .3), size = 10, vjust = 1, hjust = 1), 
     x = 0, y = 0, width = 1, height = .95
   ) + 
@@ -348,7 +348,7 @@ fig3 <-
       axis  = "lr",
       rel_heights = c(.25,.15,.2,.1,.3)
     ) +
-      draw_plot_label(c("(more accurate)","(less accurate)"), x = 0.11, y = c(.95, .785), size = 8, vjust = 1, hjust = 1, fontface = "italic") +
+      draw_plot_label(c("(more accurate)","(less accurate)"), x = 0.15, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic") +
       draw_plot_label(c("a","b","c","d","e"), x = 1, y = c(.95, .75, .6, .4, .3), size = 10, vjust = 1, hjust = 1), 
     x = 0, y = 0, width = 1, height = .95
   ) + 

### 2022-01-18 manuscript/scripts/rmd-staging.R

@@ -13,7 +13,7 @@ theme_set(
     theme(
       axis.line.y       = element_line(),
       axis.text.y       = element_text(size = rel(.75)),
-      axis.title.y      = element_text(size = rel(1), margin = margin(1,0,0,0,"lines")),
+      axis.title.y      = element_text(size = rel(.80), margin = margin(1,0,0,0,"lines")),
       axis.ticks.y      = element_line(),
       axis.line.x       = element_blank(),
       axis.text.x       = element_blank(),

### 2022-01-18 supplement/scripts/2-secondary1.R

@@ -251,21 +251,28 @@ spec_curves2 <-
       if(dv_which == "Attention-Shifting"){
         int_plots <- 
           int_plots +
-          ylab("Switch Cost (ms)\n")
+          scale_y_reverse(n.breaks = 5) +
+          ylab("Switch Cost (ms)\n") +
+          theme(legend.position = c(.25,.8))
       }
       
       if(dv_which == "Working Memory Updating"){
         int_plots <- 
           int_plots +
+          scale_y_continuous(breaks = seq(69, 77, 2)) +
           ylab("% correct\n")
       }
       
-      if(y == "SES"){
+      if(y == "SES" & dv_which == "Attention-Shifting"){
         int_plots <- 
           int_plots +
-          theme(
-            legend.position = c(.2,.2)
-          )
+            theme(legend.position = c(.2,.8))
+      }
+      
+      if(y == "SES" & dv_which == "Working Memory Updating"){
+        int_plots <- 
+          int_plots +
+            theme(legend.position = c(.2,.2))
       }
       
       list(
@@ -291,7 +298,8 @@ unp_shifting <-
     align = "v", 
     axis  = "lr",
     rel_heights = c(.25,.15,.2,.1,.3)
-  )
+  ) +
+  draw_plot_label(c("(faster)","(slower)"), x = 0.15, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")
 
 unp_updating <- 
   plot_grid(
@@ -305,7 +313,8 @@ unp_updating <-
     align = "v", 
     axis  = "lr",
     rel_heights = c(.25,.15,.2,.1,.3)
-  )
+  ) +
+  draw_plot_label(c("(more accurate)","(less accurate)"), x = 0.15, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")
 
 # Violence ----------------------------------------------------------------
 vio_shifting <- 
@@ -320,7 +329,8 @@ vio_shifting <-
     align = "v", 
     axis  = "lr",
     rel_heights = c(.25,.15,.2,.1,.3)
-  )
+  ) +
+  draw_plot_label(c("(faster)","(slower)"), x = 0.15, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")
 
 vio_updating <- 
   plot_grid(
[…]

### 2022-01-18 supplement/scripts/5-tables-r1.R

@@ -1,0 +1,30 @@
+si_table.06.0 <- 
+  data2_non_arbitrary %>% 
+  select(matches("unp_interview"), unp_perceived) %>% 
+  corr_table(
+    c.names = c("Family Disruption (interview)", "Parental Transitions (interview)", "Residential Moves (interview)", "Perceived (self-report"),
+    numbered = T,
+    stats = c("min", "median", "max", "range", "mean", "sd")
+  ) %>% 
+    add_row(Variable = "Possible Range", `1` = "0-3", `2` = "-", `3` = "-", `4` = "1-5")
+
+si_table.07.0 <- 
+  data2_non_arbitrary %>% 
+  select(matches("vio_fighting\\d"), vio_neighborhood) %>% 
+  corr_table(
+    c.names = c("Witnessing Fights", "Involvement in Fights", "Perceived Neighborhood Violence"),
+    numbered = T,
+    stats = c("min", "median", "max", "range", "mean", "sd")
+  ) %>% 
+  add_row(Variable = "Possible Range", `1` = "0-8", `2` = "0-8", `3` = "1-5")
+
+si_table.08.0 <- 
+  data3_composites %>%
+  select(matches("ses_(interview)_"), ses_school, ses_perceived) %>% 
+  corr_table(
+    c.names = c("Parental Education", "Parental Occupation", "School or Club -Provided", "Perceived"),
+    numbered = T,
+    stats = c("min", "median", "max", "range", "mean", "sd")
+  ) %>% 
+  add_row(Variable = "Possible Range", `1` = "1-3", `2` = "0-100", `3` = "-0.5, 0.5", `4` = "1-5")
+

### 2022-01-18 supplement/scripts/rmd-staging.R

@@ -48,6 +48,7 @@ source("supplement/scripts/1-covariates.R")
 source("supplement/scripts/2-secondary1.R")
 source("supplement/scripts/3-secondary2.R")
 source("supplement/scripts/4-tables.R")
+source("supplement/scripts/5-tables-r1.R")
 
 # Save the entire image ---------------------------------------------------
 save(
@@ -69,5 +70,8 @@ save(
   si_table.04.0,
   si_table.05.0,
   vio_ses_updating,
+  si_table.06.0,
+  si_table.07.0,
+  si_table.08.0,
   file = "supplement/staged-objects.Rdata"
 )

### 2022-01-28 manuscript/manuscript.Rmd
CD revision 1, integrate coauthor feedback

@@
 Harsh and unpredictable environments are thought to cause high levels of chronic stress, which can impair brain regions responsible for memory and learning [@blair2012].
-Thus, the contemporary view is that exposure to adversity undermines cognitive development and leads to a host of cognitive deficits [see @duncan2017; @hackman2010; @mclaughlin2019; @pechtel2011 for reviews].
+Thus, the contemporary view is that exposure to adversity undermines cognitive development and leads to a host of cognitive deficits [reviewed in @duncan2017; @hackman2010; @mclaughlin2019; @pechtel2011].
 Although it is clear that harsh and unpredictable environments are harmful to youth, there is growing interest in the *hidden talents approach*, which proposes that some abilities may be enhanced by adversity, especially skills and abilities that help youth meet real-world challenges in adverse environments [@ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013].
+These stress-adapted skills are referred to in this literature as *hidden talents*.
 
-The hidden talents framework assumes that development shapes the skills and abilities of individuals in relation to their environment [see @ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013 for reviews] and assumes development tailors skills and abilities in relation to their environment.
-Accordingly, exposure to adversity should shape skills and abilities well-suited for dealing with the challenges associated with harsh and unpredictable environments.However, because specific dimensions of adversity (violence versus resource-scarcity) may pose unique challenges [@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity [@frankenhuis2020].
-For instance, some evidence suggests physically abused youth can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], people living in poverty have more accurate social perception [@bjornsdottir2017; @dietze2021; @piff2018], and anxiously attached people can more accurately detect deception [@eindor2014; @shoda2013] to list a few examples [see @ellis2017; @ellis2020 for reviews].
+The hidden talents approach is rooted in an adaptation-based framework [see @ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013 for reviews], which assumes development tailors skills and abilities in relation to the environment.
+Accordingly, exposure to adversity should shape skills and abilities well-suited for dealing with the challenges and opportunities associated with harsh and unpredictable environments.
+However, because specific dimensions of adversity (e.g., violence versus resource-scarcity) may pose unique challenges [@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity [@frankenhuis2020].
+For instance, some evidence suggests that physically abused youth can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], people living in poverty have more accurate social perception [@bjornsdottir2017; @dietze2021; @piff2018], and that anxiously attached people can more accurately detect deception [@eindor2014; @shoda2013].
 
@@
 There was no performance increase under control conditions.
-However, some studies have found similar patterns without uncertainty [see @fields2021 for attention shifting and @nweze2021 for working memory].
+However, some studies have found similar patterns without uncertainty [@fields2021; @nweze2021].
 
@@
 Typical cognitive tests use abstract content that is largely detached from the real world.
-Such abstract materials may disadvantage youth with limited exposure to formal education.
+Such abstract materials may disadvantage youth whose childhood experiences involve less abstract, analytical problem solving [@ellis2020; @frankenhuis2013].
 Cultural psychologists and anthropologists have demonstrated this fact across the world.
-For example, people from non-Western cultures tend to score lower than people in Western cultures on standard versions of cognitive tests, but this performance gap closes or disappears with more ecologically relevant versions of the same tests [@banerjee2017; @greenfield2014; @ogbu1981; @richardson1991; @schliemann2002].
+For example, people from non-Western cultures tend to score lower than people in Western cultures on standard versions of cognitive tests, but this performance gap closes or disappears when more ecologically relevant measures are used [@banerjee2017; @grigorenko2004; @rogoff2017; @sternberg2001].
 This work challenges the assumption that "baseline" performance is best captured by standard/abstract tests.
-In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020].
-These ideas also pose an important question: do adversity-exposed youth score higher on tests with ecological stimuli relative to those with abstract stimuli?
+In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020; @zuilkowski2016].
+These ideas also raise an important question: do adversity-exposed youth score higher on tests with ecologically-relevant stimuli relative to those with abstract stimuli?
 
@@
 Notably, such violence exposures were associated with less accurate memory for neutral (age) relationships.
-This pattern was specific *current* exposures: people with more *childhood* exposures to violence memorized both content types less accurately.
+This pattern was specific to *current* exposures: people with more *childhood* exposures to violence memorized both content types less accurately.
 There were no associations between violence exposures and reasoning performance.
@@
 
-Together, research testing performance in ecologically relevant contexts/situations and using ecologically relevant materials have generated innovative ideas and findings.
-Nonetheless, it remains unclear whether or how these ideas and findings can be practically applied.
+Although research testing performance in ecologically relevant contexts/situations and using ecologically relevant materials have generated innovative ideas and findings, it remains unclear whether or how these ideas and findings can be practically applied.
 For example, narrow abilities, such as memorizing social dominance hierarchies or accurately detecting anger in faces, seem to have limited practical value in educational contexts.
@@
 Here we address this issue by evaluating the role of ecologically relevant content in attention-shifting and working memory tasks.
-We define ecological relevant content as testing material that resemble the local environment and therefore have more meaning and consequence.
+We define ecologically relevant content as testing material that resembles the local environment and therefore has more meaning and consequence.
 We used two criteria for stimulus selection.
@@
 For example, money is more consequential and perhaps salient to adversity-exposed youth than other neutral objects (a book, dishes, etc.).
-In addition, we target both between-subjects and within-subject improvement as patterns of interest.
-That is, improved performance compared to oneself (within-subjects -- one's performance on abstract compared to ecologically task versions), compared to others (between-subjects -- high versus low adversity), or some combination, are each theoretically important patterns of improvement.
-Our specific expectation was that all youth would score higher on tasks with ecological stimuli.
+We target both within-subject and between-subject patterns of improvement.
+That is, improvements in performance relative to oneself (within-subjects -- one's performance on abstract compared to ecological task versions), relative to others (between-subjects -- high versus low adversity), or a combination, are theoretically and practically important.
+In the current study, we expected all youth would score higher on tasks with ecological stimuli.
 However, we expected this increase to be larger among youth living in adverse conditions compared to youth in supportive conditions.
@@
 Our exploratory analyses focused on exposure to poverty.
-Poverty is both relevant to hidden talents (e.g., hidden talents could develop in response to specific challenges of poverty) and a general proxy to adversity rather than a specific exposure.
+Poverty is both relevant to hidden talents (e.g., hidden talents could develop in response to specific challenges of poverty) and a general proxy for adversity rather than a specific exposure.
 
@@
 According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers).
-The clubs (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`).
-`r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch and were also ethnically diverse.
+The club sample (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`) and were also ethnically diverse.
+`r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch.
 
@@
 A 0 indicated the participant lived in an intact family (lived with both biological parents) from birth until age 13 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 0) %>% sum(na.rm=T)`); a 1 indicated that a disruption occurred after the age of 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 1) %>% sum(na.rm=T)`); a 2 indicated that a disruption occurred before age 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 2) %>% sum(na.rm=T)`); and a 3 indicated the participant was born into a non-intact family (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 3) %>% sum(na.rm=T)`).
-`r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T)`.
 `r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T) %>% english::as.english() %>% str_to_title()` participants had missing information.
@@
 
-We assessed each participant's poverty exposure using three information sources: interview-assessed parent education and occupational prestige, school or club-provided economic information, and perceived resource scarcity.
+We assessed each participant's poverty exposure using three information sources: interview-assessed parent education and occupational prestige, school or club-provided economic information, and self-reported resource scarcity.
 
@@
     i = 1, j = 1, 
-    as_paragraph(as_i("Note: "), "The p (%) column reflects the number of analyses that produced p-values < .05 out of all analyses for a given multiverse analyses.
+    as_paragraph(as_i("Note: "), "The p (%) column reflects the number of analyses that produced p-values < .05 for a given multiverse.
 The total number of analyses for each measure was 64.
-Overall p-values were computed using a bootstrapping resampling method and reflect the probability of obtaining an effect size as extreme or more extreme given the median effect is 0."),
+Overall p-values were computed using a bootstrapped resampling method and reflect the probability of obtaining an effect size as extreme or more extreme given the median effect is 0."),
     part = "footer"
@@
 
-```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap = "Median simple effects (unstandardized) and percent significant for task version and adversity."}
+```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap = "Median simple effects for task version and adversity."}
 table.03.0 %>% 
@@
     i = 1, j = 1, 
-    as_paragraph(as_i("Note: "), "Simple effects for Task Version reflect the median effect of adversity in for the abstract version (abstract) and ecological version (ecological).
-Simple effects for Adversity reflect the effect of task version when adversity exposure is low (-1 SD) and high (+1 SD).
-P-values < .05 out of all analyses for a given multiverse analyses.
-The total number of analyses for each measure was 64."),
+    as_paragraph(as_i("Note: "), "Simple effects are unstandardized.
+Task Version reflects the median simple effect of adversity when the task version was abstract and ecological.
+Adversity reflects the median simple effect of task version when adversity is low (-1 SD) and high (+1 SD).
+The p (%) columns reflect the number of analyses that produced simple effect p-values < .05."),
     part = "footer"
@@
 For this expanded multiverse approach, we retained all original data processing decisions (i.e., original 64 combinations of decisions) and added adversity component as an additional decision.
-For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures (attention shifting and working memory).
+For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures: attention shifting and working memory).
 We applied the same approach to violence exposure (three violence variables, 384 analyses) and poverty exposure (four poverty variables, 512 analyses).
@@
 In addition, Nweze and colleagues [-@nweze2021] found no association between adversity and attention shifting, but they tested institutionalized children rather than measuring adversity dimensions.
-In general, we should interpret cautiously.
+In general, we should interpret the results cautiously.
 Although we followed field standards for calculating switch costs by computing difference scores, such scores ignore participant-level reaction times.
@@
 community/school settings).
-Future research should both address these inconsistencies and conduct more direct replications of individuals studies to converge on reliable patterns.
+Future research should both address these inconsistencies and conduct more direct replications of individual studies to converge on reliable patterns.
 
@@
 When testing materials were more concrete, adversity-exposed youth perform about as well as youth from supportive backgrounds.
+These results converge with recent work comparing stimulus types among adversity-exposed youth.
+For example, Rifkin-Graboi and colleagues [-@rifkin-graboi2021] found preschoolers exposed to caregiver adversity were more accurate on relational memory for socioemotional than non-socioemotional stimuli and Zuilkowski and colleagues [-@zuilkowski2016] found that Sub-Saharan African children from low SES backgrounds were more accurate on reasoning tests with three dimensional stimuli than two dimensional stimuli.
 
@@
 In fact, programs for gifted students from low-income backgrounds already leverage concrete learning materials [@vantassel-baska2018].
-However, our data also suggest the effect of ecological content may be specific to particular abilities: ecological content actually lowered attention shifting performance for everyone compared to abstract content.
-This negative effect is consistent with other studies reporting lowered performance on tests with ecologically relevant content [@duquennois2022; @frankenhuis2020; @muskens2019].
+However, our data also suggest the effect of ecological content may be specific to particular abilities.
+On the one hand, our data showing within-subject improvements on working memory updating is consistent with past research using ecological versions of Raven's Progressive Matrices [@richardson1991].
+On the other, ecological content actually lowered attention shifting performance for everyone compared to abstract content, possibly because shifting was more difficult with more ecologically hot or "sticky" stimuli.
+This negative effect is consistent with other studies reporting lowered performance on some tests with ecologically relevant content [@duquennois2022; @frankenhuis2020; @muskens2019].
 
@@
 Although the task structure was the same, it is unclear to what extent the ecological tests measured the same construct, especially for attention shifting.
-For example, switch costs were larger on the ecological version suggesting this version was more difficult than the abstract version.
-That is, holding ecological relevance constant, tests can vary in difficulty and vice versa.
-Here, we are unable to fully tease apart difficulty and ecological validity.
-Future research would benefit from considering the difficulty of ecological relevance manipulations.
+In addition, test difficulty may have been different across test versions (e.g., switch costs were larger on the ecological version).
+Future research should consider teasing apart test difficulty from ecological relevance.
 Second, our strategy for creating ecological test versions was to select stimuli believed to be more salient or impactful to adversity-exposed youth.
@@
 Third, we leveraged multiverse analysis to examine the robustness of our findings to arbitrary data processing decisions.
-Though powerful, the technique is relatively new and should always be interpreted with caution.
+Though powerful, the technique is relatively new and should be interpreted with caution.
 For instance, as with other statistical techniques, researchers might disagree over which data processing decisions are arbitrary [@delgiudice2021].
@@
 Theoretically, our data help to refine the hidden talents framework and illuminate future research questions surrounding the unique skills and abilities of people living in harsh conditions.
-Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might ‘even the playing field’ for adversity-exposed youth.
+Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might 'even the playing field' for adversity-exposed youth.
 

### 2022-01-28 supplement/supplement.Rmd
CD revision 1, integrate coauthor feedback

@@
 
-```{r sitables7, tab.id="sitables7", tab.cap="Correlations and descriptive statistics for witnessing and involvement in fights and perceived neighborhood violence.
-Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
+```{r sitables7, tab.id="sitables7", tab.cap="Correlations and descriptive statistics for witnessing and involvement in fights and perceived neighborhood violence."}
 si_table.07.0 %>% 

### 2022-01-28 supplement/scripts/2-secondary1.R

@@ -299,7 +299,7 @@ unp_shifting <-
     axis  = "lr",
     rel_heights = c(.25,.15,.2,.1,.3)
   ) +
-  draw_plot_label(c("(faster)","(slower)"), x = 0.15, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")
+  draw_plot_label(c("(faster)","(slower)"), x = 0.13, y = c(.975, .77), size = 8, vjust = 1, hjust = 1, fontface = "italic")
 
 unp_updating <- 
   plot_grid(
@@ -314,7 +314,7 @@ unp_updating <-
     axis  = "lr",
     rel_heights = c(.25,.15,.2,.1,.3)
   ) +
-  draw_plot_label(c("(more accurate)","(less accurate)"), x = 0.15, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")
+  draw_plot_label(c("(more accurate)","(less accurate)"), x = 0.125, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")
 
 # Violence ----------------------------------------------------------------
 vio_shifting <- 
@@ -330,7 +330,7 @@ vio_shifting <-
     axis  = "lr",
     rel_heights = c(.25,.15,.2,.1,.3)
   ) +
-  draw_plot_label(c("(faster)","(slower)"), x = 0.15, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")
+  draw_plot_label(c("(faster)","(slower)"),x = 0.13, y = c(.975, .77), size = 8, vjust = 1, hjust = 1, fontface = "italic")
 
 vio_updating <- 
   plot_grid(
@@ -345,7 +345,7 @@ vio_updating <-
     axis  = "lr",
     rel_heights = c(.25,.15,.2,.1,.3)
   ) +
-  draw_plot_label(c("(more accurate)","(less accurate)"), x = 0.15, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")
+  draw_plot_label(c("(more accurate)","(less accurate)"), x = 0.125, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")
 
 # SES  --------------------------------------------------------------------
 ses_shifting <- 
@@ -361,7 +361,7 @@ ses_shifting <-
     axis  = "lr",
[…]

### 2022-01-28 supplement/scripts/3-secondary2.R

@@ -248,4 +248,5 @@ vio_ses_updating <-
     align = "v", 
     axis  = "lr",
     rel_heights = c(.25,.15,.2,.1,.3)
-  )
+  ) +
+  draw_plot_label(c("(more accurate)","(less accurate)"), x = 0.2, y = c(.95, .78), size = 8, vjust = 1, hjust = 1, fontface = "italic")

### 2022-01-28 supplement/scripts/5-tables-r1.R

@@ -22,7 +22,7 @@ si_table.08.0 <-
   data3_composites %>%
   select(matches("ses_(interview)_"), ses_school, ses_perceived) %>% 
   corr_table(
-    c.names = c("Parental Education", "Parental Occupation", "School or Club -Provided", "Perceived"),
+    c.names = c("Parental Education", "Parental Occupation", "School or Club-Provided", "Perceived"),
     numbered = T,
     stats = c("min", "median", "max", "range", "mean", "sd")
   ) %>% 

### 2022-01-31 manuscript/manuscript.Rmd
CD revision 1, add citation

@@
 This work challenges the assumption that "baseline" performance is best captured by standard/abstract tests.
-In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020; @zuilkowski2016].
+In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@miller-cotto2021; @doebel2020; @zuilkowski2016].
 These ideas also raise an important question: do adversity-exposed youth score higher on tests with ecologically-relevant stimuli relative to those with abstract stimuli?

### 2022-03-08 README.Rmd
CD revision 2, minor changes and updates

@@
 
-This repository contains data, code, and (some) output for a manuscript entitled "Hidden talents in context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth" submitted to and under review at *Child Development*.
+This repository contains data, code, and (some) output for a manuscript entitled "Hidden talents in context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth" accepted for publication at *Child Development*.
 

### 2022-03-08 manuscript/manuscript.Rmd
CD revision 2, minor changes and updates

--- 2022-01-28 manuscript/manuscript.Rmd
@@
 However, the hidden talents approach proposes some abilities are enhanced by adversity, especially under ecologically relevant conditions.
-Sampling `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White), we administered two versions of an attention shifting and working memory updating task---one abstract, one ecological.
-We measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions.
+Two versions of an attention shifting and working memory updating task---one abstract, one ecological---were administered to `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White).
+Measures of environmental unpredictability, violence, and poverty were collected to tested adversity × task version interactions.
 There were no interactions for attention shifting.
-For working memory updating, youth exposed to violence and poverty scored lower than their peers with abstract stimuli but just as well with ecological stimuli.
-These results are striking compared to contemporary developmental science, which almost exclusively reports lowered performance among adversity-exposed youth.
+For working memory updating, youth exposed to violence and poverty scored lower than their peers with abstract stimuli but equally well with ecological stimuli.
+These results are striking compared to contemporary developmental science, which often reports lowered performance among adversity-exposed youth.
 
@@
 However, because specific dimensions of adversity (e.g., violence versus resource-scarcity) may pose unique challenges [@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity [@frankenhuis2020].
-For instance, some evidence suggests that physically abused youth can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], people living in poverty have more accurate social perception [@bjornsdottir2017; @dietze2021; @piff2018], and that anxiously attached people can more accurately detect deception [@eindor2014; @shoda2013].
+For instance, some evidence suggests that physically abused youth can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], lower perceived social class or status predicts more accurate social perceptions [@bjornsdottir2017; @dietze2021; @piff2018], and that anxiously attached people can more accurately detect deception [@eindor2014; @shoda2013].
 
@@
 For example, people from non-Western cultures tend to score lower than people in Western cultures on standard versions of cognitive tests, but this performance gap closes or disappears when more ecologically relevant measures are used [@banerjee2017; @grigorenko2004; @rogoff2017; @sternberg2001].
-This work challenges the assumption that "baseline" performance is best captured by standard/abstract tests.
-In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020; @zuilkowski2016].
+This work challenges the assumption that "baseline" performance is best captured by standard, abstract tests.
+In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020; @miller-cotto2021; @nketia2021 ; @zuilkowski2016].
 These ideas also raise an important question: do adversity-exposed youth score higher on tests with ecologically-relevant stimuli relative to those with abstract stimuli?
@@
 
-Although research testing performance in ecologically relevant contexts/situations and using ecologically relevant materials have generated innovative ideas and findings, it remains unclear whether or how these ideas and findings can be practically applied.
+Although research testing performance in ecologically relevant contexts or situations and using ecologically relevant materials have generated innovative ideas and findings, it remains unclear whether or how these ideas and findings can be practically applied.
 For example, narrow abilities, such as memorizing social dominance hierarchies or accurately detecting anger in faces, seem to have limited practical value in educational contexts.
@@
 Second, we selected stimuli believed to be more consequential or salient to adversity-exposed youth.
-For example, money is more consequential and perhaps salient to adversity-exposed youth than other neutral objects (a book, dishes, etc.).
+For example, money is more consequential to poverty-exposed youth and an angry face more salient to violence-exposed youth than neutral objects (a book, dishes, etc.).
+Although some stimuli are likely to be more relevant to one adversity dimension than another, different adversity exposures tend to co-occur [@jacobs2012; @smith2021].
+Thus, we selected stimuli that are broadly relevant in the context of correlated adversity exposures.
+
 We target both within-subject and between-subject patterns of improvement.
@@
 
-To address our research questions, we sampled `r nrow(data2_non_arbitrary)` youth from a socioeconomically diverse population.
+To address our research questions, we sampled `r nrow(data2_non_arbitrary)` youth from a socioeconomically diverse population to ensure sufficient variation in adversity-exposure.
 Using interviews, self-reports, and school records, we measured exposure to environmental unpredictability, violence, and poverty.
@@
 ```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap='Schematic display of the attention shifting and working memory updating tasks: a) abstract attention shifting, b) ecological attention shifting, c) abstract working memory updating, and d) ecological working memory updating.'}
-knitr::include_graphics("figure1.pdf")
+knitr::include_graphics("figures/figure1.pdf")
 ```
@@
 
-The current study collected data from `r txt1_sam$raw$n$total` youth (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah.
+The current study collected data from `r txt1_sam$raw$n$total` youth (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah, USA starting in the spring of 2018 and ending in early 2020.
 The first was a middle school and the second were 5 after-school clubs.
 The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse: `r data1_raw %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data1_raw %>% filter(race == 2) %>%nrow()` as Native American, `r data1_raw %>% filter(race == 3) %>% nrow()` as African American, `r data1_raw %>% filter(race == 4) %>% nrow()` as White, `r data1_raw %>% filter(race == 5) %>% nrow()` as Hispanic, `r data1_raw %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data1_raw %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data1_raw %>% filter(is.na(race)) %>% nrow()` were missing.
-According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers).
+According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and homelessness (i.e., free or reduced-price lunch or fee waivers).
 The club sample (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`) and were also ethnically diverse.
@@
 
-Data collection involved six parts: consent/assent, demographics form, cognitive testing, structured interview, questionnaire, and debriefing.
+Data collection involved six parts: consent and assent, demographics form, cognitive testing, structured interview, questionnaire, and debriefing.
 Consent was obtained from the primary parent or guardian before assessments and assent was obtained from the participant at the beginning of the session.
@@
 For each home, they reported at which ages they lived in the home.
-If they moved, they also reported any changes in their family structure (loss or gain of adults in the home), social network (e.g., a new school), and/or town or city.
+If they moved, they also reported any changes in their family structure (loss or gain of adults in the home), social network (e.g., a new school), and town or city.
 
@@
 
-Accuracy on attention-shifting tasks is normally high, and was in the current sample for both versions (*M~standard~* = `r (txt2_dvs$abs_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~standard~* = `r (txt2_dvs$abs_shifting_correct$sd/32 * 100) %>% round(2)`%; *M~ecological~* = `r (txt2_dvs$eco_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~ecological~* = `r (txt2_dvs$eco_shifting_correct$sd/32 * 100) %>% round(2)`%).Thus, instead of accuracy, attention-shifting ability is measured by comparing reaction times on repeat trials to switch trials.
+Accuracy on attention-shifting tasks is normally high, and was in the current sample for both versions (*M~standard~* = `r (txt2_dvs$abs_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~standard~* = `r (txt2_dvs$abs_shifting_correct$sd/32 * 100) %>% round(2)`%; *M~ecological~* = `r (txt2_dvs$eco_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~ecological~* = `r (txt2_dvs$eco_shifting_correct$sd/32 * 100) %>% round(2)`%).
+Thus, instead of accuracy, attention-shifting ability is measured by comparing reaction times on repeat trials to switch trials.
 Reaction times on repeat trials are normally faster than switch trials; average repeat trial reaction times on the abstract and ecological versions were `r txt2_dvs$abs_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_re_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_re_rt$sd` *ms*), respectively.
@@
 To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000].
-We removed fast and slow reaction times and removed trials after incorrect responses (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
+We removed fast and slow reaction times and removed trials after incorrect responses (see <https://osf.io/kvt5e/> for details).
 We then subtracted the average reaction time on valid repeat trials from the average reaction time on valid switch trials to calculate switch cost scores (*M~switch~* - *M~repeat~*).
@@
 
-Our measure of environmental unpredictability integrated information from the interview and questionnaire.
+Environmental unpredictability is difficult to measure and different definitions exist alongside each other [@young2020].
+Despite this, we aligned our measurement approach with previous literature in two ways.
+First, we measured caregiver and residential instability, which are both thought to be proxies to environmental unpredictability, using interview-based measures [@ellis2009].
+Second, we measured the extent to which youth perceive their family context as unpredictable using a questionnaire [@young2018].
+Our goal was to aggregate these two information sources to arrive at a best estimate of environmental unpredictability.
+
 The interview contained three variables of interest.
@@
 
-The second interview variable tabulated the number of different parental figures (defined as spouses or boyfriends/girlfriends of the participant's mother and father) who lived in the same home with the participant.
+The second interview variable tabulated the number of different parental figures (defined as spouses or boyfriends or girlfriends of the participant's mother and father) who lived in the same home with the participant.
 Trained interviewers tabulated the total number of co-residing parental figures, excluding the participant's biological mother and father (*M* = `r txt3_ivs$unp_interview_figures$mean`, *SD* = `r txt3_ivs$unp_interview_figures$sd`).
@@
 
-The questionnaire included a measure of perceived childhood unpredictability [@mittal2015; @young2018; @szepsenwol2015].
+The questionnaire included a measure of perceived childhood unpredictability [@mittal2015; @young2018].
 Participants responded to six items that assessed exposure to unpredictability up to age 13: 1) "Things were pretty calm and stable in my house" (reversed); 2) "People moved in and out of my house a lot"; 3) "I had a hard time knowing what my parent(s) or other people in my house were going to say or do from day-to-day"; 4) "My parent(s) argued or fought a lot with each other or with other people"; 5) "My parent(s) changed jobs a lot"; 6) "My parental situation changed a lot (for example, divorce or separation of parents, parents starting new romantic relationships, parents leaving the home)".
@@
 Participants also reported their perceived level of resource scarcity.
-They rated seven items from 1 (never true) to 5 (very often true): 1) "Your family had enough money to afford the kind of home you all needed"; "Your family had enough money to afford the kind of clothing you all needed"; 3) "Your family had enough money to afford the kind of food that you all needed"; 4) "Your family had enough money to afford the kind of medical care that you all needed"; 5) "I felt well-off (rich, wealthy) compared to other kids in my school"; 6) "I felt well-off (rich, wealthy) compared to other kids in my neighborhood"; and 7) "Your family struggled to make ends meet (get by financially)".
+They rated seven items from 1 (never true) to 5 (very often true): 1) "Your family had enough money to afford the kind of home you all needed"; 2) "Your family had enough money to afford the kind of clothing you all needed"; 3) "Your family had enough money to afford the kind of food that you all needed"; 4) "Your family had enough money to afford the kind of medical care that you all needed"; 5) "I felt well-off (rich, wealthy) compared to other kids in my school"; 6) "I felt well-off (rich, wealthy) compared to other kids in my neighborhood"; and 7) "Your family struggled to make ends meet (get by financially)".
 The first six items were reversed, and all items were averaged to create a perceived resource scarcity measure (*M* = `r txt3_ivs$ses_perceived$mean`, *SD* = `r txt3_ivs$ses_perceived$sd`, $\alpha$ = `r txt4_rel$ses`).
@@
 
-To create a poverty exposure composite, we combined parent education and occupational prestige (reversed), school/club reported economic disadvantage, and perceived resource scarcity.
+To create a poverty exposure composite, we combined parent education and occupational prestige (reversed), school or club reported economic disadvantage, and perceived resource scarcity.
 First, we standardized and averaged parent education and occupation (*r* = `r txt5_cor$edu_int$r`).
@@
 Specifically, those receiving free or reduced-price lunch were coded as .5, and those who were not were coded as -.5.
-To create a final composite, we averaged parent education/occupation (standardized), perceived resource scarcity (standardized), and the recoded school/club economic disadvantage.
+To create a final composite, we averaged parent education and occupation (standardized), perceived resource scarcity (standardized), and the recoded school or club economic disadvantage.
 Higher values indicated more exposure to poverty.
@@
 We included two control variables: age and interviewer-rated distractions during testing.
-We included these because older youth tend to score higher on cognitive tests than younger youth [@best2010; @best2011; @huizinga2006], and disruptions during the tasks could negatively impact performance.
+We included these because older youth tend to score higher on cognitive tests than younger youth [@best2011], and disruptions during the tasks could negatively impact performance.
 Interviewers completed quantitative ratings of the testing environment including 1) the level of noise; 2) the level of chaos; 3) how often there were interruptions; and 4) how often the participant appeared distracted.
@@
 Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded).
-Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
+Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see <https://osf.io/kvt5e/> for more information).
 
@@
 
-We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), including an [Updated Primary Analysis Plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
+We preregistered all primary analyses on the Open Science Framework (OSF; see <https://osf.io/6r95z/>, including an updated primary analysis plan (see <https://osf.io/4vsnz/>), which included more details.
 We conducted secondary analyses after our primary analyses (see [Secondary Analyses](#secondary) below).
-Before conducting these analyses, we uploaded secondary analysis plans (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), explaining the goals and purpose of each secondary analysis.
-A Red Team Critic [@redteammarket2021] successfully reproduced and verified (see this [Red Team Report](https://osf.io/xv94z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)) all analyses prior to submission.
+Before conducting these analyses, we uploaded secondary analysis plans (see <https://osf.io/7fu35/> for the first plan and <https://osf.io/wcauf/> for the second plan), explaining the goals and purpose of each secondary analysis.
+A Red Team Critic [@redteammarket2021] successfully reproduced and verified (see <https://osf.io/xv94z/> for a report) all analyses prior to submission.
+All associated data and code are included in our preregistration repository on GitHub (<https://github.com/ethan-young/hidden-talents-multiverse>) and the OSF (<https://osf.io/6r95z/>), including source code to reproduce the manuscript itself.
 
@@
 
-```{r figure2, fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results.
+```{r figure2, fig.path="figures/", dev="pdf", fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results.
 Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure (y-axis was reversed so that higher values = faster shifting), b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
@@
 
-```{r figure3, fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results.
+```{r figure3, fig.path="figures/", dev="pdf", fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results.
 Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure, b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
@@
 We followed-up our primary analyses with two sets of secondary, exploratory analyses.
-We uploaded secondary analysis plans to the OSF prior to conducting them (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)).
+We uploaded secondary analysis plans to the OSF prior to conducting them (see <https://osf.io/7fu35/> for the first plan and <https://osf.io/wcauf/> for the second plan).
 These analyses focused on two questions.
@@
 Environmental unpredictability contained two components, perceived unpredictability (self-reported) and an interview-based measure tabulating family disruptions, parental figures, and residential moves.
-Violence exposure contained two self-report components: neighborhood violence and exposure to/involvement in violence.
-Poverty exposure contained three components: parental education/occupation (interview), perceived resource scarcity (self-report), and school-coded economic disadvantage (fee waivers, free- or reduced-priced lunch, and homelessness).
+Violence exposure contained two self-report components: neighborhood violence and exposure to and involvement in violence.
+Poverty exposure contained three components: parental education and occupation (interview), perceived resource scarcity (self-report), and school-coded economic disadvantage (fee waivers, free- or reduced-priced lunch, and homelessness).
 
@@
 No interactions were significant with the neighborhood violence component of the violence composite.
-For poverty exposure, interview-based parental occupational prestige and school-reported economic disadvantage showed some interaction effects (parental education/occupational prestige `r secondary1_medians$updating.ses.Parents.iv_type_z$p_percent` of *ps* \<.05; school coded economic disadvantage `r secondary1_medians$updating.ses.School.iv_type_z$p_percent` of *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 12).
+For poverty exposure, interview-based parental occupational prestige and school-reported economic disadvantage showed some interaction effects (parental education and occupational prestige `r secondary1_medians$updating.ses.Parents.iv_type_z$p_percent` of *ps* \<.05; school coded economic disadvantage `r secondary1_medians$updating.ses.School.iv_type_z$p_percent` of *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 12).
 Self-reported perceived resource scarcity showed no interaction effects (see SI Table 2, SI Table 3, and SI Figure 12).
@@
 youth), the sampled range of adversity exposure (restricted vs.
-broad), or methods/design (within- vs.
+broad), or methods and design (within- vs.
 between-subjects design; lab vs.
-community/school settings).
+community and school settings).
 Future research should both address these inconsistencies and conduct more direct replications of individual studies to converge on reliable patterns.
@@
 For example, for attention-shifting, perceptions appeared to matter whereas objective events did for working memory updating.
-Third, although adversity components were correlated in the moderate range---as typically observed in the literature [@dong2004a; @green2010; @jacobs2012; @matsumoto2021; @mclaughlin2012; @smith2021]---they may measure different constructs.
+Third, although adversity components were correlated in the moderate range---as typically observed in the literature [@jacobs2012; @smith2021]---they may measure different constructs.
 For example, more objective indicators might capture aspects of the broader ecology but subjective, self-reported measures capture how youth have internalized and perceived their environment and family life.
@@
 Thus, when adversity-exposed youth are tested under abstract testing conditions, their cognitive processes operate at a lower level (remain inactive) but operate equally well with ecological testing materials.
-This makes sense if adversity limits energy and/or cognitive resources.
+This makes sense if adversity limits energy or cognitive resources.
 Under such constraints, it may be adaptive to activate expensive cognitive processes only when necessary.
@@
 Unlike the selective activation of cognitive resources, the additional stressors of testing are removed, allowing cognitive mechanisms to operate unimpeded.
-However, this explanation is difficult to reconcile with experimental work which finds that mild stress/uncertainty improves performance [@mittal2015; @young2018].
+However, this explanation is difficult to reconcile with experimental work which finds that mild stress and uncertainty improves performance [@mittal2015; @young2018].
 Future research should use research designs that can disentangle these explanations.

### 2022-03-08 supplement/supplement.Rmd
CD revision 2, minor changes and updates

@@
 
-```{r sifig13, fig.height=7.5, fig.width=5.25, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence and task version by poverty"}
+```{r sifig13, fig.height=7.5, fig.width=5.25, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence and task version by poverty.
+Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
 vio_ses_updating

### 2022-03-08 manuscript/scripts/figure-2-3-bw.R

@@ -1,0 +1,356 @@
+# Get bootstrapped medians ------------------------------------------------
+boot_medians <- 
+  boot_effects %>% 
+  filter((null_term == "main" & mod_term == "iv") | (null_term == "int" & mod_term == "iv:type_z")) %>% 
+  rename(term = mod_term) %>% 
+  group_by(spec_num, iv, dv, null_term) %>% 
+  summarize(
+    across(
+      starts_with("mod"), 
+      list(median = ~median(.x), lower = ~quantile(.x, probs = .025, names = F), upper = ~quantile(.x, probs = .975, names = F)),
+      .names = "{.col}_{.fn}")
+  ) %>%
+  group_by(iv, dv, null_term) %>% 
+  mutate(spec_rank = as.numeric(fct_reorder(as_factor(spec_num), mod_std_coefficient_median))) %>% 
+  select(iv, dv, null_term, contains("mod_std_coefficient"), spec_rank) %>% 
+  rename(
+    null_effect = mod_std_coefficient_median,
+    null_lower  = mod_std_coefficient_lower,
+    null_upper  = mod_std_coefficient_upper
+  ) %>% 
+  mutate(
+    iv_long = case_when(iv == "ses" ~ "SES",
+                        iv == "unp" ~ "Unpredictability",
+                        iv == "vio" ~ "Violence"),
+    dv_long = case_when(dv == "shifting" ~ "Attention-Shifting",
+                        dv == "updating" ~ "Working Memory Updating"),
+    term_long = case_when(null_term == "main" ~ "Main Effect",
+                          null_term == "int" ~ "Interaction")
+  ) %>% 
+  ungroup()
+
+# Merge primary effects with bootstrapped effects -------------------------
+primary_plots_data <- 
+  left_join(
+    primary_effects_data,
+    boot_medians %>% select(ends_with("long"), spec_rank, null_effect, null_lower, null_upper),
+    by = c("iv" = "iv_long", "dv" = "dv_long", "mod_term_group" = "term_long", "spec_rank" = "spec_rank")
+  ) %>% 
+  filter(mod_term_group %in% c("Covariate", "Task-Type", "Main Effect", "Interaction")) %>% 
+  ungroup() %>% 
+  mutate(
+    mod_term_unique = case_when(mod_term_unique == "Task Type" ~ "Task~Version",
+                                mod_term_unique == "Test Environment" ~ "Test~Environment",
[…]

### 2022-03-08 manuscript/scripts/rmd-staging.R

@@ -33,6 +33,7 @@ theme_set(
 )
 
 pval_colors <- c("pos-sig" = "#006D77", "non" = "gray70")
+pval_colors_bw <- c("pos-sig" = "black", "non" = "gray70")
 my_alphas <- c(.5, 1)
 my_limits <- c(1,70)
 
@@ -53,6 +54,7 @@ source("manuscript/scripts/table3.R")
 
 # Figures -----------------------------------------------------------------
 source("manuscript/scripts/figure-2-3.R")
+source("manuscript/scripts/figure-2-3-bw.R")
 
 # In-text statistics ------------------------------------------------------
 ## sample break downs ----
@@ -367,3 +369,6 @@ save(
   file = "manuscript/staged-objects.Rdata"
 )
 
+# save black and white figures --------------------------------------------
+ggsave(filename = "manuscript/figures/figure2-1-bw.pdf", fig2_bw, width = 6.5, height = 7.25, dpi = 600)
+ggsave(filename = "manuscript/figures/figure3-1-bw.pdf", fig3_bw, width = 6.5, height = 7.25, dpi = 600)

### 2022-03-08 supplement/scripts/5-tables-r1.R

@@ -26,5 +26,5 @@ si_table.08.0 <-
     numbered = T,
     stats = c("min", "median", "max", "range", "mean", "sd")
   ) %>% 
-  add_row(Variable = "Possible Range", `1` = "1-3", `2` = "0-100", `3` = "-0.5, 0.5", `4` = "1-5")
+  add_row(Variable = "Possible Range", `1` = "0-3", `2` = "0-100", `3` = "-0.5, 0.5", `4` = "1-5")
 

### 2022-03-16 manuscript/tables/table-1.Rmd
make separate .docx files for tables

--- 2022-01-28 manuscript/manuscript.Rmd
@@
 ---
-bibliography: references.bib
-csl: apa.csl
 output:
   officedown::rdocx_document:
-    reference_docx: reference-doc.docx
+    reference_docx: ../reference-doc.docx
     page_margins:
@@
 # load all data and objects
-load("staged-objects.Rdata")
+load("../staged-objects.Rdata")
 
@@
 ```
-
-# Abstract
-
-\noindent Adversity-exposed youth tend to score lower on cognitive tests.
-However, the hidden talents approach proposes some abilities are enhanced by adversity, especially under ecologically relevant conditions.
-Sampling `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White), we administered two versions of an attention shifting and working memory updating task---one abstract, one ecological.
-We measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions.
-There were no interactions for attention shifting.
-For working memory updating, youth exposed to violence and poverty scored lower than their peers with abstract stimuli but just as well with ecological stimuli.
-These results are striking compared to contemporary developmental science, which almost exclusively reports lowered performance among adversity-exposed youth.
-
-*Keywords*: hidden talents, working memory updating, attention shifting, adversity, adaptations to stress
-
-\pagebreak
-
-# Hidden talents in context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth
-
-Youth living in adverse conditions tend to score lower on cognitive tests than youth in supportive conditions.
-For example, youth raised in poverty are more likely to have difficulties learning in school and score lower on standardized tests [@farah2006; @hackman2010; @noble2007; @ursache2016a].
-Harsh and unpredictable environments are thought to cause high levels of chronic stress, which can impair brain regions responsible for memory and learning [@blair2012].
-Thus, the contemporary view is that exposure to adversity undermines cognitive development and leads to a host of cognitive deficits [reviewed in @duncan2017; @hackman2010; @mclaughlin2019; @pechtel2011].
-Although it is clear that harsh and unpredictable environments are harmful to youth, there is growing interest in the *hidden talents approach*, which proposes that some abilities may be enhanced by adversity, especially skills and abilities that help youth meet real-world challenges in adverse environments [@ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013].
-These stress-adapted skills are referred to in this literature as *hidden talents*.
-
-The hidden talents approach is rooted in an adaptation-based framework [see @ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013 for reviews], which assumes development tailors skills and abilities in relation to the environment.
-Accordingly, exposure to adversity should shape skills and abilities well-suited for dealing with the challenges and opportunities associated with harsh and unpredictable environments.
-However, because specific dimensions of adversity (e.g., violence versus resource-scarcity) may pose unique challenges [@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity [@frankenhuis2020].
-For instance, some evidence suggests that physically abused youth can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], people living in poverty have more accurate social perception [@bjornsdottir2017; @dietze2021; @piff2018], and that anxiously attached people can more accurately detect deception [@eindor2014; @shoda2013].
-
-Although some abilities themselves are more ecologically relevant to specific dimensions of adversity, hidden talents may also emerge under ecologically relevant conditions.
-For example, previous studies of hidden talents have tested cognition under ecologically relevant *contexts and situations*.
-In particular, studies have experimentally manipulated the current context to be uncertain and mildly stressful (or not) and measured performance on executive functioning and working memory tasks [@mittal2015; @young2018].
-Strikingly, people from unpredictable environments showed more efficient switching on attention shifting tasks and more accurate responses on working memory updating tasks, but this effect only emerged under conditions of uncertainty.
-There was no performance increase under control conditions.
-However, some studies have found similar patterns without uncertainty [@fields2021; @nweze2021].
-
-Hidden talents may also emerge when testing *content and stimuli* are more ecologically relevant and concrete.
-Typical cognitive tests use abstract content that is largely detached from the real world.
-Such abstract materials may disadvantage youth whose childhood experiences involve less abstract, analytical problem solving [@ellis2020; @frankenhuis2013].
-Cultural psychologists and anthropologists have demonstrated this fact across the world.
-For example, people from non-Western cultures tend to score lower than people in Western cultures on standard versions of cognitive tests, but this performance gap closes or disappears when more ecologically relevant measures are used [@banerjee2017; @grigorenko2004; @rogoff2017; @sternberg2001].
-This work challenges the assumption that "baseline" performance is best captured by standard/abstract tests.
-In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020; @zuilkowski2016].
-These ideas also raise an important question: do adversity-exposed youth score higher on tests with ecologically-relevant stimuli relative to those with abstract stimuli?
-
-One way to test this question is to replace sterile testing materials with ecologically relevant content from the real world.
-For example, one study tested memory and reasoning among young adults who varied in their exposures to violence [@frankenhuis2020a].
-They created two versions of a memory and reasoning task, one neutral (chronological age) and one more ecologically relevant (social dominance).
-They found that people with more *current* exposures to violence were equally, or more, accurate when memorizing social-dominance relationships than people with fewer exposures.
-Notably, such violence exposures were associated with less accurate memory for neutral (age) relationships.
-This pattern was specific to *current* exposures: people with more *childhood* exposures to violence memorized both content types less accurately.
-There were no associations between violence exposures and reasoning performance.
-Overall, this study suggests that ecologically relevant testing materials may in some conditions 'level the playing field' for adversity-exposed youth [@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
-
-Although research testing performance in ecologically relevant contexts/situations and using ecologically relevant materials have generated innovative ideas and findings, it remains unclear whether or how these ideas and findings can be practically applied.
-For example, narrow abilities, such as memorizing social dominance hierarchies or accurately detecting anger in faces, seem to have limited practical value in educational contexts.
-In addition, although executive functions and working memory are related to many educational outcomes, it is unclear how schools and teachers might leverage skills and abilities that specifically depend on inducing uncertainty.
-That seems impractical, at best, and unethical, at worst.
-
-Here we address this issue by evaluating the role of ecologically relevant content in attention-shifting and working memory tasks.
-We define ecologically relevant content as testing material that resembles the local environment and therefore has more meaning and consequence.
-We used two criteria for stimulus selection.
-First, we selected stimuli that youth would encounter and interact with on a daily basis.
-Second, we selected stimuli believed to be more consequential or salient to adversity-exposed youth.
-For example, money is more consequential and perhaps salient to adversity-exposed youth than other neutral objects (a book, dishes, etc.).
-We target both within-subject and between-subject patterns of improvement.
-That is, improvements in performance relative to oneself (within-subjects -- one's performance on abstract compared to ecological task versions), relative to others (between-subjects -- high versus low adversity), or a combination, are theoretically and practically important.
-In the current study, we expected all youth would score higher on tasks with ecological stimuli.
-However, we expected this increase to be larger among youth living in adverse conditions compared to youth in supportive conditions.
-
-To address our research questions, we sampled `r nrow(data2_non_arbitrary)` youth from a socioeconomically diverse population.
-Using interviews, self-reports, and school records, we measured exposure to environmental unpredictability, violence, and poverty.
-We used these information sources to arrive at a "best estimate" for each construct.
-Our a priori assumption was that each information source (e.g., interview, self-report, school provided information) would correlate within constructs, which was largely true (see Table \@ref(tab:table1)).
-
-We then tested performance on two widely used tasks: attention shifting and working memory updating.
-There were two versions of each task.
-The first used standard abstract stimuli and the second replaced these stimuli with more ecological stimuli from the real-world (see Figure 1).
-We then tested the interactive effect of task content and adversity exposure.
-As such, our primary analyses involved two preregistered confirmatory analyses and one exploratory analysis.
-Our confirmatory analyses focused on environmental unpredictability and violence exposure.
-Both dimensions have been associated with improved performance under ecologically relevant conditions (contexts and testing materials) and represent specific environmental challenges.
-Our exploratory analyses focused on exposure to poverty.
-Poverty is both relevant to hidden talents (e.g., hidden talents could develop in response to specific challenges of poverty) and a general proxy for adversity rather than a specific exposure.
-
-We also evaluated the relative robustness of our models to arbitrary data processing decisions using a multiverse analysis approach [@steegen2016; @simonsohn2020].
-Specifically, we systematically and explicitly generated all possible combinations of (arbitrary) data processing decisions and analyzed them simultaneously.
-We conducted a separate multiverse analysis for each task (attention shifting and working memory updating) and each measure of adversity exposure combination.
-All multiverse analyses used the same underlying statistical models.
-
-```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap='Schematic display of the attention shifting and working memory updating tasks: a) abstract attention shifting, b) ecological attention shifting, c) abstract working memory updating, and d) ecological working memory updating.'}
-knitr::include_graphics("figure1.pdf")
-```
-
-# Method {#method}
-
-## Participants {#participants}
-
-The current study collected data from `r txt1_sam$raw$n$total` youth (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah.
-The first was a middle school and the second were 5 after-school clubs.
-The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse: `r data1_raw %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data1_raw %>% filter(race == 2) %>%nrow()` as Native American, `r data1_raw %>% filter(race == 3) %>% nrow()` as African American, `r data1_raw %>% filter(race == 4) %>% nrow()` as White, `r data1_raw %>% filter(race == 5) %>% nrow()` as Hispanic, `r data1_raw %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data1_raw %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data1_raw %>% filter(is.na(race)) %>% nrow()` were missing.
-According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers).
-The club sample (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`) and were also ethnically diverse.
-`r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch.
-
-We aggregated data from both sources and applied a set of five exclusion criteria.
-We applied these criteria before inspecting or testing any relations between predictors and outcomes.
-Specifically, we excluded participants: 1) with incomplete cognitive task data, 2) with apparent cognitive impairments (e.g., head injuries, disabilities, drug use), 3) who missed two or more trap questions, 4) exposed to extreme distractions during the assessment, and 5) who received more than 60 minutes per day of special education services.
-After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).
-In terms of racial identity, `r data2_non_arbitrary %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data2_non_arbitrary %>% filter(race == 2) %>%nrow()` as Native American, `r data2_non_arbitrary %>% filter(race == 3) %>% nrow()` as African American, `r data2_non_arbitrary %>% filter(race == 4) %>% nrow()` as White, `r data2_non_arbitrary %>% filter(race == 5) %>% nrow()` as Hispanic, `r data2_non_arbitrary %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data2_non_arbitrary %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data2_non_arbitrary %>% filter(is.na(race)) %>% nrow()` were missing.
-
-## Procedure {#procedure}
-
-Data collection involved six parts: consent/assent, demographics form, cognitive testing, structured interview, questionnaire, and debriefing.
-Consent was obtained from the primary parent or guardian before assessments and assent was obtained from the participant at the beginning of the session.
-On the demographics form, participants indicated if they were left-handed, their birthdate, and their racial and ethnic background.
-
-Cognitive testing included abstract (i.e., standard) and ecological versions of an attention-shifting and working memory updating task.
-Task order (shifting versus updating) and version (abstract versus ecological) were counterbalanced across participants.
-Some participants started with the attention shifting and then moved to the updating tasks.
-For those starting with the shifting (or updating) tasks, some started with the abstract version and then completed the ecological version (and vice versa).
-Regardless of which task was first, participants always completed both versions of one task before moving to the other task.
-
-The interview contained two parts.
-The first part was about participants' home and family life, such as their family composition, the number of adults in the household, and occupation and education information about caregivers.
-Participants also reported on the number of romantic partners their caregivers had and if these partners lived with the participant.
-The second part was about residential mobility.
-Participants listed all the homes they lived in from birth to age 13.
-For each home, they reported at which ages they lived in the home.
-If they moved, they also reported any changes in their family structure (loss or gain of adults in the home), social network (e.g., a new school), and/or town or city.
-
-The questionnaire contained measures focused on the childhood environment.
-The measures included perceived unpredictability in the home, exposure to neighborhood violence, access to material resources, direct exposure to violence and fighting, and a child version of socially desirable responding.
-
-Procedures across the middle school and after-school clubs were the same, with a few minor differences.
-First, participants in the clubs completed the tasks before the interview, but the opposite occurred in the middle school.
-The second was that, in the middle school, the questionnaire was completed in a separate session.
-Whereas the tasks and interview were completed in a small room, alone with the interviewer, the questionnaire was completed approximately two weeks later in a mass testing context (large computer room).
-This was done because the middle school was on a strict class schedule, which limited the length of individual sessions.
-In the clubs, sessions were conducted in the summer during flexible hours.
-
-## Measures {#measures}
-
-### Attention Shifting {#shifting}
-
-We measured attention shifting with two versions of the color--shape task [@mittal2015; @miyake2012; @friedman2008], which involves categorizing stimuli according to one of two rules (see below).
-On each trial, the rule is displayed on the top of the screen.
-Using arrow keys, participants categorized the stimulus as quickly and accurately as possible.
-Response options appeared at the bottom of the screen (see Figure \@ref(fig:figure1)).
-
-On the abstract (standard) attention-shifting task, participants categorized colored (blue or yellow) shapes (squares or triangles) according to the 'color' or 'shape' rule (see Figure \@ref(fig:figure1)a).
-For example, if a blue triangle appeared on the screen and the rule was 'color', participants categorized the blue triangle as blue.
-However, if the rule was 'shape', participants instead categorized the blue triangle as a triangle.
-
-The ecological attention-shifting task replaced shapes and colors with faces (see Figure \@ref(fig:figure1)b).
-Faces were either male or female (gender), and were happy or angry (emotion).
-If a happy female face appeared on screen and the rule was 'gender', for example, participants categorized the face as female.
-If the rule was 'emotion', participants instead categorized the face as happy.
-The stimuli for the ecological attention-shifting task were selected from the NimStim library [@tottenham2009].
-The same female and male models were used for happy and angry expressions.
-
-For both versions, there were two types of trials: repeat and switch.
-Repeat trials use the same rule as the previous trial.
-If the current and previous rule is 'color', for instance, the current trial is a repeat trial.
-Switch trials are trials where the rule changes from the previous trial.
-If the current rule is 'color' but the previous was 'shape' (or vice versa), the current trial is a switch trial.
-
-Accuracy on attention-shifting tasks is normally high, and was in the current sample for both versions (*M~standard~* = `r (txt2_dvs$abs_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~standard~* = `r (txt2_dvs$abs_shifting_correct$sd/32 * 100) %>% round(2)`%; *M~ecological~* = `r (txt2_dvs$eco_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~ecological~* = `r (txt2_dvs$eco_shifting_correct$sd/32 * 100) %>% round(2)`%).Thus, instead of accuracy, attention-shifting ability is measured by comparing reaction times on repeat trials to switch trials.
-Reaction times on repeat trials are normally faster than switch trials; average repeat trial reaction times on the abstract and ecological versions were `r txt2_dvs$abs_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_re_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_re_rt$sd` *ms*), respectively.
-On switch trials, average reaction times were `r txt2_dvs$abs_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sw_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sw_rt$sd` *ms*) on the standard and ecological versions.
-
-To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000].
-We removed fast and slow reaction times and removed trials after incorrect responses (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
-We then subtracted the average reaction time on valid repeat trials from the average reaction time on valid switch trials to calculate switch cost scores (*M~switch~* - *M~repeat~*).
-The switch cost measures the relative delay in reaction time caused by switching between categorization rules.
-Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sc$sd` *ms*), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`).
-Higher switch costs mean longer reaction times on switch trials compared to repeat trials.
-Higher switch costs indicate less efficient attention shifting.
-
-### Working Memory Updating {#updating}
-
-Working memory updating was measured using two versions of the continuous counters task [@unsworth2015; @unsworth2008; @young2018], in which participants track a sequence of stimuli containing three different objects (see Figure \@ref(fig:figure1)).
-Participants keep running counts of each object in sequences nine items long.
-Each object was displayed for one second at a time.
-At the end of each sequence, participants reported the number of times each object appeared.
-For each round, there were three possible correct answers, one for each object type.
-
-In the abstract (standard) version, participants kept running counts of squares, circles, and triangles (see Figure \@ref(fig:figure1)c).
-The participant must keep track of each shape, updating counts as new shapes appeared, and report them at the end of the sequence.
-The ecological version followed the same format, but participants kept running counts of three different real-world objects (see Figure \@ref(fig:figure1)d): one positive (five-dollar bill), one negative (angry face), and one neutral (Salt Lake City bus).
-
-Participants completed five rounds of both versions.
-The maximum score was 15 for each version (five rounds × three possible correct).
-On the abstract and ecological versions, participants averaged `r txt2_dvs$abs_updating$mean * 15` (*SD* = `r txt2_dvs$abs_updating$sd * 15`) and `r txt2_dvs$eco_updating$mean * 15` (*SD* = `r txt2_dvs$eco_updating$sd * 15`), respectively (*r* = `r txt5_cor$updating$r`).
-Higher scores indicate better working memory updating performance.
-
-### Environmental Unpredictability {#unp}
-
-Our measure of environmental unpredictability integrated information from the interview and questionnaire.
-The interview contained three variables of interest.
-The first measured the level of exposure to living in a biologically non-intact family from birth to age 13.
-Interviewers asked participants about their family composition and the adults that lived with them in the home.
-If a participant's family composition changed, for example, because of a divorce, interviewers recorded the ages when participants experienced the change and for how long it persisted.
-A family was considered non-intact if the participant did not live with both biological parents during any period from birth to age 13.
-Based on the earliest age of disruption, we indexed the onset of exposure to a non-intact family by creating a four-level variable from 0 to 3.
-A 0 indicated the participant lived in an intact family (lived with both biological parents) from birth until age 13 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 0) %>% sum(na.rm=T)`); a 1 indicated that a disruption occurred after the age of 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 1) %>% sum(na.rm=T)`); a 2 indicated that a disruption occurred before age 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 2) %>% sum(na.rm=T)`); and a 3 indicated the participant was born into a non-intact family (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 3) %>% sum(na.rm=T)`).
-`r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T) %>% english::as.english() %>% str_to_title()` participants had missing information.
-
-The second interview variable tabulated the number of different parental figures (defined as spouses or boyfriends/girlfriends of the participant's mother and father) who lived in the same home with the participant.
-Trained interviewers tabulated the total number of co-residing parental figures, excluding the participant's biological mother and father (*M* = `r txt3_ivs$unp_interview_figures$mean`, *SD* = `r txt3_ivs$unp_interview_figures$sd`).
-
-The third interview variable focused on residential changes from birth to age 13 (reported retrospectively).
-Specifically, interviewers probed participants about the number of different homes they lived in and, in particular, whether moving to a new home involved living with new or different adults.
-On average, participants experienced `r txt3_ivs$unp_interview_moves$mean` (*SD* = `r txt3_ivs$unp_interview_moves$sd`) moves that involved changes in residential adults.
-
-The questionnaire included a measure of perceived childhood unpredictability [@mittal2015; @young2018; @szepsenwol2015].
-Participants responded to six items that assessed exposure to unpredictability up to age 13: 1) "Things were pretty calm and stable in my house" (reversed); 2) "People moved in and out of my house a lot"; 3) "I had a hard time knowing what my parent(s) or other people in my house were going to say or do from day-to-day"; 4) "My parent(s) argued or fought a lot with each other or with other people"; 5) "My parent(s) changed jobs a lot"; 6) "My parental situation changed a lot (for example, divorce or separation of parents, parents starting new romantic relationships, parents leaving the home)".
-Participants rated each item on a scale from 1 (never true) to 5 (very often true).
-Responses to these items were averaged to create a self-reported perceived childhood unpredictability measure (*M* = `r txt3_ivs$unp_perceived$mean`, *SD* = `r txt3_ivs$unp_perceived$sd`, $\alpha$ = `r txt4_rel$unp`).
-Higher scores indicated more perceived exposure to unpredictable environments.
-
-To create a composite measure of unpredictability, we aggregated across the interview and questionnaire.
-First, we created an interview-based measure of unpredictability using family intactness or disruptions, exposure to different parental figures, and residential moves involving new adults living in the home.
-We standardized these interview measures and then averaged them together ($\alpha$ = `r txt4_rel$unp_int`).
-We then aggregated this interview measure with self-reported perceived unpredictability from the questionnaire, standardizing each before averaging (*r* = `r txt5_cor$unp$r`).
-Higher scores indicated more exposure to unpredictability.
-
-### Violence Exposure {#vio}
-
-We measured violence exposure using the Neighborhood Violence Scale [@frankenhuis2020a; @frankenhuis2018] and two items about witnessing and involvement in physical fights.
-The measure contains 7 items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm".
-The physical fighting items asked about witnessing fights: "Based on your experiences at school and in your neighborhood, how many times did you see or hear someone being beaten up in real life?"; and involvement in fights: "How many times were you in a physical fight at school or in your neighborhood?".
-Both items were rated on a scale from 1 (0 times) to 8 (12 or more times).
-
-Responses were averaged to create a composite measure of neighborhood violence (*M* = `r txt3_ivs$vio_neighborhood$mean`, *SD* = `r txt3_ivs$vio_neighborhood$sd`, $\alpha$ = `r txt4_rel$vio`).
-Likewise, the two fighting items were averaged together (*M* = `r txt3_ivs$vio_fighting$mean`, *SD* = `r txt3_ivs$vio_fighting$sd`).
-To create a violence exposure composite, the neighborhood violence composite and fighting composite were standardized and then averaged (*r* = `r txt5_cor$vio$r`).
-Higher scores indicated more exposure to violence.
-
-### Poverty Exposure {#poverty}
-
-We assessed each participant's poverty exposure using three information sources: interview-assessed parent education and occupational prestige, school or club-provided economic information, and self-reported resource scarcity.
-
-During the interview, participants reported their parents' education and primary occupation.
-For parental education level, participants reported whether their mother and father graduated high school, went to college, and if they obtained a bachelor's degree or higher.
-Responses to each question were coded as 0 = 'no' and 1 = 'yes'.
-These items were summed to create a four-level variable for each parent where 0 = did not graduate high school, 1 = graduated high school but did not attend any college, 2 = graduated high school and completed some college, and 3 = went to college and obtained a bachelor's degree or higher.
-Mother and father education were averaged to create a parental education score (*M* = `r txt3_ivs$ses_interview_edu$mean`, *SD* = `r txt3_ivs$ses_interview_edu$sd`).
-
-Participants also reported their parents' occupation.
-Participants described, in general terms, their mother's and father's jobs and the kind of work involved.
-Trained coders cross-referenced these descriptions with 2010 census job codes [@hout2018].
-We calculated mother and father occupational prestige by matching census codes with prestige ratings from an established occupational prestige rating dataset [@hout2016].
-Prestige codes ranged from 0-100, with higher scores indicating higher occupational prestige for a particular job code.
-Mother and father prestige codes were averaged to create a parent occupational prestige score (*M* = `r txt3_ivs$ses_interview_occup$mean`, *SD* = `r txt3_ivs$ses_interview_occup$sd`).
-
-We also obtained school or club-provided economic information.
-The middle school provided four information sources: 1) whether or not students were receiving free lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_frl == 1) %>% sum(na.rm=T)`); 2) whether or not they were receiving reduced-price lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_rel == 1) %>% sum(na.rm=T)`); 3) whether they were receiving fee waivers (*n* = `r (data2_non_arbitrary$ses_school_wjms_fee == 1) %>% sum(na.rm=T)`); and 4) if they were experiencing homelessness (*n* = `r (data2_non_arbitrary$ses_school_wjms_hom == 1) %>% sum(na.rm=T)`).
-These information sources were compiled to create a binary economic disadvantage variable.
-A participant was economically disadvantaged if they were receiving any benefits or experiencing homelessness (*n* = `r txt1_sam$non_arb$free_lunch$wjms`).
-In the afterschool clubs, free or reduced-price lunch status was provided by self-report, staff, and club enrollment forms and cross-referenced to determine economic disadvantage in the clubs (*n* = `r txt1_sam$non_arb$free_lunch$bgc`).
-Overall, `r (data2_non_arbitrary$ses_school_freelunch == 1) %>% sum(na.rm=T)` participants were receiving economic assistance, `r (data2_non_arbitrary$ses_school_freelunch == 0) %>% sum(na.rm=T)` were not, and `r sum(is.na(data2_non_arbitrary$ses_school_freelunch))` had missing economic information.
-
-Participants also reported their perceived level of resource scarcity.
-They rated seven items from 1 (never true) to 5 (very often true): 1) "Your family had enough money to afford the kind of home you all needed"; "Your family had enough money to afford the kind of clothing you all needed"; 3) "Your family had enough money to afford the kind of food that you all needed"; 4) "Your family had enough money to afford the kind of medical care that you all needed"; 5) "I felt well-off (rich, wealthy) compared to other kids in my school"; 6) "I felt well-off (rich, wealthy) compared to other kids in my neighborhood"; and 7) "Your family struggled to make ends meet (get by financially)".
-The first six items were reversed, and all items were averaged to create a perceived resource scarcity measure (*M* = `r txt3_ivs$ses_perceived$mean`, *SD* = `r txt3_ivs$ses_perceived$sd`, $\alpha$ = `r txt4_rel$ses`).
-Higher scores indicated more perceived resource scarcity.
-
-To create a poverty exposure composite, we combined parent education and occupational prestige (reversed), school/club reported economic disadvantage, and perceived resource scarcity.
-First, we standardized and averaged parent education and occupation (*r* = `r txt5_cor$edu_int$r`).
-Then, we recoded school-provided economic codes to be equal to half of a standard deviation above and below the mean (in terms of z-scores).
-Specifically, those receiving free or reduced-price lunch were coded as .5, and those who were not were coded as -.5.
-To create a final composite, we averaged parent education/occupation (standardized), perceived resource scarcity (standardized), and the recoded school/club economic disadvantage.
-Higher values indicated more exposure to poverty.
-
-### Control Variables {#controls}
-
-We included two control variables: age and interviewer-rated distractions during testing.
-We included these because older youth tend to score higher on cognitive tests than younger youth [@best2010; @best2011; @huizinga2006], and disruptions during the tasks could negatively impact performance.
-Interviewers completed quantitative ratings of the testing environment including 1) the level of noise; 2) the level of chaos; 3) how often there were interruptions; and 4) how often the participant appeared distracted.
-Interviewers rated each item on a scale from 1 (not at all) to 7 (much more than average).
-Items were averaged to create a composite (*M* = `r txt3_ivs$test_envr$mean`, *SD* = `r txt3_ivs$test_envr$sd`), where higher scores indicate more distractions.
-
-We also included the Child Social Desirability scale [@miller2014].
-The measure includes 14 items such as "Have you ever broken a rule?" and "Do you sometimes feel angry when you don't get your way?".
-Participants indicated 1 (yes) or 0 (no) for each item.
-More socially desirable responses were scored as 1.
-Items were then summed to create a social desirability index (*M* = `r txt3_ivs$csd$mean`, *SD* = `r txt3_ivs$csd$sd`, $\alpha$ = `r txt4_rel$csd`).
-
-# Results {#results}
-
-## Data Analysis Strategy {#multiverse}
-
-We used a multiverse analysis approach for all analyses to systematically evaluate the robustness (or sensitivity) of analyses across all arbitrary data processing decisions [see @simonsohn2020; @steegen2016 for details].
-We identified six arbitrary data processing decisions.
-First, we conducted analyses with and without the after-school club sample.
-We did this because our procedure was slightly different across the two samples and the testing environment was more disruptive in the clubs compared with the middle school.
-Second, we conducted analyses with and without participants with minor distractions during testing.
-Third, we analyzed the data with and without participants who missed one trap question (those who missed more than 1 were already excluded).
-Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded).
-Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
-
-Our last arbitrary data processing decision pertained to socially desirable responses.
-It is well-known that some youth tend to describe themselves in socially desirable ways.
-This raises concerns about the validity of self-reported childhood adversity measures: youth scoring higher on social desirability might underreport or underrate their exposures to negative experiences.
-Indeed, scores on the Child Social Desirability scale were correlated with exposures to unpredictability (*r* = `r txt5_cor$csd_unp$r`) and violence (*r* = `r txt5_cor$csd_vio$r`), though not with poverty.
-One way to handle this issue is to statistically remove overlapping variance between social desirability and each predictor, using the leftover variance (e.g., the residual variance in childhood adversity exposures not associated with social desirability) as a predictor.
-Because it is unclear how social desirability might affect the interpretation of our models, we analyzed our data with residualized and non-residualized predictors.
-
-To test our hypotheses, we performed a set of primary and secondary analyses on attention-shifting and working memory performance.
-Our primary analyses tested the effects of task version, adversity dimensions, and adversity dimension × task version interactions.
-Specifically, we tested the main effect of environmental unpredictability (confirmatory), violence exposure (confirmatory), and poverty exposure (exploratory), and the interaction between each adversity dimension with task version (abstract vs.
-ecological) on attention-shifting and working memory performance.
-We ran separate analyses for each adversity dimension and outcome combination.
-Using all possible combinations of arbitrary decisions, we constructed a multiverse of `r length(multi_data_list)` datasets.
-The minimum and maximum sample sizes were `r map_dbl(multi_data_list, "n") %>% min()` and `r map_dbl(multi_data_list, "n") %>% max()`, respectively.
-
-We ran the same underlying mixed-effects linear regression model.
-Analyses were conducted using R [@rcoreteam2020] and mixed models were fit using the lme4 package [@bates2015].
-Our mixed-effects models included five fixed terms: the main effect of task version (ecological or abstract version, within-subjects), the main effect of childhood adversity (between-subjects), the interaction between task version and adversity exposure, the main effect of age (control variable), and the main effect of test distraction ratings (control variable).
-Task version was grand mean centered (abstract versions = -1, ecological versions = 1).
-All childhood adversity measures were standardized before model fitting, and all models included a random intercept for task version nested in participants.
-
-Our models for attention shifting and working memory updating differed in one respect.
-Our sample included a small subset of siblings (*n* = `r txt6_sib$n`, `r txt6_sib$families` families).
-All sibling groups were pairs of two (`r txt6_sib$sizes$two` sibling pairs) except for `r english::as.english(txt6_sib$sizes$three)` group of three and `r english::as.english(txt6_sib$sizes$four)` group of four siblings.
-We computed intraclass correlations (ICCs) for sibling groups for attention-shifting and working memory updating scores.
-ICCs for attention shifting were essentially zero, but they were non-zero for working memory updating scores (*ICC~standard~* = `r txt6_sib$iccs$abs_update`, *ICC~ecological~* = `r txt6_sib$iccs$eco_update`).
-Thus, all models analyzing working memory updating included an additional random intercept for siblings.
-Non-siblings were given the same sibling-group code, so the model could compute an intercept for non-siblings.
-
-To facilitate interpretation of multiverse results, we report median standardized $\beta$s, median 95% confidence intervals, and percent significant for each term in our model (see Table \@ref(tab:table2)).
-Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect (two-sided *p*-value \< .05) for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions.
-For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique to compute overall *p*-values.
-The technique makes it possible to know if a multiverse analysis produced a median effect size larger than expected, given the null hypothesis that the median $\beta$ = 0 [see @simonsohn2020 for details].
-
-Table \@ref(tab:table1) displays bivariate associations between all composite measures of adversity, including components of each, and descriptive statistics.
-Our primary interests were the main effect of adversity and the interaction of adversity with task-version.
-Table \@ref(tab:table2) shows median effect sizes ($\beta$-coefficients), sample sizes, and bootstrapped *p*-values for attention-shifting and working memory updating analyses for the main effect of adversity (unpredictability, violence, and poverty) and the interaction term (task version × adversity).
-Table \@ref(tab:table3) reports median simple effects of task version across high and low levels of adversity and median simple effects of adversity across abstract and ecologically relevant task versions.
 
@@
 ```
-
-Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction $\beta$-coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).
-
-We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), including an [Updated Primary Analysis Plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
-We conducted secondary analyses after our primary analyses (see [Secondary Analyses](#secondary) below).
-Before conducting these analyses, we uploaded secondary analysis plans (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), explaining the goals and purpose of each secondary analysis.
-A Red Team Critic [@redteammarket2021] successfully reproduced and verified (see this [Red Team Report](https://osf.io/xv94z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)) all analyses prior to submission.
-
-## Primary Analyses {#primary}
-
-### Attention Shifting {#primary-shifting}
-
-Across each set of multiverse analyses, there were significant main effects of task version.
-All median effects sizes for task version were $\beta$s = `r c(mod_terms1$shifting.unp.type_z$median_beta, mod_terms1$shifting.vio.type_z$median_beta, mod_terms1$shifting.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for multiverse models testing unpredictability, violence exposure, and poverty exposure, indicating that switch costs (see [Attention Shifting](#shifting) for switch cost explanation) were moderately higher for the ecological version compared to the abstract version (see SI Figures 1-3).
-That is, reaction times on switch trials, compared to repeat trials, were longer when stimuli were ecologically relevant as opposed to abstract.
-However, there were no effects of age (all median $\beta$s = `r c(mod_terms1$shifting.unp.age$median_beta, mod_terms1$shifting.vio.age$median_beta, mod_terms1$shifting.ses.age$median_beta) %>% mean()`, all *ps* \>.05) or test distraction ratings (all median $\beta$ = `r c(mod_terms1$shifting.unp.test_envr$median_beta, mod_terms1$shifting.vio.test_envr$median_beta, mod_terms1$shifting.ses.test_envr$median_beta) %>% mean()`, all *ps* \> .05) on overall switch costs (see SI Figures 1-3).
-
-```{r figure2, fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure (y-axis was reversed so that higher values = faster shifting), b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
-fig2
-```
-
-Overall, there were no significant interaction effects between task version and unpredictability, violence exposure, or poverty exposure (see Table \@ref(tab:table2), Table \@ref(tab:table3), and Figure \@ref(fig:figure2)b).
-However, analyses produced main effects of unpredictability (median $\beta$ = `r mod_terms2$shifting.unp$median_beta_main`, `r mod_terms2$shifting.unp$p_percent_main %>% str_remove("\\.00")` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.unp$p_overall_main`) and violence exposure (median $\beta$ = `r mod_terms2$shifting.vio$median_beta_main`, `r mod_terms2$shifting.vio$p_percent_main` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.vio$p_overall_main`; see Table \@ref(tab:table2)).
-There were no main effects of poverty exposure (median $\beta$ = `r mod_terms2$shifting.ses$median_beta_main`, no *ps* \< .05, overall *p* = `r mod_terms2$shifting.ses$p_overall_main`; see Table \@ref(tab:table2)).
-That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures were associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecologically relevant.
-
-```{r table2, tab.id = "table2", tab.cap.style = "Table Caption", tab.cap = "Median standardized effects, 95% confidence intervals, percent significant, and bootstrapped p-values for the main effect of adversity and adversity by task version interactions."}
-table.02.0 %>% 
-  ungroup() %>% 
-  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
-  arrange(dv,iv) %>% 
-  select(-dv) %>% 
-  add_column(.after = 5,"empty1" = "") %>% 
-  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
-  add_row(.after = 4, "iv" = "Working Memory Updating") %>% 
-  flextable() %>% 
-  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
-  merge_h_range(i = 5, j1 = 1, j2 = 10) %>% 
-  bold(i = c(1,5), j = 1) %>% 
-  padding(i = c(2:4, 6:8), j = 1, padding.left = 10) %>% 
-  width("empty1", width = .2) %>% 
-  set_header_labels(iv = "", empty1 = "", ci_main = "95% CI", ci_int = "95% CI") %>% 
-  add_header_row(
-    values = c(" ", "Main Effect", " ", "Interaction"),
-    colwidths = c(1, 4, 1, 4)
-  ) %>% 
-  compose(i = 2, j = c(2,7), as_paragraph("\U1D6FD"), part = "header") %>% 
-  compose(i = 2, j = c(4,9), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
-  compose(i = 2, j = c(5,10), as_paragraph(as_i("p")), part = "header") %>% 
-  align(i = 1:2, align = "center", part = "header") %>% 
-  border_remove() %>% 
-  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
-  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 8, border.bottom = fp_border_default(), part = "body") %>% 
-  bold(i = 1:2, part = "header") %>% 
-  set_table_properties(width = 1, layout = "autofit") %>% 
-  add_footer_row(
-    values = " ",
-    colwidths = 10
-  ) %>% 
-    add_footer_row(
-    values = " ",
-    colwidths = 10
-  ) %>% 
-  compose(
-    i = 1, j = 1, 
-    as_paragraph(as_i("Note: "), "The p (%) column reflects the number of analyses that produced p-values < .05 for a given multiverse.
-The total number of analyses for each measure was 64.
-Overall p-values were computed using a bootstrapped resampling method and reflect the probability of obtaining an effect size as extreme or more extreme given the median effect is 0."),
-    part = "footer"
-  )
-```
-
-### Working Memory Updating {#primary-updating}
-
-Across each set of multiverse analyses, there were again significant main effects of task version.
-All median effects sizes for task version were $\beta$s = `r c(mod_terms1$updating.unp.type_z$median_beta, mod_terms1$updating.vio.type_z$median_beta, mod_terms1$updating.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for models testing unpredictability, violence exposure, and poverty exposure, indicating that updating performance was better when stimuli were ecological relevant compared to abstract, on average (see SI Figures 4-6).
-There were also consistent main effects of age; median effects were $\beta$ = `r mod_terms1$updating.unp.age$median_beta` (all *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.age$median_beta` (all *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.age$median_beta` (all *ps* \< .05) for poverty exposure models (see SI Figures 4-6).
-That is, older youth scored higher on working memory updating, on average.
-Finally, there were some main effects of test environment distraction ratings.
-Median effects sizes were $\beta$ = `r mod_terms1$updating.unp.test_envr$median_beta` (`r (mod_terms1$updating.unp.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.test_envr$median_beta` (`r (mod_terms1$updating.vio.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.test_envr$median_beta` (`r (mod_terms1$updating.ses.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for poverty exposure models, indicating that more test distractions reduced working memory updating performance, on average (see SI Figures 4-6).
-
-Multiverse analyses revealed a main effect of poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_main`, all *ps* \< .05, bootstrapped *p* \< .001) but no main effects of unpredictability (median $\beta$ = `r mod_terms2$updating.unp$median_beta_main`, no *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.unp$p_overall_main`) or violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_main`, `r mod_terms2$updating.vio$p_percent_main` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_main`).
-Analyses also revealed two significant interactions: task version × violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_int`, `r mod_terms2$updating.vio$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_int`) and task version × poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_int`, `r mod_terms2$updating.ses$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.ses$p_overall_int`).
-Youth exposed to low levels of violence or poverty tended to perform better on the abstract working memory updating task (violence exposure median *b~abstract~* = `r simple_effects$updating.vio$beta_abs`, `r simple_effects$updating.vio$p_percent_abs` of *ps* \< .05; poverty exposure median *b~abstract~* = `r simple_effects$updating.ses$beta_abs`, all *ps* \< .05), compared to youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)).
-However, this performance gap closed on the ecological working memory task (violence exposure median *b~ecological~* = `r simple_effects$updating.vio$beta_eco`, no *ps* \< .05; poverty exposure median *b~ecological~* = `r simple_effects$updating.ses$beta_eco`, `r simple_effects$updating.ses$p_percent_eco` of *ps* \< .05).
-Put differently, youth exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically relevant version compared to their own performance on the abstract version (median simple *b~high-violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high-poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas youth exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low-violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low-poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
-In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
-
-```{r figure3, fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure, b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
-Proportions of each arbitrary decision with p-values < .05 are indicated on the right side of each specification grid.
-Blank proportions indicate proportions = 0.
-Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
-fig3
-```
-
-## Secondary Analyses {#secondary}
-
-We followed-up our primary analyses with two sets of secondary, exploratory analyses.
-We uploaded secondary analysis plans to the OSF prior to conducting them (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)).
-These analyses focused on two questions.
-First, in contrast to prior work [@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting).
-However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures.
-Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure; see [Measures](#measures) section) have unique associations with attention shifting and working memory updating performance.
-To address this, we expanded our multiverse approach to include each component of our predictor variables as additional arbitrary decisions.
-
-The second question focused on the interactive effects of task version × violence exposure and task version × poverty exposure on working memory updating performance.
-Specifically, primary analyses revealed an equalization effect for both violence and poverty exposures on working memory updating.
-However, because measures of violence and poverty were not included in the same statistical model, it is unclear whether these interactions are independent.
-For example, one possibility is that exposures to violence and poverty are independently associated with working memory updating performance.
-Alternatively, they may overlap, reflecting the same association.
-To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty in the same model.
-If violence and poverty exposures interact independently with task version, both interaction terms should remain significant.
-However, if they represent overlapping effects on working memory updating performance, one or the other may drop out of significance, which would suggest that one or the other adversity dimension is driving the effects of the other.
-
-```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap = "Median simple effects for task version and adversity."}
-table.03.0 %>% 
-  ungroup() %>%
-  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
-  arrange(dv,iv) %>% 
-  select(-dv) %>% 
-  add_column(.after = 5,"empty1" = "") %>% 
-  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
-  add_row(.after = 4, "iv" = "Working Memory Updating") %>% 
-  flextable() %>% 
-  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
-  merge_h_range(i = 5, j1 = 1, j2 = 10) %>% 
-  bold(i = c(1,5), j = 1) %>% 
-  padding(i = c(2:4, 6:8), j = 1, padding.left = 10) %>% 
-  width("empty1", width = .2) %>% 
-  set_header_labels(iv = "", empty1 = "") %>% 
-  add_header_row(
-    values = c(" ", "Task Version", " ", "Adversity Exposure"),
-    colwidths = c(1, 4, 1, 4)
-  ) %>% 
-  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
-  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
-  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
-  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
-  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
-  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
-  align(i = 1:2, align = "center", part = "header") %>% 
-  border_remove() %>% 
-  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
-  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 8, border.bottom = fp_border_default(), part = "body") %>% 
-  bold(i = 1:2, part = "header") %>% 
-  fontsize(size = 11, part = "body") %>%
-  set_table_properties(width = 1, layout = "autofit") %>% 
-  add_footer_row(
-    values = " ",
-    colwidths = 10
-  ) %>% 
-    add_footer_row(
-    values = " ",
-    colwidths = 10
-  ) %>% 
-  compose(
-    i = 1, j = 1, 
-    as_paragraph(as_i("Note: "), "Simple effects are unstandardized.
-Task Version reflects the median simple effect of adversity when the task version was abstract and ecological.
-Adversity reflects the median simple effect of task version when adversity is low (-1 SD) and high (+1 SD).
-The p (%) columns reflect the number of analyses that produced simple effect p-values < .05."),
-    part = "footer"
-  )
-```
-
-### Exploring Components of Adversity Dimensions {#secondary1}
-
-We ran an expanded multiverse analysis to explore the effects of each component of our adversity composites (see [Measures](#measures) section) on attention shifting and working memory updating performance.
-Environmental unpredictability contained two components, perceived unpredictability (self-reported) and an interview-based measure tabulating family disruptions, parental figures, and residential moves.
-Violence exposure contained two self-report components: neighborhood violence and exposure to/involvement in violence.
-Poverty exposure contained three components: parental education/occupation (interview), perceived resource scarcity (self-report), and school-coded economic disadvantage (fee waivers, free- or reduced-priced lunch, and homelessness).
-
-For this expanded multiverse approach, we retained all original data processing decisions (i.e., original 64 combinations of decisions) and added adversity component as an additional decision.
-For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures: attention shifting and working memory).
-We applied the same approach to violence exposure (three violence variables, 384 analyses) and poverty exposure (four poverty variables, 512 analyses).
-The full results of these analyses are reported in the supplement (see SI Table 2).
-
-For attention shifting, consistent with our primary analyses, there were no interactions for any component of adversity and task version (see SI Table 2 and SI Figures 7-9).
-However, there were a few main effects of adversity.
-First, primary analyses revealed, under some analytic decisions, a main effect of unpredictability.
-Upon inspection of each unpredictability component, this effect appeared to be entirely driven by self-reported perceived unpredictability.
-Specifically, no main effect *p*-values for interview-based unpredictability were \< .05, whereas `r secondary1_medians$shifting.unp.Perceived.iv$p_percent` were for perceived unpredictability (see SI Table 2, SI Table 3, and SI Figure 7).
-In addition, violence exposure revealed that our primary analyses were driven by neighborhood violence (`r secondary1_medians$shifting.vio.Neighborhood.iv$p_percent` of *ps* \< .05) and not by direct witnessing or involvement in fights (no *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 8).
-There were no main effects of poverty exposure components on attention shifting (see SI Table 2, SI Table 3, and SI Figure 9).
-
-For working memory updating, there were no interaction between any unpredictability component (perceived or interview-based) and task-version (see SI Figure 10).
-However, our expanded analysis with violence exposure revealed that interactions obtained with the composite measure were not driven by neighborhood violence but instead by witnessing or involvement in violence (`r secondary1_medians$updating.vio.Fighting.iv_type_z$p_percent %>% str_remove("\\.00")` of interaction *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 11).
-No interactions were significant with the neighborhood violence component of the violence composite.
-For poverty exposure, interview-based parental occupational prestige and school-reported economic disadvantage showed some interaction effects (parental education/occupational prestige `r secondary1_medians$updating.ses.Parents.iv_type_z$p_percent` of *ps* \<.05; school coded economic disadvantage `r secondary1_medians$updating.ses.School.iv_type_z$p_percent` of *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 12).
-Self-reported perceived resource scarcity showed no interaction effects (see SI Table 2, SI Table 3, and SI Figure 12).
-
-### Comparing Violence and Poverty Exposure Interactions with Task-Version {#secondary2}
-
-Our next secondary analysis was designed to compare the violence exposure × task-version interaction with poverty exposure × task-version interaction on working memory updating performance in the same model.
-To do so, we ran a multiverse analysis using the original set of `r length(multi_data_list)` data processing decisions.
-We entered the same controls, main effects of task-version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty exposure.
-Analyses revealed a main effect of poverty (`r secondary2_medians$ses_agg_z$p_percent` of *ps* \< .05); consistent with the primary analyses, lower poverty was associated with better updating performance under most analytic decisions.
-However, there were no main effects of violence exposure (no *ps* \< .05).
-For interactions, there were no effects of task version × poverty (no *ps* \< .05, see SI Figure 13) and only a small number of significant task version × violence exposure effects (`r secondary2_medians$type_z_vio_agg_z$p_percent` of *ps* \< .05, see SI Figure 13).
-More specifically, when both interactions were entered into the same model, only task-version × violence exposure remained significant, although only under a small set of analytic decisions.
-
-Violence and poverty exposure interaction patterns were qualitatively similar to those obtained in our primary analyses (see Figure \@ref(fig:figure3)a and SI Figure 13).
-However, these secondary results suggest that the violence exposure interaction with task-version may be driving our poverty × task version results for working memory updating.
-One possibility is that the shared variance between poverty and violence exposures (*r* = `r txt5_cor$ses_vio$r`) is responsible for both interaction effects.
-In other words, although poverty and violence exposure are theoretically distinct, our poverty composite may capture poverty-related violence exposures (e.g., high poverty neighborhoods contain more crime) and therefore interact with task-version.
-When directly compared, explicit measures of violence exposure remained significant (although only under a small set of analytical decisions), whereas poverty interactions dropped out entirely.
-
-# Discussion {#discussion}
-
-We examined how ecologically relevant testing materials affect cognitive performance among adversity-exposed youth.
-We measured three dimensions of adversity--- environmental unpredictability, violence exposure, and poverty---and tested performance on attention-shifting and working memory updating tasks.
-We administered two versions of each task: one using abstract stimuli and the other using ecological, real-world stimuli, allowing us to compare performance within- and between-subjects.
-
-Leveraging multiverse analysis [@simonsohn2020; @steegen2016], we tested interactions between dimensions of adversity and task version on attention shifting and working memory updating performance.
-We did not find interaction effects for attention shifting.
-However, youth exposed to unpredictability and violence showed lower switch costs on average, suggesting slightly improved attention shifting performance irrespective of task content.
-These findings are consistent with a recent study showing that higher caregiving instability was associated with improved attention shifting [@fields2021].
-However, our findings also partially diverge from prior work [@mittal2015; @nweze2021].
-For example, whereas we found unpredictability was associated with improved attention shifting on average, Mittal and colleagues [-@mittal2015] found no difference in performance under neutral conditions.
-And, although they found improved attention shifting for those exposed to high unpredictability under uncertainty, it remains unclear how this effect relates to those obtained in the current study.
-In addition, Nweze and colleagues [-@nweze2021] found no association between adversity and attention shifting, but they tested institutionalized children rather than measuring adversity dimensions.
-In general, we should interpret the results cautiously.
-Although we followed field standards for calculating switch costs by computing difference scores, such scores ignore participant-level reaction times.
-Mixed-modeling approaches can account for both overall reaction times and differences across switch and repeat trials, but require more statistical power to test three-way interactions.
-Future research should consider modeling approaches that capture participant-level reaction times and differences across conditions.
-
-For working memory updating, we found lowered performance among violence- and poverty-exposed youth on the abstract working memory updating task than peers with reduced exposures.
-However, ecological materials produced an equalization effect: the updating performance gap between low and high adversity-exposed youth narrowed on the ecological updating task.
-Interestingly, updating performance was unrelated to unpredictability.
-These findings are partially consistent with prior work on adversity exposure and working memory updating performance [@nweze2021; @young2018].
-For example, both Young and colleagues [-@young2018] and the current study found lowered abstract working memory performance among high adversity-exposed individuals.
-Although performance with ecological stimuli is not directly comparable to performance under manipulated uncertainty, both studies reduced the updating performance gap under ecologically relevant conditions.
-However, there are also discrepancies.
-For example, Young and colleagues [-@young2018] found effects with unpredictability and not poverty, whereas the current study found associations with violence and poverty but not unpredictability.
-Finally, Nweze and colleagues [-@nweze2021] found improved working memory performance among institutionalized youth without ecological stimuli or uncertainty manipulations.
-However, both their adversity and working memory measures were different.
-
-Overall, inconsistencies across prior work and the current attention-shifting and working memory updating findings could be attributed to differences in sampling (adults vs.
-youth), the sampled range of adversity exposure (restricted vs.
-broad), or methods/design (within- vs.
-between-subjects design; lab vs.
-community/school settings).
-Future research should both address these inconsistencies and conduct more direct replications of individual studies to converge on reliable patterns.
-
-Our first set of secondary analyses focused on the components of our adversity composites.
-For attention shifting performance, the main effect of our unpredictability composite appeared to be driven by self-reported perceived unpredictability and not by the interview-based measure which captured changes in youths' living situations.
-Likewise, the main effect of violence exposure appeared to be driven by neighborhood violence and not involvement or witnessing fights.
-For working memory updating, interaction effects involving violence exposure were driven by involvement or witnessing fights but not perceptions of neighborhood violence.
-All components of poverty exposure measures, except self-reported perceptions of resource scarcity, showed interactive effects with task version on working memory updating.
-Our second set of secondary analyses compared violence to poverty exposure in the same model.
-Findings suggest, at least when directly comparing interaction terms, violence exposure × task version predicted the working memory updating equalization effect whereas the poverty × task version interaction did not.
-
-There are many possible explanations for the diverging adversity component patterns.
-First, some information sources may be more accurate than others.
-For example, asking about the number of fights one has been involved in or witnessed might be easier to report than asking broader questions about neighborhood danger.
-Second, for different cognitive abilities, objective versus subjective reports may be more relevant.
-For example, for attention-shifting, perceptions appeared to matter whereas objective events did for working memory updating.
-Third, although adversity components were correlated in the moderate range---as typically observed in the literature [@dong2004a; @green2010; @jacobs2012; @matsumoto2021; @mclaughlin2012; @smith2021]---they may measure different constructs.
-For example, more objective indicators might capture aspects of the broader ecology but subjective, self-reported measures capture how youth have internalized and perceived their environment and family life.
-Although interesting, all secondary analyses are exploratory, and should be interpreted with caution.
-Nonetheless, these analyses highlight the need to measure multiple dimensions of adversity, compare them, and consider each measure's report format and source.
-
-Taken together, our equalization patterns of results are striking compared to the backdrop of developmental science, which almost exclusively reports lowered cognitive performance in people exposed to harsh environments.
-We also document lowered performance among adversity-exposed youth, but this effect was specific to abstract stimuli, at least for working memory updating.
-When testing materials were more concrete, adversity-exposed youth perform about as well as youth from supportive backgrounds.
-These results converge with recent work comparing stimulus types among adversity-exposed youth.
-For example, Rifkin-Graboi and colleagues [-@rifkin-graboi2021] found preschoolers exposed to caregiver adversity were more accurate on relational memory for socioemotional than non-socioemotional stimuli and Zuilkowski and colleagues [-@zuilkowski2016] found that Sub-Saharan African children from low SES backgrounds were more accurate on reasoning tests with three dimensional stimuli than two dimensional stimuli.
-
-These effects have both practical and theoretical implications.
-Practically, these effects support the idea that ecologically relevant testing materials may 'even the playing field' for adversity-exposed youth.
-That is, pending replication and extension, our data suggest leveraging ecologically relevant materials in education may hold promise for closing achievement gaps [@ellis2017; @ellis2020; @frankenhuis2020].
-In fact, programs for gifted students from low-income backgrounds already leverage concrete learning materials [@vantassel-baska2018].
-However, our data also suggest the effect of ecological content may be specific to particular abilities.
-On the one hand, our data showing within-subject improvements on working memory updating is consistent with past research using ecological versions of Raven's Progressive Matrices [@richardson1991].
-On the other, ecological content actually lowered attention shifting performance for everyone compared to abstract content, possibly because shifting was more difficult with more ecologically hot or "sticky" stimuli.
-This negative effect is consistent with other studies reporting lowered performance on some tests with ecologically relevant content [@duquennois2022; @frankenhuis2020; @muskens2019].
-
-Theoretically, our findings support the notion that hidden talents may emerge when using ecologically relevant testing materials, but they also raise questions.
-In particular, why should ecologically relevant stimuli equalize working memory updating performance for adversity-exposed youth than youth with reduced exposures?
-There are at least three possibilities.
-First, adversity exposure could simultaneously lower and improve performance.
-While abstract working memory updating performance is lowered, ecological working memory updating performance is improved.
-However, this explanation requires that different cognitive mechanisms process different classes of stimuli, even on tests of the same ability.
-If this is true, those mechanisms that process abstract content underperform compared to those that process ecological content.
-Second, there may be no actual differences in underlying abilities.
-Instead, ecologically relevant stimuli may activate intact, but dormant or underrecruited, working memory updating processes.
-Thus, when adversity-exposed youth are tested under abstract testing conditions, their cognitive processes operate at a lower level (remain inactive) but operate equally well with ecological testing materials.
-This makes sense if adversity limits energy and/or cognitive resources.
-Under such constraints, it may be adaptive to activate expensive cognitive processes only when necessary.
-Third, ecological testing materials may remove barriers, such as testing anxiety or test unfamiliarity, that disadvantage adversity-exposed youth.
-Unlike the selective activation of cognitive resources, the additional stressors of testing are removed, allowing cognitive mechanisms to operate unimpeded.
-However, this explanation is difficult to reconcile with experimental work which finds that mild stress/uncertainty improves performance [@mittal2015; @young2018].
-Future research should use research designs that can disentangle these explanations.
-
-Our study has several strengths and limitations.
-First, we leveraged a within-person design, which illuminated the effects of ecological testing materials in the same person.
-However, the correspondence between each version of our tests was modest for working memory updating (*r* = `r txt5_cor$updating$r`) and low for attention shifting (*r* = `r txt5_cor$shifting$r`).
-Although the task structure was the same, it is unclear to what extent the ecological tests measured the same construct, especially for attention shifting.
-In addition, test difficulty may have been different across test versions (e.g., switch costs were larger on the ecological version).
-Future research should consider teasing apart test difficulty from ecological relevance.
-Second, our strategy for creating ecological test versions was to select stimuli believed to be more salient or impactful to adversity-exposed youth.
-However, we did not independently assess the ecological validity of our real-world stimuli.
-Thus, it is unclear whether our tests were specifically matched to the actual experiences of adversity-exposed youth or more ecologically relevant for these youth than for those from supportive conditions.
-Third, we leveraged multiverse analysis to examine the robustness of our findings to arbitrary data processing decisions.
-Though powerful, the technique is relatively new and should be interpreted with caution.
-For instance, as with other statistical techniques, researchers might disagree over which data processing decisions are arbitrary [@delgiudice2021].
-Fourth, although we found some effects of ecological testing materials, we measured abilities that have shown some evidence of adversity-related enhancement.
-To explore generalizability of ecological content across abilities, future research may create ecological versions of tests known to disadvantage adversity-exposed youth, such as inhibition or working memory retrieval [@mittal2015; @young2018], and compare performance to abstract versions.
-Finally, although we used interviews and self-report methods, all of our childhood adversity measures were cross-sectional and some were retrospective.
-These measurement limitations may be partially offset because our sample was still living in their developmental environment.
-However, this does not replace the need for prospective, longitudinal measures and cannot eliminate all biases associated with retrospective reporting [@reuben2016].
-Thus, it remains unclear to what extent the current environment, rather than the developmental environment, is driving our findings.
-
-Until recently, developmental science has almost exclusively reported lowered cognitive performance in people from harsh conditions.
-The hidden talents framework has challenged this notion and inspired researchers to document the strengths and abilities of people from adversity.
-Theoretically, our data help to refine the hidden talents framework and illuminate future research questions surrounding the unique skills and abilities of people living in harsh conditions.
-Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might 'even the playing field' for adversity-exposed youth.
-
-\pagebreak
-
-# References {#refs}

### 2022-03-16 manuscript/tables/table-2.Rmd
make separate .docx files for tables

--- 2022-01-28 manuscript/manuscript.Rmd
@@
 ```
-
-# Abstract
-
-\noindent Adversity-exposed youth tend to score lower on cognitive tests.
-However, the hidden talents approach proposes some abilities are enhanced by adversity, especially under ecologically relevant conditions.
-Sampling `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White), we administered two versions of an attention shifting and working memory updating task---one abstract, one ecological.
-We measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions.
-There were no interactions for attention shifting.
-For working memory updating, youth exposed to violence and poverty scored lower than their peers with abstract stimuli but just as well with ecological stimuli.
-These results are striking compared to contemporary developmental science, which almost exclusively reports lowered performance among adversity-exposed youth.
-
-*Keywords*: hidden talents, working memory updating, attention shifting, adversity, adaptations to stress
-
-\pagebreak
-
-# Hidden talents in context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth
-
-Youth living in adverse conditions tend to score lower on cognitive tests than youth in supportive conditions.
-For example, youth raised in poverty are more likely to have difficulties learning in school and score lower on standardized tests [@farah2006; @hackman2010; @noble2007; @ursache2016a].
-Harsh and unpredictable environments are thought to cause high levels of chronic stress, which can impair brain regions responsible for memory and learning [@blair2012].
-Thus, the contemporary view is that exposure to adversity undermines cognitive development and leads to a host of cognitive deficits [reviewed in @duncan2017; @hackman2010; @mclaughlin2019; @pechtel2011].
-Although it is clear that harsh and unpredictable environments are harmful to youth, there is growing interest in the *hidden talents approach*, which proposes that some abilities may be enhanced by adversity, especially skills and abilities that help youth meet real-world challenges in adverse environments [@ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013].
-These stress-adapted skills are referred to in this literature as *hidden talents*.
-
-The hidden talents approach is rooted in an adaptation-based framework [see @ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013 for reviews], which assumes development tailors skills and abilities in relation to the environment.
-Accordingly, exposure to adversity should shape skills and abilities well-suited for dealing with the challenges and opportunities associated with harsh and unpredictable environments.
-However, because specific dimensions of adversity (e.g., violence versus resource-scarcity) may pose unique challenges [@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity [@frankenhuis2020].
-For instance, some evidence suggests that physically abused youth can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], people living in poverty have more accurate social perception [@bjornsdottir2017; @dietze2021; @piff2018], and that anxiously attached people can more accurately detect deception [@eindor2014; @shoda2013].
-
-Although some abilities themselves are more ecologically relevant to specific dimensions of adversity, hidden talents may also emerge under ecologically relevant conditions.
-For example, previous studies of hidden talents have tested cognition under ecologically relevant *contexts and situations*.
-In particular, studies have experimentally manipulated the current context to be uncertain and mildly stressful (or not) and measured performance on executive functioning and working memory tasks [@mittal2015; @young2018].
-Strikingly, people from unpredictable environments showed more efficient switching on attention shifting tasks and more accurate responses on working memory updating tasks, but this effect only emerged under conditions of uncertainty.
-There was no performance increase under control conditions.
-However, some studies have found similar patterns without uncertainty [@fields2021; @nweze2021].
-
-Hidden talents may also emerge when testing *content and stimuli* are more ecologically relevant and concrete.
-Typical cognitive tests use abstract content that is largely detached from the real world.
-Such abstract materials may disadvantage youth whose childhood experiences involve less abstract, analytical problem solving [@ellis2020; @frankenhuis2013].
-Cultural psychologists and anthropologists have demonstrated this fact across the world.
-For example, people from non-Western cultures tend to score lower than people in Western cultures on standard versions of cognitive tests, but this performance gap closes or disappears when more ecologically relevant measures are used [@banerjee2017; @grigorenko2004; @rogoff2017; @sternberg2001].
-This work challenges the assumption that "baseline" performance is best captured by standard/abstract tests.
-In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020; @zuilkowski2016].
-These ideas also raise an important question: do adversity-exposed youth score higher on tests with ecologically-relevant stimuli relative to those with abstract stimuli?
-
-One way to test this question is to replace sterile testing materials with ecologically relevant content from the real world.
-For example, one study tested memory and reasoning among young adults who varied in their exposures to violence [@frankenhuis2020a].
-They created two versions of a memory and reasoning task, one neutral (chronological age) and one more ecologically relevant (social dominance).
-They found that people with more *current* exposures to violence were equally, or more, accurate when memorizing social-dominance relationships than people with fewer exposures.
-Notably, such violence exposures were associated with less accurate memory for neutral (age) relationships.
-This pattern was specific to *current* exposures: people with more *childhood* exposures to violence memorized both content types less accurately.
-There were no associations between violence exposures and reasoning performance.
-Overall, this study suggests that ecologically relevant testing materials may in some conditions 'level the playing field' for adversity-exposed youth [@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
-
-Although research testing performance in ecologically relevant contexts/situations and using ecologically relevant materials have generated innovative ideas and findings, it remains unclear whether or how these ideas and findings can be practically applied.
-For example, narrow abilities, such as memorizing social dominance hierarchies or accurately detecting anger in faces, seem to have limited practical value in educational contexts.
-In addition, although executive functions and working memory are related to many educational outcomes, it is unclear how schools and teachers might leverage skills and abilities that specifically depend on inducing uncertainty.
-That seems impractical, at best, and unethical, at worst.
-
-Here we address this issue by evaluating the role of ecologically relevant content in attention-shifting and working memory tasks.
-We define ecologically relevant content as testing material that resembles the local environment and therefore has more meaning and consequence.
-We used two criteria for stimulus selection.
-First, we selected stimuli that youth would encounter and interact with on a daily basis.
-Second, we selected stimuli believed to be more consequential or salient to adversity-exposed youth.
-For example, money is more consequential and perhaps salient to adversity-exposed youth than other neutral objects (a book, dishes, etc.).
-We target both within-subject and between-subject patterns of improvement.
-That is, improvements in performance relative to oneself (within-subjects -- one's performance on abstract compared to ecological task versions), relative to others (between-subjects -- high versus low adversity), or a combination, are theoretically and practically important.
-In the current study, we expected all youth would score higher on tasks with ecological stimuli.
-However, we expected this increase to be larger among youth living in adverse conditions compared to youth in supportive conditions.
-
-To address our research questions, we sampled `r nrow(data2_non_arbitrary)` youth from a socioeconomically diverse population.
-Using interviews, self-reports, and school records, we measured exposure to environmental unpredictability, violence, and poverty.
-We used these information sources to arrive at a "best estimate" for each construct.
-Our a priori assumption was that each information source (e.g., interview, self-report, school provided information) would correlate within constructs, which was largely true (see Table \@ref(tab:table1)).
-
-We then tested performance on two widely used tasks: attention shifting and working memory updating.
-There were two versions of each task.
-The first used standard abstract stimuli and the second replaced these stimuli with more ecological stimuli from the real-world (see Figure 1).
-We then tested the interactive effect of task content and adversity exposure.
-As such, our primary analyses involved two preregistered confirmatory analyses and one exploratory analysis.
-Our confirmatory analyses focused on environmental unpredictability and violence exposure.
-Both dimensions have been associated with improved performance under ecologically relevant conditions (contexts and testing materials) and represent specific environmental challenges.
-Our exploratory analyses focused on exposure to poverty.
-Poverty is both relevant to hidden talents (e.g., hidden talents could develop in response to specific challenges of poverty) and a general proxy for adversity rather than a specific exposure.
-
-We also evaluated the relative robustness of our models to arbitrary data processing decisions using a multiverse analysis approach [@steegen2016; @simonsohn2020].
-Specifically, we systematically and explicitly generated all possible combinations of (arbitrary) data processing decisions and analyzed them simultaneously.
-We conducted a separate multiverse analysis for each task (attention shifting and working memory updating) and each measure of adversity exposure combination.
-All multiverse analyses used the same underlying statistical models.
-
-```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap='Schematic display of the attention shifting and working memory updating tasks: a) abstract attention shifting, b) ecological attention shifting, c) abstract working memory updating, and d) ecological working memory updating.'}
-knitr::include_graphics("figure1.pdf")
-```
-
-# Method {#method}
-
-## Participants {#participants}
-
-The current study collected data from `r txt1_sam$raw$n$total` youth (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah.
-The first was a middle school and the second were 5 after-school clubs.
-The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse: `r data1_raw %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data1_raw %>% filter(race == 2) %>%nrow()` as Native American, `r data1_raw %>% filter(race == 3) %>% nrow()` as African American, `r data1_raw %>% filter(race == 4) %>% nrow()` as White, `r data1_raw %>% filter(race == 5) %>% nrow()` as Hispanic, `r data1_raw %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data1_raw %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data1_raw %>% filter(is.na(race)) %>% nrow()` were missing.
-According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers).
-The club sample (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`) and were also ethnically diverse.
-`r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch.
-
-We aggregated data from both sources and applied a set of five exclusion criteria.
-We applied these criteria before inspecting or testing any relations between predictors and outcomes.
-Specifically, we excluded participants: 1) with incomplete cognitive task data, 2) with apparent cognitive impairments (e.g., head injuries, disabilities, drug use), 3) who missed two or more trap questions, 4) exposed to extreme distractions during the assessment, and 5) who received more than 60 minutes per day of special education services.
-After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).
-In terms of racial identity, `r data2_non_arbitrary %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data2_non_arbitrary %>% filter(race == 2) %>%nrow()` as Native American, `r data2_non_arbitrary %>% filter(race == 3) %>% nrow()` as African American, `r data2_non_arbitrary %>% filter(race == 4) %>% nrow()` as White, `r data2_non_arbitrary %>% filter(race == 5) %>% nrow()` as Hispanic, `r data2_non_arbitrary %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data2_non_arbitrary %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data2_non_arbitrary %>% filter(is.na(race)) %>% nrow()` were missing.
-
-## Procedure {#procedure}
-
-Data collection involved six parts: consent/assent, demographics form, cognitive testing, structured interview, questionnaire, and debriefing.
-Consent was obtained from the primary parent or guardian before assessments and assent was obtained from the participant at the beginning of the session.
-On the demographics form, participants indicated if they were left-handed, their birthdate, and their racial and ethnic background.
-
-Cognitive testing included abstract (i.e., standard) and ecological versions of an attention-shifting and working memory updating task.
-Task order (shifting versus updating) and version (abstract versus ecological) were counterbalanced across participants.
-Some participants started with the attention shifting and then moved to the updating tasks.
-For those starting with the shifting (or updating) tasks, some started with the abstract version and then completed the ecological version (and vice versa).
-Regardless of which task was first, participants always completed both versions of one task before moving to the other task.
-
-The interview contained two parts.
-The first part was about participants' home and family life, such as their family composition, the number of adults in the household, and occupation and education information about caregivers.
-Participants also reported on the number of romantic partners their caregivers had and if these partners lived with the participant.
-The second part was about residential mobility.
-Participants listed all the homes they lived in from birth to age 13.
-For each home, they reported at which ages they lived in the home.
-If they moved, they also reported any changes in their family structure (loss or gain of adults in the home), social network (e.g., a new school), and/or town or city.
-
-The questionnaire contained measures focused on the childhood environment.
-The measures included perceived unpredictability in the home, exposure to neighborhood violence, access to material resources, direct exposure to violence and fighting, and a child version of socially desirable responding.
-
-Procedures across the middle school and after-school clubs were the same, with a few minor differences.
-First, participants in the clubs completed the tasks before the interview, but the opposite occurred in the middle school.
-The second was that, in the middle school, the questionnaire was completed in a separate session.
-Whereas the tasks and interview were completed in a small room, alone with the interviewer, the questionnaire was completed approximately two weeks later in a mass testing context (large computer room).
-This was done because the middle school was on a strict class schedule, which limited the length of individual sessions.
-In the clubs, sessions were conducted in the summer during flexible hours.
-
-## Measures {#measures}
-
-### Attention Shifting {#shifting}
-
-We measured attention shifting with two versions of the color--shape task [@mittal2015; @miyake2012; @friedman2008], which involves categorizing stimuli according to one of two rules (see below).
-On each trial, the rule is displayed on the top of the screen.
-Using arrow keys, participants categorized the stimulus as quickly and accurately as possible.
-Response options appeared at the bottom of the screen (see Figure \@ref(fig:figure1)).
-
-On the abstract (standard) attention-shifting task, participants categorized colored (blue or yellow) shapes (squares or triangles) according to the 'color' or 'shape' rule (see Figure \@ref(fig:figure1)a).
-For example, if a blue triangle appeared on the screen and the rule was 'color', participants categorized the blue triangle as blue.
-However, if the rule was 'shape', participants instead categorized the blue triangle as a triangle.
-
-The ecological attention-shifting task replaced shapes and colors with faces (see Figure \@ref(fig:figure1)b).
-Faces were either male or female (gender), and were happy or angry (emotion).
-If a happy female face appeared on screen and the rule was 'gender', for example, participants categorized the face as female.
-If the rule was 'emotion', participants instead categorized the face as happy.
-The stimuli for the ecological attention-shifting task were selected from the NimStim library [@tottenham2009].
-The same female and male models were used for happy and angry expressions.
-
-For both versions, there were two types of trials: repeat and switch.
-Repeat trials use the same rule as the previous trial.
-If the current and previous rule is 'color', for instance, the current trial is a repeat trial.
-Switch trials are trials where the rule changes from the previous trial.
-If the current rule is 'color' but the previous was 'shape' (or vice versa), the current trial is a switch trial.
-
-Accuracy on attention-shifting tasks is normally high, and was in the current sample for both versions (*M~standard~* = `r (txt2_dvs$abs_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~standard~* = `r (txt2_dvs$abs_shifting_correct$sd/32 * 100) %>% round(2)`%; *M~ecological~* = `r (txt2_dvs$eco_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~ecological~* = `r (txt2_dvs$eco_shifting_correct$sd/32 * 100) %>% round(2)`%).Thus, instead of accuracy, attention-shifting ability is measured by comparing reaction times on repeat trials to switch trials.
-Reaction times on repeat trials are normally faster than switch trials; average repeat trial reaction times on the abstract and ecological versions were `r txt2_dvs$abs_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_re_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_re_rt$sd` *ms*), respectively.
-On switch trials, average reaction times were `r txt2_dvs$abs_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sw_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sw_rt$sd` *ms*) on the standard and ecological versions.
-
-To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000].
-We removed fast and slow reaction times and removed trials after incorrect responses (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
-We then subtracted the average reaction time on valid repeat trials from the average reaction time on valid switch trials to calculate switch cost scores (*M~switch~* - *M~repeat~*).
-The switch cost measures the relative delay in reaction time caused by switching between categorization rules.
-Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sc$sd` *ms*), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`).
-Higher switch costs mean longer reaction times on switch trials compared to repeat trials.
-Higher switch costs indicate less efficient attention shifting.
-
-### Working Memory Updating {#updating}
-
-Working memory updating was measured using two versions of the continuous counters task [@unsworth2015; @unsworth2008; @young2018], in which participants track a sequence of stimuli containing three different objects (see Figure \@ref(fig:figure1)).
-Participants keep running counts of each object in sequences nine items long.
-Each object was displayed for one second at a time.
-At the end of each sequence, participants reported the number of times each object appeared.
-For each round, there were three possible correct answers, one for each object type.
-
-In the abstract (standard) version, participants kept running counts of squares, circles, and triangles (see Figure \@ref(fig:figure1)c).
-The participant must keep track of each shape, updating counts as new shapes appeared, and report them at the end of the sequence.
-The ecological version followed the same format, but participants kept running counts of three different real-world objects (see Figure \@ref(fig:figure1)d): one positive (five-dollar bill), one negative (angry face), and one neutral (Salt Lake City bus).
-
-Participants completed five rounds of both versions.
-The maximum score was 15 for each version (five rounds × three possible correct).
-On the abstract and ecological versions, participants averaged `r txt2_dvs$abs_updating$mean * 15` (*SD* = `r txt2_dvs$abs_updating$sd * 15`) and `r txt2_dvs$eco_updating$mean * 15` (*SD* = `r txt2_dvs$eco_updating$sd * 15`), respectively (*r* = `r txt5_cor$updating$r`).
-Higher scores indicate better working memory updating performance.
-
-### Environmental Unpredictability {#unp}
-
-Our measure of environmental unpredictability integrated information from the interview and questionnaire.
-The interview contained three variables of interest.
-The first measured the level of exposure to living in a biologically non-intact family from birth to age 13.
-Interviewers asked participants about their family composition and the adults that lived with them in the home.
-If a participant's family composition changed, for example, because of a divorce, interviewers recorded the ages when participants experienced the change and for how long it persisted.
-A family was considered non-intact if the participant did not live with both biological parents during any period from birth to age 13.
-Based on the earliest age of disruption, we indexed the onset of exposure to a non-intact family by creating a four-level variable from 0 to 3.
-A 0 indicated the participant lived in an intact family (lived with both biological parents) from birth until age 13 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 0) %>% sum(na.rm=T)`); a 1 indicated that a disruption occurred after the age of 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 1) %>% sum(na.rm=T)`); a 2 indicated that a disruption occurred before age 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 2) %>% sum(na.rm=T)`); and a 3 indicated the participant was born into a non-intact family (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 3) %>% sum(na.rm=T)`).
-`r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T) %>% english::as.english() %>% str_to_title()` participants had missing information.
-
-The second interview variable tabulated the number of different parental figures (defined as spouses or boyfriends/girlfriends of the participant's mother and father) who lived in the same home with the participant.
-Trained interviewers tabulated the total number of co-residing parental figures, excluding the participant's biological mother and father (*M* = `r txt3_ivs$unp_interview_figures$mean`, *SD* = `r txt3_ivs$unp_interview_figures$sd`).
-
-The third interview variable focused on residential changes from birth to age 13 (reported retrospectively).
-Specifically, interviewers probed participants about the number of different homes they lived in and, in particular, whether moving to a new home involved living with new or different adults.
-On average, participants experienced `r txt3_ivs$unp_interview_moves$mean` (*SD* = `r txt3_ivs$unp_interview_moves$sd`) moves that involved changes in residential adults.
-
-The questionnaire included a measure of perceived childhood unpredictability [@mittal2015; @young2018; @szepsenwol2015].
-Participants responded to six items that assessed exposure to unpredictability up to age 13: 1) "Things were pretty calm and stable in my house" (reversed); 2) "People moved in and out of my house a lot"; 3) "I had a hard time knowing what my parent(s) or other people in my house were going to say or do from day-to-day"; 4) "My parent(s) argued or fought a lot with each other or with other people"; 5) "My parent(s) changed jobs a lot"; 6) "My parental situation changed a lot (for example, divorce or separation of parents, parents starting new romantic relationships, parents leaving the home)".
-Participants rated each item on a scale from 1 (never true) to 5 (very often true).
-Responses to these items were averaged to create a self-reported perceived childhood unpredictability measure (*M* = `r txt3_ivs$unp_perceived$mean`, *SD* = `r txt3_ivs$unp_perceived$sd`, $\alpha$ = `r txt4_rel$unp`).
-Higher scores indicated more perceived exposure to unpredictable environments.
-
-To create a composite measure of unpredictability, we aggregated across the interview and questionnaire.
-First, we created an interview-based measure of unpredictability using family intactness or disruptions, exposure to different parental figures, and residential moves involving new adults living in the home.
-We standardized these interview measures and then averaged them together ($\alpha$ = `r txt4_rel$unp_int`).
-We then aggregated this interview measure with self-reported perceived unpredictability from the questionnaire, standardizing each before averaging (*r* = `r txt5_cor$unp$r`).
-Higher scores indicated more exposure to unpredictability.
-
-### Violence Exposure {#vio}
-
-We measured violence exposure using the Neighborhood Violence Scale [@frankenhuis2020a; @frankenhuis2018] and two items about witnessing and involvement in physical fights.
-The measure contains 7 items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm".
-The physical fighting items asked about witnessing fights: "Based on your experiences at school and in your neighborhood, how many times did you see or hear someone being beaten up in real life?"; and involvement in fights: "How many times were you in a physical fight at school or in your neighborhood?".
-Both items were rated on a scale from 1 (0 times) to 8 (12 or more times).
-
-Responses were averaged to create a composite measure of neighborhood violence (*M* = `r txt3_ivs$vio_neighborhood$mean`, *SD* = `r txt3_ivs$vio_neighborhood$sd`, $\alpha$ = `r txt4_rel$vio`).
-Likewise, the two fighting items were averaged together (*M* = `r txt3_ivs$vio_fighting$mean`, *SD* = `r txt3_ivs$vio_fighting$sd`).
-To create a violence exposure composite, the neighborhood violence composite and fighting composite were standardized and then averaged (*r* = `r txt5_cor$vio$r`).
-Higher scores indicated more exposure to violence.
-
-### Poverty Exposure {#poverty}
-
-We assessed each participant's poverty exposure using three information sources: interview-assessed parent education and occupational prestige, school or club-provided economic information, and self-reported resource scarcity.
-
-During the interview, participants reported their parents' education and primary occupation.
-For parental education level, participants reported whether their mother and father graduated high school, went to college, and if they obtained a bachelor's degree or higher.
-Responses to each question were coded as 0 = 'no' and 1 = 'yes'.
-These items were summed to create a four-level variable for each parent where 0 = did not graduate high school, 1 = graduated high school but did not attend any college, 2 = graduated high school and completed some college, and 3 = went to college and obtained a bachelor's degree or higher.
-Mother and father education were averaged to create a parental education score (*M* = `r txt3_ivs$ses_interview_edu$mean`, *SD* = `r txt3_ivs$ses_interview_edu$sd`).
-
-Participants also reported their parents' occupation.
-Participants described, in general terms, their mother's and father's jobs and the kind of work involved.
-Trained coders cross-referenced these descriptions with 2010 census job codes [@hout2018].
-We calculated mother and father occupational prestige by matching census codes with prestige ratings from an established occupational prestige rating dataset [@hout2016].
-Prestige codes ranged from 0-100, with higher scores indicating higher occupational prestige for a particular job code.
-Mother and father prestige codes were averaged to create a parent occupational prestige score (*M* = `r txt3_ivs$ses_interview_occup$mean`, *SD* = `r txt3_ivs$ses_interview_occup$sd`).
-
-We also obtained school or club-provided economic information.
-The middle school provided four information sources: 1) whether or not students were receiving free lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_frl == 1) %>% sum(na.rm=T)`); 2) whether or not they were receiving reduced-price lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_rel == 1) %>% sum(na.rm=T)`); 3) whether they were receiving fee waivers (*n* = `r (data2_non_arbitrary$ses_school_wjms_fee == 1) %>% sum(na.rm=T)`); and 4) if they were experiencing homelessness (*n* = `r (data2_non_arbitrary$ses_school_wjms_hom == 1) %>% sum(na.rm=T)`).
-These information sources were compiled to create a binary economic disadvantage variable.
-A participant was economically disadvantaged if they were receiving any benefits or experiencing homelessness (*n* = `r txt1_sam$non_arb$free_lunch$wjms`).
-In the afterschool clubs, free or reduced-price lunch status was provided by self-report, staff, and club enrollment forms and cross-referenced to determine economic disadvantage in the clubs (*n* = `r txt1_sam$non_arb$free_lunch$bgc`).
-Overall, `r (data2_non_arbitrary$ses_school_freelunch == 1) %>% sum(na.rm=T)` participants were receiving economic assistance, `r (data2_non_arbitrary$ses_school_freelunch == 0) %>% sum(na.rm=T)` were not, and `r sum(is.na(data2_non_arbitrary$ses_school_freelunch))` had missing economic information.
-
-Participants also reported their perceived level of resource scarcity.
-They rated seven items from 1 (never true) to 5 (very often true): 1) "Your family had enough money to afford the kind of home you all needed"; "Your family had enough money to afford the kind of clothing you all needed"; 3) "Your family had enough money to afford the kind of food that you all needed"; 4) "Your family had enough money to afford the kind of medical care that you all needed"; 5) "I felt well-off (rich, wealthy) compared to other kids in my school"; 6) "I felt well-off (rich, wealthy) compared to other kids in my neighborhood"; and 7) "Your family struggled to make ends meet (get by financially)".
-The first six items were reversed, and all items were averaged to create a perceived resource scarcity measure (*M* = `r txt3_ivs$ses_perceived$mean`, *SD* = `r txt3_ivs$ses_perceived$sd`, $\alpha$ = `r txt4_rel$ses`).
-Higher scores indicated more perceived resource scarcity.
-
-To create a poverty exposure composite, we combined parent education and occupational prestige (reversed), school/club reported economic disadvantage, and perceived resource scarcity.
-First, we standardized and averaged parent education and occupation (*r* = `r txt5_cor$edu_int$r`).
-Then, we recoded school-provided economic codes to be equal to half of a standard deviation above and below the mean (in terms of z-scores).
-Specifically, those receiving free or reduced-price lunch were coded as .5, and those who were not were coded as -.5.
-To create a final composite, we averaged parent education/occupation (standardized), perceived resource scarcity (standardized), and the recoded school/club economic disadvantage.
-Higher values indicated more exposure to poverty.
-
-### Control Variables {#controls}
-
-We included two control variables: age and interviewer-rated distractions during testing.
-We included these because older youth tend to score higher on cognitive tests than younger youth [@best2010; @best2011; @huizinga2006], and disruptions during the tasks could negatively impact performance.
-Interviewers completed quantitative ratings of the testing environment including 1) the level of noise; 2) the level of chaos; 3) how often there were interruptions; and 4) how often the participant appeared distracted.
-Interviewers rated each item on a scale from 1 (not at all) to 7 (much more than average).
-Items were averaged to create a composite (*M* = `r txt3_ivs$test_envr$mean`, *SD* = `r txt3_ivs$test_envr$sd`), where higher scores indicate more distractions.
-
-We also included the Child Social Desirability scale [@miller2014].
-The measure includes 14 items such as "Have you ever broken a rule?" and "Do you sometimes feel angry when you don't get your way?".
-Participants indicated 1 (yes) or 0 (no) for each item.
-More socially desirable responses were scored as 1.
-Items were then summed to create a social desirability index (*M* = `r txt3_ivs$csd$mean`, *SD* = `r txt3_ivs$csd$sd`, $\alpha$ = `r txt4_rel$csd`).
-
-# Results {#results}
-
-## Data Analysis Strategy {#multiverse}
-
-We used a multiverse analysis approach for all analyses to systematically evaluate the robustness (or sensitivity) of analyses across all arbitrary data processing decisions [see @simonsohn2020; @steegen2016 for details].
-We identified six arbitrary data processing decisions.
-First, we conducted analyses with and without the after-school club sample.
-We did this because our procedure was slightly different across the two samples and the testing environment was more disruptive in the clubs compared with the middle school.
-Second, we conducted analyses with and without participants with minor distractions during testing.
-Third, we analyzed the data with and without participants who missed one trap question (those who missed more than 1 were already excluded).
-Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded).
-Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
-
-Our last arbitrary data processing decision pertained to socially desirable responses.
-It is well-known that some youth tend to describe themselves in socially desirable ways.
-This raises concerns about the validity of self-reported childhood adversity measures: youth scoring higher on social desirability might underreport or underrate their exposures to negative experiences.
-Indeed, scores on the Child Social Desirability scale were correlated with exposures to unpredictability (*r* = `r txt5_cor$csd_unp$r`) and violence (*r* = `r txt5_cor$csd_vio$r`), though not with poverty.
-One way to handle this issue is to statistically remove overlapping variance between social desirability and each predictor, using the leftover variance (e.g., the residual variance in childhood adversity exposures not associated with social desirability) as a predictor.
-Because it is unclear how social desirability might affect the interpretation of our models, we analyzed our data with residualized and non-residualized predictors.
-
-To test our hypotheses, we performed a set of primary and secondary analyses on attention-shifting and working memory performance.
-Our primary analyses tested the effects of task version, adversity dimensions, and adversity dimension × task version interactions.
-Specifically, we tested the main effect of environmental unpredictability (confirmatory), violence exposure (confirmatory), and poverty exposure (exploratory), and the interaction between each adversity dimension with task version (abstract vs.
-ecological) on attention-shifting and working memory performance.
-We ran separate analyses for each adversity dimension and outcome combination.
-Using all possible combinations of arbitrary decisions, we constructed a multiverse of `r length(multi_data_list)` datasets.
-The minimum and maximum sample sizes were `r map_dbl(multi_data_list, "n") %>% min()` and `r map_dbl(multi_data_list, "n") %>% max()`, respectively.
-
-We ran the same underlying mixed-effects linear regression model.
-Analyses were conducted using R [@rcoreteam2020] and mixed models were fit using the lme4 package [@bates2015].
-Our mixed-effects models included five fixed terms: the main effect of task version (ecological or abstract version, within-subjects), the main effect of childhood adversity (between-subjects), the interaction between task version and adversity exposure, the main effect of age (control variable), and the main effect of test distraction ratings (control variable).
-Task version was grand mean centered (abstract versions = -1, ecological versions = 1).
-All childhood adversity measures were standardized before model fitting, and all models included a random intercept for task version nested in participants.
-
-Our models for attention shifting and working memory updating differed in one respect.
-Our sample included a small subset of siblings (*n* = `r txt6_sib$n`, `r txt6_sib$families` families).
-All sibling groups were pairs of two (`r txt6_sib$sizes$two` sibling pairs) except for `r english::as.english(txt6_sib$sizes$three)` group of three and `r english::as.english(txt6_sib$sizes$four)` group of four siblings.
-We computed intraclass correlations (ICCs) for sibling groups for attention-shifting and working memory updating scores.
-ICCs for attention shifting were essentially zero, but they were non-zero for working memory updating scores (*ICC~standard~* = `r txt6_sib$iccs$abs_update`, *ICC~ecological~* = `r txt6_sib$iccs$eco_update`).
-Thus, all models analyzing working memory updating included an additional random intercept for siblings.
-Non-siblings were given the same sibling-group code, so the model could compute an intercept for non-siblings.
-
-To facilitate interpretation of multiverse results, we report median standardized $\beta$s, median 95% confidence intervals, and percent significant for each term in our model (see Table \@ref(tab:table2)).
-Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect (two-sided *p*-value \< .05) for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions.
-For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique to compute overall *p*-values.
-The technique makes it possible to know if a multiverse analysis produced a median effect size larger than expected, given the null hypothesis that the median $\beta$ = 0 [see @simonsohn2020 for details].
-
-Table \@ref(tab:table1) displays bivariate associations between all composite measures of adversity, including components of each, and descriptive statistics.
-Our primary interests were the main effect of adversity and the interaction of adversity with task-version.
-Table \@ref(tab:table2) shows median effect sizes ($\beta$-coefficients), sample sizes, and bootstrapped *p*-values for attention-shifting and working memory updating analyses for the main effect of adversity (unpredictability, violence, and poverty) and the interaction term (task version × adversity).
-Table \@ref(tab:table3) reports median simple effects of task version across high and low levels of adversity and median simple effects of adversity across abstract and ecologically relevant task versions.
-
-```{r table1, tab.id = "table1", tab.cap.style = "Table Caption", tab.cap="Bivariate correlations and descriptive statistics for adversity measures."}
-table.01.0 %>% 
-  add_column(.after = 4,"empty1" = "") %>% 
-  add_column(.after = 8,"empty2" = "") %>% 
-  flextable() %>%
-  width("empty1", width = .2) %>% 
-  width("empty2", width = .2) %>% 
-  width(j = 1, width = .75) %>% 
-  set_header_labels(Variable = "", empty1 = "", empty2 = "") %>% 
-  add_header_row(
-    values = c(" ", "Unpredictability", " ", "Violence", " ", "Poverty"),
-    colwidths = c(1, 3, 1, 3, 1, 4)
-  ) %>% 
-  border_remove() %>% 
-  border(i = 1, j = c("1","2","3","4","5","6","7","8","9","10"), border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
-  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 16, border.bottom = fp_border_default(), part = "body") %>% 
-  align(i = 1:2, align = "center", part = "header") %>% 
-  bold(i = 1:2, part = "header") %>% 
-  set_table_properties(width = 1, layout = "autofit") %>% 
-  add_footer_row(
-    values = " ",
-    colwidths = 13
-  ) %>% 
-  add_footer_row(
-    values = " ",
-    colwidths = 13
-  ) %>% 
-  compose(
-    i = 1, j = 1, 
-    as_paragraph(as_i("Note: "), "Column headers denote adversity constructs and rows indicate components. The upper triangle contains sample sizes for each correlation."), 
-    part = "footer"
-  ) %>% 
-  compose(
-    i = 2, j = 1, 
-    as_paragraph(as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
-    part = "footer"
-  ) 
-```
-
-Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction $\beta$-coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).
-
-We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), including an [Updated Primary Analysis Plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
-We conducted secondary analyses after our primary analyses (see [Secondary Analyses](#secondary) below).
-Before conducting these analyses, we uploaded secondary analysis plans (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), explaining the goals and purpose of each secondary analysis.
-A Red Team Critic [@redteammarket2021] successfully reproduced and verified (see this [Red Team Report](https://osf.io/xv94z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)) all analyses prior to submission.
-
-## Primary Analyses {#primary}
-
-### Attention Shifting {#primary-shifting}
-
-Across each set of multiverse analyses, there were significant main effects of task version.
-All median effects sizes for task version were $\beta$s = `r c(mod_terms1$shifting.unp.type_z$median_beta, mod_terms1$shifting.vio.type_z$median_beta, mod_terms1$shifting.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for multiverse models testing unpredictability, violence exposure, and poverty exposure, indicating that switch costs (see [Attention Shifting](#shifting) for switch cost explanation) were moderately higher for the ecological version compared to the abstract version (see SI Figures 1-3).
-That is, reaction times on switch trials, compared to repeat trials, were longer when stimuli were ecologically relevant as opposed to abstract.
-However, there were no effects of age (all median $\beta$s = `r c(mod_terms1$shifting.unp.age$median_beta, mod_terms1$shifting.vio.age$median_beta, mod_terms1$shifting.ses.age$median_beta) %>% mean()`, all *ps* \>.05) or test distraction ratings (all median $\beta$ = `r c(mod_terms1$shifting.unp.test_envr$median_beta, mod_terms1$shifting.vio.test_envr$median_beta, mod_terms1$shifting.ses.test_envr$median_beta) %>% mean()`, all *ps* \> .05) on overall switch costs (see SI Figures 1-3).
-
-```{r figure2, fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure (y-axis was reversed so that higher values = faster shifting), b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
-fig2
-```
-
-Overall, there were no significant interaction effects between task version and unpredictability, violence exposure, or poverty exposure (see Table \@ref(tab:table2), Table \@ref(tab:table3), and Figure \@ref(fig:figure2)b).
-However, analyses produced main effects of unpredictability (median $\beta$ = `r mod_terms2$shifting.unp$median_beta_main`, `r mod_terms2$shifting.unp$p_percent_main %>% str_remove("\\.00")` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.unp$p_overall_main`) and violence exposure (median $\beta$ = `r mod_terms2$shifting.vio$median_beta_main`, `r mod_terms2$shifting.vio$p_percent_main` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.vio$p_overall_main`; see Table \@ref(tab:table2)).
-There were no main effects of poverty exposure (median $\beta$ = `r mod_terms2$shifting.ses$median_beta_main`, no *ps* \< .05, overall *p* = `r mod_terms2$shifting.ses$p_overall_main`; see Table \@ref(tab:table2)).
-That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures were associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecologically relevant.
 
@@
 ```
-
-### Working Memory Updating {#primary-updating}
-
-Across each set of multiverse analyses, there were again significant main effects of task version.
-All median effects sizes for task version were $\beta$s = `r c(mod_terms1$updating.unp.type_z$median_beta, mod_terms1$updating.vio.type_z$median_beta, mod_terms1$updating.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for models testing unpredictability, violence exposure, and poverty exposure, indicating that updating performance was better when stimuli were ecological relevant compared to abstract, on average (see SI Figures 4-6).
-There were also consistent main effects of age; median effects were $\beta$ = `r mod_terms1$updating.unp.age$median_beta` (all *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.age$median_beta` (all *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.age$median_beta` (all *ps* \< .05) for poverty exposure models (see SI Figures 4-6).
-That is, older youth scored higher on working memory updating, on average.
-Finally, there were some main effects of test environment distraction ratings.
-Median effects sizes were $\beta$ = `r mod_terms1$updating.unp.test_envr$median_beta` (`r (mod_terms1$updating.unp.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.test_envr$median_beta` (`r (mod_terms1$updating.vio.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.test_envr$median_beta` (`r (mod_terms1$updating.ses.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for poverty exposure models, indicating that more test distractions reduced working memory updating performance, on average (see SI Figures 4-6).
-
-Multiverse analyses revealed a main effect of poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_main`, all *ps* \< .05, bootstrapped *p* \< .001) but no main effects of unpredictability (median $\beta$ = `r mod_terms2$updating.unp$median_beta_main`, no *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.unp$p_overall_main`) or violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_main`, `r mod_terms2$updating.vio$p_percent_main` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_main`).
-Analyses also revealed two significant interactions: task version × violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_int`, `r mod_terms2$updating.vio$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_int`) and task version × poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_int`, `r mod_terms2$updating.ses$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.ses$p_overall_int`).
-Youth exposed to low levels of violence or poverty tended to perform better on the abstract working memory updating task (violence exposure median *b~abstract~* = `r simple_effects$updating.vio$beta_abs`, `r simple_effects$updating.vio$p_percent_abs` of *ps* \< .05; poverty exposure median *b~abstract~* = `r simple_effects$updating.ses$beta_abs`, all *ps* \< .05), compared to youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)).
-However, this performance gap closed on the ecological working memory task (violence exposure median *b~ecological~* = `r simple_effects$updating.vio$beta_eco`, no *ps* \< .05; poverty exposure median *b~ecological~* = `r simple_effects$updating.ses$beta_eco`, `r simple_effects$updating.ses$p_percent_eco` of *ps* \< .05).
-Put differently, youth exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically relevant version compared to their own performance on the abstract version (median simple *b~high-violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high-poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas youth exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low-violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low-poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
-In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
-
-```{r figure3, fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure, b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
-Proportions of each arbitrary decision with p-values < .05 are indicated on the right side of each specification grid.
-Blank proportions indicate proportions = 0.
-Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
-fig3
-```
-
-## Secondary Analyses {#secondary}
-
-We followed-up our primary analyses with two sets of secondary, exploratory analyses.
-We uploaded secondary analysis plans to the OSF prior to conducting them (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)).
-These analyses focused on two questions.
-First, in contrast to prior work [@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting).
-However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures.
-Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure; see [Measures](#measures) section) have unique associations with attention shifting and working memory updating performance.
-To address this, we expanded our multiverse approach to include each component of our predictor variables as additional arbitrary decisions.
-
-The second question focused on the interactive effects of task version × violence exposure and task version × poverty exposure on working memory updating performance.
-Specifically, primary analyses revealed an equalization effect for both violence and poverty exposures on working memory updating.
-However, because measures of violence and poverty were not included in the same statistical model, it is unclear whether these interactions are independent.
-For example, one possibility is that exposures to violence and poverty are independently associated with working memory updating performance.
-Alternatively, they may overlap, reflecting the same association.
-To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty in the same model.
-If violence and poverty exposures interact independently with task version, both interaction terms should remain significant.
-However, if they represent overlapping effects on working memory updating performance, one or the other may drop out of significance, which would suggest that one or the other adversity dimension is driving the effects of the other.
-
-```{r table3, tab.id = "table3", tab.cap.style = "Table Caption", tab.cap = "Median simple effects for task version and adversity."}
-table.03.0 %>% 
-  ungroup() %>%
-  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
-  arrange(dv,iv) %>% 
-  select(-dv) %>% 
-  add_column(.after = 5,"empty1" = "") %>% 
-  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
-  add_row(.after = 4, "iv" = "Working Memory Updating") %>% 
-  flextable() %>% 
-  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
-  merge_h_range(i = 5, j1 = 1, j2 = 10) %>% 
-  bold(i = c(1,5), j = 1) %>% 
-  padding(i = c(2:4, 6:8), j = 1, padding.left = 10) %>% 
-  width("empty1", width = .2) %>% 
-  set_header_labels(iv = "", empty1 = "") %>% 
-  add_header_row(
-    values = c(" ", "Task Version", " ", "Adversity Exposure"),
-    colwidths = c(1, 4, 1, 4)
-  ) %>% 
-  compose(i = 2, j = c(2), as_paragraph(as_i("b "), "(abstract)"), part = "header") %>% 
-  compose(i = 2, j = c(4), as_paragraph(as_i("b "), "(ecological)"), part = "header") %>% 
-  compose(i = 2, j = c(7), as_paragraph(as_i("b "), "(low)"), part = "header") %>% 
-  compose(i = 2, j = c(9), as_paragraph(as_i("b "), "(high)"), part = "header") %>% 
-  compose(i = 2, j = c(3,8), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
-  compose(i = 2, j = c(5,10), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
-  align(i = 1:2, align = "center", part = "header") %>% 
-  border_remove() %>% 
-  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
-  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 8, border.bottom = fp_border_default(), part = "body") %>% 
-  bold(i = 1:2, part = "header") %>% 
-  fontsize(size = 11, part = "body") %>%
-  set_table_properties(width = 1, layout = "autofit") %>% 
-  add_footer_row(
-    values = " ",
-    colwidths = 10
-  ) %>% 
-    add_footer_row(
-    values = " ",
-    colwidths = 10
-  ) %>% 
-  compose(
-    i = 1, j = 1, 
-    as_paragraph(as_i("Note: "), "Simple effects are unstandardized.
-Task Version reflects the median simple effect of adversity when the task version was abstract and ecological.
-Adversity reflects the median simple effect of task version when adversity is low (-1 SD) and high (+1 SD).
-The p (%) columns reflect the number of analyses that produced simple effect p-values < .05."),
-    part = "footer"
-  )
-```
-
-### Exploring Components of Adversity Dimensions {#secondary1}
-
-We ran an expanded multiverse analysis to explore the effects of each component of our adversity composites (see [Measures](#measures) section) on attention shifting and working memory updating performance.
-Environmental unpredictability contained two components, perceived unpredictability (self-reported) and an interview-based measure tabulating family disruptions, parental figures, and residential moves.
-Violence exposure contained two self-report components: neighborhood violence and exposure to/involvement in violence.
-Poverty exposure contained three components: parental education/occupation (interview), perceived resource scarcity (self-report), and school-coded economic disadvantage (fee waivers, free- or reduced-priced lunch, and homelessness).
-
-For this expanded multiverse approach, we retained all original data processing decisions (i.e., original 64 combinations of decisions) and added adversity component as an additional decision.
-For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures: attention shifting and working memory).
-We applied the same approach to violence exposure (three violence variables, 384 analyses) and poverty exposure (four poverty variables, 512 analyses).
-The full results of these analyses are reported in the supplement (see SI Table 2).
-
-For attention shifting, consistent with our primary analyses, there were no interactions for any component of adversity and task version (see SI Table 2 and SI Figures 7-9).
-However, there were a few main effects of adversity.
-First, primary analyses revealed, under some analytic decisions, a main effect of unpredictability.
-Upon inspection of each unpredictability component, this effect appeared to be entirely driven by self-reported perceived unpredictability.
-Specifically, no main effect *p*-values for interview-based unpredictability were \< .05, whereas `r secondary1_medians$shifting.unp.Perceived.iv$p_percent` were for perceived unpredictability (see SI Table 2, SI Table 3, and SI Figure 7).
-In addition, violence exposure revealed that our primary analyses were driven by neighborhood violence (`r secondary1_medians$shifting.vio.Neighborhood.iv$p_percent` of *ps* \< .05) and not by direct witnessing or involvement in fights (no *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 8).
-There were no main effects of poverty exposure components on attention shifting (see SI Table 2, SI Table 3, and SI Figure 9).
-
-For working memory updating, there were no interaction between any unpredictability component (perceived or interview-based) and task-version (see SI Figure 10).
-However, our expanded analysis with violence exposure revealed that interactions obtained with the composite measure were not driven by neighborhood violence but instead by witnessing or involvement in violence (`r secondary1_medians$updating.vio.Fighting.iv_type_z$p_percent %>% str_remove("\\.00")` of interaction *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 11).
-No interactions were significant with the neighborhood violence component of the violence composite.
-For poverty exposure, interview-based parental occupational prestige and school-reported economic disadvantage showed some interaction effects (parental education/occupational prestige `r secondary1_medians$updating.ses.Parents.iv_type_z$p_percent` of *ps* \<.05; school coded economic disadvantage `r secondary1_medians$updating.ses.School.iv_type_z$p_percent` of *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 12).
-Self-reported perceived resource scarcity showed no interaction effects (see SI Table 2, SI Table 3, and SI Figure 12).
-
-### Comparing Violence and Poverty Exposure Interactions with Task-Version {#secondary2}
-
-Our next secondary analysis was designed to compare the violence exposure × task-version interaction with poverty exposure × task-version interaction on working memory updating performance in the same model.
-To do so, we ran a multiverse analysis using the original set of `r length(multi_data_list)` data processing decisions.
-We entered the same controls, main effects of task-version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty exposure.
-Analyses revealed a main effect of poverty (`r secondary2_medians$ses_agg_z$p_percent` of *ps* \< .05); consistent with the primary analyses, lower poverty was associated with better updating performance under most analytic decisions.
-However, there were no main effects of violence exposure (no *ps* \< .05).
-For interactions, there were no effects of task version × poverty (no *ps* \< .05, see SI Figure 13) and only a small number of significant task version × violence exposure effects (`r secondary2_medians$type_z_vio_agg_z$p_percent` of *ps* \< .05, see SI Figure 13).
-More specifically, when both interactions were entered into the same model, only task-version × violence exposure remained significant, although only under a small set of analytic decisions.
-
-Violence and poverty exposure interaction patterns were qualitatively similar to those obtained in our primary analyses (see Figure \@ref(fig:figure3)a and SI Figure 13).
-However, these secondary results suggest that the violence exposure interaction with task-version may be driving our poverty × task version results for working memory updating.
-One possibility is that the shared variance between poverty and violence exposures (*r* = `r txt5_cor$ses_vio$r`) is responsible for both interaction effects.
-In other words, although poverty and violence exposure are theoretically distinct, our poverty composite may capture poverty-related violence exposures (e.g., high poverty neighborhoods contain more crime) and therefore interact with task-version.
-When directly compared, explicit measures of violence exposure remained significant (although only under a small set of analytical decisions), whereas poverty interactions dropped out entirely.
-
-# Discussion {#discussion}
-
-We examined how ecologically relevant testing materials affect cognitive performance among adversity-exposed youth.
-We measured three dimensions of adversity--- environmental unpredictability, violence exposure, and poverty---and tested performance on attention-shifting and working memory updating tasks.
-We administered two versions of each task: one using abstract stimuli and the other using ecological, real-world stimuli, allowing us to compare performance within- and between-subjects.
-
-Leveraging multiverse analysis [@simonsohn2020; @steegen2016], we tested interactions between dimensions of adversity and task version on attention shifting and working memory updating performance.
-We did not find interaction effects for attention shifting.
-However, youth exposed to unpredictability and violence showed lower switch costs on average, suggesting slightly improved attention shifting performance irrespective of task content.
-These findings are consistent with a recent study showing that higher caregiving instability was associated with improved attention shifting [@fields2021].
-However, our findings also partially diverge from prior work [@mittal2015; @nweze2021].
-For example, whereas we found unpredictability was associated with improved attention shifting on average, Mittal and colleagues [-@mittal2015] found no difference in performance under neutral conditions.
-And, although they found improved attention shifting for those exposed to high unpredictability under uncertainty, it remains unclear how this effect relates to those obtained in the current study.
-In addition, Nweze and colleagues [-@nweze2021] found no association between adversity and attention shifting, but they tested institutionalized children rather than measuring adversity dimensions.
-In general, we should interpret the results cautiously.
-Although we followed field standards for calculating switch costs by computing difference scores, such scores ignore participant-level reaction times.
-Mixed-modeling approaches can account for both overall reaction times and differences across switch and repeat trials, but require more statistical power to test three-way interactions.
-Future research should consider modeling approaches that capture participant-level reaction times and differences across conditions.
-
-For working memory updating, we found lowered performance among violence- and poverty-exposed youth on the abstract working memory updating task than peers with reduced exposures.
-However, ecological materials produced an equalization effect: the updating performance gap between low and high adversity-exposed youth narrowed on the ecological updating task.
-Interestingly, updating performance was unrelated to unpredictability.
-These findings are partially consistent with prior work on adversity exposure and working memory updating performance [@nweze2021; @young2018].
-For example, both Young and colleagues [-@young2018] and the current study found lowered abstract working memory performance among high adversity-exposed individuals.
-Although performance with ecological stimuli is not directly comparable to performance under manipulated uncertainty, both studies reduced the updating performance gap under ecologically relevant conditions.
-However, there are also discrepancies.
-For example, Young and colleagues [-@young2018] found effects with unpredictability and not poverty, whereas the current study found associations with violence and poverty but not unpredictability.
-Finally, Nweze and colleagues [-@nweze2021] found improved working memory performance among institutionalized youth without ecological stimuli or uncertainty manipulations.
-However, both their adversity and working memory measures were different.
-
-Overall, inconsistencies across prior work and the current attention-shifting and working memory updating findings could be attributed to differences in sampling (adults vs.
-youth), the sampled range of adversity exposure (restricted vs.
-broad), or methods/design (within- vs.
-between-subjects design; lab vs.
-community/school settings).
-Future research should both address these inconsistencies and conduct more direct replications of individual studies to converge on reliable patterns.
-
-Our first set of secondary analyses focused on the components of our adversity composites.
-For attention shifting performance, the main effect of our unpredictability composite appeared to be driven by self-reported perceived unpredictability and not by the interview-based measure which captured changes in youths' living situations.
-Likewise, the main effect of violence exposure appeared to be driven by neighborhood violence and not involvement or witnessing fights.
-For working memory updating, interaction effects involving violence exposure were driven by involvement or witnessing fights but not perceptions of neighborhood violence.
-All components of poverty exposure measures, except self-reported perceptions of resource scarcity, showed interactive effects with task version on working memory updating.
-Our second set of secondary analyses compared violence to poverty exposure in the same model.
-Findings suggest, at least when directly comparing interaction terms, violence exposure × task version predicted the working memory updating equalization effect whereas the poverty × task version interaction did not.
-
-There are many possible explanations for the diverging adversity component patterns.
-First, some information sources may be more accurate than others.
-For example, asking about the number of fights one has been involved in or witnessed might be easier to report than asking broader questions about neighborhood danger.
-Second, for different cognitive abilities, objective versus subjective reports may be more relevant.
-For example, for attention-shifting, perceptions appeared to matter whereas objective events did for working memory updating.
-Third, although adversity components were correlated in the moderate range---as typically observed in the literature [@dong2004a; @green2010; @jacobs2012; @matsumoto2021; @mclaughlin2012; @smith2021]---they may measure different constructs.
-For example, more objective indicators might capture aspects of the broader ecology but subjective, self-reported measures capture how youth have internalized and perceived their environment and family life.
-Although interesting, all secondary analyses are exploratory, and should be interpreted with caution.
-Nonetheless, these analyses highlight the need to measure multiple dimensions of adversity, compare them, and consider each measure's report format and source.
-
-Taken together, our equalization patterns of results are striking compared to the backdrop of developmental science, which almost exclusively reports lowered cognitive performance in people exposed to harsh environments.
-We also document lowered performance among adversity-exposed youth, but this effect was specific to abstract stimuli, at least for working memory updating.
-When testing materials were more concrete, adversity-exposed youth perform about as well as youth from supportive backgrounds.
-These results converge with recent work comparing stimulus types among adversity-exposed youth.
-For example, Rifkin-Graboi and colleagues [-@rifkin-graboi2021] found preschoolers exposed to caregiver adversity were more accurate on relational memory for socioemotional than non-socioemotional stimuli and Zuilkowski and colleagues [-@zuilkowski2016] found that Sub-Saharan African children from low SES backgrounds were more accurate on reasoning tests with three dimensional stimuli than two dimensional stimuli.
-
-These effects have both practical and theoretical implications.
-Practically, these effects support the idea that ecologically relevant testing materials may 'even the playing field' for adversity-exposed youth.
-That is, pending replication and extension, our data suggest leveraging ecologically relevant materials in education may hold promise for closing achievement gaps [@ellis2017; @ellis2020; @frankenhuis2020].
-In fact, programs for gifted students from low-income backgrounds already leverage concrete learning materials [@vantassel-baska2018].
-However, our data also suggest the effect of ecological content may be specific to particular abilities.
-On the one hand, our data showing within-subject improvements on working memory updating is consistent with past research using ecological versions of Raven's Progressive Matrices [@richardson1991].
-On the other, ecological content actually lowered attention shifting performance for everyone compared to abstract content, possibly because shifting was more difficult with more ecologically hot or "sticky" stimuli.
-This negative effect is consistent with other studies reporting lowered performance on some tests with ecologically relevant content [@duquennois2022; @frankenhuis2020; @muskens2019].
-
-Theoretically, our findings support the notion that hidden talents may emerge when using ecologically relevant testing materials, but they also raise questions.
-In particular, why should ecologically relevant stimuli equalize working memory updating performance for adversity-exposed youth than youth with reduced exposures?
-There are at least three possibilities.
-First, adversity exposure could simultaneously lower and improve performance.
-While abstract working memory updating performance is lowered, ecological working memory updating performance is improved.
-However, this explanation requires that different cognitive mechanisms process different classes of stimuli, even on tests of the same ability.
-If this is true, those mechanisms that process abstract content underperform compared to those that process ecological content.
-Second, there may be no actual differences in underlying abilities.
-Instead, ecologically relevant stimuli may activate intact, but dormant or underrecruited, working memory updating processes.
-Thus, when adversity-exposed youth are tested under abstract testing conditions, their cognitive processes operate at a lower level (remain inactive) but operate equally well with ecological testing materials.
-This makes sense if adversity limits energy and/or cognitive resources.
-Under such constraints, it may be adaptive to activate expensive cognitive processes only when necessary.
-Third, ecological testing materials may remove barriers, such as testing anxiety or test unfamiliarity, that disadvantage adversity-exposed youth.
-Unlike the selective activation of cognitive resources, the additional stressors of testing are removed, allowing cognitive mechanisms to operate unimpeded.
-However, this explanation is difficult to reconcile with experimental work which finds that mild stress/uncertainty improves performance [@mittal2015; @young2018].
-Future research should use research designs that can disentangle these explanations.
-
-Our study has several strengths and limitations.
-First, we leveraged a within-person design, which illuminated the effects of ecological testing materials in the same person.
-However, the correspondence between each version of our tests was modest for working memory updating (*r* = `r txt5_cor$updating$r`) and low for attention shifting (*r* = `r txt5_cor$shifting$r`).
-Although the task structure was the same, it is unclear to what extent the ecological tests measured the same construct, especially for attention shifting.
-In addition, test difficulty may have been different across test versions (e.g., switch costs were larger on the ecological version).
-Future research should consider teasing apart test difficulty from ecological relevance.
-Second, our strategy for creating ecological test versions was to select stimuli believed to be more salient or impactful to adversity-exposed youth.
-However, we did not independently assess the ecological validity of our real-world stimuli.
-Thus, it is unclear whether our tests were specifically matched to the actual experiences of adversity-exposed youth or more ecologically relevant for these youth than for those from supportive conditions.
-Third, we leveraged multiverse analysis to examine the robustness of our findings to arbitrary data processing decisions.
-Though powerful, the technique is relatively new and should be interpreted with caution.
-For instance, as with other statistical techniques, researchers might disagree over which data processing decisions are arbitrary [@delgiudice2021].
-Fourth, although we found some effects of ecological testing materials, we measured abilities that have shown some evidence of adversity-related enhancement.
-To explore generalizability of ecological content across abilities, future research may create ecological versions of tests known to disadvantage adversity-exposed youth, such as inhibition or working memory retrieval [@mittal2015; @young2018], and compare performance to abstract versions.
-Finally, although we used interviews and self-report methods, all of our childhood adversity measures were cross-sectional and some were retrospective.
-These measurement limitations may be partially offset because our sample was still living in their developmental environment.
-However, this does not replace the need for prospective, longitudinal measures and cannot eliminate all biases associated with retrospective reporting [@reuben2016].
-Thus, it remains unclear to what extent the current environment, rather than the developmental environment, is driving our findings.
-
-Until recently, developmental science has almost exclusively reported lowered cognitive performance in people from harsh conditions.
-The hidden talents framework has challenged this notion and inspired researchers to document the strengths and abilities of people from adversity.
-Theoretically, our data help to refine the hidden talents framework and illuminate future research questions surrounding the unique skills and abilities of people living in harsh conditions.
-Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might 'even the playing field' for adversity-exposed youth.
-
-\pagebreak
-
-# References {#refs}

### 2022-03-16 manuscript/tables/table-3.Rmd
make separate .docx files for tables

--- 2022-01-28 manuscript/manuscript.Rmd
@@
 ```
-
-# Abstract
-
-\noindent Adversity-exposed youth tend to score lower on cognitive tests.
-However, the hidden talents approach proposes some abilities are enhanced by adversity, especially under ecologically relevant conditions.
-Sampling `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White), we administered two versions of an attention shifting and working memory updating task---one abstract, one ecological.
-We measured environmental unpredictability, violence, and poverty, and tested adversity × task version interactions.
-There were no interactions for attention shifting.
-For working memory updating, youth exposed to violence and poverty scored lower than their peers with abstract stimuli but just as well with ecological stimuli.
-These results are striking compared to contemporary developmental science, which almost exclusively reports lowered performance among adversity-exposed youth.
-
-*Keywords*: hidden talents, working memory updating, attention shifting, adversity, adaptations to stress
-
-\pagebreak
-
-# Hidden talents in context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth
-
-Youth living in adverse conditions tend to score lower on cognitive tests than youth in supportive conditions.
-For example, youth raised in poverty are more likely to have difficulties learning in school and score lower on standardized tests [@farah2006; @hackman2010; @noble2007; @ursache2016a].
-Harsh and unpredictable environments are thought to cause high levels of chronic stress, which can impair brain regions responsible for memory and learning [@blair2012].
-Thus, the contemporary view is that exposure to adversity undermines cognitive development and leads to a host of cognitive deficits [reviewed in @duncan2017; @hackman2010; @mclaughlin2019; @pechtel2011].
-Although it is clear that harsh and unpredictable environments are harmful to youth, there is growing interest in the *hidden talents approach*, which proposes that some abilities may be enhanced by adversity, especially skills and abilities that help youth meet real-world challenges in adverse environments [@ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013].
-These stress-adapted skills are referred to in this literature as *hidden talents*.
-
-The hidden talents approach is rooted in an adaptation-based framework [see @ellis2017; @ellis2020; @frankenhuis2020; @frankenhuis2013 for reviews], which assumes development tailors skills and abilities in relation to the environment.
-Accordingly, exposure to adversity should shape skills and abilities well-suited for dealing with the challenges and opportunities associated with harsh and unpredictable environments.
-However, because specific dimensions of adversity (e.g., violence versus resource-scarcity) may pose unique challenges [@ellis2020; @frankenhuis2020; @mclaughlin2019; @sheridan2014], the hidden talents approach proposes that cognitive skills should match specific dimensions of adversity [@frankenhuis2020].
-For instance, some evidence suggests that physically abused youth can detect angry facial expressions quickly and accurately [@gibb2009; @pollak2008; @pollak2009], people living in poverty have more accurate social perception [@bjornsdottir2017; @dietze2021; @piff2018], and that anxiously attached people can more accurately detect deception [@eindor2014; @shoda2013].
-
-Although some abilities themselves are more ecologically relevant to specific dimensions of adversity, hidden talents may also emerge under ecologically relevant conditions.
-For example, previous studies of hidden talents have tested cognition under ecologically relevant *contexts and situations*.
-In particular, studies have experimentally manipulated the current context to be uncertain and mildly stressful (or not) and measured performance on executive functioning and working memory tasks [@mittal2015; @young2018].
-Strikingly, people from unpredictable environments showed more efficient switching on attention shifting tasks and more accurate responses on working memory updating tasks, but this effect only emerged under conditions of uncertainty.
-There was no performance increase under control conditions.
-However, some studies have found similar patterns without uncertainty [@fields2021; @nweze2021].
-
-Hidden talents may also emerge when testing *content and stimuli* are more ecologically relevant and concrete.
-Typical cognitive tests use abstract content that is largely detached from the real world.
-Such abstract materials may disadvantage youth whose childhood experiences involve less abstract, analytical problem solving [@ellis2020; @frankenhuis2013].
-Cultural psychologists and anthropologists have demonstrated this fact across the world.
-For example, people from non-Western cultures tend to score lower than people in Western cultures on standard versions of cognitive tests, but this performance gap closes or disappears when more ecologically relevant measures are used [@banerjee2017; @grigorenko2004; @rogoff2017; @sternberg2001].
-This work challenges the assumption that "baseline" performance is best captured by standard/abstract tests.
-In fact, they suggest that abstract stimuli, and more broadly standard testing conditions, are specific contexts that may not match one's lived experience [@doebel2020; @zuilkowski2016].
-These ideas also raise an important question: do adversity-exposed youth score higher on tests with ecologically-relevant stimuli relative to those with abstract stimuli?
-
-One way to test this question is to replace sterile testing materials with ecologically relevant content from the real world.
-For example, one study tested memory and reasoning among young adults who varied in their exposures to violence [@frankenhuis2020a].
-They created two versions of a memory and reasoning task, one neutral (chronological age) and one more ecologically relevant (social dominance).
-They found that people with more *current* exposures to violence were equally, or more, accurate when memorizing social-dominance relationships than people with fewer exposures.
-Notably, such violence exposures were associated with less accurate memory for neutral (age) relationships.
-This pattern was specific to *current* exposures: people with more *childhood* exposures to violence memorized both content types less accurately.
-There were no associations between violence exposures and reasoning performance.
-Overall, this study suggests that ecologically relevant testing materials may in some conditions 'level the playing field' for adversity-exposed youth [@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
-
-Although research testing performance in ecologically relevant contexts/situations and using ecologically relevant materials have generated innovative ideas and findings, it remains unclear whether or how these ideas and findings can be practically applied.
-For example, narrow abilities, such as memorizing social dominance hierarchies or accurately detecting anger in faces, seem to have limited practical value in educational contexts.
-In addition, although executive functions and working memory are related to many educational outcomes, it is unclear how schools and teachers might leverage skills and abilities that specifically depend on inducing uncertainty.
-That seems impractical, at best, and unethical, at worst.
-
-Here we address this issue by evaluating the role of ecologically relevant content in attention-shifting and working memory tasks.
-We define ecologically relevant content as testing material that resembles the local environment and therefore has more meaning and consequence.
-We used two criteria for stimulus selection.
-First, we selected stimuli that youth would encounter and interact with on a daily basis.
-Second, we selected stimuli believed to be more consequential or salient to adversity-exposed youth.
-For example, money is more consequential and perhaps salient to adversity-exposed youth than other neutral objects (a book, dishes, etc.).
-We target both within-subject and between-subject patterns of improvement.
-That is, improvements in performance relative to oneself (within-subjects -- one's performance on abstract compared to ecological task versions), relative to others (between-subjects -- high versus low adversity), or a combination, are theoretically and practically important.
-In the current study, we expected all youth would score higher on tasks with ecological stimuli.
-However, we expected this increase to be larger among youth living in adverse conditions compared to youth in supportive conditions.
-
-To address our research questions, we sampled `r nrow(data2_non_arbitrary)` youth from a socioeconomically diverse population.
-Using interviews, self-reports, and school records, we measured exposure to environmental unpredictability, violence, and poverty.
-We used these information sources to arrive at a "best estimate" for each construct.
-Our a priori assumption was that each information source (e.g., interview, self-report, school provided information) would correlate within constructs, which was largely true (see Table \@ref(tab:table1)).
-
-We then tested performance on two widely used tasks: attention shifting and working memory updating.
-There were two versions of each task.
-The first used standard abstract stimuli and the second replaced these stimuli with more ecological stimuli from the real-world (see Figure 1).
-We then tested the interactive effect of task content and adversity exposure.
-As such, our primary analyses involved two preregistered confirmatory analyses and one exploratory analysis.
-Our confirmatory analyses focused on environmental unpredictability and violence exposure.
-Both dimensions have been associated with improved performance under ecologically relevant conditions (contexts and testing materials) and represent specific environmental challenges.
-Our exploratory analyses focused on exposure to poverty.
-Poverty is both relevant to hidden talents (e.g., hidden talents could develop in response to specific challenges of poverty) and a general proxy for adversity rather than a specific exposure.
-
-We also evaluated the relative robustness of our models to arbitrary data processing decisions using a multiverse analysis approach [@steegen2016; @simonsohn2020].
-Specifically, we systematically and explicitly generated all possible combinations of (arbitrary) data processing decisions and analyzed them simultaneously.
-We conducted a separate multiverse analysis for each task (attention shifting and working memory updating) and each measure of adversity exposure combination.
-All multiverse analyses used the same underlying statistical models.
-
-```{r figure1, fig.width=6, dpi=600, fig.id = "figure1", fig.cap.style = "Image Caption", fig.cap='Schematic display of the attention shifting and working memory updating tasks: a) abstract attention shifting, b) ecological attention shifting, c) abstract working memory updating, and d) ecological working memory updating.'}
-knitr::include_graphics("figure1.pdf")
-```
-
-# Method {#method}
-
-## Participants {#participants}
-
-The current study collected data from `r txt1_sam$raw$n$total` youth (*M~age~* = `r txt1_sam$raw$age$mean`, *SD~age~* = `r txt1_sam$raw$age$sd`) from two sources across Salt Lake City, Utah.
-The first was a middle school and the second were 5 after-school clubs.
-The middle school sample (seventh and eighth graders, *N* = `r txt1_sam$raw$n$wjms`; `r txt1_sam$raw$sex$wjms$females` females) formed `r (txt1_sam$raw$n$wjms/txt1_sam$raw$n$total * 100) %>% round(2)`% of the total sample and is socioeconomically and ethnically diverse: `r data1_raw %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data1_raw %>% filter(race == 2) %>%nrow()` as Native American, `r data1_raw %>% filter(race == 3) %>% nrow()` as African American, `r data1_raw %>% filter(race == 4) %>% nrow()` as White, `r data1_raw %>% filter(race == 5) %>% nrow()` as Hispanic, `r data1_raw %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data1_raw %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data1_raw %>% filter(is.na(race)) %>% nrow()` were missing.
-According to school district records, `r (txt1_sam$raw$free_lunch$wjms/txt1_sam$raw$n$wjms * 100) %>% round(2)`% of students were receiving economic assistance based on family income and/or homelessness (i.e., free or reduced-price lunch or fee waivers).
-The club sample (*N* = `r txt1_sam$raw$n$bgc`; `r txt1_sam$raw$sex$bgc$female` females) contained a wider age range (*M~age~*= `r txt1_sam$raw$age$bgc$mean`, *SD~age~* = `r txt1_sam$raw$age$bgc$sd`) and were also ethnically diverse.
-`r (txt1_sam$raw$free_lunch$bgc/txt1_sam$raw$n$bgc * 100) %>% round(2)`% were receiving free or reduced-price lunch.
-
-We aggregated data from both sources and applied a set of five exclusion criteria.
-We applied these criteria before inspecting or testing any relations between predictors and outcomes.
-Specifically, we excluded participants: 1) with incomplete cognitive task data, 2) with apparent cognitive impairments (e.g., head injuries, disabilities, drug use), 3) who missed two or more trap questions, 4) exposed to extreme distractions during the assessment, and 5) who received more than 60 minutes per day of special education services.
-After exclusions, the final sample contained `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r txt1_sam$non_arb$sex$females` females; `r (txt1_sam$non_arb$n$wjms/txt1_sam$non_arb$n$total * 100) %>% round(2)`% from the middle school).
-In terms of racial identity, `r data2_non_arbitrary %>% filter(race == 1) %>% nrow()` youth identified as Asian, `r data2_non_arbitrary %>% filter(race == 2) %>%nrow()` as Native American, `r data2_non_arbitrary %>% filter(race == 3) %>% nrow()` as African American, `r data2_non_arbitrary %>% filter(race == 4) %>% nrow()` as White, `r data2_non_arbitrary %>% filter(race == 5) %>% nrow()` as Hispanic, `r data2_non_arbitrary %>% filter(race == 6)  %>% nrow()` as Pacific Islander, `r data2_non_arbitrary %>% filter(race == 7) %>% nrow()` with multiple racial identities, and `r data2_non_arbitrary %>% filter(is.na(race)) %>% nrow()` were missing.
-
-## Procedure {#procedure}
-
-Data collection involved six parts: consent/assent, demographics form, cognitive testing, structured interview, questionnaire, and debriefing.
-Consent was obtained from the primary parent or guardian before assessments and assent was obtained from the participant at the beginning of the session.
-On the demographics form, participants indicated if they were left-handed, their birthdate, and their racial and ethnic background.
-
-Cognitive testing included abstract (i.e., standard) and ecological versions of an attention-shifting and working memory updating task.
-Task order (shifting versus updating) and version (abstract versus ecological) were counterbalanced across participants.
-Some participants started with the attention shifting and then moved to the updating tasks.
-For those starting with the shifting (or updating) tasks, some started with the abstract version and then completed the ecological version (and vice versa).
-Regardless of which task was first, participants always completed both versions of one task before moving to the other task.
-
-The interview contained two parts.
-The first part was about participants' home and family life, such as their family composition, the number of adults in the household, and occupation and education information about caregivers.
-Participants also reported on the number of romantic partners their caregivers had and if these partners lived with the participant.
-The second part was about residential mobility.
-Participants listed all the homes they lived in from birth to age 13.
-For each home, they reported at which ages they lived in the home.
-If they moved, they also reported any changes in their family structure (loss or gain of adults in the home), social network (e.g., a new school), and/or town or city.
-
-The questionnaire contained measures focused on the childhood environment.
-The measures included perceived unpredictability in the home, exposure to neighborhood violence, access to material resources, direct exposure to violence and fighting, and a child version of socially desirable responding.
-
-Procedures across the middle school and after-school clubs were the same, with a few minor differences.
-First, participants in the clubs completed the tasks before the interview, but the opposite occurred in the middle school.
-The second was that, in the middle school, the questionnaire was completed in a separate session.
-Whereas the tasks and interview were completed in a small room, alone with the interviewer, the questionnaire was completed approximately two weeks later in a mass testing context (large computer room).
-This was done because the middle school was on a strict class schedule, which limited the length of individual sessions.
-In the clubs, sessions were conducted in the summer during flexible hours.
-
-## Measures {#measures}
-
-### Attention Shifting {#shifting}
-
-We measured attention shifting with two versions of the color--shape task [@mittal2015; @miyake2012; @friedman2008], which involves categorizing stimuli according to one of two rules (see below).
-On each trial, the rule is displayed on the top of the screen.
-Using arrow keys, participants categorized the stimulus as quickly and accurately as possible.
-Response options appeared at the bottom of the screen (see Figure \@ref(fig:figure1)).
-
-On the abstract (standard) attention-shifting task, participants categorized colored (blue or yellow) shapes (squares or triangles) according to the 'color' or 'shape' rule (see Figure \@ref(fig:figure1)a).
-For example, if a blue triangle appeared on the screen and the rule was 'color', participants categorized the blue triangle as blue.
-However, if the rule was 'shape', participants instead categorized the blue triangle as a triangle.
-
-The ecological attention-shifting task replaced shapes and colors with faces (see Figure \@ref(fig:figure1)b).
-Faces were either male or female (gender), and were happy or angry (emotion).
-If a happy female face appeared on screen and the rule was 'gender', for example, participants categorized the face as female.
-If the rule was 'emotion', participants instead categorized the face as happy.
-The stimuli for the ecological attention-shifting task were selected from the NimStim library [@tottenham2009].
-The same female and male models were used for happy and angry expressions.
-
-For both versions, there were two types of trials: repeat and switch.
-Repeat trials use the same rule as the previous trial.
-If the current and previous rule is 'color', for instance, the current trial is a repeat trial.
-Switch trials are trials where the rule changes from the previous trial.
-If the current rule is 'color' but the previous was 'shape' (or vice versa), the current trial is a switch trial.
-
-Accuracy on attention-shifting tasks is normally high, and was in the current sample for both versions (*M~standard~* = `r (txt2_dvs$abs_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~standard~* = `r (txt2_dvs$abs_shifting_correct$sd/32 * 100) %>% round(2)`%; *M~ecological~* = `r (txt2_dvs$eco_shifting_correct$mean/32 * 100) %>% round(2)`%, *SD~ecological~* = `r (txt2_dvs$eco_shifting_correct$sd/32 * 100) %>% round(2)`%).Thus, instead of accuracy, attention-shifting ability is measured by comparing reaction times on repeat trials to switch trials.
-Reaction times on repeat trials are normally faster than switch trials; average repeat trial reaction times on the abstract and ecological versions were `r txt2_dvs$abs_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_re_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_re_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_re_rt$sd` *ms*), respectively.
-On switch trials, average reaction times were `r txt2_dvs$abs_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sw_rt$sd` *ms*) and `r txt2_dvs$eco_shifting_sw_rt$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sw_rt$sd` *ms*) on the standard and ecological versions.
-
-To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000].
-We removed fast and slow reaction times and removed trials after incorrect responses (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details).
-We then subtracted the average reaction time on valid repeat trials from the average reaction time on valid switch trials to calculate switch cost scores (*M~switch~* - *M~repeat~*).
-The switch cost measures the relative delay in reaction time caused by switching between categorization rules.
-Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$eco_shifting_sc$sd` *ms*), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`).
-Higher switch costs mean longer reaction times on switch trials compared to repeat trials.
-Higher switch costs indicate less efficient attention shifting.
-
-### Working Memory Updating {#updating}
-
-Working memory updating was measured using two versions of the continuous counters task [@unsworth2015; @unsworth2008; @young2018], in which participants track a sequence of stimuli containing three different objects (see Figure \@ref(fig:figure1)).
-Participants keep running counts of each object in sequences nine items long.
-Each object was displayed for one second at a time.
-At the end of each sequence, participants reported the number of times each object appeared.
-For each round, there were three possible correct answers, one for each object type.
-
-In the abstract (standard) version, participants kept running counts of squares, circles, and triangles (see Figure \@ref(fig:figure1)c).
-The participant must keep track of each shape, updating counts as new shapes appeared, and report them at the end of the sequence.
-The ecological version followed the same format, but participants kept running counts of three different real-world objects (see Figure \@ref(fig:figure1)d): one positive (five-dollar bill), one negative (angry face), and one neutral (Salt Lake City bus).
-
-Participants completed five rounds of both versions.
-The maximum score was 15 for each version (five rounds × three possible correct).
-On the abstract and ecological versions, participants averaged `r txt2_dvs$abs_updating$mean * 15` (*SD* = `r txt2_dvs$abs_updating$sd * 15`) and `r txt2_dvs$eco_updating$mean * 15` (*SD* = `r txt2_dvs$eco_updating$sd * 15`), respectively (*r* = `r txt5_cor$updating$r`).
-Higher scores indicate better working memory updating performance.
-
-### Environmental Unpredictability {#unp}
-
-Our measure of environmental unpredictability integrated information from the interview and questionnaire.
-The interview contained three variables of interest.
-The first measured the level of exposure to living in a biologically non-intact family from birth to age 13.
-Interviewers asked participants about their family composition and the adults that lived with them in the home.
-If a participant's family composition changed, for example, because of a divorce, interviewers recorded the ages when participants experienced the change and for how long it persisted.
-A family was considered non-intact if the participant did not live with both biological parents during any period from birth to age 13.
-Based on the earliest age of disruption, we indexed the onset of exposure to a non-intact family by creating a four-level variable from 0 to 3.
-A 0 indicated the participant lived in an intact family (lived with both biological parents) from birth until age 13 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 0) %>% sum(na.rm=T)`); a 1 indicated that a disruption occurred after the age of 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 1) %>% sum(na.rm=T)`); a 2 indicated that a disruption occurred before age 5 (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 2) %>% sum(na.rm=T)`); and a 3 indicated the participant was born into a non-intact family (*n* = `r (data2_non_arbitrary$unp_interview_disrupted == 3) %>% sum(na.rm=T)`).
-`r is.na(data2_non_arbitrary$unp_interview_disrupted) %>% sum(na.rm=T) %>% english::as.english() %>% str_to_title()` participants had missing information.
-
-The second interview variable tabulated the number of different parental figures (defined as spouses or boyfriends/girlfriends of the participant's mother and father) who lived in the same home with the participant.
-Trained interviewers tabulated the total number of co-residing parental figures, excluding the participant's biological mother and father (*M* = `r txt3_ivs$unp_interview_figures$mean`, *SD* = `r txt3_ivs$unp_interview_figures$sd`).
-
-The third interview variable focused on residential changes from birth to age 13 (reported retrospectively).
-Specifically, interviewers probed participants about the number of different homes they lived in and, in particular, whether moving to a new home involved living with new or different adults.
-On average, participants experienced `r txt3_ivs$unp_interview_moves$mean` (*SD* = `r txt3_ivs$unp_interview_moves$sd`) moves that involved changes in residential adults.
-
-The questionnaire included a measure of perceived childhood unpredictability [@mittal2015; @young2018; @szepsenwol2015].
-Participants responded to six items that assessed exposure to unpredictability up to age 13: 1) "Things were pretty calm and stable in my house" (reversed); 2) "People moved in and out of my house a lot"; 3) "I had a hard time knowing what my parent(s) or other people in my house were going to say or do from day-to-day"; 4) "My parent(s) argued or fought a lot with each other or with other people"; 5) "My parent(s) changed jobs a lot"; 6) "My parental situation changed a lot (for example, divorce or separation of parents, parents starting new romantic relationships, parents leaving the home)".
-Participants rated each item on a scale from 1 (never true) to 5 (very often true).
-Responses to these items were averaged to create a self-reported perceived childhood unpredictability measure (*M* = `r txt3_ivs$unp_perceived$mean`, *SD* = `r txt3_ivs$unp_perceived$sd`, $\alpha$ = `r txt4_rel$unp`).
-Higher scores indicated more perceived exposure to unpredictable environments.
-
-To create a composite measure of unpredictability, we aggregated across the interview and questionnaire.
-First, we created an interview-based measure of unpredictability using family intactness or disruptions, exposure to different parental figures, and residential moves involving new adults living in the home.
-We standardized these interview measures and then averaged them together ($\alpha$ = `r txt4_rel$unp_int`).
-We then aggregated this interview measure with self-reported perceived unpredictability from the questionnaire, standardizing each before averaging (*r* = `r txt5_cor$unp$r`).
-Higher scores indicated more exposure to unpredictability.
-
-### Violence Exposure {#vio}
-
-We measured violence exposure using the Neighborhood Violence Scale [@frankenhuis2020a; @frankenhuis2018] and two items about witnessing and involvement in physical fights.
-The measure contains 7 items rated on a scale from 1 (never true) to 5 (very often true): 1) "I grew up in a safe neighborhood"; 2) "Crime was common in the neighborhood where I grew up"; 3) "In the neighborhood where I grew up, people had plenty of money" (reversed); 4) "In the neighborhood where I grew up, physical fights were common"; 5) "In the neighborhood where I grew up, shootings or stabbings occurred"; 6) "In the neighborhood where I grew up, most people felt unsafe walking alone after dark"; 7) "Where I grew up, it was important to be able to defend yourself against physical harm".
-The physical fighting items asked about witnessing fights: "Based on your experiences at school and in your neighborhood, how many times did you see or hear someone being beaten up in real life?"; and involvement in fights: "How many times were you in a physical fight at school or in your neighborhood?".
-Both items were rated on a scale from 1 (0 times) to 8 (12 or more times).
-
-Responses were averaged to create a composite measure of neighborhood violence (*M* = `r txt3_ivs$vio_neighborhood$mean`, *SD* = `r txt3_ivs$vio_neighborhood$sd`, $\alpha$ = `r txt4_rel$vio`).
-Likewise, the two fighting items were averaged together (*M* = `r txt3_ivs$vio_fighting$mean`, *SD* = `r txt3_ivs$vio_fighting$sd`).
-To create a violence exposure composite, the neighborhood violence composite and fighting composite were standardized and then averaged (*r* = `r txt5_cor$vio$r`).
-Higher scores indicated more exposure to violence.
-
-### Poverty Exposure {#poverty}
-
-We assessed each participant's poverty exposure using three information sources: interview-assessed parent education and occupational prestige, school or club-provided economic information, and self-reported resource scarcity.
-
-During the interview, participants reported their parents' education and primary occupation.
-For parental education level, participants reported whether their mother and father graduated high school, went to college, and if they obtained a bachelor's degree or higher.
-Responses to each question were coded as 0 = 'no' and 1 = 'yes'.
-These items were summed to create a four-level variable for each parent where 0 = did not graduate high school, 1 = graduated high school but did not attend any college, 2 = graduated high school and completed some college, and 3 = went to college and obtained a bachelor's degree or higher.
-Mother and father education were averaged to create a parental education score (*M* = `r txt3_ivs$ses_interview_edu$mean`, *SD* = `r txt3_ivs$ses_interview_edu$sd`).
-
-Participants also reported their parents' occupation.
-Participants described, in general terms, their mother's and father's jobs and the kind of work involved.
-Trained coders cross-referenced these descriptions with 2010 census job codes [@hout2018].
-We calculated mother and father occupational prestige by matching census codes with prestige ratings from an established occupational prestige rating dataset [@hout2016].
-Prestige codes ranged from 0-100, with higher scores indicating higher occupational prestige for a particular job code.
-Mother and father prestige codes were averaged to create a parent occupational prestige score (*M* = `r txt3_ivs$ses_interview_occup$mean`, *SD* = `r txt3_ivs$ses_interview_occup$sd`).
-
-We also obtained school or club-provided economic information.
-The middle school provided four information sources: 1) whether or not students were receiving free lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_frl == 1) %>% sum(na.rm=T)`); 2) whether or not they were receiving reduced-price lunch (*n* = `r (data2_non_arbitrary$ses_school_wjms_rel == 1) %>% sum(na.rm=T)`); 3) whether they were receiving fee waivers (*n* = `r (data2_non_arbitrary$ses_school_wjms_fee == 1) %>% sum(na.rm=T)`); and 4) if they were experiencing homelessness (*n* = `r (data2_non_arbitrary$ses_school_wjms_hom == 1) %>% sum(na.rm=T)`).
-These information sources were compiled to create a binary economic disadvantage variable.
-A participant was economically disadvantaged if they were receiving any benefits or experiencing homelessness (*n* = `r txt1_sam$non_arb$free_lunch$wjms`).
-In the afterschool clubs, free or reduced-price lunch status was provided by self-report, staff, and club enrollment forms and cross-referenced to determine economic disadvantage in the clubs (*n* = `r txt1_sam$non_arb$free_lunch$bgc`).
-Overall, `r (data2_non_arbitrary$ses_school_freelunch == 1) %>% sum(na.rm=T)` participants were receiving economic assistance, `r (data2_non_arbitrary$ses_school_freelunch == 0) %>% sum(na.rm=T)` were not, and `r sum(is.na(data2_non_arbitrary$ses_school_freelunch))` had missing economic information.
-
-Participants also reported their perceived level of resource scarcity.
-They rated seven items from 1 (never true) to 5 (very often true): 1) "Your family had enough money to afford the kind of home you all needed"; "Your family had enough money to afford the kind of clothing you all needed"; 3) "Your family had enough money to afford the kind of food that you all needed"; 4) "Your family had enough money to afford the kind of medical care that you all needed"; 5) "I felt well-off (rich, wealthy) compared to other kids in my school"; 6) "I felt well-off (rich, wealthy) compared to other kids in my neighborhood"; and 7) "Your family struggled to make ends meet (get by financially)".
-The first six items were reversed, and all items were averaged to create a perceived resource scarcity measure (*M* = `r txt3_ivs$ses_perceived$mean`, *SD* = `r txt3_ivs$ses_perceived$sd`, $\alpha$ = `r txt4_rel$ses`).
-Higher scores indicated more perceived resource scarcity.
-
-To create a poverty exposure composite, we combined parent education and occupational prestige (reversed), school/club reported economic disadvantage, and perceived resource scarcity.
-First, we standardized and averaged parent education and occupation (*r* = `r txt5_cor$edu_int$r`).
-Then, we recoded school-provided economic codes to be equal to half of a standard deviation above and below the mean (in terms of z-scores).
-Specifically, those receiving free or reduced-price lunch were coded as .5, and those who were not were coded as -.5.
-To create a final composite, we averaged parent education/occupation (standardized), perceived resource scarcity (standardized), and the recoded school/club economic disadvantage.
-Higher values indicated more exposure to poverty.
-
-### Control Variables {#controls}
-
-We included two control variables: age and interviewer-rated distractions during testing.
-We included these because older youth tend to score higher on cognitive tests than younger youth [@best2010; @best2011; @huizinga2006], and disruptions during the tasks could negatively impact performance.
-Interviewers completed quantitative ratings of the testing environment including 1) the level of noise; 2) the level of chaos; 3) how often there were interruptions; and 4) how often the participant appeared distracted.
-Interviewers rated each item on a scale from 1 (not at all) to 7 (much more than average).
-Items were averaged to create a composite (*M* = `r txt3_ivs$test_envr$mean`, *SD* = `r txt3_ivs$test_envr$sd`), where higher scores indicate more distractions.
-
-We also included the Child Social Desirability scale [@miller2014].
-The measure includes 14 items such as "Have you ever broken a rule?" and "Do you sometimes feel angry when you don't get your way?".
-Participants indicated 1 (yes) or 0 (no) for each item.
-More socially desirable responses were scored as 1.
-Items were then summed to create a social desirability index (*M* = `r txt3_ivs$csd$mean`, *SD* = `r txt3_ivs$csd$sd`, $\alpha$ = `r txt4_rel$csd`).
-
-# Results {#results}
-
-## Data Analysis Strategy {#multiverse}
-
-We used a multiverse analysis approach for all analyses to systematically evaluate the robustness (or sensitivity) of analyses across all arbitrary data processing decisions [see @simonsohn2020; @steegen2016 for details].
-We identified six arbitrary data processing decisions.
-First, we conducted analyses with and without the after-school club sample.
-We did this because our procedure was slightly different across the two samples and the testing environment was more disruptive in the clubs compared with the middle school.
-Second, we conducted analyses with and without participants with minor distractions during testing.
-Third, we analyzed the data with and without participants who missed one trap question (those who missed more than 1 were already excluded).
-Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded).
-Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [Attention Shifting Data Cleaning Procedure](https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
-
-Our last arbitrary data processing decision pertained to socially desirable responses.
-It is well-known that some youth tend to describe themselves in socially desirable ways.
-This raises concerns about the validity of self-reported childhood adversity measures: youth scoring higher on social desirability might underreport or underrate their exposures to negative experiences.
-Indeed, scores on the Child Social Desirability scale were correlated with exposures to unpredictability (*r* = `r txt5_cor$csd_unp$r`) and violence (*r* = `r txt5_cor$csd_vio$r`), though not with poverty.
-One way to handle this issue is to statistically remove overlapping variance between social desirability and each predictor, using the leftover variance (e.g., the residual variance in childhood adversity exposures not associated with social desirability) as a predictor.
-Because it is unclear how social desirability might affect the interpretation of our models, we analyzed our data with residualized and non-residualized predictors.
-
-To test our hypotheses, we performed a set of primary and secondary analyses on attention-shifting and working memory performance.
-Our primary analyses tested the effects of task version, adversity dimensions, and adversity dimension × task version interactions.
-Specifically, we tested the main effect of environmental unpredictability (confirmatory), violence exposure (confirmatory), and poverty exposure (exploratory), and the interaction between each adversity dimension with task version (abstract vs.
-ecological) on attention-shifting and working memory performance.
-We ran separate analyses for each adversity dimension and outcome combination.
-Using all possible combinations of arbitrary decisions, we constructed a multiverse of `r length(multi_data_list)` datasets.
-The minimum and maximum sample sizes were `r map_dbl(multi_data_list, "n") %>% min()` and `r map_dbl(multi_data_list, "n") %>% max()`, respectively.
-
-We ran the same underlying mixed-effects linear regression model.
-Analyses were conducted using R [@rcoreteam2020] and mixed models were fit using the lme4 package [@bates2015].
-Our mixed-effects models included five fixed terms: the main effect of task version (ecological or abstract version, within-subjects), the main effect of childhood adversity (between-subjects), the interaction between task version and adversity exposure, the main effect of age (control variable), and the main effect of test distraction ratings (control variable).
-Task version was grand mean centered (abstract versions = -1, ecological versions = 1).
-All childhood adversity measures were standardized before model fitting, and all models included a random intercept for task version nested in participants.
-
-Our models for attention shifting and working memory updating differed in one respect.
-Our sample included a small subset of siblings (*n* = `r txt6_sib$n`, `r txt6_sib$families` families).
-All sibling groups were pairs of two (`r txt6_sib$sizes$two` sibling pairs) except for `r english::as.english(txt6_sib$sizes$three)` group of three and `r english::as.english(txt6_sib$sizes$four)` group of four siblings.
-We computed intraclass correlations (ICCs) for sibling groups for attention-shifting and working memory updating scores.
-ICCs for attention shifting were essentially zero, but they were non-zero for working memory updating scores (*ICC~standard~* = `r txt6_sib$iccs$abs_update`, *ICC~ecological~* = `r txt6_sib$iccs$eco_update`).
-Thus, all models analyzing working memory updating included an additional random intercept for siblings.
-Non-siblings were given the same sibling-group code, so the model could compute an intercept for non-siblings.
-
-To facilitate interpretation of multiverse results, we report median standardized $\beta$s, median 95% confidence intervals, and percent significant for each term in our model (see Table \@ref(tab:table2)).
-Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect (two-sided *p*-value \< .05) for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions.
-For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique to compute overall *p*-values.
-The technique makes it possible to know if a multiverse analysis produced a median effect size larger than expected, given the null hypothesis that the median $\beta$ = 0 [see @simonsohn2020 for details].
-
-Table \@ref(tab:table1) displays bivariate associations between all composite measures of adversity, including components of each, and descriptive statistics.
-Our primary interests were the main effect of adversity and the interaction of adversity with task-version.
-Table \@ref(tab:table2) shows median effect sizes ($\beta$-coefficients), sample sizes, and bootstrapped *p*-values for attention-shifting and working memory updating analyses for the main effect of adversity (unpredictability, violence, and poverty) and the interaction term (task version × adversity).
-Table \@ref(tab:table3) reports median simple effects of task version across high and low levels of adversity and median simple effects of adversity across abstract and ecologically relevant task versions.
-
-```{r table1, tab.id = "table1", tab.cap.style = "Table Caption", tab.cap="Bivariate correlations and descriptive statistics for adversity measures."}
-table.01.0 %>% 
-  add_column(.after = 4,"empty1" = "") %>% 
-  add_column(.after = 8,"empty2" = "") %>% 
-  flextable() %>%
-  width("empty1", width = .2) %>% 
-  width("empty2", width = .2) %>% 
-  width(j = 1, width = .75) %>% 
-  set_header_labels(Variable = "", empty1 = "", empty2 = "") %>% 
-  add_header_row(
-    values = c(" ", "Unpredictability", " ", "Violence", " ", "Poverty"),
-    colwidths = c(1, 3, 1, 3, 1, 4)
-  ) %>% 
-  border_remove() %>% 
-  border(i = 1, j = c("1","2","3","4","5","6","7","8","9","10"), border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
-  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 16, border.bottom = fp_border_default(), part = "body") %>% 
-  align(i = 1:2, align = "center", part = "header") %>% 
-  bold(i = 1:2, part = "header") %>% 
-  set_table_properties(width = 1, layout = "autofit") %>% 
-  add_footer_row(
-    values = " ",
-    colwidths = 13
-  ) %>% 
-  add_footer_row(
-    values = " ",
-    colwidths = 13
-  ) %>% 
-  compose(
-    i = 1, j = 1, 
-    as_paragraph(as_i("Note: "), "Column headers denote adversity constructs and rows indicate components. The upper triangle contains sample sizes for each correlation."), 
-    part = "footer"
-  ) %>% 
-  compose(
-    i = 2, j = 1, 
-    as_paragraph(as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
-    part = "footer"
-  ) 
-```
-
-Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction $\beta$-coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).
-
-We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), including an [Updated Primary Analysis Plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details.
-We conducted secondary analyses after our primary analyses (see [Secondary Analyses](#secondary) below).
-Before conducting these analyses, we uploaded secondary analysis plans (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)), explaining the goals and purpose of each secondary analysis.
-A Red Team Critic [@redteammarket2021] successfully reproduced and verified (see this [Red Team Report](https://osf.io/xv94z/?view_only=92d55bd3b9834468acd3a7cef5c3febd)) all analyses prior to submission.
-
-## Primary Analyses {#primary}
-
-### Attention Shifting {#primary-shifting}
-
-Across each set of multiverse analyses, there were significant main effects of task version.
-All median effects sizes for task version were $\beta$s = `r c(mod_terms1$shifting.unp.type_z$median_beta, mod_terms1$shifting.vio.type_z$median_beta, mod_terms1$shifting.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for multiverse models testing unpredictability, violence exposure, and poverty exposure, indicating that switch costs (see [Attention Shifting](#shifting) for switch cost explanation) were moderately higher for the ecological version compared to the abstract version (see SI Figures 1-3).
-That is, reaction times on switch trials, compared to repeat trials, were longer when stimuli were ecologically relevant as opposed to abstract.
-However, there were no effects of age (all median $\beta$s = `r c(mod_terms1$shifting.unp.age$median_beta, mod_terms1$shifting.vio.age$median_beta, mod_terms1$shifting.ses.age$median_beta) %>% mean()`, all *ps* \>.05) or test distraction ratings (all median $\beta$ = `r c(mod_terms1$shifting.unp.test_envr$median_beta, mod_terms1$shifting.vio.test_envr$median_beta, mod_terms1$shifting.ses.test_envr$median_beta) %>% mean()`, all *ps* \> .05) on overall switch costs (see SI Figures 1-3).
-
-```{r figure2, fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure (y-axis was reversed so that higher values = faster shifting), b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
-fig2
-```
-
-Overall, there were no significant interaction effects between task version and unpredictability, violence exposure, or poverty exposure (see Table \@ref(tab:table2), Table \@ref(tab:table3), and Figure \@ref(fig:figure2)b).
-However, analyses produced main effects of unpredictability (median $\beta$ = `r mod_terms2$shifting.unp$median_beta_main`, `r mod_terms2$shifting.unp$p_percent_main %>% str_remove("\\.00")` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.unp$p_overall_main`) and violence exposure (median $\beta$ = `r mod_terms2$shifting.vio$median_beta_main`, `r mod_terms2$shifting.vio$p_percent_main` of *ps* \< .05, overall *p* = `r mod_terms2$shifting.vio$p_overall_main`; see Table \@ref(tab:table2)).
-There were no main effects of poverty exposure (median $\beta$ = `r mod_terms2$shifting.ses$median_beta_main`, no *ps* \< .05, overall *p* = `r mod_terms2$shifting.ses$p_overall_main`; see Table \@ref(tab:table2)).
-That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures were associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecologically relevant.
-
-```{r table2, tab.id = "table2", tab.cap.style = "Table Caption", tab.cap = "Median standardized effects, 95% confidence intervals, percent significant, and bootstrapped p-values for the main effect of adversity and adversity by task version interactions."}
-table.02.0 %>% 
-  ungroup() %>% 
-  mutate(iv = factor(iv, c("Unpredictability","Violence","Poverty"))) %>%
-  arrange(dv,iv) %>% 
-  select(-dv) %>% 
-  add_column(.after = 5,"empty1" = "") %>% 
-  add_row(.before = 1, "iv" = "Attention Shifting") %>% 
-  add_row(.after = 4, "iv" = "Working Memory Updating") %>% 
-  flextable() %>% 
-  merge_h_range(i = 1, j1 = 1, j2 = 10) %>% 
-  merge_h_range(i = 5, j1 = 1, j2 = 10) %>% 
-  bold(i = c(1,5), j = 1) %>% 
-  padding(i = c(2:4, 6:8), j = 1, padding.left = 10) %>% 
-  width("empty1", width = .2) %>% 
-  set_header_labels(iv = "", empty1 = "", ci_main = "95% CI", ci_int = "95% CI") %>% 
-  add_header_row(
-    values = c(" ", "Main Effect", " ", "Interaction"),
-    colwidths = c(1, 4, 1, 4)
-  ) %>% 
-  compose(i = 2, j = c(2,7), as_paragraph("\U1D6FD"), part = "header") %>% 
-  compose(i = 2, j = c(4,9), as_paragraph(as_i("p "), "(%)"), part = "header") %>% 
-  compose(i = 2, j = c(5,10), as_paragraph(as_i("p")), part = "header") %>% 
-  align(i = 1:2, align = "center", part = "header") %>% 
-  border_remove() %>% 
-  border(i = 1, border.top = fp_border_default(), part = "header") %>% 
-  border(i = 1, j = c(2:5,7:10), border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
-  border(i = 8, border.bottom = fp_border_default(), part = "body") %>% 
-  bold(i = 1:2, part = "header") %>% 
-  set_table_properties(width = 1, layout = "autofit") %>% 
-  add_footer_row(
-    values = " ",
-    colwidths = 10
-  ) %>% 
-    add_footer_row(
-    values = " ",
-    colwidths = 10
-  ) %>% 
-  compose(
-    i = 1, j = 1, 
-    as_paragraph(as_i("Note: "), "The p (%) column reflects the number of analyses that produced p-values < .05 for a given multiverse.
-The total number of analyses for each measure was 64.
-Overall p-values were computed using a bootstrapped resampling method and reflect the probability of obtaining an effect size as extreme or more extreme given the median effect is 0."),
-    part = "footer"
-  )
-```
-
-### Working Memory Updating {#primary-updating}
-
-Across each set of multiverse analyses, there were again significant main effects of task version.
-All median effects sizes for task version were $\beta$s = `r c(mod_terms1$updating.unp.type_z$median_beta, mod_terms1$updating.vio.type_z$median_beta, mod_terms1$updating.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for models testing unpredictability, violence exposure, and poverty exposure, indicating that updating performance was better when stimuli were ecological relevant compared to abstract, on average (see SI Figures 4-6).
-There were also consistent main effects of age; median effects were $\beta$ = `r mod_terms1$updating.unp.age$median_beta` (all *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.age$median_beta` (all *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.age$median_beta` (all *ps* \< .05) for poverty exposure models (see SI Figures 4-6).
-That is, older youth scored higher on working memory updating, on average.
-Finally, there were some main effects of test environment distraction ratings.
-Median effects sizes were $\beta$ = `r mod_terms1$updating.unp.test_envr$median_beta` (`r (mod_terms1$updating.unp.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.test_envr$median_beta` (`r (mod_terms1$updating.vio.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.test_envr$median_beta` (`r (mod_terms1$updating.ses.test_envr$p_percent *100) %>% round(2)`% of *ps* \< .05) for poverty exposure models, indicating that more test distractions reduced working memory updating performance, on average (see SI Figures 4-6).
-
-Multiverse analyses revealed a main effect of poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_main`, all *ps* \< .05, bootstrapped *p* \< .001) but no main effects of unpredictability (median $\beta$ = `r mod_terms2$updating.unp$median_beta_main`, no *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.unp$p_overall_main`) or violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_main`, `r mod_terms2$updating.vio$p_percent_main` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_main`).
-Analyses also revealed two significant interactions: task version × violence exposure (median $\beta$ = `r mod_terms2$updating.vio$median_beta_int`, `r mod_terms2$updating.vio$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.vio$p_overall_int`) and task version × poverty exposure (median $\beta$ = `r mod_terms2$updating.ses$median_beta_int`, `r mod_terms2$updating.ses$p_percent_int` of *ps* \< .05, bootstrapped *p* = `r mod_terms2$updating.ses$p_overall_int`).
-Youth exposed to low levels of violence or poverty tended to perform better on the abstract working memory updating task (violence exposure median *b~abstract~* = `r simple_effects$updating.vio$beta_abs`, `r simple_effects$updating.vio$p_percent_abs` of *ps* \< .05; poverty exposure median *b~abstract~* = `r simple_effects$updating.ses$beta_abs`, all *ps* \< .05), compared to youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)).
-However, this performance gap closed on the ecological working memory task (violence exposure median *b~ecological~* = `r simple_effects$updating.vio$beta_eco`, no *ps* \< .05; poverty exposure median *b~ecological~* = `r simple_effects$updating.ses$beta_eco`, `r simple_effects$updating.ses$p_percent_eco` of *ps* \< .05).
-Put differently, youth exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically relevant version compared to their own performance on the abstract version (median simple *b~high-violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high-poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas youth exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low-violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low-poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
-In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
-
-```{r figure3, fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure, b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
-Proportions of each arbitrary decision with p-values < .05 are indicated on the right side of each specification grid.
-Blank proportions indicate proportions = 0.
-Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
-fig3
-```
-
-## Secondary Analyses {#secondary}
-
-We followed-up our primary analyses with two sets of secondary, exploratory analyses.
-We uploaded secondary analysis plans to the OSF prior to conducting them (see the [First Secondary Analysis Plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [Second Plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)).
-These analyses focused on two questions.
-First, in contrast to prior work [@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting).
-However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures.
-Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure; see [Measures](#measures) section) have unique associations with attention shifting and working memory updating performance.
-To address this, we expanded our multiverse approach to include each component of our predictor variables as additional arbitrary decisions.
-
-The second question focused on the interactive effects of task version × violence exposure and task version × poverty exposure on working memory updating performance.
-Specifically, primary analyses revealed an equalization effect for both violence and poverty exposures on working memory updating.
-However, because measures of violence and poverty were not included in the same statistical model, it is unclear whether these interactions are independent.
-For example, one possibility is that exposures to violence and poverty are independently associated with working memory updating performance.
-Alternatively, they may overlap, reflecting the same association.
-To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty in the same model.
-If violence and poverty exposures interact independently with task version, both interaction terms should remain significant.
-However, if they represent overlapping effects on working memory updating performance, one or the other may drop out of significance, which would suggest that one or the other adversity dimension is driving the effects of the other.
 
@@
 ```
-
-### Exploring Components of Adversity Dimensions {#secondary1}
-
-We ran an expanded multiverse analysis to explore the effects of each component of our adversity composites (see [Measures](#measures) section) on attention shifting and working memory updating performance.
-Environmental unpredictability contained two components, perceived unpredictability (self-reported) and an interview-based measure tabulating family disruptions, parental figures, and residential moves.
-Violence exposure contained two self-report components: neighborhood violence and exposure to/involvement in violence.
-Poverty exposure contained three components: parental education/occupation (interview), perceived resource scarcity (self-report), and school-coded economic disadvantage (fee waivers, free- or reduced-priced lunch, and homelessness).
-
-For this expanded multiverse approach, we retained all original data processing decisions (i.e., original 64 combinations of decisions) and added adversity component as an additional decision.
-For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures: attention shifting and working memory).
-We applied the same approach to violence exposure (three violence variables, 384 analyses) and poverty exposure (four poverty variables, 512 analyses).
-The full results of these analyses are reported in the supplement (see SI Table 2).
-
-For attention shifting, consistent with our primary analyses, there were no interactions for any component of adversity and task version (see SI Table 2 and SI Figures 7-9).
-However, there were a few main effects of adversity.
-First, primary analyses revealed, under some analytic decisions, a main effect of unpredictability.
-Upon inspection of each unpredictability component, this effect appeared to be entirely driven by self-reported perceived unpredictability.
-Specifically, no main effect *p*-values for interview-based unpredictability were \< .05, whereas `r secondary1_medians$shifting.unp.Perceived.iv$p_percent` were for perceived unpredictability (see SI Table 2, SI Table 3, and SI Figure 7).
-In addition, violence exposure revealed that our primary analyses were driven by neighborhood violence (`r secondary1_medians$shifting.vio.Neighborhood.iv$p_percent` of *ps* \< .05) and not by direct witnessing or involvement in fights (no *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 8).
-There were no main effects of poverty exposure components on attention shifting (see SI Table 2, SI Table 3, and SI Figure 9).
-
-For working memory updating, there were no interaction between any unpredictability component (perceived or interview-based) and task-version (see SI Figure 10).
-However, our expanded analysis with violence exposure revealed that interactions obtained with the composite measure were not driven by neighborhood violence but instead by witnessing or involvement in violence (`r secondary1_medians$updating.vio.Fighting.iv_type_z$p_percent %>% str_remove("\\.00")` of interaction *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 11).
-No interactions were significant with the neighborhood violence component of the violence composite.
-For poverty exposure, interview-based parental occupational prestige and school-reported economic disadvantage showed some interaction effects (parental education/occupational prestige `r secondary1_medians$updating.ses.Parents.iv_type_z$p_percent` of *ps* \<.05; school coded economic disadvantage `r secondary1_medians$updating.ses.School.iv_type_z$p_percent` of *ps* \< .05, see SI Table 2, SI Table 3, and SI Figure 12).
-Self-reported perceived resource scarcity showed no interaction effects (see SI Table 2, SI Table 3, and SI Figure 12).
-
-### Comparing Violence and Poverty Exposure Interactions with Task-Version {#secondary2}
-
-Our next secondary analysis was designed to compare the violence exposure × task-version interaction with poverty exposure × task-version interaction on working memory updating performance in the same model.
-To do so, we ran a multiverse analysis using the original set of `r length(multi_data_list)` data processing decisions.
-We entered the same controls, main effects of task-version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty exposure.
-Analyses revealed a main effect of poverty (`r secondary2_medians$ses_agg_z$p_percent` of *ps* \< .05); consistent with the primary analyses, lower poverty was associated with better updating performance under most analytic decisions.
-However, there were no main effects of violence exposure (no *ps* \< .05).
-For interactions, there were no effects of task version × poverty (no *ps* \< .05, see SI Figure 13) and only a small number of significant task version × violence exposure effects (`r secondary2_medians$type_z_vio_agg_z$p_percent` of *ps* \< .05, see SI Figure 13).
-More specifically, when both interactions were entered into the same model, only task-version × violence exposure remained significant, although only under a small set of analytic decisions.
-
-Violence and poverty exposure interaction patterns were qualitatively similar to those obtained in our primary analyses (see Figure \@ref(fig:figure3)a and SI Figure 13).
-However, these secondary results suggest that the violence exposure interaction with task-version may be driving our poverty × task version results for working memory updating.
-One possibility is that the shared variance between poverty and violence exposures (*r* = `r txt5_cor$ses_vio$r`) is responsible for both interaction effects.
-In other words, although poverty and violence exposure are theoretically distinct, our poverty composite may capture poverty-related violence exposures (e.g., high poverty neighborhoods contain more crime) and therefore interact with task-version.
-When directly compared, explicit measures of violence exposure remained significant (although only under a small set of analytical decisions), whereas poverty interactions dropped out entirely.
-
-# Discussion {#discussion}
-
-We examined how ecologically relevant testing materials affect cognitive performance among adversity-exposed youth.
-We measured three dimensions of adversity--- environmental unpredictability, violence exposure, and poverty---and tested performance on attention-shifting and working memory updating tasks.
-We administered two versions of each task: one using abstract stimuli and the other using ecological, real-world stimuli, allowing us to compare performance within- and between-subjects.
-
-Leveraging multiverse analysis [@simonsohn2020; @steegen2016], we tested interactions between dimensions of adversity and task version on attention shifting and working memory updating performance.
-We did not find interaction effects for attention shifting.
-However, youth exposed to unpredictability and violence showed lower switch costs on average, suggesting slightly improved attention shifting performance irrespective of task content.
-These findings are consistent with a recent study showing that higher caregiving instability was associated with improved attention shifting [@fields2021].
-However, our findings also partially diverge from prior work [@mittal2015; @nweze2021].
-For example, whereas we found unpredictability was associated with improved attention shifting on average, Mittal and colleagues [-@mittal2015] found no difference in performance under neutral conditions.
-And, although they found improved attention shifting for those exposed to high unpredictability under uncertainty, it remains unclear how this effect relates to those obtained in the current study.
-In addition, Nweze and colleagues [-@nweze2021] found no association between adversity and attention shifting, but they tested institutionalized children rather than measuring adversity dimensions.
-In general, we should interpret the results cautiously.
-Although we followed field standards for calculating switch costs by computing difference scores, such scores ignore participant-level reaction times.
-Mixed-modeling approaches can account for both overall reaction times and differences across switch and repeat trials, but require more statistical power to test three-way interactions.
-Future research should consider modeling approaches that capture participant-level reaction times and differences across conditions.
-
-For working memory updating, we found lowered performance among violence- and poverty-exposed youth on the abstract working memory updating task than peers with reduced exposures.
-However, ecological materials produced an equalization effect: the updating performance gap between low and high adversity-exposed youth narrowed on the ecological updating task.
-Interestingly, updating performance was unrelated to unpredictability.
-These findings are partially consistent with prior work on adversity exposure and working memory updating performance [@nweze2021; @young2018].
-For example, both Young and colleagues [-@young2018] and the current study found lowered abstract working memory performance among high adversity-exposed individuals.
-Although performance with ecological stimuli is not directly comparable to performance under manipulated uncertainty, both studies reduced the updating performance gap under ecologically relevant conditions.
-However, there are also discrepancies.
-For example, Young and colleagues [-@young2018] found effects with unpredictability and not poverty, whereas the current study found associations with violence and poverty but not unpredictability.
-Finally, Nweze and colleagues [-@nweze2021] found improved working memory performance among institutionalized youth without ecological stimuli or uncertainty manipulations.
-However, both their adversity and working memory measures were different.
-
-Overall, inconsistencies across prior work and the current attention-shifting and working memory updating findings could be attributed to differences in sampling (adults vs.
-youth), the sampled range of adversity exposure (restricted vs.
-broad), or methods/design (within- vs.
-between-subjects design; lab vs.
-community/school settings).
-Future research should both address these inconsistencies and conduct more direct replications of individual studies to converge on reliable patterns.
-
-Our first set of secondary analyses focused on the components of our adversity composites.
-For attention shifting performance, the main effect of our unpredictability composite appeared to be driven by self-reported perceived unpredictability and not by the interview-based measure which captured changes in youths' living situations.
-Likewise, the main effect of violence exposure appeared to be driven by neighborhood violence and not involvement or witnessing fights.
-For working memory updating, interaction effects involving violence exposure were driven by involvement or witnessing fights but not perceptions of neighborhood violence.
-All components of poverty exposure measures, except self-reported perceptions of resource scarcity, showed interactive effects with task version on working memory updating.
-Our second set of secondary analyses compared violence to poverty exposure in the same model.
-Findings suggest, at least when directly comparing interaction terms, violence exposure × task version predicted the working memory updating equalization effect whereas the poverty × task version interaction did not.
-
-There are many possible explanations for the diverging adversity component patterns.
-First, some information sources may be more accurate than others.
-For example, asking about the number of fights one has been involved in or witnessed might be easier to report than asking broader questions about neighborhood danger.
-Second, for different cognitive abilities, objective versus subjective reports may be more relevant.
-For example, for attention-shifting, perceptions appeared to matter whereas objective events did for working memory updating.
-Third, although adversity components were correlated in the moderate range---as typically observed in the literature [@dong2004a; @green2010; @jacobs2012; @matsumoto2021; @mclaughlin2012; @smith2021]---they may measure different constructs.
-For example, more objective indicators might capture aspects of the broader ecology but subjective, self-reported measures capture how youth have internalized and perceived their environment and family life.
-Although interesting, all secondary analyses are exploratory, and should be interpreted with caution.
-Nonetheless, these analyses highlight the need to measure multiple dimensions of adversity, compare them, and consider each measure's report format and source.
-
-Taken together, our equalization patterns of results are striking compared to the backdrop of developmental science, which almost exclusively reports lowered cognitive performance in people exposed to harsh environments.
-We also document lowered performance among adversity-exposed youth, but this effect was specific to abstract stimuli, at least for working memory updating.
-When testing materials were more concrete, adversity-exposed youth perform about as well as youth from supportive backgrounds.
-These results converge with recent work comparing stimulus types among adversity-exposed youth.
-For example, Rifkin-Graboi and colleagues [-@rifkin-graboi2021] found preschoolers exposed to caregiver adversity were more accurate on relational memory for socioemotional than non-socioemotional stimuli and Zuilkowski and colleagues [-@zuilkowski2016] found that Sub-Saharan African children from low SES backgrounds were more accurate on reasoning tests with three dimensional stimuli than two dimensional stimuli.
-
-These effects have both practical and theoretical implications.
-Practically, these effects support the idea that ecologically relevant testing materials may 'even the playing field' for adversity-exposed youth.
-That is, pending replication and extension, our data suggest leveraging ecologically relevant materials in education may hold promise for closing achievement gaps [@ellis2017; @ellis2020; @frankenhuis2020].
-In fact, programs for gifted students from low-income backgrounds already leverage concrete learning materials [@vantassel-baska2018].
-However, our data also suggest the effect of ecological content may be specific to particular abilities.
-On the one hand, our data showing within-subject improvements on working memory updating is consistent with past research using ecological versions of Raven's Progressive Matrices [@richardson1991].
-On the other, ecological content actually lowered attention shifting performance for everyone compared to abstract content, possibly because shifting was more difficult with more ecologically hot or "sticky" stimuli.
-This negative effect is consistent with other studies reporting lowered performance on some tests with ecologically relevant content [@duquennois2022; @frankenhuis2020; @muskens2019].
-
-Theoretically, our findings support the notion that hidden talents may emerge when using ecologically relevant testing materials, but they also raise questions.
-In particular, why should ecologically relevant stimuli equalize working memory updating performance for adversity-exposed youth than youth with reduced exposures?
-There are at least three possibilities.
-First, adversity exposure could simultaneously lower and improve performance.
-While abstract working memory updating performance is lowered, ecological working memory updating performance is improved.
-However, this explanation requires that different cognitive mechanisms process different classes of stimuli, even on tests of the same ability.
-If this is true, those mechanisms that process abstract content underperform compared to those that process ecological content.
-Second, there may be no actual differences in underlying abilities.
-Instead, ecologically relevant stimuli may activate intact, but dormant or underrecruited, working memory updating processes.
-Thus, when adversity-exposed youth are tested under abstract testing conditions, their cognitive processes operate at a lower level (remain inactive) but operate equally well with ecological testing materials.
-This makes sense if adversity limits energy and/or cognitive resources.
-Under such constraints, it may be adaptive to activate expensive cognitive processes only when necessary.
-Third, ecological testing materials may remove barriers, such as testing anxiety or test unfamiliarity, that disadvantage adversity-exposed youth.
-Unlike the selective activation of cognitive resources, the additional stressors of testing are removed, allowing cognitive mechanisms to operate unimpeded.
-However, this explanation is difficult to reconcile with experimental work which finds that mild stress/uncertainty improves performance [@mittal2015; @young2018].
-Future research should use research designs that can disentangle these explanations.
-
-Our study has several strengths and limitations.
-First, we leveraged a within-person design, which illuminated the effects of ecological testing materials in the same person.
-However, the correspondence between each version of our tests was modest for working memory updating (*r* = `r txt5_cor$updating$r`) and low for attention shifting (*r* = `r txt5_cor$shifting$r`).
-Although the task structure was the same, it is unclear to what extent the ecological tests measured the same construct, especially for attention shifting.
-In addition, test difficulty may have been different across test versions (e.g., switch costs were larger on the ecological version).
-Future research should consider teasing apart test difficulty from ecological relevance.
-Second, our strategy for creating ecological test versions was to select stimuli believed to be more salient or impactful to adversity-exposed youth.
-However, we did not independently assess the ecological validity of our real-world stimuli.
-Thus, it is unclear whether our tests were specifically matched to the actual experiences of adversity-exposed youth or more ecologically relevant for these youth than for those from supportive conditions.
-Third, we leveraged multiverse analysis to examine the robustness of our findings to arbitrary data processing decisions.
-Though powerful, the technique is relatively new and should be interpreted with caution.
-For instance, as with other statistical techniques, researchers might disagree over which data processing decisions are arbitrary [@delgiudice2021].
-Fourth, although we found some effects of ecological testing materials, we measured abilities that have shown some evidence of adversity-related enhancement.
-To explore generalizability of ecological content across abilities, future research may create ecological versions of tests known to disadvantage adversity-exposed youth, such as inhibition or working memory retrieval [@mittal2015; @young2018], and compare performance to abstract versions.
-Finally, although we used interviews and self-report methods, all of our childhood adversity measures were cross-sectional and some were retrospective.
-These measurement limitations may be partially offset because our sample was still living in their developmental environment.
-However, this does not replace the need for prospective, longitudinal measures and cannot eliminate all biases associated with retrospective reporting [@reuben2016].
-Thus, it remains unclear to what extent the current environment, rather than the developmental environment, is driving our findings.
-
-Until recently, developmental science has almost exclusively reported lowered cognitive performance in people from harsh conditions.
-The hidden talents framework has challenged this notion and inspired researchers to document the strengths and abilities of people from adversity.
-Theoretically, our data help to refine the hidden talents framework and illuminate future research questions surrounding the unique skills and abilities of people living in harsh conditions.
-Though much is yet to be done, our data have exciting practical implications, such as developing ecologically relevant materials for education, that might 'even the playing field' for adversity-exposed youth.
-
-\pagebreak
-
-# References {#refs}

### 2022-04-05 manuscript/manuscript.Rmd
small fixes at the proofs stage

@@
 Two versions of an attention shifting and working memory updating task---one abstract, one ecological---were administered to `r txt1_sam$non_arb$n$total` youth (*M~age~* = `r txt1_sam$non_arb$age$mean`, *SD~age~* = `r txt1_sam$non_arb$age$sd`; `r (txt1_sam$non_arb$sex$females/txt1_sam$non_arb$n$total * 100) %>% round(2)`% female; `r ((txt1_sam$non_arb$n$total-txt1_sam$non_arb$race$non_white)/txt1_sam$non_arb$n$total * 100) %>% round(2)`% White).
-Measures of environmental unpredictability, violence, and poverty were collected to tested adversity × task version interactions.
+Measures of environmental unpredictability, violence, and poverty were collected to test adversity × task version interactions.
 There were no interactions for attention shifting.
@@
 There were no associations between violence exposures and reasoning performance.
-Overall, this study suggests that ecologically relevant testing materials may in some conditions 'level the playing field' for adversity-exposed youth [@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
+Overall, this study suggests that ecologically relevant testing materials may, in some conditions, 'level the playing field' for adversity-exposed youth [@ellis2020; @frankenhuis2020; @rifkin-graboi2021; @vantassel-baska2018].
 
-Although research testing performance in ecologically relevant contexts or situations and using ecologically relevant materials have generated innovative ideas and findings, it remains unclear whether or how these ideas and findings can be practically applied.
+Although research testing performance in ecologically relevant contexts or situations and using ecologically relevant materials have generated innovative ideas and findings, it remains unclear whether or how they can be practically applied.
 For example, narrow abilities, such as memorizing social dominance hierarchies or accurately detecting anger in faces, seem to have limited practical value in educational contexts.
@@
 Second, we measured the extent to which youth perceive their family context as unpredictable using a questionnaire [@young2018].
-Our goal was to aggregate these two information sources to arrive at a best estimate of environmental unpredictability.
+Our goal was to aggregate these two information sources to arrive at a "best estimate" of environmental unpredictability.
 
@@
 All sibling groups were pairs of two (`r txt6_sib$sizes$two` sibling pairs) except for `r english::as.english(txt6_sib$sizes$three)` group of three and `r english::as.english(txt6_sib$sizes$four)` group of four siblings.
-We computed intraclass correlations (ICCs) for sibling groups for attention-shifting and working memory updating scores.
-ICCs for attention shifting were essentially zero, but they were non-zero for working memory updating scores (*ICC~standard~* = `r txt6_sib$iccs$abs_update`, *ICC~ecological~* = `r txt6_sib$iccs$eco_update`).
+We computed intraclass correlations for sibling groups for attention-shifting and working memory updating scores.
+Intraclass correlations for attention shifting were essentially zero.
+However, for working memory updating scores, intraclass correlations were `r txt6_sib$iccs$abs_update` and `r txt6_sib$iccs$eco_update` for the standard and ecological versions, respectively.
 Thus, all models analyzing working memory updating included an additional random intercept for siblings.
@@
 Our primary interests were the main effect of adversity and the interaction of adversity with task-version.
-Table \@ref(tab:table2) shows median effect sizes ($\beta$-coefficients), sample sizes, and bootstrapped *p*-values for attention-shifting and working memory updating analyses for the main effect of adversity (unpredictability, violence, and poverty) and the interaction term (task version × adversity).
+Table \@ref(tab:table2) shows median effect sizes ($\beta$-coefficients) and bootstrapped *p*-values for attention-shifting and working memory updating analyses for the main effect of adversity (unpredictability, violence, and poverty) and the interaction term (task version × adversity).
 Table \@ref(tab:table3) reports median simple effects of task version across high and low levels of adversity and median simple effects of adversity across abstract and ecologically relevant task versions.
@@
 
-Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction $\beta$-coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).
+Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory updating performance, including depictions of performance on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), *p*-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction $\beta$-coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).
 
-We preregistered all primary analyses on the Open Science Framework (OSF; see <https://osf.io/6r95z/>, including an updated primary analysis plan (see <https://osf.io/4vsnz/>), which included more details.
+We preregistered all primary analyses on the Open Science Framework (OSF; see <https://osf.io/6r95z/>), including an updated primary analysis plan (see <https://osf.io/4vsnz/>), which included more details.
 We conducted secondary analyses after our primary analyses (see [Secondary Analyses](#secondary) below).
@@
 There were no main effects of poverty exposure (median $\beta$ = `r mod_terms2$shifting.ses$median_beta_main`, no *ps* \< .05, overall *p* = `r mod_terms2$shifting.ses$p_overall_main`; see Table \@ref(tab:table2)).
-That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures were associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecologically relevant.
+That is, exposure to more unpredictability and violence was associated with smaller switch costs, suggesting such exposures were associated with somewhat better shifting performance on average, irrespective of whether stimuli were abstract or ecological.
 
@@
 Across each set of multiverse analyses, there were again significant main effects of task version.
-All median effects sizes for task version were $\beta$s = `r c(mod_terms1$updating.unp.type_z$median_beta, mod_terms1$updating.vio.type_z$median_beta, mod_terms1$updating.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for models testing unpredictability, violence exposure, and poverty exposure, indicating that updating performance was better when stimuli were ecological relevant compared to abstract, on average (see SI Figures 4-6).
+All median effects sizes for task version were $\beta$s = `r c(mod_terms1$updating.unp.type_z$median_beta, mod_terms1$updating.vio.type_z$median_beta, mod_terms1$updating.ses.type_z$median_beta) %>% mean()` (all *ps* \< .05) for models testing unpredictability, violence exposure, and poverty exposure, indicating that updating performance was better when stimuli were ecological compared to abstract, on average (see SI Figures 4-6).
 There were also consistent main effects of age; median effects were $\beta$ = `r mod_terms1$updating.unp.age$median_beta` (all *ps* \< .05) for unpredictability models, $\beta$ = `r mod_terms1$updating.vio.age$median_beta` (all *ps* \< .05) for violence exposure models, and $\beta$ = `r mod_terms1$updating.ses.age$median_beta` (all *ps* \< .05) for poverty exposure models (see SI Figures 4-6).
@@
 However, this performance gap closed on the ecological working memory task (violence exposure median *b~ecological~* = `r simple_effects$updating.vio$beta_eco`, no *ps* \< .05; poverty exposure median *b~ecological~* = `r simple_effects$updating.ses$beta_eco`, `r simple_effects$updating.ses$p_percent_eco` of *ps* \< .05).
-Put differently, youth exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecologically relevant version compared to their own performance on the abstract version (median simple *b~high-violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high-poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas youth exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low-violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low-poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
-In this sense, ecologically relevant stimuli appeared to equalize working memory updating performance among youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
+Put differently, youth exposed to high levels of violence or poverty ($+$ 1 *SD*) performed better on the ecological version compared to their own performance on the abstract version (median simple *b~high-violence~* = `r simple_effects$updating.vio$beta_high`, all *ps* \< .05; median simple *b~high-poverty~* = `r simple_effects$updating.ses$beta_high`, all *ps* \< .05), whereas youth exposed to low violence or poverty ($-$ 1 *SD*) performed similarly across task versions (median simple *b~low-violence~* = `r simple_effects$updating.vio$beta_low`, no *ps* \< .05; median simple *b~low-poverty~* = `r simple_effects$updating.ses$beta_low`, no *ps* \< .05).
+In this sense, ecological stimuli appeared to equalize working memory updating performance among youth exposed to high levels of violence and poverty (see Table \@ref(tab:table3) and Figure \@ref(fig:figure3)a).
 
@@
 Alternatively, they may overlap, reflecting the same association.
-To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty in the same model.
+To test this question, we ran a focused multiverse analysis with the same controls, main effects of task version, poverty and violence exposure, and two interaction terms: task-version × violence exposure and task-version × poverty exposure in the same model.
 If violence and poverty exposures interact independently with task version, both interaction terms should remain significant.
@@
 For this expanded multiverse approach, we retained all original data processing decisions (i.e., original 64 combinations of decisions) and added adversity component as an additional decision.
-For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures: attention shifting and working memory).
+For unpredictability, we analyzed each unpredictability component and the composite measure (composite analyses are redundant with primary analyses but were retained for comparison purposes), which resulted in 384 analyses (64 original × three versions of unpredictability × two performance measures: attention shifting and working memory updating).
 We applied the same approach to violence exposure (three violence variables, 384 analyses) and poverty exposure (four poverty variables, 512 analyses).
@@
 Violence and poverty exposure interaction patterns were qualitatively similar to those obtained in our primary analyses (see Figure \@ref(fig:figure3)a and SI Figure 13).
-However, these secondary results suggest that the violence exposure interaction with task-version may be driving our poverty × task version results for working memory updating.
+However, these secondary results suggest that the violence exposure interaction with task version may be driving our poverty × task version results for working memory updating.
 One possibility is that the shared variance between poverty and violence exposures (*r* = `r txt5_cor$ses_vio$r`) is responsible for both interaction effects.
-In other words, although poverty and violence exposure are theoretically distinct, our poverty composite may capture poverty-related violence exposures (e.g., high poverty neighborhoods contain more crime) and therefore interact with task-version.
+In other words, although poverty and violence exposure are theoretically distinct, our poverty composite may capture poverty-related violence exposures (e.g., high poverty neighborhoods contain more crime) and therefore interact with task version.
 When directly compared, explicit measures of violence exposure remained significant (although only under a small set of analytical decisions), whereas poverty interactions dropped out entirely.
@@
 Second, for different cognitive abilities, objective versus subjective reports may be more relevant.
-For example, for attention-shifting, perceptions appeared to matter whereas objective events did for working memory updating.
+For example, for attention shifting, perceptions appeared to matter whereas objective events did for working memory updating.
 Third, although adversity components were correlated in the moderate range---as typically observed in the literature [@jacobs2012; @smith2021]---they may measure different constructs.
@@
 These results converge with recent work comparing stimulus types among adversity-exposed youth.
-For example, Rifkin-Graboi and colleagues [-@rifkin-graboi2021] found preschoolers exposed to caregiver adversity were more accurate on relational memory for socioemotional than non-socioemotional stimuli and Zuilkowski and colleagues [-@zuilkowski2016] found that Sub-Saharan African children from low SES backgrounds were more accurate on reasoning tests with three dimensional stimuli than two dimensional stimuli.
+For example, Rifkin-Graboi and colleagues [-@rifkin-graboi2021] found preschoolers exposed to caregiver adversity were more accurate on relational memory for socioemotional than non-socioemotional stimuli and Zuilkowski and colleagues [-@zuilkowski2016] found that Sub-Saharan African children from high poverty backgrounds were more accurate on reasoning tests with three dimensional stimuli than two dimensional stimuli.
 
@@
 Theoretically, our findings support the notion that hidden talents may emerge when using ecologically relevant testing materials, but they also raise questions.
-In particular, why should ecologically relevant stimuli equalize working memory updating performance for adversity-exposed youth than youth with reduced exposures?
+In particular, why should ecologically relevant stimuli equalize working memory updating performance for adversity-exposed youth?
 There are at least three possibilities.
@@
 However, this explanation is difficult to reconcile with experimental work which finds that mild stress and uncertainty improves performance [@mittal2015; @young2018].
-Future research should use research designs that can disentangle these explanations.
+Future research should use methods and designs that can disentangle these explanations.
 

### 2022-04-05 manuscript/scripts/figure-2-3.R

@@ -354,3 +354,176 @@ fig3 <-
   ) + 
   draw_label("Working Memory Updating", x = 0.6, y = .975, hjust = .5, vjust = 0, fontface = "bold")
 
+# For presentations and posters -------------------------------------------
+fig2_simple <- 
+  ggdraw() +
+  draw_plot(
+    plot_grid(
+      spec_curves[[1]]$interactions + theme(panel.background = element_blank(), plot.background = element_blank()),
+      spec_curves[[1]]$p_curve + theme(panel.background = element_blank(), plot.background = element_blank()),
+      nrow  = 2,
+      ncol  = 1, 
+      align = "v", 
+      axis  = "lr",
+      rel_heights = c(.6, .4)
+    ) +
+      draw_plot_label(c("faster","slower"), x = 0.065, y = c(.885, .475), size = 7, vjust = 1, hjust = 1, fontface = "italic"),
+    x = 0, y = 0, width = 1, height = 1
+  ) 
+
+fig3_simple <- 
+  ggdraw() +
+  draw_plot(
+    plot_grid(
+      spec_curves[[2]]$interactions,
+      spec_curves[[2]]$p_curve,
+      nrow  = 2,
+      ncol  = 1, 
+      align = "v", 
+      axis  = "lr",
+      rel_heights = c(.6, .4)
+    ) +
+      draw_plot_label(c("more\naccurate","less\naccurate"), x = 0.04, y = c(.95, .465), size = 7, vjust = 1, hjust = .5, fontface = "italic"),
+    x = 0, y = 0, width = 1, height = 1
+  )
+
+sysfonts::font_add_google("Lato")
+showtext::showtext_auto()
+
+fig_2_3 <- 
+  ggdraw() +
+  draw_plot(
+    plot_grid(
+      spec_curves[[2]]$interactions + 
+        ggtitle("Working Memory Updating\n") + 
+        theme(
+          text = element_text(family = "Lato", color = "white"),
+          element_line(color = "white"),
+          panel.background = element_blank(),
+          plot.background = element_blank(),
+          plot.title = element_text(hjust = 0.5, size = rel(1.75)),
+          plot.margin = margin(1,1,1,1, unit = "lines"),
+          axis.text = element_text(size = rel(1.15), color = "white")
+        ),
+      spec_curves[[1]]$interactions + 
+        ggtitle("Attention Shifting\n") + 
+        scale_color_manual(values = c("")) +
[…]

### 2022-04-05 manuscript/scripts/rmd-staging.R

@@ -369,6 +369,14 @@ save(
   file = "manuscript/staged-objects.Rdata"
 )
 
+# save color figures ------------------------------------------------------
+ggsave(filename = "manuscript/figures/figure2-1.jpg", fig2, width = 6.5, height = 7.25, dpi = 600)
+ggsave(filename = "manuscript/figures/figure3-1.jpg", fig3, width = 6.5, height = 7.25, dpi = 600)
+
 # save black and white figures --------------------------------------------
+## PDF
 ggsave(filename = "manuscript/figures/figure2-1-bw.pdf", fig2_bw, width = 6.5, height = 7.25, dpi = 600)
 ggsave(filename = "manuscript/figures/figure3-1-bw.pdf", fig3_bw, width = 6.5, height = 7.25, dpi = 600)
+## JPEG
+ggsave(filename = "manuscript/figures/figure2-1-bw.jpg", fig2_bw, width = 6.5, height = 7.25, dpi = 600)
+ggsave(filename = "manuscript/figures/figure3-1-bw.jpg", fig3_bw, width = 6.5, height = 7.25, dpi = 600)

### 2022-04-05 scripts/2-primary-analyses/3-extract-effects.R

@@ -46,6 +46,13 @@ primary_effects_data <-
           .fns = ~ifelse(str_detect(mod_term,"ses"), .x * -1, .x)
         )
       ) %>% 
+      mutate(
+        mod_ci_low1  = ifelse(str_detect(mod_term,"ses"), mod_ci_high, mod_ci_low),
+        mod_ci_high1 = ifelse(str_detect(mod_term,"ses"), mod_ci_low, mod_ci_high),
+        mod_ci_low   = mod_ci_low1,
+        mod_ci_high  = mod_ci_high1
+      ) %>% 
+      select(-mod_ci_low1, -mod_ci_high1) %>% 
       group_by(mod_term) %>% 
       mutate(
         spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),

### 2022-04-05 scripts/3-secondary-analyses/set-1/a2-extract-effects.R

@@ -30,6 +30,12 @@ secondary1a_effects_data <-
       .fns = ~ifelse(str_detect(mod_term,"ses"), .x * -1, .x)
     )
   ) %>% 
+  mutate(
+    mod_ci_low1  = ifelse(str_detect(mod_term,"ses"), mod_ci_high, mod_ci_low),
+    mod_ci_high1 = ifelse(str_detect(mod_term,"ses"), mod_ci_low, mod_ci_high),
+    mod_ci_low   = mod_ci_low1,
+    mod_ci_high  = mod_ci_high1
+  ) %>% 
   group_by(mod_term) %>% 
   mutate(
     spec_rank  = as.numeric(fct_reorder(as_factor(spec_number), mod_std_coefficient)),

### 2022-04-05 scripts/3-secondary-analyses/set-2/a2-extract-effects.R

@@ -42,11 +42,16 @@ secondary_set2_effects <-
         # Do this to reverse code SES to match low SES to High poverty
         across(
           .cols = c(mod_estimate, mod_std.error, mod_statistic, mod_std_coefficient, mod_ci, mod_ci_low, mod_ci_high),
-          .fns = ~ifelse(str_detect(iv,"ses"), .x * -1, .x)
+          .fns = ~ifelse(str_detect(iv,"ses") & str_detect(mod_term,"iv"), .x * -1, .x)
         )
-      )
-      filter(!str_detect(mod_term, "^sd__"))
-      filter(!str_detect(mod_term, "^sd__"))
+      ) %>% 
+      mutate(
+        mod_ci_low1  = ifelse(str_detect(iv,"ses") & str_detect(mod_term,"iv"), mod_ci_high, mod_ci_low),
+        mod_ci_high1 = ifelse(str_detect(iv,"ses") & str_detect(mod_term,"iv"), mod_ci_low, mod_ci_high),
+        mod_ci_low   = mod_ci_low1,
+        mod_ci_high  = mod_ci_high1
+      ) %>% 
+      select(-mod_ci_low1, -mod_ci_high1)
   })
 
 secondary_set2_effects_clean <- 

### 2022-04-05 supplement/scripts/1-covariates.R

@@ -8,10 +8,12 @@ primary_plots_data <-
                                 mod_term_unique == "Test Environment" ~ "Test~Environment",
                                 str_detect(mod_term_unique,"symbol") ~ str_replace(mod_term_unique,"Task-Version","Task~Version"),
                                 T ~ mod_term_unique),
-    mod_term_num   = case_when(str_detect(mod_term_unique, "Unp~sym") ~ 4,
-                               str_detect(mod_term_unique, "Vio~sym") ~ 5,
-                               str_detect(mod_term_unique, "SES~sym") ~ 6,
-                               T ~ mod_term_num),
+    mod_term_unique = str_replace(mod_term_unique, "SES", "Poverty"),
+    mod_term_unique = str_replace(mod_term_unique, "Poverty~sym", "Pov.~sym"),
+    mod_term_num    = case_when(str_detect(mod_term_unique, "Unp~sym") ~ 4,
+                                str_detect(mod_term_unique, "Vio~sym") ~ 5,
+                                str_detect(mod_term_unique, "Poverty~sym") ~ 6,
+                                T ~ mod_term_num),
     mod_term_label = fct_reorder(mod_term_unique, mod_term_num)
   )
 

### 2022-04-05 manuscript/manuscript.Rmd
fix figure captions in manuscript

@@
 ```{r figure2, fig.path="figures/", dev="pdf", fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure (y-axis was reversed so that higher values = faster shifting), b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
+Unpredictability and violence exposure multiverse analyses were confirmatory and poverty analyses were exploratory.
+a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure (y-axis was reversed so that higher values = faster shifting), b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
 fig2
@@
 ```{r figure3, fig.path="figures/", dev="pdf", fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results.
-Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure, b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
+Unpredictability and violence exposure multiverse analyses were confirmatory and poverty analyses were exploratory.
+a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure, b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect.
 Proportions of each arbitrary decision with p-values < .05 are indicated on the right side of each specification grid.

### 2022-04-08 manuscript/scripts/figure-2-3.R
write a script for presentation and poster figures

@@ -353,177 +353,3 @@ fig3 <-
     x = 0, y = 0, width = 1, height = .95
   ) + 
   draw_label("Working Memory Updating", x = 0.6, y = .975, hjust = .5, vjust = 0, fontface = "bold")
-
-# For presentations and posters -------------------------------------------
-fig2_simple <- 
-  ggdraw() +
-  draw_plot(
-    plot_grid(
-      spec_curves[[1]]$interactions + theme(panel.background = element_blank(), plot.background = element_blank()),
-      spec_curves[[1]]$p_curve + theme(panel.background = element_blank(), plot.background = element_blank()),
-      nrow  = 2,
-      ncol  = 1, 
-      align = "v", 
-      axis  = "lr",
-      rel_heights = c(.6, .4)
-    ) +
-      draw_plot_label(c("faster","slower"), x = 0.065, y = c(.885, .475), size = 7, vjust = 1, hjust = 1, fontface = "italic"),
-    x = 0, y = 0, width = 1, height = 1
-  ) 
-
-fig3_simple <- 
-  ggdraw() +
-  draw_plot(
-    plot_grid(
-      spec_curves[[2]]$interactions,
-      spec_curves[[2]]$p_curve,
-      nrow  = 2,
-      ncol  = 1, 
-      align = "v", 
-      axis  = "lr",
-      rel_heights = c(.6, .4)
-    ) +
-      draw_plot_label(c("more\naccurate","less\naccurate"), x = 0.04, y = c(.95, .465), size = 7, vjust = 1, hjust = .5, fontface = "italic"),
-    x = 0, y = 0, width = 1, height = 1
-  )
-
-sysfonts::font_add_google("Lato")
-showtext::showtext_auto()
-
-fig_2_3 <- 
-  ggdraw() +
-  draw_plot(
-    plot_grid(
-      spec_curves[[2]]$interactions + 
-        ggtitle("Working Memory Updating\n") + 
-        theme(
-          text = element_text(family = "Lato", color = "white"),
-          element_line(color = "white"),
-          panel.background = element_blank(),
-          plot.background = element_blank(),
-          plot.title = element_text(hjust = 0.5, size = rel(1.75)),
-          plot.margin = margin(1,1,1,1, unit = "lines"),
-          axis.text = element_text(size = rel(1.15), color = "white")
-        ),
-      spec_curves[[1]]$interactions + 
-        ggtitle("Attention Shifting\n") + 
-        scale_color_manual(values = c("")) +
[…]

### 2022-04-08 manuscript/scripts/presentations-posters.R

@@ -1,0 +1,286 @@
+# Packages ----------------------------------------------------------------
+library(tidyverse)
+library(cowplot)
+library(see)
+library(gt)
+library(psych)
+library(lme4)
+library(performance)
+
+# ggplot2 theme -----------------------------------------------------------
+theme_set(
+  theme_bw() +
+    theme(
+      axis.line.y       = element_line(),
+      axis.text.y       = element_text(size = rel(.75)),
+      axis.title.y      = element_text(size = rel(.80), margin = margin(1,0,0,0,"lines")),
+      axis.ticks.y      = element_line(),
+      axis.line.x       = element_blank(),
+      axis.text.x       = element_blank(),
+      axis.ticks.x      = element_blank(),
+      axis.title.x      = element_blank(),
+      panel.border      = element_blank(), 
+      panel.spacing.y   = unit(0.5, "lines"),
+      plot.margin       = margin(.25,.25,.25,.25,"lines"),
+      plot.background   = element_rect(color = NA),
+      plot.title        = element_text(size = rel(.85), hjust = 0, margin = margin(0,0,.5,0, "lines")),
+      plot.subtitle     = element_blank(),
+      panel.grid        = element_line(color = NA),
+      strip.background  = element_blank(), 
+      strip.placement   = "outside",
+      strip.text        = element_text(size = rel(.85), angle = 0)
+    )
+)
+
+pval_colors <- c("pos-sig" = "#334257", "non" = "gray70")
+my_alphas <- c(.5, 1)
+my_limits <- c(1,70)
+
+# get data ----------------------------------------------------------------
+load("multiverse-objects/2-primary-analyses/3-extracted-effects.Rdata")
+load("multiverse-objects/2-primary-analyses/5-bootstrapped-effects.Rdata")
+source("manuscript/scripts/figure-2-3.R")
+
+# For presentations and posters -------------------------------------------
+fig2_simple <- 
+  ggdraw() +
+  draw_plot(
+    plot_grid(
+      spec_curves[[1]]$interactions + theme(panel.background = element_blank(), plot.background = element_blank()),
+      spec_curves[[1]]$p_curve + theme(panel.background = element_blank(), plot.background = element_blank()),
+      nrow  = 2,
+      ncol  = 1, 
+      align = "v", 
+      axis  = "lr",
+      rel_heights = c(.6, .4)
+    ) +
[…]
